\small
\arrayrulecolor{black!22}
\begin{longtable}{L{0.035\linewidth} L{0.12\linewidth} L{0.31\linewidth} L{0.12\linewidth} L{0.17\linewidth} L{0.14\linewidth} L{0.09\linewidth}}
\hline
\textbf{ID} & \textbf{Postulate} & \textbf{Precise formulation} & \textbf{Allowed primitive} & \textbf{Derived-only consequences} & \textbf{Forbidden primitive imports} & \textbf{Enforcement}\\
\hline
\endfirsthead
\hline
\textbf{ID} & \textbf{Postulate} & \textbf{Precise formulation} & \textbf{Allowed primitive} & \textbf{Derived-only consequences} & \textbf{Forbidden primitive imports} & \textbf{Enforcement}\\
\hline
\endhead
POST1 & CNNA ontic subsystem-minimality & The only primitive ontic emergence trigger is subsystem-being: the selection of a finite or local subsystem, cut, or approximant inside the formal IDEAL\_infty provenance whole. IDEAL\_infty is the formal relational/\allowbreak{}provenance background, not a physical dynamics input. All dynamics, spectra, operator algebra, arithmetic, geometry, stochasticity, openness, unitarity claims and physical interpretation must be derived from the subsystem/\allowbreak{}complement relation and its Schur/\allowbreak{}DtN consequences. & Subsystem/\allowbreak{}cut/\allowbreak{}approximant selection within the formal IDEAL\_infty provenance whole. & boundary;\newline inside/\allowbreak{}outside distinction;\newline complement families;\newline regime noOuter/\allowbreak{}HasOuter;\newline Schur/\allowbreak{}DtN effective operator;\newline spectra;\newline algebra;\newline arithmetic;\newline geometry;\newline dynamics;\newline physics & dynamics;\newline time evolution;\newline stochasticity/\allowbreak{}noise;\newline environment;\newline geometry/\allowbreak{}lattice;\newline arithmetic/\allowbreak{}discriminant;\newline operator algebra;\newline AQFT/\allowbreak{}physics;\newline Cayley-Dickson structures & Implemented through LEG35, GNG22, phase 1.1.1.1.0.16, object proof dossiers, scratchpad inheritance, and consumer-phase audits.\\
\hline
\addlinespace[0.24em]
POST2 & Root partial order and finite subsystem regime split & The externally visible CNNA foundation contains no free physical parameters. Its foundation axioms are: (1) there exists a root-based, empty-set-based infinite partial order of nodes and edges;\newline (2) every subsystem selected inside this partial order is finite;\newline (2a) exactly when the subsystem is approximated from the root/\allowbreak{}empty-set branch, the selected system is closed, has no dark/\allowbreak{}interface contribution and is the only regime eligible for later closed/\allowbreak{}unitary evolution after the corresponding time-evolution operator is derived;\newline (2b) when the subsystem is approximated by any non-root selection, a complement exists and the subsystem is effectively open as a bright/\allowbreak{}interface/\allowbreak{}dark split, while the total bright+interface+dark structure remains closed. & Root/\allowbreak{}empty-set based partial order;\newline finite subsystem selection;\newline formal complement relation induced by non-root subsystem selection. & closed/\allowbreak{}root regime;\newline open/\allowbreak{}non-root regime;\newline bright/\allowbreak{}interface/\allowbreak{}dark split;\newline complement visibility;\newline later unitarity/\allowbreak{}open-system claims only through the regime-specific derivation chain. & free physical parameters in the foundation;\newline pre-assumed stochasticity;\newline pre-assumed spacetime horizon;\newline pre-assumed QFT/\allowbreak{}AQFT/\allowbreak{}OQS dynamics;\newline direct unitary/\allowbreak{}open labels without derived regime evidence. & Source/\allowbreak{}audit evidence: Astronews CNNA thread page 2, posts \#27-\#29;\newline especially \#29 lines 330-341 in the 2026-05-12 web readout.\\
\hline
\addlinespace[0.24em]
POST3 & Generated-data operational closure requirement & Derived-only closure is not achieved by a compiled algebraic skeleton alone. A path may be called derived-only only after the structural skeleton exists, the local proof obligations for its components are discharged, and genuine generated data pass through the complete operational smoke path relevant to the claim. & The already accepted CNNA source objects and their proof-carrying/\allowbreak{}generated operational data path. & Green closure;\newline arithmetic seed claims;\newline Eisenstein/\allowbreak{}Gauss/\allowbreak{}CM-style smoke claims;\newline physics-facing operator or regime claims. & declaring closure from framework shape alone;\newline treating algebraic idle-run success as generated-data validation;\newline marking target-theory resemblance as derived-only evidence. & Source/\allowbreak{}audit evidence: Astronews CNNA thread page 2, post \#27 lines 237-243 in the 2026-05-12 web readout.\\
\hline
\addlinespace[0.24em]
\end{longtable}
\arrayrulecolor{black}
\normalsize
