\footnotesize
\arrayrulecolor{black!22}
\begin{longtable}{L{0.042\linewidth} L{0.105\linewidth} L{0.195\linewidth} L{0.08\linewidth} L{0.185\linewidth} L{0.19\linewidth} L{0.118\linewidth} L{0.055\linewidth}}
\hline
\textbf{Phase} & \textbf{Name} & \textbf{Primary purpose} & \textbf{Tool mode} & \textbf{Load-control rule} & \textbf{Theory semantics} & \textbf{Generated artifacts} & \textbf{Lean-data effect}\\
\hline
\endfirsthead
\hline
\textbf{Phase} & \textbf{Name} & \textbf{Primary purpose} & \textbf{Tool mode} & \textbf{Load-control rule} & \textbf{Theory semantics} & \textbf{Generated artifacts} & \textbf{Lean-data effect}\\
\hline
\endhead
1.1.1.5.1 & Tool-mode split and lean-focus contract & Define audit-full, phase-check, and lean-focus modes so routine Lean work consumes compact implementation packets instead of full PDF/\allowbreak{}table scans. & lean-focus foundation & Full PDF regeneration is not part of ordinary Lean coding;\newline use compact packets unless a governance or audit phase explicitly requests audit-full. & No theory classification yet;\newline this phase only fixes the mode boundary. & workflow-policy row;\newline scaling-plan TSV/\allowbreak{}TeX;\newline no Lean code & none\\
\hline
\addlinespace[0.24em]
1.1.1.5.2 & Implementation Packet Generator & Generate the phase-local packet with goal, source objects, producer/\allowbreak{}consumer modules, red blockers, yellow risks, forbidden shortcuts, expected artifacts, and comparison-only warnings. & lean-focus & Packet should fit on a small number of pages/\allowbreak{}rows and link to full TSV/\allowbreak{}JSON exports rather than embedding full inventories. & Consumes module-theory/\allowbreak{}end-theory ledgers once available;\newline before then marks theory context as unknown-not-input. & active-phase implementation packet TSV/\allowbreak{}JSON/\allowbreak{}TeX & none unless the user explicitly edits Lean code afterwards\\
\hline
\addlinespace[0.24em]
1.1.1.5.3 & Incremental Lean inventory and file-hash cache & Avoid rescanning/\allowbreak{}rendering everything by caching file hashes, module declarations, import edges, and symbol-reference candidates between Lean-data updates. & phase-check performance layer & Only changed Lean files and dependent generated summaries are refreshed;\newline full inventory rebuild remains available as audit-full. & May infer rough local background categories from imports, but must mark them heuristic until semantically confirmed. & file-hash cache;\newline declaration cache;\newline inventory-delta TSV & changes only when Lean files or frozen inventory data change\\
\hline
\addlinespace[0.24em]
1.1.1.5.4 & Module theory context ledger & Track local established mathematical background per module as formal language, proof method, library/\allowbreak{}API context, implementation substrate, or comparison lemma context. & phase-check plus lean-focus lookup & Start with active/\allowbreak{}relevant modules only;\newline do not manually annotate all modules at once. Python proposes rows from imports;\newline semantic closure is explicit and phase-bound. & Local established theory is allowed formalization context, never ontic CNNA generator. Examples: Matrix, Finset, Polynomial, graph/\allowbreak{}linear algebra, Schur-style algebraic methods. & module-theory-context ledger TSV;\newline active-module slice & none for ledger-only updates\\
\hline
\addlinespace[0.24em]
1.1.1.5.5 & End-theory comparison ledger & Track large established target theories as comparison-only horizons: AQFT/\allowbreak{}QFT, OQS, modular forms, CM, elliptic functions/\allowbreak{}curves, L-functions, Moonshine, renormalization, operator algebras, spectral geometry, etc. & phase-check comparison layer & Only record end theories that constrain current or near-future phases;\newline do not build encyclopedia entries. & End theories are target structures, consistency checks, terminology alignment, or obstruction/\allowbreak{}comparison mirrors;\newline forbidden as CNNA producers. & end-theory-comparison ledger TSV;\newline comparison-boundary table & none for ledger-only updates\\
\hline
\addlinespace[0.24em]
1.1.1.5.6 & Active object graph slices & Render small producer-consumer/\allowbreak{}provenance neighborhoods around the active phase and active CNNA objects rather than dumping the full object/\allowbreak{}declaration graph into the PDF. & lean-focus visualization & Depth 1-2 graph slices only in PDF;\newline full graph exported as DOT/\allowbreak{}JSON for optional audit. & Graph edges distinguish internal provenance, local formalization context, and external comparison-only references. & active-object-neighborhood DOT/\allowbreak{}SVG/\allowbreak{}PDF;\newline graph-slice TSV/\allowbreak{}JSON & none unless generated from changed Lean inventory\\
\hline
\addlinespace[0.24em]
1.1.1.5.7 & Red-blocker addressing-phase generator & When the pre-implementation thought experiment marks a future phase red, propose an upstream addressing phase at the earliest natural source layer before the blocked phase becomes active. & phase-check governance layer & Generate concise phase proposals only for red blockers;\newline yellow risks remain notes in the implementation packet. & If the blocker is an imported end-theory assumption, route to internal derivation/\allowbreak{}comparison-boundary phase rather than patching the consumer. & red-blocker phase-proposal TSV;\newline accepted phase rows only after approval & none until an accepted phase later changes Lean code\\
\hline
\addlinespace[0.24em]
1.1.1.5.8 & Database-ready YAML schema and review-link normalization & Normalize IDs, phase/\allowbreak{}object/\allowbreak{}proof-dossier references, review statuses, and theory-reference markers so the YAML master can later be exported to relational or graph database tables without semantic loss. & phase-check plus documentation infrastructure & Do not manually annotate the whole repository at once. Start with active/\allowbreak{}near-active rows and generated consistency checks;\newline keep full database realization as a later export task. & Database fields are review metadata. They may mark local background theory or end-theory comparison context, but they do not create CNNA generators. & database-readiness checklist TSV;\newline normalized ID/\allowbreak{}reference audit;\newline review-status export slice & none for schema/\allowbreak{}metadata-only changes\\
\hline
\addlinespace[0.24em]
1.1.1.5.9 & Database export, round-trip, and interactive documentation scaffold & Prepare future YAML-to-DB exports, database-to-generated-view round-trip checks, interactive object/\allowbreak{}phase exploration, online documentation, and discipline-separated expert-review views. & audit-full optional plus generated export layer & Keep export scripts reproducible and optional. Lean implementation packets must remain compact and must not depend on full database exploration. & Interactive views are secondary/\allowbreak{}generated. They expose review obligations and comparison horizons but never certify semantic truth. & future SQL/\allowbreak{}SQLite/\allowbreak{}graph export scripts;\newline schema diagrams;\newline interactive-view JSON;\newline round-trip consistency report & none unless future scripts read changed Lean inventory data\\
\hline
\addlinespace[0.24em]
1.1.1.5.10 & Context documentation slices & Reduce documentation overhead by producing topic/\allowbreak{}phase-specific packets that preserve full section topology while filtering rows to the requested context. & Python context generator over YAML and generated TSV exports;\newline optional pdflatex compilation. & Use for targeted requests and phase closeouts;\newline reserve full PDF regeneration for tool releases, global audits, or explicit full-document requests. & Generated-secondary navigation/\allowbreak{}review view only. Absence from a slice is not proof of semantic irrelevance;\newline expert review and blue/\allowbreak{}reference audit obligations remain. & context\_docs/\allowbreak{}<slug>/\allowbreak{}context\_filter\_manifest.json;\newline context\_section\_summary.tsv;\newline <slug>\_context\_documentation.tex/\allowbreak{}pdf;\newline compile log. & None;\newline no Lean source mutation and no Lean build claim.\\
\hline
\addlinespace[0.24em]
1.1.1.5.11 & Stats front section and interface-metaphor documentation surface & Keep project-scale facts, repository inventory, graph views, license notices and the tool-interface Leitmetapher visible without creating another truth layer. & Python-generated documentation/\allowbreak{}front matter & Do not expand the opening section into prose-heavy explanation;\newline keep it as compact facts, concise metaphor, licensing note and existing inventory/\allowbreak{}graph inclusion. & Generated-secondary review architecture only. The metaphor is operational, not ontic or theorematic;\newline Lean-primary and expert-review rules remain dominant. & project\_stats.generated.tsv;\newline tables/\allowbreak{}project\_stats\_table.tex;\newline tables/\allowbreak{}stats.tex;\newline updated V1.09 full PDF. & none;\newline no Lean source or Lean-data timestamp change.\\
\hline
\addlinespace[0.24em]
1.1.1.5.12 & Root artifact retention and disposable documentation outputs & Keep the project root clean and source-oriented while preserving on-demand generation of full PDFs/\allowbreak{}TeX and archival access to historical reports. & Python full-document generator plus root cleanup script. & Do not package regenerated full PDFs/\allowbreak{}TeX by default. Generate them only for review/\allowbreak{}export tasks, then keep them in generated\_docs/\allowbreak{}full/\allowbreak{} or delete them before release packaging. & Generated documentation outputs remain generated-secondary. Archival Markdown reports are trace records, not authoritative theory sources. & generated\_docs/\allowbreak{}full/\allowbreak{}<version>.tex/\allowbreak{}pdf/\allowbreak{}log when explicitly generated;\newline archive/\allowbreak{}reports/\allowbreak{}*.md for historical reports;\newline generated\_exports/\allowbreak{}root\_artifact\_cleanup.generated.json when cleanup runs. & none;\newline no Lean source mutation and no Lean build claim.\\
\hline
\addlinespace[0.24em]
1.1.1.5.13 & Root license and PDF credit surface & Keep license, editor/\allowbreak{}assistant credits and minimum tested ChatGPT workflow requirements visible without creating duplicate documentation entry points. & Root README/\allowbreak{}LICENSE plus generator metadata rendering for full/\allowbreak{}context PDFs. & Do not duplicate README files in subdirectories;\newline keep license and credit text compact and generated-secondary. & Licensing/\allowbreak{}credits are governance metadata only. They do not affect CNNA derivations, Lean truth status, or expert-review obligations. & Updated license\_notice.generated.tsv;\newline tables/\allowbreak{}license\_notice.tex;\newline generated full/\allowbreak{}context PDFs with author credits when explicitly compiled. & none;\newline no Lean source mutation and no Lean build claim.\\
\hline
\addlinespace[0.24em]
1.1.1.5.14 & provider-neutral SQL database public read-only mirror and cnna-project.net frontend sidechain & Prepare a public query/\allowbreak{}visualization layer for CNNA planning metadata without replacing Lean/\allowbreak{}YAML truth and without public write authority. & SQL/\allowbreak{}database mirror schemas and read-only api views;\newline local importer;\newline future static/\allowbreak{}web frontend;\newline no live DB connection in V1.22. & Start as schema/\allowbreak{}import/\allowbreak{}view contracts, not as full web application. No PDFs/\allowbreak{}ZIPs in DB, no admin write credential key in browser/\allowbreak{}chat, no manual production table edits. & Database/\allowbreak{}web layer is generated-secondary/\allowbreak{}publication infrastructure. It can query, visualize and review Lean/\allowbreak{}YAML-derived metadata, but cannot generate CNNA axioms or release Lean phases. & Future SQL migrations, import reports, snapshot checksums, read-only access policy test reports, frontend data-contract docs and public views;\newline V1.22 adds planning records only. & none;\newline no Lean source mutation and no Lean build claim.\\
\hline
\addlinespace[0.24em]
1.1.1.5.15 & GitHub backup-gated CI snapshot automation bridge & Prepare a safe automated path from repository commit to Lean build, inventory scan and versioned snapshot artifacts without direct unprotected main mutation. & GitHub Actions plus backup tag/\allowbreak{}branch and work-branch/\allowbreak{}PR policy;\newline no live repository mutation in P1.37. & Begin with contracts and dry-run artifacts;\newline do not automate merge/\allowbreak{}deploy until branch protection, backup refs, manifests and CI failure behavior are tested. & CI status is formal/\allowbreak{}build evidence only. Green does not imply semantic infallibility, and artifacts are generated-secondary. & Future workflow logs, snapshot\_manifest.json, YAML/\allowbreak{}JSON/\allowbreak{}TSV/\allowbreak{}SQL artifacts, commit/\allowbreak{}toolchain/\allowbreak{}hash manifests and CI status badges/\allowbreak{}reports. & none in P1.37;\newline future CI may build Lean but must not change Lean source unless a separate PR does so.\\
\hline
\addlinespace[0.24em]
1.1.1.5.16 & Webhosting MySQL staging import, read-only swap and rollback bridge & Prepare the practical classic Webhosting/\allowbreak{}MySQL deployment path for the CNNA Explorer while preserving strict read-only public access and rollback. & Server-local importer, staging/\allowbreak{}current table swap, least-privilege DB users, snapshot validation and rollback scripts;\newline no live DB connection in P1.37. & Import only generated snapshot payloads;\newline validate staging before swap;\newline keep previous current snapshot and SQL dump until new snapshot passes review. & MySQL is a presentation mirror and audit surface, not CNNA truth. Manual DB edits cannot release phases or define objects. & Future SQL migrations, importer logs, validation reports, read-only access tests, rollback reports, database dumps and local archive manifests. & none;\newline no Lean source mutation and no Lean build claim.\\
\hline
\addlinespace[0.24em]
\end{longtable}
\arrayrulecolor{black}
\normalsize
