\footnotesize
\arrayrulecolor{black!22}
\begin{longtable}{L{0.42\linewidth} L{0.16\linewidth} L{0.07\linewidth} L{0.08\linewidth} L{0.1\linewidth} L{0.09\linewidth}}
\hline
\textbf{Module} & \textbf{Group} & \textbf{Imports} & \textbf{Imported by} & \textbf{Transitive imports} & \textbf{Flags}\\
\hline
\endfirsthead
\hline
\textbf{Module} & \textbf{Group} & \textbf{Imports} & \textbf{Imported by} & \textbf{Transitive imports} & \textbf{Flags}\\
\hline
\endhead
\href{run:repo_snapshot/CNNA/PillarA/Arithmetic/BuildAll.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Arithmetic.\allowbreak{}BuildAll} & PillarA/\allowbreak{}Arithmetic & 126 & 1 & 204 & BuildAll\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Arithmetic/Notation.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Arithmetic.\allowbreak{}Notation} & PillarA/\allowbreak{}Arithmetic & 80 & 2 & 175 & Notation\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Structural/CayleyDickson/BuildAll.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Structural.\allowbreak{}CayleyDickson.\allowbreak{}BuildAll} & PillarA/\allowbreak{}Structural & 35 & 1 & 75 & BuildAll\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Finite/BuildAll.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Finite.\allowbreak{}BuildAll} & PillarA/\allowbreak{}Finite & 17 & 1 & 46 & BuildAll\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Foundation/BuildAll.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Foundation.\allowbreak{}BuildAll} & PillarA/\allowbreak{}Foundation & 16 & 1 & 16 & BuildAll\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/BuildAll.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}BuildAll} & PillarA & 13 & 2 & 274 & BuildAll\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Finite/Notation.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Finite.\allowbreak{}Notation} & PillarA/\allowbreak{}Finite & 12 & 2 & 45 & Notation\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Notation.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Notation} & PillarA & 11 & 2 & 225 & Notation\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Foundation/Notation.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Foundation.\allowbreak{}Notation} & PillarA/\allowbreak{}Foundation & 10 & 4 & 13 & Notation\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Handoff/BuildAll.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Handoff.\allowbreak{}BuildAll} & PillarA/\allowbreak{}Handoff & 8 & 1 & 75 & BuildAll\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Sectors/BuildAll.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Sectors.\allowbreak{}BuildAll} & PillarA/\allowbreak{}Sectors & 8 & 1 & 35 & BuildAll\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/ToC/BuildAll.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}ToC.\allowbreak{}BuildAll} & PillarA/\allowbreak{}ToC & 7 & 2 & 21 & BuildAll\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Finite/ExecSpectral/BuildAll.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Finite.\allowbreak{}ExecSpectral.\allowbreak{}BuildAll} & PillarA/\allowbreak{}Finite & 6 & 2 & 32 & BuildAll\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Handoff/Notation.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Handoff.\allowbreak{}Notation} & PillarA/\allowbreak{}Handoff & 6 & 2 & 74 & Notation\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Handoff/Outputs/BuildAll.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Handoff.\allowbreak{}Outputs.\allowbreak{}BuildAll} & PillarA/\allowbreak{}Handoff & 6 & 2 & 61 & BuildAll\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Network/BuildAll.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Network.\allowbreak{}BuildAll} & PillarA/\allowbreak{}Network & 6 & 1 & 37 & BuildAll\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Handoff/Core/SectorExport.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Handoff.\allowbreak{}Core.\allowbreak{}SectorExport} & PillarA/\allowbreak{}Handoff & 5 & 5 & 42 & \\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Foundation/Interfaces.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Foundation.\allowbreak{}Interfaces} & PillarA/\allowbreak{}Foundation & 4 & 3 & 6 & \\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Geometry/BuildAll.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Geometry.\allowbreak{}BuildAll} & PillarA/\allowbreak{}Geometry & 4 & 1 & 20 & BuildAll\\
\hline
\addlinespace[0.24em]
\href{run:repo_snapshot/CNNA/PillarA/Handoff/Inputs/BuildAll.lean}{CNNA.\allowbreak{}PillarA.\allowbreak{}Handoff.\allowbreak{}Inputs.\allowbreak{}BuildAll} & PillarA/\allowbreak{}Handoff & 4 & 2 & 51 & BuildAll\\
\hline
\addlinespace[0.24em]
\end{longtable}
\arrayrulecolor{black}
\normalsize
