\footnotesize
\par\smallskip\noindent\begin{minipage}{0.99\linewidth}\footnotesize\raggedright\textbf{Table legend.} \colorbox{white}{\strut W} = white/finished public object; \colorbox{cyan!20}{\strut B} = blue/proof-carrying but semantic/API correction still open; \colorbox{green!18}{\strut G} = green/locally closable; \colorbox{yellow!25}{\strut Y} = yellow/known route with prerequisites; \colorbox{red!20}{\strut R} = red/derivation layer incomplete or unclear; \colorbox{black!18}{\strut K} = black/registered side or future target. Context class is orthogonal to status.\end{minipage}\par\vspace{0.25em}
\arrayrulecolor{black!22}
\begin{longtable}{L{0.022\linewidth} L{0.082\linewidth} L{0.065\linewidth} L{0.032\linewidth} L{0.042\linewidth} L{0.028\linewidth} L{0.18\linewidth} L{0.145\linewidth} L{0.115\linewidth} L{0.145\linewidth} L{0.042\linewidth} L{0.022\linewidth}}
\hline
\textbf{ID} & \textbf{Object} & \textbf{Context class} & \textbf{Tier} & \textbf{Lifecycle} & \textbf{Object status} & \textbf{Canonical CNNA definition} & \textbf{Natural provenance} & \textbf{Computed from} & \textbf{ExecComplex/\allowbreak{}computable path} & \textbf{Priority} & \textbf{Phase}\\
\hline
\endfirsthead
\hline
\textbf{ID} & \textbf{Object} & \textbf{Context class} & \textbf{Tier} & \textbf{Lifecycle} & \textbf{Object status} & \textbf{Canonical CNNA definition} & \textbf{Natural provenance} & \textbf{Computed from} & \textbf{ExecComplex/\allowbreak{}computable path} & \textbf{Priority} & \textbf{Phase}\\
\hline
\endhead
\hyperlink{object-row-G00}{G00} & Generator provenance & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{green!18}G & Canonical A-internal generator/\allowbreak{}provenance record;\newline no pillar consumer generates its own sources. & Generated substrate + proof-carrying Schur/\allowbreak{}Exec chain. & substrate, branching, level, partition, Schur data. & ExecComplex arises downstream;\newline provenance itself is structural. & high & \hyperlink{phase-row-1-2-2}{1.2.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-H00}{H00} & A input handoff B->A & Lean;\newline Handoff;\newline Contract;\newline Object & F0 & current & \cellcolor{yellow!25}Y & BToAInputProfile. & Declared handoff input only. & B-derived theorem/\allowbreak{}data, if explicitly allowed. & May carry non-Exec analytic data;\newline must be typed. & medium & \hyperlink{phase-row-2-3-1}{2.3.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-H01}{H01} & A input handoff C->A & Lean;\newline Handoff;\newline Contract;\newline Object & F0 & current & \cellcolor{yellow!25}Y & CToAInputProfile. & Declared handoff input only. & C-derived data. & Typed;\newline Exec mirror if numeric. & medium & \hyperlink{phase-row-2-3-1}{2.3.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-H02}{H02} & A input handoff D->A & Lean;\newline Handoff;\newline Contract;\newline Object & F0 & current & \cellcolor{yellow!25}Y & DToAInputProfile. & Declared handoff input only. & D-derived data. & Typed;\newline may include time/\allowbreak{}dynamics. & medium & \hyperlink{phase-row-2-3-1}{2.3.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-H03}{H03} & A input handoff E->A & Lean;\newline Handoff;\newline Contract;\newline Object & F0 & current & \cellcolor{yellow!25}Y & EToAInputProfile. & Declared handoff input only. & E-derived data. & Typed;\newline not default. & low & \hyperlink{phase-row-2-3-1}{2.3.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-O00}{O00} & ExecComplex & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{white}W & ExecComplex as rational-pair operational scalar floor QxQ;\newline not a complete Complex layer. It owns executable rational complex arithmetic only. & Already in code. & Rational pair /\allowbreak{} operational complex implementation. & Direct QxQ executable path. Algebraic irrational coordinates require O09 or mirror-only treatment;\newline analytic Complex is reached only through ExecComplexBridge. & critical & \hyperlink{phase-row-1-2-1}{1.2.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-G01}{G01} & substrate: regular branching & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{yellow!25}Y & RegularSubstrateProfile. & GeneratedBranchFamily /\allowbreak{} RegularCell-path. & code-b, arity, level carrier. & No scalar;\newline generates Exec-matrix indices. & high & \hyperlink{phase-row-1-2-3}{1.2.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-G02}{G02} & substrate: variable branching & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{yellow!25}Y & VariableSubstrateProfile. & LevelVariableCell/\allowbreak{}Policy-path. & Branching policy beta, level history. & No scalar;\newline Exec-Matrix downstream. & medium & \hyperlink{phase-row-1-2-4}{1.2.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-G03}{G03} & Level /\allowbreak{} Cutoff & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{yellow!25}Y & LevelProfile with selectedLevel/\allowbreak{}cutoff/\allowbreak{}levelSpec. & Generator request or existing Step1/\allowbreak{}Handoff core. & Request + admissibility proof. & Nat;\newline optional ExecComplex-mirror for numeric reports. & high & \hyperlink{phase-row-1-2-5}{1.2.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-G04}{G04} & Carrier /\allowbreak{} index type & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{yellow!25}Y & CarrierProfile: carrier, Fintype, DecidableEq, cardinality, equiv-to-Fin. & LevelProfile + generated level-history. & GeneratedLevelHistoryIndex or neutral Carrier. & Not Skalar;\newline Matrix via Carrier in ExecComplex. & high & \hyperlink{phase-row-1-2-6}{1.2.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-G05}{G05} & Boundary /\allowbreak{} interface /\allowbreak{} interior partition & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{yellow!25}Y & PartitionProfile. & GeneratedBoundaryInteriorPartition /\allowbreak{} sources near SM3a/\allowbreak{}SM3b. & Carrier + cut/\allowbreak{}BoundarySpec. & indicator values operational as Bool/\allowbreak{}Finset;\newline matrix entries Exec. & high & \hyperlink{phase-row-1-3-1}{1.3.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-G06}{G06} & Regime: noOuterEnvironment & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{yellow!25}Y & RegimeProfile.noOuter. & Split-/\allowbreak{}environment proofs from A, not from B. & Partition + complement/\allowbreak{}environment proof. & No Exec-Skalar;\newline affects operator/\allowbreak{}dynamics Profile. & high & \hyperlink{phase-row-1-3-2}{1.3.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-G07}{G07} & Regime: hasOuterEnvironment & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{yellow!25}Y & RegimeProfile.hasOuter. & Complementfamilien/\allowbreak{}outer environment proof. & Approximant + complement proof. & No Exec-Skalar;\newline open matrix/\allowbreak{}channel Profile downstream. & high & \hyperlink{phase-row-1-3-2}{1.3.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-G08}{G08} & Complement families: UV tail & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{red!20}R & UVComplementProfile. & Generated complement/\allowbreak{}provenance;\newline not consumer-invented. & Approximant + infinite carrier. & Structural;\newline effect can in Exec-Operator mixed sein. & high & \hyperlink{phase-row-1-3-3}{1.3.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-G09}{G09} & Complement families: IR/\allowbreak{}parent-path tail & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{red!20}R & IRComplementProfile. & Generated complement/\allowbreak{}provenance. & Approximant + parent/\allowbreak{}level structure. & Structural;\newline Exec downstream via operator effect. & medium & \hyperlink{phase-row-1-3-3}{1.3.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-G10}{G10} & Complement families: sideways environment & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{red!20}R & SideEnvironmentProfile. & Generated complement/\allowbreak{}provenance. & Branching + nonselected sectors. & Structural;\newline Exec downstream via operator effect. & medium & \hyperlink{phase-row-1-3-3}{1.3.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CD0}{CD0} & Cayley-Dickson source & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{cyan!20}B & CayleyDicksonSourceProfile. & Structural/\allowbreak{}CayleyDickson + Handoff adapter. & carrier/\allowbreak{}regularization/\allowbreak{}schur from closed A data. & Not inherently Exec;\newline arithmetic compatibility path must state mirror. & high & \hyperlink{phase-row-1-4-1}{1.4.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CD1}{CD1} & Scalar part & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{cyan!20}B & CDScalarPartProfile. & CD source. & CD algebra data. & Exec bridge only if coordinates available. & medium & \hyperlink{phase-row-1-4-2}{1.4.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CD2}{CD2} & Cayley-Dickson star/\allowbreak{}conjugation & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{cyan!20}B & CDStarProfile. & CD source/\allowbreak{}scalar part. & CD algebra data. & Coordinate-level mirror optional. & medium & \hyperlink{phase-row-1-4-3}{1.4.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CD3}{CD3} & CD normSq & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{cyan!20}B & CDNormSqProfile. & star + product. & CD algebra. & Exec bridge only after arithmetic compatibility. & medium & \hyperlink{phase-row-1-4-4}{1.4.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CD4}{CD4} & CD multiplication/\allowbreak{}product & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{cyan!20}B & CDProductProfile. & CD source. & CD coordinates. & Coordinate calculations possible;\newline not automatic ExecComplex. & medium & \hyperlink{phase-row-1-4-5}{1.4.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CD5}{CD5} & Alternative law & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{cyan!20}B & CDAlternativeLawCertificate. & CD product. & Product associator. & Proof-level;\newline computations by coordinates if available. & medium & \hyperlink{phase-row-1-4-6}{1.4.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CD6}{CD6} & Norm multiplicativity & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{cyan!20}B & CDNormMultiplicativityCertificate. & CD norm/\allowbreak{}product. & normSq, product. & Proof-level;\newline arithmetic bridge later. & medium & \hyperlink{phase-row-1-4-7}{1.4.7}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CD7}{CD7} & Hurwitz stop /\allowbreak{} R,C,H,O classification & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{cyan!20}B & HurwitzStopProfile. & CD duties closed. & alternative + norm + division. & Not Exec;\newline structural theorem. & medium & \hyperlink{phase-row-1-4-8}{1.4.8}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-S00}{S00} & Dirichlet-Laplacian & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{yellow!25}Y & DirichletLaplacianProfile. & Generated Dirichlet data. & Partition + weights + adjacency. & Matrix carrier carrier ExecComplex or bridge from Real to ExecComplex. & high & \hyperlink{phase-row-3-1}{3.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-S01}{S01} & Interior block & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{cyan!20}B & InteriorBlockProfile. & Dirichlet-Laplacian + partition. & Interior indices + matrix. & ExecComplex-matrix or proven bridge. & high & \hyperlink{phase-row-3-2}{3.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-S02}{S02} & Interior inverse candidate & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{cyan!20}B & InteriorInverseCandidateProfile. & SM3db trace/\allowbreak{}fold candidate chain. & Trace + accumulated entry fold. & Matrix ExecComplex/\allowbreak{}Real with bridge. & high & \hyperlink{phase-row-3-3}{3.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-S03}{S03} & Two-sided inverse certificate & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{cyan!20}B & Two-sided inverse certificate. & Candidate + product identities. & Interior block + candidate. & Matrixprodukt-Statements operational pruefbar. & high & \hyperlink{phase-row-3-4}{3.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-S04}{S04} & InteriorEliminationData & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{cyan!20}B & InteriorEliminationProfile. & TwoSidedInv + partition + blocks. & Interior block, inverse, couplings. & ExecComplex Schur-formula downstream. & high & \hyperlink{phase-row-3-5}{3.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-S05}{S05} & DtN boundary operator & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{cyan!20}B & BoundaryOperatorProfile. & Interior elimination /\allowbreak{} Schur complement. & Laplacian blocks + inverse certificate. Route must be checked against BR06 before public-final promotion. & Matrix boundary boundary ExecComplex;\newline Pflicht for Part 2. & high & \hyperlink{phase-row-3-6}{3.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-S06}{S06} & GeneralizedDtN /\allowbreak{} MultiSchur & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{cyan!20}B & GeneralizedBoundaryOperatorProfile. & Generated generalized DtN/\allowbreak{}MultiSchur chain. & Boundary operator + additional ports. & ExecComplex matrix profile. & high & \hyperlink{phase-row-3-7}{3.7}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-O01}{O01} & Boundary matrix over ExecComplex & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{cyan!20}B & ExecMatrixProfile. & DtN/\allowbreak{}MultiSchur -> Exec mirror. & Boundary operator + Exec bridge. & Matrix carrier carrier ExecComplex. & high & \hyperlink{phase-row-4-1}{4.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-O02}{O02} & Determinant coefficient recurrence & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{cyan!20}B & CoefficientRecurrenceProfile. & SM9e recurrence. & Exec matrix + recurrence. & Nat -> ExecComplex. & high & \hyperlink{phase-row-4-2}{4.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-O03}{O03} & Operational polynomial profile & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{cyan!20}B & OperationalPolynomialProfile. & SM9c/\allowbreak{}SM9d/\allowbreak{}SM9e chain. & Coefficient recurrence. & Coefficients ExecComplex. & high & \hyperlink{phase-row-4-3}{4.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-O04}{O04} & Quadratic coefficient window & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{cyan!20}B & QuadraticWindowCertificate. & SM9g1 from recurrence/\allowbreak{}window. & CoefficientAt source. & a,b,c : ExecComplex. & high & \hyperlink{phase-row-4-4}{4.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-O05}{O05} & Operational discriminant D\_op & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{cyan!20}B & OperationalDiscriminantCertificate. & SM9h. & QuadraticWindow. & discriminantValue : ExecComplex. & critical & \hyperlink{phase-row-4-5}{4.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-O06}{O06} & Comparison target policy & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{green!18}G & ComparisonTargetPolicy. Also governs heuristic lattice test targets: comparison rows may not feed back into operational generation. & theory register + target-source proof. & D\_op + target definition. BR07 must audit thread-recursion provenance before comparison interpretation. & Operational side may use only rational/\allowbreak{}integer comparison invariants computed from D\_op. General algebraic target data lives in mirror/\allowbreak{}non-operational layers under EXEC-2. & high & \hyperlink{phase-row-4-6}{4.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-O07}{O07} & General finite computation test matrix profile & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & Reusable proof-carrying finite test matrix over code-defined generated instances, branch modes, L\_max rows, operational output witnesses, and optional comparison sentinel columns. v34 adds O08 as the regime-typed extension;\newline O07 remains the generic/\allowbreak{}non-specialized base. & canonical smoke-test generator;\newline concrete computable instance traversal;\newline operational arithmetic path;\newline generalization of L09/\allowbreak{}L10 special lattice tests. & code-defined generator/\allowbreak{}branching API, finite L\_max, static/\allowbreak{}dynamic branch-mode tags, finite carriers/\allowbreak{}matrices/\allowbreak{}profiles, executable output witness records. & Core fields are operational finite/\allowbreak{}rational/\allowbreak{}integer;\newline mirror comparison columns are explicitly non-operational. & early before specialized computation claims & \hyperlink{phase-row-4-0-1}{4.0.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N00}{N00} & Fundamental discriminant D\_fund & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{green!18}G & FundamentalDiscriminantProfile. & Normalization of D\_op. & D\_op, square factor/\allowbreak{}congreence proof. & Integer/\allowbreak{}rat mirror;\newline ExecComplex embedding for reports. & high & \hyperlink{phase-row-5-1}{5.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N01}{N01} & Conductor f & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{green!18}G & ConductorProfile. & Discriminant normalization. & D\_op, D\_fund. & Nat/\allowbreak{}Int;\newline ExecComplex mirror optional. & high & \hyperlink{phase-row-5-1}{5.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N02}{N02} & Quadratic field K=Q(sqrt(D)) & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{yellow!25}Y & QuadraticFieldProfile. & D\_fund. & D\_fund + sign/\allowbreak{}non-square proof.;\newline exact quadratic coordinates only through O09/\allowbreak{}O10/\allowbreak{}BR14 when required & Not purely ExecComplex;\newline operational embedding optional. Derived-quadratic update: no free sqrt(D);\newline exact coordinates require proof-carrying D-source. & medium & \hyperlink{phase-row-5-2}{5.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N03}{N03} & Quadratic order O\_D & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{yellow!25}Y & QuadraticOrderProfile. & D\_fund + conductor. & K, f. & Coordinates can be operational;\newline ring laws proof layer. & high & \hyperlink{phase-row-5-3}{5.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N04}{N04} & Integral basis /\allowbreak{} omega\_D & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{yellow!25}Y & IntegralBasisProfile. & OrderProfile. & D congreence, conductor.;\newline exact quadratic coordinates only through O09/\allowbreak{}O10/\allowbreak{}BR14 when required & Coordinates in rationas/\allowbreak{}ExecComplex embedding. Derived-quadratic update: no free sqrt(D);\newline exact coordinates require proof-carrying D-source. & high & \hyperlink{phase-row-5-4}{5.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N05}{N05} & Trace form & Lean;\newline Target;\newline Object & F1 & current & \cellcolor{yellow!25}Y & TraceFormProfile. & Order/\allowbreak{}field. & Conjugation + basis. & Rational/\allowbreak{}Exec mirror for coefficients. & medium & \hyperlink{phase-row-5-5}{5.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N06}{N06} & Norm form & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{yellow!25}Y & AlgebraicNormProfile. & Order + conjugation. & Integral basis.;\newline exact quadratic coordinates only through O09/\allowbreak{}O10/\allowbreak{}BR14 when required & Integer/\allowbreak{}ExecComplex values. Derived-quadratic update: no free sqrt(D);\newline exact coordinates require proof-carrying D-source. & high & \hyperlink{phase-row-5-5}{5.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N07}{N07} & Conjugation & Lean;\newline Target;\newline Object & F1 & current & \cellcolor{yellow!25}Y & ConjugationProfile. & QuadraticFieldProfile. & sqrt(D) -> -sqrt(D). & Coordinate-level operational reflection. & medium & \hyperlink{phase-row-5-5}{5.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N08}{N08} & Unit group O\_D\textasciicircum{}* & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & UnitGroupProfile. & OrderProfile + norm one classification. & O\_D + norm form. & Units as coordinates;\newline group order operational. & high & \hyperlink{phase-row-6-1}{6.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N09}{N09} & Class group Cl(O\_D) & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & ClassGroupProfile. & OrderProfile + ideas. & Fractional ideas modulo principal. & Finite group data;\newline order mirrored as Nat/\allowbreak{}Exec. & medium & \hyperlink{phase-row-6-2}{6.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N10}{N10} & Class number h(D) & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & ClassNumberProfile. & ClassGroupProfile. & Cl(O\_D). & Nat/\allowbreak{}Exec mirror. & medium & \hyperlink{phase-row-6-2}{6.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N11}{N11} & Fractional/\allowbreak{}integral ideas & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & IdealProfile. & OrderProfile. & O\_D modules/\allowbreak{}submodules. & Not Exec;\newline invariants operational. & medium & \hyperlink{phase-row-6-2-1}{6.2.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N12}{N12} & Principal ideal predicate & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & PrincipalIdealProfile. & IdealProfile + generator existence. & Ideas and norm. & Witness coordinates operational if present. & medium & \hyperlink{phase-row-6-2-2}{6.2.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N13}{N13} & Heegner/\allowbreak{}PID/\allowbreak{}UFD indicator & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & HeegnerIndicatorProfile. It classifies number-theoretic class-number-one/\allowbreak{}PID/\allowbreak{}UFD data only;\newline it does not classify CNNA closed/\allowbreak{}noOuter regime status. & Class number + order data. & h(D), D\_fund. & Bool/\allowbreak{}Nat;\newline target list only as comparison. & medium & \hyperlink{phase-row-6-3}{6.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N14}{N14} & Prime splitting behavior & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & PrimeSplittingProfile. & Kronecker character. & D\_fund, primes. & Values -1/\allowbreak{}0/\allowbreak{}1 as Exec mirror. & medium & \hyperlink{phase-row-6-4}{6.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N15}{N15} & Kronecker/\allowbreak{}Dirichlet character chi\_D & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & CharacterProfile. & D\_fund. & Kronecker symbol. & Function Nat -> \{-1,0,1\};\newline operational mirror. & medium & \hyperlink{phase-row-6-4}{6.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CD8}{CD8} & Arithmetic-CD compatibility as Schur-duality corollary & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & CDArithmeticCompatibilityProfile as a corollary of BR08, not as an independently injected norm analogy. & Order/\allowbreak{}norm + CD Profile + horizontal/\allowbreak{}vertical Schur-duality bridge. & BR08, BR09, CD3/\allowbreak{}CD6/\allowbreak{}CD7, O05, and later number-theory norm objects when available. & Requires explicit coordinate bridge and concrete finite witness;\newline no compatibility is accepted before the Schur bridge proof. & medium & \hyperlink{phase-row-10-4-2}{10.4.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-L00}{L00} & Lattice embedding Lambda -> C & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & ComplexEmbeddingProfile. & Order + selected embedding. & Integral basis + sqrt(D) branch.;\newline exact quadratic coordinates only through O09/\allowbreak{}O10/\allowbreak{}BR14 when required & Mirror-only for general algebraic embeddings involving sqrt(D). Operational return is restricted to rational/\allowbreak{}integer invariants such as discriminant/\allowbreak{}norm data when separately proved. Derived-quadratic update: no free sqrt(D);\newline exact coordinates require proof-carrying D-source. & high & \hyperlink{phase-row-7-1}{7.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-L01}{L01} & Lattice basis & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & LatticeBasisProfile. & Embedding + integral basis. & OrderProfile. & Coordinates operational if encoded. & high & \hyperlink{phase-row-7-1}{7.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-L02}{L02} & Gram matrix & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & GramProfile. & Lattice basis + scalar product. & Embedding.;\newline exact quadratic coordinates only through O09/\allowbreak{}O10/\allowbreak{}BR14 when required & Operational only for rational Gram entries or integer/\allowbreak{}rational invariants such as determinant/\allowbreak{}discriminant;\newline general algebraic/\allowbreak{}real Gram data is mirror-only under EXEC-2. Derived-quadratic update: no free sqrt(D);\newline exact coordinates require proof-carrying D-source. & high & \hyperlink{phase-row-7-2}{7.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-L03}{L03} & Lattice determinant /\allowbreak{} covolume & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & CovolumeProfile. & GramProfile. & Gram. & Numeric/\allowbreak{}Exec mirror if exact rational. & medium & \hyperlink{phase-row-7-2}{7.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-L04}{L04} & Period ratio tau & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & PeriodRatioProfile. & Lattice basis + orientation. & Embedding, basis.;\newline exact quadratic coordinates only through O09/\allowbreak{}O10/\allowbreak{}BR14 when required & General tau is mirror-only. Operational path may record rational special cases or integer/\allowbreak{}rational invariants only when derived from prior objects and separately proved. Under EXEC-2 tau is mirror/\allowbreak{}comparison unless a rational/\allowbreak{}integer invariant is exported. Derived-quadratic update: no free sqrt(D);\newline exact coordinates require proof-carrying D-source. & high & \hyperlink{phase-row-7-3}{7.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-L05}{L05} & Upper half-plane condition & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & UpperHalfPlaneCertificate. & Period ratio + orientation. & tau. & Inequality may need real/\allowbreak{}mirror layer. & medium & \hyperlink{phase-row-7-3}{7.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-L06}{L06} & Angle /\allowbreak{} cosine profile & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & AngleProfile. Includes future test-matrix consumption by L09/\allowbreak{}L10;\newline angle values are profiles, not generator inputs. & GramProfile. & Gram entries;\newline cos = <u,v>/\allowbreak{}sqrt(...). & Cosine ratio operational;\newline arccos in analytic mirror. & medium & \hyperlink{phase-row-7-4}{7.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-L07}{L07} & Lattice automorphism group & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & LatticeAutomorphismProfile. & UnitGroup + embedding action. & Units + lattice basis. & Permutation/\allowbreak{}action finite operational. & medium & \hyperlink{phase-row-7-5}{7.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-M02}{M02} & Eisenstein series G4,G6 & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & EisensteinSeriesProfile. & Lattice/\allowbreak{}period ratio. v37: retained in modular/\allowbreak{}CM Path A. & Lattice sums or q-expansion. & Truncated sums/\allowbreak{}q-series operational;\newline exact analytic mirror. & medium & \hyperlink{phase-row-8-1}{8.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-M03}{M03} & Weierstrass invariants g2,g3 & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & WeierstrassInvariantProfile. & G4,G6. v37: retained in modular/\allowbreak{}CM Path A. & Eisenstein series. & Operational if finite/\allowbreak{}truncated or h=1 closed source. & medium & \hyperlink{phase-row-8-2}{8.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-M04}{M04} & Modular discriminant Delta\_mod & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & ModularDiscriminantProfile. & g2,g3. v37: retained in modular/\allowbreak{}CM Path A. & Weierstrass invariants. & ExecComplex if g2,g3 operational. & medium & \hyperlink{phase-row-8-3}{8.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-M05}{M05} & j-invariant & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & JInvariantProfile. & Delta\_mod + g2, or q-expansion. v37: retained in modular/\allowbreak{}CM Path A. & g2, Delta\_mod, tau. & General j-invariant computation is mirror/\allowbreak{}non-operational. Operational return is allowed only for proved integer/\allowbreak{}rational special invariants, e.g. h=1 anchors, and must not source the derivation. Future M08 may record j=0 and j=1728 as integer comparison targets;\newline analytic j evaluation remains non-operational unless separately justified. & medium & \hyperlink{phase-row-8-4}{8.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-SP0}{SP0} & Eigenvalue profile & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{yellow!25}Y & FiniteSpectrumProfile. & Exec matrix /\allowbreak{} charpoly. v37: placed on independent spectral/\allowbreak{}physical Path B after Phase 4.1, not behind modular/\allowbreak{}j path. & Matrix, polynomial. & General algebraic eigenvalues are mirror-only. Operational spectral path carries charpoly/\allowbreak{}coefficients/\allowbreak{}discriminants/\allowbreak{}gaps or other rational/\allowbreak{}integer certificates unless algebraic values are confined to mirror. & medium & \hyperlink{phase-row-10-1}{10.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-SP1}{SP1} & Spectral gap & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{yellow!25}Y & SpectralGapProfile. & FiniteSpectrumProfile. v37: placed on independent spectral/\allowbreak{}physical Path B after Phase 4.1, not behind modular/\allowbreak{}j path. & Eigenvalues/\allowbreak{}order. & Needs comparison/\allowbreak{}order;\newline operational if finite exact/\allowbreak{}approx bridge. & medium & \hyperlink{phase-row-10-1}{10.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P00}{P00} & Operator algebra & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{yellow!25}Y & OperatorAlgebraProfile. & Carrier + matrix algebra + star. v37: placed on independent spectral/\allowbreak{}physical Path B after Phase 4.1, not behind modular/\allowbreak{}j path. & Boundary matrix. & Matrix algebra over ExecComplex;\newline C-mirror later. & medium & \hyperlink{phase-row-10-2}{10.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P01}{P01} & Star operation & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{yellow!25}Y & StarOperationProfile. & ExecComplex conjugation + matrix transpose. v37: placed on independent spectral/\allowbreak{}physical Path B after Phase 4.1, not behind modular/\allowbreak{}j path. & Matrix algebra. & Computable over ExecComplex if conjugation defined. & medium & \hyperlink{phase-row-10-2}{10.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P02}{P02} & State functional & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{yellow!25}Y & StateFunctionalProfile. & Trace/\allowbreak{}Gibbs from operator profile. v37: placed on independent spectral/\allowbreak{}physical Path B after Phase 4.1, not behind modular/\allowbreak{}j path. & Matrix, weights. & Finite trace operational;\newline positivity maybe mirror/\allowbreak{}proof. & medium & \hyperlink{phase-row-10-2}{10.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P03}{P03} & Gibbs state & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{yellow!25}Y & GibbsStateProfile. & Matrix exponential seed. v37: placed on independent spectral/\allowbreak{}physical Path B after Phase 4.1, not behind modular/\allowbreak{}j path. & H, beta. & Exp not purely ExecComplex unless truncated/\allowbreak{}seed;\newline mirror boundary. & medium & \hyperlink{phase-row-10-2}{10.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P04}{P04} & Time evolution & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{yellow!25}Y & TimeEvolutionProfile. & Operator + regime. v37: placed on independent spectral/\allowbreak{}physical Path B after Phase 4.1, not behind modular/\allowbreak{}j path. & H, t. & Finite approximations;\newline exp mirror. & medium & \hyperlink{phase-row-10-2}{10.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P05}{P05} & Unitarity certificate & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{yellow!25}Y & UnitarityCertificate. & Time evolution + noOuter. v37: placed on independent spectral/\allowbreak{}physical Path B after Phase 4.1, not behind modular/\allowbreak{}j path. & H, star, state. & Matrix identities operational if finite exact. & medium & \hyperlink{phase-row-10-2}{10.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P06}{P06} & Open channel /\allowbreak{} effective openness & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{red!20}R & OpenChannelProfile. & Regime hasOuter + complement effects. v37: placed on independent spectral/\allowbreak{}physical Path B after Phase 4.1, not behind modular/\allowbreak{}j path. & Boundary operator + environment profile. & Krfrom/\allowbreak{}Lindblad only if derived;\newline Exec matrices if finite. & medium & \hyperlink{phase-row-10-2}{10.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N16}{N16} & Dirichlet L-function L(s,chi\_D) & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & LFunctionProfile. & CharacterProfile + analytic layer. v37: analytic far target in Path A, not a source for finite spectral/\allowbreak{}physical Path B. & chi\_D. & Finite truncations operational;\newline exact analytic object mirror. & low & \hyperlink{phase-row-9-2}{9.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N17}{N17} & Class number formula & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & ClassNumberFormulaProfile. & LFunction + unit group + D. v37: analytic far target in Path A, not a source for finite spectral/\allowbreak{}physical Path B. & chi\_D, units, D\_fund. & Approximation only operational;\newline theorem analytic. & low & \hyperlink{phase-row-9-3}{9.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-L08}{L08} & Theta series Theta\_Lambda & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & ThetaSeriesProfile. & Lattice + norm form. & Norm form over lattice. & Truncated coefficients operational;\newline full series formal/\allowbreak{}mirror. & low & \hyperlink{phase-row-9-1}{9.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-M00}{M00} & Modular group action SL2Z & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & ModularActionProfile. & Upper half-plane + integer matrices. v37: retained in modular/\allowbreak{}CM Path A. & tau. & Action formulas operational for finite transformations. & low & \hyperlink{phase-row-8-0}{8.0}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-M01}{M01} & Fundamental domain representative & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & FundamentalDomainProfile. & ModularActionProfile. v37: retained in modular/\allowbreak{}CM Path A. & tau + reduction algorithm/\allowbreak{}proof. & Algorithmic reduction possible. & low & \hyperlink{phase-row-8-0}{8.0}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-M06}{M06} & q-expansion of j & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & JQExpansionProfile. & tau/\allowbreak{}q. v37: retained in modular/\allowbreak{}CM Path A. & q=exp(2pi i tau). & Truncated coefficients operational if q path exists;\newline exact series formal. & low & \hyperlink{phase-row-8-8}{8.8}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-M07}{M07} & Hilbert class polynomial H\_D & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & HilbertClassPolynomialProfile. & Class group + j-values. v37: retained in modular/\allowbreak{}CM Path A. & Cl(O\_D), j. & Polynomial coefficients operational if constructed. & low & \hyperlink{phase-row-8-8}{8.8}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-TM0}{TM0} & Transfermatrix T\_k & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & TransferMatrixProfile. & Schur recurrence. v37: moved to Schur/\allowbreak{}transfer Path B and late BR08 bridge, not modular-form path. & Local recursion step. & Entries operational in polynomial/\allowbreak{}ring representation. & low & \hyperlink{phase-row-10-4}{10.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-TM1}{TM1} & Transfermatrix product & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & TransferProductProfile. & TransferMatrixProfile. v37: moved to Schur/\allowbreak{}transfer Path B and late BR08 bridge, not modular-form path. & Trace/\allowbreak{}fold/\allowbreak{}product. & Operational finite product. & low & \hyperlink{phase-row-10-4}{10.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-TM2}{TM2} & Moebius/\allowbreak{}continued fraction relation & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & MobiusSchurProfile. & Transfermatrix. v37: moved to Schur/\allowbreak{}transfer Path B and late BR08 bridge, not modular-form path. & T\_k action. & Operational finite map. & low & \hyperlink{phase-row-10-4}{10.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-SP2}{SP2} & Heat kernel K(t) & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & HeatKernelProfile. & Spectrum/\allowbreak{}operator. v37: placed on independent spectral/\allowbreak{}physical Path B after Phase 4.1, not behind modular/\allowbreak{}j path. & Eigenvalues or matrix exponential seed. & Finite approximations operational;\newline real exp mirror. & low & \hyperlink{phase-row-10-3}{10.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-SP3}{SP3} & Spectral zeta zeta\_H & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & SpectralZetaProfile. & Spectrum. v37: placed on independent spectral/\allowbreak{}physical Path B after Phase 4.1, not behind modular/\allowbreak{}j path. & Eigenvalues. & Analytic object;\newline finite/\allowbreak{}truncated operational. & low & \hyperlink{phase-row-10-3}{10.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-SP4}{SP4} & Spectral dimension & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & SpectralDimensionProfile. & HeatKernelProfile + limit. v37: placed on independent spectral/\allowbreak{}physical Path B after Phase 4.1, not behind modular/\allowbreak{}j path. & K(t). & Limit/\allowbreak{}mirror;\newline finite estimator operational. & low & \hyperlink{phase-row-10-3}{10.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-SP5}{SP5} & Zeta-regularized determinant & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & ZetaDeterminantProfile. & SpectralZetaProfile. v37: placed on independent spectral/\allowbreak{}physical Path B after Phase 4.1, not behind modular/\allowbreak{}j path. & zeta\_H. & Analytic mirror;\newline finite determinant operational. & low & \hyperlink{phase-row-10-3}{10.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P07}{P07} & KMS condition & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & KMSProfile. & State + time evolution. & State, dynamics. & Analytic strip not Exec;\newline finite checks/\allowbreak{}truncations operational. & low & \hyperlink{phase-row-13-4}{13.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P08}{P08} & GNS Hilbert space & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & GNSProfile. & State functional. & Algebra quotient/\allowbreak{}completion. & Finite quotient operational;\newline completion mirror. & low & \hyperlink{phase-row-13-4}{13.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P09}{P09} & Tomita operator S & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & TomitaOperatorProfile. & GNS + star. & GNS state algebra. & Finite matrix profile possible;\newline closure analytic. & low & \hyperlink{phase-row-13-5}{13.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P10}{P10} & Modular operator Delta & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & ModularOperatorProfile. & Tomita S. & S. & Finite matrix possible;\newline analytic layer. & low & \hyperlink{phase-row-13-5}{13.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P11}{P11} & Modular conjugation J & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & ModularConjugationProfile. & Tomita-Takesaki. & S, Delta. & Not direct Exec;\newline finite mirror only if polar decomposition derived. & low & \hyperlink{phase-row-13-5}{13.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P12}{P12} & Bisognano-Wichmann/\allowbreak{}CPT bridge & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & CPTBridgeProfile. & Modular J + spacetime/\allowbreak{}wedge data. & J, local net, geometry. & Analytic/\allowbreak{}geometric, not pure Exec. & low & \hyperlink{phase-row-13-6}{13.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P13}{P13} & Spin-statistics & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & SpinStatisticsProfile. & Modular + redations. & J, covariance, redations. & Not Exec except finite symmetry shadows. & low & \hyperlink{phase-row-13-6}{13.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P14}{P14} & Kramers degeneracy & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & KramersProfile. & Time reversal + state/\allowbreak{}symmetry. & Antiunitary T, spectrum. & Finite spectral shadows possible. & low & \hyperlink{phase-row-13-6}{13.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P15}{P15} & Split property & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & SplitPropertyProfile. & Operator algebra + collar/\allowbreak{}regime. & Local net, inclusion. & Finite type-I checks operational;\newline full split analytic. & low & \hyperlink{phase-row-13-6}{13.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-P16}{P16} & Local net /\allowbreak{} Haag-Kastler algebraic axioms & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & LocalNetProfile. & RegionNet + operator algebra. & Regions, inclusions, operators. & Finite net operational;\newline spacetime axioms need C/\allowbreak{}D. & low & \hyperlink{phase-row-13-3}{13.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-H10}{H10} & A->B bright handoff & Lean;\newline Handoff;\newline Contract;\newline Object & F0 & current & \cellcolor{yellow!25}Y & AToBBrightOutputProfile. & A operational boundary profile. & Omega, L, regime, operator;\newline no hidden complement. & ExecComplex operator may be included;\newline B may mirror to C. & high & \hyperlink{phase-row-11-1}{11.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-H11}{H11} & A->B prime/\allowbreak{}dark future handoff & Lean;\newline Handoff;\newline Contract;\newline Object & F0 & current & \cellcolor{red!20}R & AToBDarkOutputProfile. & A complement profile;\newline separate from bright. & Dark/\allowbreak{}complement data. & Likely not finite Exec-only;\newline must specify. & low & \hyperlink{phase-row-11-2}{11.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-H12}{H12} & A->C handoff & Lean;\newline Handoff;\newline Contract;\newline Object & F0 & current & \cellcolor{yellow!25}Y & AToCOutputProfile. & A arithmetic/\allowbreak{}geometric Profile. & Carrier, lattice, Gram, tau, regime as allowed. & ExecComplex mirrors for coordinates where available. & medium & \hyperlink{phase-row-11-3}{11.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-H13}{H13} & A->D handoff & Lean;\newline Handoff;\newline Contract;\newline Object & F0 & current & \cellcolor{yellow!25}Y & AToDOutputProfile. & Operator/\allowbreak{}regime/\allowbreak{}spectral Profile. & Boundary operator, state seeds, regime. & Exec matrices;\newline time evolution maybe mirror/\allowbreak{}analytic. & medium & \hyperlink{phase-row-11-4}{11.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-H14}{H14} & A->E handoff & Lean;\newline Handoff;\newline Contract;\newline Object & F0 & current & \cellcolor{black!18}K & AToEOutputProfile. & Arithmetic/\allowbreak{}theory register Profile. & D, CM, class data, j, etc. & Exec mirrors where present. & low & \hyperlink{phase-row-11-5}{11.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-MOON0}{MOON0} & j coefficient stream & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & CNNA-derived q-expansion coefficient stream of j after j is derived. & q-expansion of j;\newline modular forms chain. & M06 q-expansion object. & Computable only after q-expansion representation;\newline may require mirror arithmetic for infinite series. & low & \hyperlink{phase-row-12-1}{12.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-MOON1}{MOON1} & Monster dimension comparison profile & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & Comparison profile between derived j coefficients and established Monster representation dimensions. & j coefficient stream plus external established Monster data as comparison target only. & MOON0 plus external established Monster representation dimension data as comparison target only;\newline no reverse dependency into j derivation. & Comparison layer;\newline no Exec path into foundation. & low & \hyperlink{phase-row-12-2}{12.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-MOON2}{MOON2} & McKay-Thompson comparison profile & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & Comparison-only profile for McKay-Thompson series. & Moonshine comparison layer after j/\allowbreak{}q data. & MOON0 and optional external named McKay-Thompson/\allowbreak{}Hauptmodul series as targets. & Comparison-only;\newline no foundation Exec source. & low & \hyperlink{phase-row-12-3}{12.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-B00}{B00} & Pillar B input contract from A & Lean;\newline Handoff;\newline Contract;\newline Object & F0 & current & \cellcolor{black!18}K & B consumes exactly the A->B bright handoff and nothing else. & A->B handoff H10. & H10;\newline exported boundary/\allowbreak{}operator/\allowbreak{}regime profiles. & Exec data only if exported in A->B profile. & medium & \hyperlink{phase-row-13-1}{13.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-B01}{B01} & Boundary star-algebra /\allowbreak{} observable algebra & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Finite *-algebra of boundary observables derived from exported A boundary operator data. & A->B bright boundary carrier/\allowbreak{}operator. & B00;\newline ExecBoundaryMatrix;\newline BoundaryOperator. & Finite matrix algebra can have ExecComplex operational mirror;\newline analytic mirror later. & medium & \hyperlink{phase-row-13-2}{13.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-B02}{B02} & Local net /\allowbreak{} QFT algebraic profile & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Net of algebras derived from boundary/\allowbreak{}region data;\newline algebraic QFT consumer. & B boundary star-algebra plus exported region/\allowbreak{}localization profile. & B01;\newline A->B region/\allowbreak{}interface data. & Finite operational net first;\newline continuum/\allowbreak{}AQFT mirror later. & medium & \hyperlink{phase-row-13-3}{13.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-B03}{B03} & B state/\allowbreak{}GNS/\allowbreak{}KMS profile & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & State functional, GNS construction, and KMS gate over B observable algebra. & B algebra;\newline exported dynamics/\allowbreak{}state seeds from A if available. & B01;\newline P01/\allowbreak{}P02/\allowbreak{}P03;\newline Gibbs/\allowbreak{}time-evolution seeds. & Finite state/\allowbreak{}GNS may be operational;\newline KMS analyticity belongs to mirror/\allowbreak{}far target. & medium & \hyperlink{phase-row-13-4}{13.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-B04}{B04} & Tomita-Takesaki modular data & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Tomita operator S, modular operator Delta, and modular conjugation J derived from B GNS/\allowbreak{}KMS data. & B03 state/\allowbreak{}GNS/\allowbreak{}KMS profile. & B03;\newline local net. & Mostly analytic mirror;\newline finite pre-versions may be operational only if matrices are finite. & medium & \hyperlink{phase-row-13-5}{13.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-B05}{B05} & CPT/\allowbreak{}BW/\allowbreak{}spin-statistics/\allowbreak{}split gates & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Structural theorem gates derived from B local net and modular data. & B02 local net plus B04 modular data. & B02;\newline B04. & Analytic theorem layer;\newline no Exec source except finite prerequisites. & low & \hyperlink{phase-row-13-6}{13.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-B06}{B06} & B->A allowed output profile & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Typed B output that A may consume only through B->A input handoff. & B-derived theorem/\allowbreak{}data after B phases. & B01-B05 if completed. & Typed;\newline Exec mirror if numeric. & medium & \hyperlink{phase-row-13-7}{13.7}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-C00}{C00} & Pillar C OQS input contract from A & Lean;\newline Handoff;\newline Contract;\newline Object & F0 & current & \cellcolor{black!18}K & C consumes explicit A->C open/\allowbreak{}regime/\allowbreak{}complement outputs. & A->C handoff;\newline HasOuter regime;\newline complement profile. & H12;\newline RegimeProfile;\newline ComplementProfile. & Exec only through exported finite channel/\allowbreak{}operator data. & medium & \hyperlink{phase-row-14-1}{14.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-C01}{C01} & Finite CP/\allowbreak{}channel profile & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Completely-positive/\allowbreak{}channel profile derived from finite exported data. & A finite channel seed and open regime. & C00;\newline P06;\newline ChannelSeed. & Finite ExecComplex channel path if matrices and Kraus/\allowbreak{}Choi data are derived. & medium & \hyperlink{phase-row-14-2}{14.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-C02}{C02} & Effective OQS generator /\allowbreak{} Lindblad gate & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Effective generator and Lindblad/\allowbreak{}GKSL gate if derived from finite channel/\allowbreak{}semigroup data. & C01 plus time-evolution/\allowbreak{}semigroup data. & C01;\newline finite dynamics seeds. & Operational finite generator first;\newline analytic continuous-time mirror later. & medium & \hyperlink{phase-row-14-3}{14.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-C03}{C03} & Decoherence/\allowbreak{}noise profile & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Effective decoherence/\allowbreak{}noise profile derived from complement/\allowbreak{}environment data. & HasOuter regime and C channel/\allowbreak{}effective dynamics. & C00-C02;\newline ComplementProfile. & Finite operational noise kernel if exported matrices exist. & medium & \hyperlink{phase-row-14-4}{14.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-C04}{C04} & C->A allowed output profile & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Typed C output that A may consume only through C->A input. & C-derived OQS theorem/\allowbreak{}data. & C01-C03. & Typed;\newline Exec mirror if numeric. & medium & \hyperlink{phase-row-14-5}{14.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-D00}{D00} & Pillar D spacetime input contract & Lean;\newline Handoff;\newline Contract;\newline Object & F0 & current & \cellcolor{black!18}K & D consumes explicit A/\allowbreak{}C geometry, regime, and localization outputs. & A->D handoff;\newline C outputs when available. & H13;\newline lattice/\allowbreak{}region/\allowbreak{}spectral geometry objects. & Finite/\allowbreak{}computable geometry where derived;\newline continuum mirror later. & low & \hyperlink{phase-row-15-1}{15.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-D01}{D01} & Region/\allowbreak{}localization/\allowbreak{}causal-order candidate & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Candidate region poset, localization profile, and causal order derived from CNNA relational/\allowbreak{}geometric data. & D00;\newline region/\allowbreak{}localization/\allowbreak{}geometry profiles. & A geometry;\newline C open-system profiles if available. & Finite relational/\allowbreak{}computable representation first. & low & \hyperlink{phase-row-15-2}{15.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-D02}{D02} & Metric/\allowbreak{}coarse-geometry/\allowbreak{}covariance gate & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Metric candidate, coarse geometry, and covariance gate derived from D localization/\allowbreak{}spectral data. & D01 plus spectral geometry. & D01;\newline SP0-SP5 if available. & Finite/\allowbreak{}spectral computable approximants;\newline continuum analytic mirror later. & low & \hyperlink{phase-row-15-3}{15.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-D03}{D03} & D->A allowed output profile & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Typed D output that A may consume only through D->A input. & D-derived geometry/\allowbreak{}covariance theorem/\allowbreak{}data. & D01-D02. & Typed;\newline Exec mirror if numeric. & low & \hyperlink{phase-row-15-4}{15.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-E00}{E00} & Pillar E matter input contract & Lean;\newline Handoff;\newline Contract;\newline Object & F0 & current & \cellcolor{black!18}K & E consumes permitted A/\allowbreak{}B/\allowbreak{}C/\allowbreak{}D outputs for matter/\allowbreak{}observable comparison. & A->E handoff;\newline B/\allowbreak{}C/\allowbreak{}D outputs when available. & H14;\newline B/\allowbreak{}C/\allowbreak{}D outputs. & Exec only for exported finite observable data. & low & \hyperlink{phase-row-16-1}{16.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-E01}{E01} & Matter sector and internal symmetry candidate & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Candidate matter sectors and internal symmetries derived from CNNA symmetry/\allowbreak{}arithmetic data. & E00;\newline unit groups, CD path, B/\allowbreak{}D symmetries when available. & Units/\allowbreak{}CD/\allowbreak{}symmetry objects;\newline B/\allowbreak{}D outputs. & Computable only through finite exported symmetry/\allowbreak{}observable data. & low & \hyperlink{phase-row-16-2}{16.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-E02}{E02} & Observable coupling and phenomenology comparison & Reference;\newline Gate;\newline Object & F3 & current & \cellcolor{black!18}K & Observable coupling and empirical comparison layer, not foundational input. & E01 plus B/\allowbreak{}C/\allowbreak{}D observable structures. & E01;\newline B/\allowbreak{}C/\allowbreak{}D outputs. & Finite observed comparison values are external targets, not CNNA sources. & low & \hyperlink{phase-row-16-3}{16.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-E03}{E03} & E->A allowed output profile & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Typed E output that A may consume only through E->A input. & E-derived matter/\allowbreak{}phenomenology theorem/\allowbreak{}data. & E01-E02. & Typed;\newline Exec mirror if numeric. & low & \hyperlink{phase-row-16-4}{16.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR00}{BR00} & Backreaction input DAG & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{black!18}K & DAG of allowed B/\allowbreak{}C/\allowbreak{}D/\allowbreak{}E -> A input handoffs. & Explicit input handoff profiles only. & B06;\newline C04;\newline D03;\newline E03. & Typed;\newline not necessarily Exec. & medium & \hyperlink{phase-row-17}{17}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR01}{BR01} & B->A backreaction input gate & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Gate for B-derived theorem/\allowbreak{}data entering A. & B06. & B06. & Typed;\newline Exec if numeric. & medium & \hyperlink{phase-row-17-1}{17.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR02}{BR02} & C->A OQS backreaction input gate & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Gate for C-derived OQS data entering A. & C04. & C04. & Typed;\newline Exec if numeric. & medium & \hyperlink{phase-row-17-2}{17.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR03}{BR03} & D->A spacetime backreaction input gate & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Gate for D-derived geometry/\allowbreak{}covariance data entering A. & D03. & D03. & Typed;\newline Exec if numeric. & low & \hyperlink{phase-row-17-3}{17.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR04}{BR04} & E->A matter backreaction input gate & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{black!18}K & Gate for E-derived matter/\allowbreak{}phenomenology data entering A. & E03. & E03. & Typed;\newline Exec if numeric. & low & \hyperlink{phase-row-17-4}{17.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR05}{BR05} & Pre/\allowbreak{}post-emergence switch for A statements & Lean;\newline Source;\newline Object & F0 & current & \cellcolor{black!18}K & Profile distinguishing pre-emergence and post-emergence interpretation of A statements. & Allowed input gates plus emergence criteria. & BR00-BR04;\newline regime profile. & Mostly structural;\newline Exec if numeric thresholds are derived. & medium & \hyperlink{phase-row-17-5}{17.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-SIDE0}{SIDE0} & Full ToE comparison profile & Reference;\newline Gate;\newline Object & F4 & current & \cellcolor{black!18}K & Comparison-only placeholder for any future full ToE interpretation that falls out of CNNA. & Completed B/\allowbreak{}C/\allowbreak{}D/\allowbreak{}E/\allowbreak{}backreaction outputs if ever available. & CNNA mature outputs;\newline no ToE assumptions. & No Exec source;\newline comparison target only. & low & \hyperlink{phase-row-18-1}{18.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-SIDE1}{SIDE1} & String-theory comparison profile & Reference;\newline Gate;\newline Object & F4 & current & \cellcolor{black!18}K & Comparison-only placeholder for string-theory-like structures if derivable from CNNA outputs. & D/\allowbreak{}E outputs if ever available. & CNNA outputs;\newline no string assumptions. & No Exec source;\newline comparison target only. & low & \hyperlink{phase-row-18-2}{18.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-SIDE2}{SIDE2} & Loop quantum gravity comparison profile & Reference;\newline Gate;\newline Object & F4 & current & \cellcolor{black!18}K & Comparison-only placeholder for LQG-like structures if derivable from CNNA outputs. & D spacetime outputs if ever available. & CNNA outputs;\newline no LQG assumptions. & No Exec source;\newline comparison target only. & low & \hyperlink{phase-row-18-3}{18.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-SIDE3}{SIDE3} & Noncommutative geometry comparison profile & Reference;\newline Gate;\newline Object & F4 & current & \cellcolor{black!18}K & Comparison-only placeholder for NCG-like structures if derivable from CNNA outputs. & B algebra and D geometry outputs if ever available. & CNNA outputs;\newline no NCG axioms as foundation. & No Exec source;\newline comparison target only. & low & \hyperlink{phase-row-18-4}{18.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-MOON3}{MOON3} & Finite simple group comparison profile & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & Comparison-only profile for CFSG taxonomy: cyclic prime-order, alternating, Lie-type, sporadic. & External established mathematics used only after CNNA has derived a candidate graded/\allowbreak{}symmetry output. & CNNA-derived q/\allowbreak{}graded/\allowbreak{}symmetry profile plus external comparison taxonomy. & Comparison tags can be finite data;\newline no operational foundation source. & low & \hyperlink{phase-row-12-4}{12.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-MOON4}{MOON4} & Sporadic/\allowbreak{}Monster comparison boundary & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & Boundary profile separating sporadic-group/\allowbreak{}Monster comparison data from CNNA-generative objects. & Finite simple group comparison context plus post-j coefficient stream. & MOON0/\allowbreak{}MOON3 and external Monster representation dimension table as target. & Finite comparison table only;\newline no foundation Exec source. & low & \hyperlink{phase-row-12-4}{12.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-MOON5}{MOON5} & Leech lattice comparison profile & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & Comparison-only profile for a rootless even unimodular 24-dimensional lattice target. & External Leech-lattice mathematics;\newline CNNA may only compare after deriving an internal lattice/\allowbreak{}theta-like invariant. & Derived CNNA lattice/\allowbreak{}theta candidate plus external Leech target data. & Finite Gram/\allowbreak{}basis/\allowbreak{}shell data can be represented operationally as comparison tables;\newline not a source object. & low & \hyperlink{phase-row-12-5}{12.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-MOON6}{MOON6} & Leech theta/\allowbreak{}shell coefficient comparison & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & Comparison profile for Leech theta series and shell-count/\allowbreak{}kissing-number coefficients. & Leech lattice comparison target plus derived CNNA q/\allowbreak{}theta coefficient stream. & MOON5 and CNNA-derived q/\allowbreak{}theta stream. & Coefficient comparison is computable once both streams are represented;\newline no oracle in derivation. & low & \hyperlink{phase-row-12-6}{12.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-MOON7}{MOON7} & VOA/\allowbreak{}moonshine-module comparison profile & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & Comparison-only profile for vertex-operator-algebra/\allowbreak{}moonshine-module structures. & Post-j/\allowbreak{}Moonshine comparison horizon;\newline possible later graded algebra from B/\allowbreak{}A outputs. & CNNA-derived graded algebra/\allowbreak{}q-character output, if any, plus external VOA/\allowbreak{}moonshine-module target data. & Not an operational source;\newline finite graded truncations may be computable comparison artifacts. & low & \hyperlink{phase-row-12-7}{12.7}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-MOON8}{MOON8} & Common-indicator /\allowbreak{} Hauptmodul bridge-test profile & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & Comparison profile testing whether CNNA-derived q-characters match known Hauptmoduln or McKay-Thompson-type series. & Thread-motivated bridge-test after j/\allowbreak{}q-expansion and graded data;\newline not a prior assumption. & CNNA-derived q-character/\allowbreak{}coefficient stream and external normalized Hauptmodul target list. & Finite coefficient-prefix comparison is computable;\newline equality theorem belongs to mirror/\allowbreak{}proof layer. & low & \hyperlink{phase-row-12-8}{12.8}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG0}{LEG0} & Consumption and split inventory umbrella & Governance;\newline Policy;\newline Object & F3 & current & \cellcolor{yellow!25}Y & SplitInventoryProfile with declaration-consumption map, not a code object. & repo inventory + Arithmetic/\allowbreak{}Notation.lean audit + object register. & static module/\allowbreak{}declaration/\allowbreak{}reference summaries. & n/\allowbreak{}a: planning/\allowbreak{}refactor artifact, not mathematical computation. & active & \hyperlink{phase-row-1-1-1}{1.1.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG1}{LEG1} & Legacy single-constructor status gates & Lean;\newline Refactor;\newline Object & F3 & current & \cellcolor{yellow!25}Y & Historical single-constructor status enums retained for compatibility but quarantined outside the neutral public surface. & Existing historical declarations in Arithmetic/\allowbreak{}Notation.lean. & frozen SM9h legacy status declarations;\newline no new semantics. & n/\allowbreak{}a: legacy gate/\allowbreak{}status declarations. & near & \hyperlink{phase-row-1-1-2}{1.1.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG2}{LEG2} & CoreSymbols true notation surface & Lean;\newline Refactor;\newline Object & F3 & current & \cellcolor{yellow!25}Y & Minimal notation/\allowbreak{}core-symbol module containing only actual notation/\allowbreak{}syntax/\allowbreak{}domain-role symbols needed by later neutral APIs. & Declarations classified as true notation/\allowbreak{}core symbols by LEG0. & Notation split inventory. & n/\allowbreak{}a: syntax/\allowbreak{}API surface. & near & \hyperlink{phase-row-1-1-3}{1.1.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG3}{LEG3} & Legacy phase aliases compatibility surface & Lean;\newline Refactor;\newline Object & F3 & current & \cellcolor{yellow!25}Y & Historical phase-semantic aliases and old names are retained behind a legacy module, not exposed as new public API. & Existing SM*/\allowbreak{}S6*/\allowbreak{}R*/\allowbreak{}Audit naming surface. & Notation split inventory and frozen historical modules. & n/\allowbreak{}a: compatibility surface. & near & \hyperlink{phase-row-1-1-4}{1.1.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG4}{LEG4} & Neutral import firewall for post-notation phases & Governance;\newline Policy;\newline Object & F3 & current & \cellcolor{yellow!25}Y & Audit rule and generated module inventory check that Phase 3+ imports neutral/\allowbreak{}CoreSymbols surfaces and not Legacy.StatusGates. & Generated module inventory after the split. & Lean import graph and phase-object DAG. & n/\allowbreak{}a: import governance artifact. & near & \hyperlink{phase-row-1-1-5}{1.1.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG5}{LEG5} & Declaration consumption classification map & Governance;\newline Policy;\newline Object & F3 & current & \cellcolor{green!18}G & ConsumptionClassificationMap with classes core-computational, proof-bridge, public-wrapper, legacy-status, legacy-policy, phase-alias, audit-only, blue-semantic-correction, dead-candidate, final-output. & Static module graph + symbol/\allowbreak{}declaration reference summary + direct code audit. & repo\_inventory/\allowbreak{}raw\_export, repo\_snapshot Lean source, object register, LEG10 module manifest, LEG11 reuse/\allowbreak{}duplication ledger. & not applicable;\newline planning/\allowbreak{}audit layer only & critical & \hyperlink{phase-row-1-1-1-1-4}{1.1.1.1.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG7}{LEG7} & Blue-object semantic correction ledger & Governance;\newline Policy;\newline Object & F3 & current & \cellcolor{yellow!25}Y & BlueCorrectionLedger mapping each Object status B record to semantic defect, allowed temporary consumers, forbidden public consumers, neutral target API, and exit-to-white condition. & Object register B rows + consumption classification + TomS/\allowbreak{}source guardrails where applicable. & CD/\allowbreak{}S/\allowbreak{}O blue object rows and their current code derivation sites. & not applicable;\newline planning/\allowbreak{}audit layer only & critical & \hyperlink{phase-row-1-1-1-2}{1.1.1.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG6}{LEG6} & Public API contract and consumer whitelist & Governance;\newline Policy;\newline Object & F3 & current & \cellcolor{yellow!25}Y & PublicAPIContract listing allowed neutral modules/\allowbreak{}declarations and forbidden imports for Phase 3+ and later handoffs. & Consumption map + blue correction ledger + access policy. & LEG5, LEG7, object access register, phase dependency table. & not applicable;\newline planning/\allowbreak{}audit layer only & critical & \hyperlink{phase-row-1-1-1-3}{1.1.1.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG8}{LEG8} & Pruning and dead-candidate ledger & Governance;\newline Policy;\newline Object & F3 & current & \cellcolor{yellow!25}Y & PruningLedger classifying declarations/\allowbreak{}modules as keep, quarantine, wrap, reexport, archive, or deletion-candidate. & Consumption map + public API contract + reference summaries. & LEG5, LEG6, symbol reference summaries, import graph. & not applicable;\newline planning/\allowbreak{}audit layer only & critical & \hyperlink{phase-row-1-1-1-4}{1.1.1.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG9}{LEG9} & Generated-view authority and implementation-lock contract & Governance;\newline Policy;\newline Object & F3 & current & \cellcolor{yellow!25}Y & GeneratedViewAuthorityLock tying YAML master, generated tables/\allowbreak{}PDF, and local-build evidence rule to the next implementation prompt. & Single-YAML rule + generated table validation + PDF render check. & 1.1.1.1-1.1.1.4 records and generate\_tables.py output. & not applicable;\newline planning/\allowbreak{}audit layer only & critical & \hyperlink{phase-row-1-1-1-5}{1.1.1.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG10}{LEG10} & Implementation module manifest and semantic placement contract & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{green!18}G & ModuleImplementationManifest: for each implementation phase, record exact proposed added modules, modified modules, module budget, semantic placement rationale, existing-module fit check, public/\allowbreak{}legacy role, import direction, expected consumers, phase type, regression protocol, version impact, concrete-instance traversal, generic test placement, mathlib/\allowbreak{}noncomputable risk, and rejection reason for alternative placements. & Generated module inventory + phase/\allowbreak{}object DAG + active scratchpad + frozen Lean source snapshot. & repo\_inventory/\allowbreak{}raw\_export/\allowbreak{}modules.json, import graph, object register, current phase target objects, implementation scratchpad fields, and existing module semantics. & not applicable;\newline planning/\allowbreak{}audit layer only & critical & \hyperlink{phase-row-1-1-1-1-1}{1.1.1.1.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG11}{LEG11} & Reuse/\allowbreak{}duplication ledger and canonical generator policy & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{green!18}G & ReuseDuplicationLedger plus CanonicalGeneratorPolicy: no second implementation of an already available semantic operation;\newline generator-like request/\allowbreak{}output, smoke-test, extraction, and ledger code must reuse or extend the canonical theory/\allowbreak{}smoke-test generator seam. & Existing Smoke/\allowbreak{}Test generator chain, static symbol/\allowbreak{}reference summaries, and current phase target semantics. & LEG10, repo\_inventory/\allowbreak{}raw\_export/\allowbreak{}symbol\_reference\_summary.json, existing Smoke/\allowbreak{}Test generator modules, and planned target objects. & not applicable;\newline planning/\allowbreak{}audit layer only & critical & \hyperlink{phase-row-1-1-1-1-2}{1.1.1.1.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG12}{LEG12} & Object and size proof-documentation infrastructure & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{green!18}G & Generated proofbook infrastructure that links each registered object/\allowbreak{}size to a dossier containing source objects, definitions, proof target, proof sketch, and verification/\allowbreak{}audit status. & Object register + code derivation sites + blue-object correction requirements + generated single-master views. & registered object IDs, phase IDs, derivation-site fields, proof-documentation status fields. & No ExecComplex computation;\newline documentation governance only. ExecComplex objects must document operational/\allowbreak{}mirror boundary in their own dossier. & high & \hyperlink{phase-row-1-1-1-1-3}{1.1.1.1.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG13}{LEG13} & Global no-go guardrail contract & Governance;\newline Policy;\newline Object & F0 & current & \cellcolor{green!18}G & GlobalNoGoGuardrailContract: top-level invariant list for operational path, mirror isolation, inverse derivations, formula provenance, backjump discipline, positive-path ordering, public API naming, structural proof strategy, legacy quarantine, Phase 3+ import firewall, and YAML-only roadmap authority. & Prior Lean implementation failure modes, user-specified global constraints, legacy quarantine requirement, and single-YAML planning architecture. & global\_no\_go\_guardrails YAML section, workflow\_policy inheritance rule, and per-phase global\_no\_go\_inheritance scratchpad field. & No ExecComplex computation;\newline governance-only invariant. Operational ExecComplex phases must still inherit the listed constraints. & critical & \hyperlink{phase-row-1-1-1-1-0}{1.1.1.1.0}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG14}{LEG14} & Concrete computable instance traversal contract & Governance;\newline Policy;\newline Object & F3 & current & \cellcolor{green!18}G & Global scratchpad contract requiring every operational computable phase to traverse the path with a concrete finite instance or to declare itself infrastructure-only. & Observed risk that computable code can become a proof-shaped skeleton without executable instance pressure. & active phase target declarations;\newline existing generator route;\newline concrete finite substrate/\allowbreak{}window;\newline expected executable output witness. & Directly governs the operational computable path;\newline not a mathematical input. & critical & \hyperlink{phase-row-1-1-1-1-0-1}{1.1.1.1.0.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG15}{LEG15} & Mathlib complication and noncomputable-boundary log & Governance;\newline Policy;\newline Object & F3 & current & \cellcolor{green!18}G & Per-phase scratchpad log for mathlib import availability, noncomputable leaks, executable-code barriers, mirror-layer isolation, and required natural backjump/\allowbreak{}refactor layer. & Prior Lean phases encountered mathlib APIs whose algebraic interfaces compile only noncomputably;\newline operational CNNA must record and isolate these complications. & expected\_mathlib\_imports;\newline observed compiler/\allowbreak{}noncomputable errors;\newline operational vs mirror-layer classification;\newline mitigation decision. & Protects the operational path from hidden noncomputable dependencies;\newline mirror-only usage must be isolated and documented. & critical & \hyperlink{phase-row-1-1-1-1-0-1}{1.1.1.1.0.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG16}{LEG16} & Semi-automated existing-code documentation coverage & Reference;\newline Gate;\newline Object & F3 & current & \cellcolor{black!18}K & A generated coverage/\allowbreak{}documentation ledger tying Lean modules/\allowbreak{}declarations to object proof dossiers, consumers, and provenance classifications. & repo\_inventory/\allowbreak{}raw\_export plus object register, proof dossiers, and declaration consumption classification. & modules.json, import\_edges.json, symbol\_reference\_summary.json, object\_proof\_dossiers, implementation\_scratchpad. & Non-operational documentation metadata;\newline may reference executable witnesses but does not execute them. & secondary-long-term & \hyperlink{phase-row-19-1}{19.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG17}{LEG17} & Derivation-graph geometry diagnostics & Reference;\newline Gate;\newline Object & F3 & current & \cellcolor{black!18}K & A non-operational diagnostic profile for the repository derivation graph: import edges, dominators, layers, source-sink paths, bottlenecks, cuts, and discipline clusters. & Generated Lean module inventory and graph exports. & import\_edges.json, dominator/\allowbreak{}layer/\allowbreak{}path summaries, module\_group\_dependency\_graph, core\_robust\_semantic\_mainline. & Graph-metadata computation only;\newline not part of CNNA operational mathematics. & secondary-long-term & \hyperlink{phase-row-19-2}{19.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG18}{LEG18} & Open-system emergence-path forensics & Reference;\newline Gate;\newline Object & F3 & current & \cellcolor{black!18}K & A diagnostic map locating formal proof/\allowbreak{}module paths from regime/\allowbreak{}complement/\allowbreak{}boundary data toward effective open-system dynamics consumers. & Checked A regime/\allowbreak{}complement, DtN/\allowbreak{}Schur, A->C, and C/\allowbreak{}OQS derivation paths plus graph analysis. & future checked object dossiers and source-sink/\allowbreak{}dominator path analysis over relevant modules. & Non-operational path forensics. It may point to executable witnesses but does not generate OQS behavior. & secondary-long-term & \hyperlink{phase-row-19-3}{19.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG19}{LEG19} & Reflective CNNA/\allowbreak{}formalization graph comparison boundary & Reference;\newline Gate;\newline Object & F3 & current & \cellcolor{black!18}K & A boundary object marking any comparison between CNNA object-structure and the formalization graph as meta-level, observational, and non-generative. & Stable CNNA object proof dossiers plus generated graph metrics. & core object dossiers, discipline subgraphs, graph cuts, layers, signal paths, and cluster analysis after stabilization. & Non-operational meta-comparison only. & secondary-long-term & \hyperlink{phase-row-19-4}{19.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG20}{LEG20} & EXEC-2 rational ExecComplex boundary policy & Lean;\newline Governance;\newline Object & F1 & current & \cellcolor{green!18}G & ExecComplexRationalBoundaryPolicy Superseded/\allowbreak{}refined by LEG31/\allowbreak{}EXEC-3 for exact quadratic candidate policy. & Review of ExecComplex = Q x Q and later algebraic CM/\allowbreak{}lattice requirements & O00/\allowbreak{}O01/\allowbreak{}O06 plus L00/\allowbreak{}L02/\allowbreak{}L04/\allowbreak{}M05/\allowbreak{}SP0 boundary risks & Governance object;\newline forces rational/\allowbreak{}integer operational return only, mirror-only algebraic irrational data & high & \hyperlink{phase-row-1-1-1-1-0-2}{1.1.1.1.0.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG21}{LEG21} & Refactor regression and incremental migration protocol & Lean;\newline Governance;\newline Object & F1 & current & \cellcolor{green!18}G & RefactorRegressionProtocol & Notation split and legacy-quarantine risk audit & module manifest, consumer list, import graph delta, local build evidence & Infrastructure-only;\newline no operational witness, but requires build-regression evidence for refactor code packages & high & \hyperlink{phase-row-1-1-1-1-0-3}{1.1.1.1.0.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG22}{LEG22} & Lean/\allowbreak{}mathlib version migration policy & Lean;\newline Governance;\newline Object & F1 & current & \cellcolor{green!18}G & LeanMathlibVersionPolicy & Frozen baseline plus future mathlib/\allowbreak{}API pressure & Lean 4.28.0/\allowbreak{}mathlib snapshot and explicit upgrade gate decisions & Infrastructure-only;\newline blocks silent noncomputable/\allowbreak{}classical/\allowbreak{}import drift into operational code & high & \hyperlink{phase-row-1-1-1-1-0-4}{1.1.1.1.0.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG23}{LEG23} & Phase-type-specific scratchpad schema and governance retrospective & Documentation;\newline Object & F3 & current & \cellcolor{green!18}G & PhaseTypeScratchpadPolicy & Review that refactor, derivation, infrastructure and comparison phases need different evidence & phase\_type, type-specific contract, governance\_overhead\_review & Infrastructure-only;\newline prevents proof-rehearsal ballast in pure refactor phases and missing migration metrics & high & \hyperlink{phase-row-1-1-1-1-0-5}{1.1.1.1.0.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG24}{LEG24} & Phase 3 to Phase 4 consumer-contract direction & Lean;\newline Governance;\newline Object & F1 & current & \cellcolor{green!18}G & Phase3ToPhase4ConsumerContract & GEN-1 generator policy and Schur/\allowbreak{}DtN -> Exec arithmetic dependency direction & Phase 3.6 BoundaryOperatorProfile and Phase 4.1 ExecBoundaryMatrix & Infrastructure-only;\newline records import direction and avoids duplicate Schur/\allowbreak{}generator logic & high & \hyperlink{phase-row-1-1-1-1-0-6}{1.1.1.1.0.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG25}{LEG25} & IdealThread/\allowbreak{}CutSpec.full extremal-route contract & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{white}W & Planning contract separating the singleton IdealThread route from the maximal CutSpec.full route and marking string-like interpretation as comparison-only. & Code-checked IdealThread and CutSpec.full definitions plus ExistingIdealThreadNoGo and FullBoundaryAudit. & SubstrateClass.InfiniteThread;\newline ToC.IdealThread.carrier/\allowbreak{}family/\allowbreak{}coarsen;\newline Finite.CutSpec.full;\newline boundary-source audits. & No operational scalar introduced. Constrains later operational uses of scalar/\allowbreak{}thread versus full-boundary paths. & high & \hyperlink{phase-row-1-1-1-1-0-7}{1.1.1.1.0.7}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-S07}{S07} & IdealThread singleton directed-family profile & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{green!18}G & Neutral profile of an IdealThread U with carrier(L) = \{U.cell L\}, its DirectedFamily embedding, rootedness, forward property, and deterministic coarsen fixed-point behavior. & InfiniteThread + IdealThread.carrier + IdealThread.family in ToC.Contract. & SubstrateClass, InfiniteThread, IdealThread definitions;\newline DeterministicSubstrateClass for coarsen fixed-point theorem. & Pure structural finite-set profile;\newline no ExecComplex arithmetic. Concrete instance traversal must use reference/\allowbreak{}variation thread carriers and show singleton cardinality at finite levels. & high & \hyperlink{phase-row-1-2-7}{1.2.7}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-S08}{S08} & CutSpec.full maximal-carrier profile & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{green!18}G & Neutral profile of CutSpec.full T where carrier(L) = T.carrier L;\newline represents the maximal finite cut/\allowbreak{}full-region route. & Finite.CutSpec.full and full\_carrier theorem. & TruncatedFamily carrier and CutSpec carrier\_subset proof. & Pure finite-set/\allowbreak{}cut profile;\newline later matrix/\allowbreak{}operator computations consume the resulting full boundary/\allowbreak{}region data, not IdealThread singleton data. & high & \hyperlink{phase-row-1-2-8}{1.2.8}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR06}{BR06} & Boundary-route extrema contract & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{green!18}G & Contract separating full-boundary matrix geometry from IdealThread scalar/\allowbreak{}singleton collapse before Schur/\allowbreak{}DtN neutral wrappers. & S07 + S08 + ExistingIdealThreadNoGo + FullBoundaryAudit. & IdealThread singleton profile, CutSpec.full profile, boundary ports subset/\allowbreak{}carrier facts, and planned BoundaryOperatorProfile consumers. & Constrains later ExecComplex matrices: nontrivial boundary matrices must come from full/\allowbreak{}generated boundary route;\newline thread route may only supply scalar audits unless lifted by theorem. & high & \hyperlink{phase-row-3-0}{3.0}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR07}{BR07} & Thread-recursion arithmetic-shadow audit profile & Lean;\newline Source;\newline Object & F1 & current & \cellcolor{yellow!25}Y & Audit profile determining whether scalar Schur/\allowbreak{}Mobius recurrence data is sourced from IdealThread singleton carriers, full-boundary diagonal entries, or another generated boundary source. & RecursiveSchurSource, MobiusTransfer, CharpolyExec, operational discriminant chain, plus S07/\allowbreak{}BR06 route separation. & Code references to recurrence source fields, boundaryMatrixAt diagonal entries, transfer parameters, and discriminant outputs. & Operational only after concrete finite instance traversal proves the recurrence path and executable witness;\newline otherwise mirror/\allowbreak{}comparison-only. & high & \hyperlink{phase-row-4-0}{4.0}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR09}{BR09} & Subsystem-induced invariant bifurcation profile & Lean;\newline Target;\newline Object & F1 & current & \cellcolor{black!18}K & SubsystemSchurInvariantBifurcationProfile: cutting the infinite substrate creates boundary/\allowbreak{}interior data whose Schur complements expose horizontal algebraic invariants and vertical arithmetic invariants as two audited output families, without treating the slogan as proof. & Finite CutSpec/\allowbreak{}subsystem boundary plus multiscale Schur decomposition. & BR08 plus route-specific invariant records CD7/\allowbreak{}O05/\allowbreak{}TM0/\allowbreak{}S05. & Diagnostic/\allowbreak{}profile layer;\newline operational witnesses must be concrete finite cuts and scalar recursion examples. & low & \hyperlink{phase-row-10-4-1}{10.4.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR08}{BR08} & Horizontal/\allowbreak{}vertical Schur-duality bridge & Lean;\newline Target;\newline Object & F1 & current & \cellcolor{black!18}K & SchurHorizontalVerticalDualityProfile: horizontal sector Schur elimination and vertical level-recursion Schur elimination are compatible factorizations/\allowbreak{}aspects of one multiscale Schur decomposition of the derived Dirichlet-Laplacian, with explicit commutation/\allowbreak{}naturality conditions. & Derived DtN boundary operator, sector decomposition, IdealThread/\allowbreak{}CutSpec route split, transfermatrix recursion, and CD/\allowbreak{}Hurwitz profile. & S05, BR06, BR07, S07, S08, TM0, TM1, TM2, CD7, O05. & Bridge theorem may use finite operational witnesses;\newline no algebraic irrationality is admitted except through EXEC-2 allowed mirror/\allowbreak{}invariant boundaries. & medium & \hyperlink{phase-row-10-4-1}{10.4.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG26}{LEG26} & Reflective thread/\allowbreak{}full-boundary analogy diagnostic boundary & Governance;\newline Policy;\newline Object & F4 & current & \cellcolor{black!18}K & Boundary object ensuring thread/\allowbreak{}full-boundary and string-like analogies remain documentation/\allowbreak{}diagnostic comparisons until formal CNNA objects and proofs are closed. & LEG25, LT5, repository derivation graph metadata, later S07/\allowbreak{}S08/\allowbreak{}BR06/\allowbreak{}BR07 dossiers. & Closed proof dossiers and generated derivation-graph metadata only after not-before gates. & None. Diagnostic/\allowbreak{}meta-documentation only;\newline never an operational input. & low & \hyperlink{phase-row-19-5}{19.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG27}{LEG27} & Horizontal/\allowbreak{}vertical Schur-duality dependency-order lock & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{green!18}G & SchurDualityOrderLock: horizontal-sector Schur and vertical-level Schur may be compared only after their source routes are derived and exported. & Review insight plus existing route plan S07/\allowbreak{}S08/\allowbreak{}BR06/\allowbreak{}BR07/\allowbreak{}CD7/\allowbreak{}O05/\allowbreak{}TM0. & Planning master and dependency order. & No operational computation;\newline constrains future bridge phases. & high & \hyperlink{phase-row-1-1-1-1-0-8}{1.1.1.1.0.8}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG28}{LEG28} & Heuristic Eisenstein/\allowbreak{}Gauss lattice test-matrix boundary contract & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{green!18}G & A global planning contract saying that post-97 b-ary-tree spiral constructions are test and comparison targets, not generator definitions. & TomS-thread post \#97 audit plus EXEC-2 rational boundary and canonical generator policy. & post-97 source notes, code-defined branching policy, L\_max sweep requirement, CM/\allowbreak{}j target boundary. & Operational path records rational/\allowbreak{}integer finite invariants only;\newline irrational coordinates, tau, sqrt(D), and analytic j evaluation remain mirror/\allowbreak{}comparison. & high & \hyperlink{phase-row-1-1-1-1-0-9}{1.1.1.1.0.9}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG29}{LEG29} & General early finite computation test-matrix contract & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{green!18}G & Global contract requiring early, general finite test matrices for operational computable paths;\newline special Eisenstein/\allowbreak{}Gauss rows are sentinel rows only. & Concrete computable instance traversal contract;\newline v32 heuristic lattice test matrix;\newline user requirement for early non-specialized theory testing. & phase manifest, canonical generator policy, finite code-defined inputs, expected executable witness schema, sentinel-row separation. & Operational rows may contain only finite/\allowbreak{}rational/\allowbreak{}integer fields;\newline mirror-only columns hold tau, sqrt(D), analytic j, or geometric coordinates. & immediate governance before code implementation & \hyperlink{phase-row-1-1-1-1-0-10}{1.1.1.1.0.10}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-L09}{L09} & Static branching Eisenstein/\allowbreak{}Gauss lattice test matrix & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{yellow!25}Y & Static-branching sentinel extension of the general finite computation test matrix, including Eisenstein/\allowbreak{}Gauss rows as special comparisons rather than the full test harness. v34 further requires that its Eisenstein/\allowbreak{}Gauss rows be tagged as noOuter-root sentinel candidates, not as universal Heegner representatives. & Consumes canonical generator/\allowbreak{}branching profile, L06 angle/\allowbreak{}cosine profile, L04 tau target, O05 discriminant target, and M05 j target after those are available. & O07 generic test matrix profile, code-defined b, L\_max, finite addresses, selected angle profile, rational cos(theta), closure-depth witness, target D and j comparison row., derived regime tag from O08 & Computable part: b, finite address counts/\allowbreak{}relations, rational cos(theta), rational/\allowbreak{}integer Gram/\allowbreak{}determinant surrogates, D target. Mirror-only: complex coordinates, tau, analytic j. & high & \hyperlink{phase-row-8-5}{8.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-L10}{L10} & Dynamic branching and L\_max lattice test sweep & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{yellow!25}Y & Dynamic-branching extension of the general finite computation test matrix over code-defined branch families and L\_max values. & Consumes generated branch-family route and the static L09 matrix. & O07 generic test matrix profile, canonical generator outputs, branch policy at each level, finite address sets, selected angle/\allowbreak{}sentinel profiles, closure/\allowbreak{}collision finite relations. & Operational outputs are finite relations and rational/\allowbreak{}integer invariants;\newline mirror outputs remain separated. & high & \hyperlink{phase-row-8-6}{8.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-M08}{M08} & Eisenstein/\allowbreak{}Gauss CM and j special-value test targets & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{yellow!25}Y & Comparison target row linking Eisenstein rho to D=-3 and j=0, and Gauss i to D=-4 and j=1728, used only as sentinel columns after generic coverage exists. In v34 these are noOuter-root sentinel targets only if the row carries derived noOuter provenance. & Consumes L04 tau, O05 D, M05 j-invariant;\newline supported as established special-value targets but not operationally evaluated in ExecComplex. v37: retained in modular/\allowbreak{}CM Path A. & CM-target records and mirror/\allowbreak{}comparison layer;\newline not from geometric drawing input.;\newline exact quadratic coordinates only through O09/\allowbreak{}O10/\allowbreak{}BR14 when required & j target values 0 and 1728 are integer comparison targets;\newline analytic j evaluation and tau live outside operational ExecComplex. Derived-quadratic update: no free sqrt(D);\newline exact coordinates require proof-carrying D-source. & high & \hyperlink{phase-row-8-5}{8.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR10}{BR10} & Hierarchical versus spiral embedding collision and closure audit & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{yellow!25}Y & Audit profile separating angle-invariant hierarchical address overlays from angle-dependent spiral embedding closure/\allowbreak{}collision behavior. & Consumes finite address structure, code-defined branching, L09/\allowbreak{}L10 test rows, and post-97 heuristic source notes. & O07 generic rows plus finite address words, level L\_max, embedding-kind tag, angle profile, finite collision/\allowbreak{}closure relation witnesses. & Finite address/\allowbreak{}collision relations are operationally computable;\newline geometric coordinates remain mirror-only unless encoded by rational surrogates. & medium & \hyperlink{phase-row-8-6}{8.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG30}{LEG30} & Regime-typed early test-matrix contract & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{green!18}G & Global contract requiring early finite test rows to carry a derived regime tag: generic, noOuter-root/\allowbreak{}closed candidate, or HasOuter/\allowbreak{}complement-projection/\allowbreak{}comparison. h(D)=1 or Heegner-list membership is never itself noOuter evidence. & v33 O07 general test matrix;\newline noOuter/\allowbreak{}HasOuter regime discipline;\newline IDEAL\_infty projection/\allowbreak{}complement-family interpretation;\newline post \#97 Eisenstein/\allowbreak{}Gauss sentinel hypothesis. & planning decision locks, regime split objects, O07 row schema, EXEC-2 boundary, external Heegner/\allowbreak{}class-number-one information as comparison-only source material. & Operational rows remain finite/\allowbreak{}rational/\allowbreak{}integer and carry regime tags;\newline mirror/\allowbreak{}comparison columns may mention tau, sqrt(D), j, CM or Heegner labels. & immediate governance before code implementation & \hyperlink{phase-row-1-1-1-1-0-11}{1.1.1.1.0.11}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-O08}{O08} & Regime-typed finite computation test matrix profile & Lean;\newline Target;\newline Object & F2 & current & \cellcolor{yellow!25}Y & Extension of O07 whose rows include branch mode, L\_max, executable witness, and a derived regime tag separating noOuter-root closed candidates from HasOuter/\allowbreak{}complement-projection/\allowbreak{}comparison cases. & O07 generic finite computation test matrix plus noOuter/\allowbreak{}HasOuter regime split and concrete computable instance traversal. & canonical generator outputs, finite L\_max rows, static/\allowbreak{}dynamic branch-mode tags, regime split witness, rational/\allowbreak{}integer operational outputs, optional mirror comparison targets. & Core row fields are operational finite/\allowbreak{}rational/\allowbreak{}integer;\newline tau, sqrt(D), analytic j, and general algebraic coordinates remain mirror-only. & early before specialized computation claims & \hyperlink{phase-row-4-0-2}{4.0.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-N18}{N18} & Heegner regime-projection classification profile & Lean;\newline Target;\newline Object & F1 & current & \cellcolor{yellow!25}Y & Consumer-only profile classifying class-number-one/\allowbreak{}Heegner and order-discriminant targets by derived CNNA regime: closed noOuter-root sentinel candidate versus HasOuter/\allowbreak{}complement-family projection/\allowbreak{}comparison. & ClassNumberProfile, HeegnerIndicatorProfile, O08 regime-typed test matrix, IDEAL\_infty projection discipline. & h(D), discriminant/\allowbreak{}order data, units/\allowbreak{}class group evidence, derived regime tag, complement-family/\allowbreak{}projection metadata. External Heegner lists are comparison checks, not sources. & Integer/\allowbreak{}rational invariants such as D and h(D) may be operational after derivation;\newline tau/\allowbreak{}j/\allowbreak{}CM analytic interpretation remains mirror/\allowbreak{}comparison. & medium/\allowbreak{}high before Heegner interpretations are used & \hyperlink{phase-row-7-2-1}{7.2.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR11}{BR11} & IDEAL\_infty projection and complement-family Heegner boundary & Lean;\newline Target;\newline Object & F1 & current & \cellcolor{yellow!25}Y & Boundary statement that additional Heegner/\allowbreak{}class-number-one phenomena beyond noOuter-root sentinels, if they appear, are interpreted first as projections/\allowbreak{}approximations of IDEAL\_infty through complement-family/\allowbreak{}regime choices, not as multiple closed roots. & IDEAL\_infty projection discipline, complement-family architecture, noOuter/\allowbreak{}HasOuter split, N18 classification. & formal regime data, complement-family metadata, finite approximant rows, class-number-one comparison rows. & No direct computation;\newline consumes operational finite rows and rational/\allowbreak{}integer invariants;\newline mirror-only CM labels remain separated. & medium & \hyperlink{phase-row-7-2-1}{7.2.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR12}{BR12} & noOuter REAL-root Eisenstein/\allowbreak{}Gauss sentinel hypothesis & Lean;\newline Target;\newline Object & F1 & current & \cellcolor{yellow!25}Y & Hypothesis/\allowbreak{}test profile that Eisenstein D=-3/\allowbreak{}j=0 and Gauss D=-4/\allowbreak{}j=1728 are the likely sentinel cases for the closed noOuter/\allowbreak{}empty-set REAL approximant, not a blanket statement about all Heegner targets. & post \#97 angle/\allowbreak{}closure heuristic;\newline noOuter REAL-root regime discipline;\newline O08 regime-typed test matrix;\newline EXEC-2. & derived noOuter-root finite rows, closure-depth witness, rational angle/\allowbreak{}cosine sentinel data, later O05/\allowbreak{}M08 comparison targets. & Operational row uses finite/\allowbreak{}rational/\allowbreak{}integer witnesses and target integers;\newline tau and analytic j remain mirror-only. & high as early sentinel hypothesis & \hyperlink{phase-row-4-0-2}{4.0.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG31}{LEG31} & Computable scalar architecture contract & Governance;\newline Policy;\newline Object & F0 & current & \cellcolor{green!18}G & ScalarArchitectureContract: ExecComplex is the rational operational floor;\newline exact quadratic algebraic scalar data require a separate proof-carrying operational layer;\newline analytic Complex/\allowbreak{}Real remains mirror-only;\newline CD-derived C-layer use is blocked until noncircular bridge proof. & ExecComplex code audit, ExecComplexBridge, CD bridge no-identification status, mathlib Complex/\allowbreak{}QuadraticAlgebra docs & O00, LEG20, LEG22, current code import boundaries, mathlib docs & Governance object protecting executable path;\newline no direct computation. & critical & \hyperlink{phase-row-1-1-1-1-0-12}{1.1.1.1.0.12}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG32}{LEG32} & Derived-only exact quadratic provenance contract & Governance;\newline Policy;\newline Object & F0 & current & \cellcolor{green!18}G & Contract that the exact quadratic layer is a canonical algebra generated from a previously derived discriminant parameter D, not a free sqrt(D), axiom, analytic Complex object, or Cayley-Dickson early scalar source. & User-derived-only objection to introducing sqrt(D);\newline scalar architecture review;\newline mathlib QuadraticAlgebra/\allowbreak{}AdjoinRoot reference models for adjoining generators by relations. & LEG31, O00, O05/\allowbreak{}O06 discriminant-source plan, mathlib reference docs, CD9 noncircularity constraint & Protects operational computability: exact quadratic coordinates are generated only from proof-carrying D and project/\allowbreak{}rationalize invariants back to QxQ/\allowbreak{}Int where allowed. & critical & \hyperlink{phase-row-1-1-1-1-0-13}{1.1.1.1.0.13}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG33}{LEG33} & Phase 5-10 bifurcation and dependency repair contract & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{green!18}G & PhasePathBifurcationContract. & v36 phase/\allowbreak{}object audit found artificial dependency of SP/\allowbreak{}P objects on modular-form Phase 8/\allowbreak{}9;\newline v37 records corrected path split. & Phase/\allowbreak{}object register;\newline dependency audit;\newline Phase 4.1 consumer requirements. & planning-only;\newline no operational scalar content. & high & \hyperlink{phase-row-1-1-1-1-0-14}{1.1.1.1.0.14}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-O09}{O09} & Required exact quadratic operational scalar schema & Lean;\newline Target;\newline Object & F1 & current & \cellcolor{yellow!25}Y & Required minimal discriminant-indexed schema for elements a + b*theta with theta\textasciicircum{}2 = D over Q, where D is only a parameter at schema level and must later come from a proof-carrying operational discriminant ledger before instantiation. & CM/\allowbreak{}lattice coordinates require algebraic quadratic data, but derived-only discipline forbids free sqrt(D);\newline the schema is the canonical algebraic wrapper over a later D-source. & LEG31, LEG32, O00;\newline concrete instantiations require O05/\allowbreak{}O06 via O10/\allowbreak{}BR14 & Executable coordinate arithmetic over Q if implemented directly/\allowbreak{}wrapped safely;\newline not a replacement for general Complex and not instantiated without D-source. & critical & \hyperlink{phase-row-1-2-1-2}{1.2.1.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-O10}{O10} & Proof-carrying discriminant-indexed quadratic scalar instance & Lean;\newline Target;\newline Object & F1 & current & \cellcolor{yellow!25}Y & An instantiation of the exact quadratic scalar schema from a ledger-proved D : Int, producing theta with theta\textasciicircum{}2 = D and coordinate elements a + b theta only after D has been derived operationally. & O09 schema cannot be instantiated freely;\newline it must consume O05/\allowbreak{}O06 or equivalent operational discriminant certificate. & O05/\allowbreak{}O06 proof-carrying discriminant ledger, O09 schema, LEG32 & Coordinates are exact rational pairs tagged by D;\newline projected trace/\allowbreak{}norm/\allowbreak{}discriminant/\allowbreak{}integer invariants may flow to ExecComplex-compatible reports. No analytic sqrt or Complex coordinate is required. & critical & \hyperlink{phase-row-4-5-1}{4.5.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR13}{BR13} & ExecComplex to exact-quadratic projection bridge & Lean;\newline Target;\newline Object & F1 & current & \cellcolor{yellow!25}Y & Bridge that relates rational ExecComplex outputs, exact quadratic scalar rows, D-source instantiations, and integer/\allowbreak{}rational invariants without allowing quadratic coordinates to replace generator semantics or appear without provenance. & Operational finite tests need exact algebraic sentinels while preserving QxQ boundary. & O00, O09, O10, BR14, O07, O08, LEG31/\allowbreak{}LEG32 & Operational bridge only for rational/\allowbreak{}integer invariants and exact quadratic arithmetic if O09 exists;\newline analytic Complex remains mirror-only. & high & \hyperlink{phase-row-4-0-3}{4.0.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-BR14}{BR14} & Discriminant-source to exact-quadratic algebra instantiation bridge & Lean;\newline Target;\newline Object & F1 & current & \cellcolor{yellow!25}Y & Bridge proving that an exact quadratic scalar instance is generated from a proof-carrying operational discriminant D and that all exported invariants are projections from this instance, not independent formulas. & Derived-only scalar provenance requirement: theta is generated by the relation theta\textasciicircum{}2 = D after D is computed. & O05/\allowbreak{}O06, O09, O10, LEG32 & Exports only rational/\allowbreak{}integer invariants to QxQ path;\newline keeps quadratic coordinates in the exact quadratic layer. & critical & \hyperlink{phase-row-4-5-1}{4.5.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CD9}{CD9} & Cayley-Dickson C-layer noncircularity audit & Reference;\newline Gate;\newline Object & F1 & current & \cellcolor{black!18}K & Late audit asking whether a CD-generated complex scalar surface can be compared to or bridge O09/\allowbreak{}O10 without consuming ExecComplex, analytic Complex, free sqrt(D), or later arithmetic data circularly. & User question about deriving C through Cayley-Dickson and avoiding ExecComplex circularity. & CD7, CD8, BR08, BR09, O09/\allowbreak{}O10, current ArithmeticCDBridge no-identification ledger & Not operational until a theorem proves noncircular scalar-surface provenance. Current code keeps CD and Exec/\allowbreak{}mirror scalar surfaces separate. & medium & \hyperlink{phase-row-10-4-3}{10.4.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG34}{LEG34} & Phase-object-link policy contract & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{green!18}G & Global planning contract classifying every phase-object relation as direct ownership, scope-only umbrella, no-direct-object audit/\allowbreak{}baseline/\allowbreak{}closeout, or moved placeholder. & v37 linked-object ambiguity: generator showed blank cells whenever no object had Phase equal to the phase id, even if child phases owned objects or the phase was a valid audit/\allowbreak{}umbrella. & phase hierarchy;\newline object register Phase field;\newline generator direct-object map;\newline child phase scopes;\newline moved/\allowbreak{}audit/\allowbreak{}closeout markers & not mathematical computation;\newline generated planning validation only & active-infrastructure & \hyperlink{phase-row-1-1-1-1-0-15}{1.1.1.1.0.15}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG35}{LEG35} & Ontic subsystem-minimality contract & Governance;\newline Policy;\newline Object & F0 & current & \cellcolor{green!18}G & Global postulate: the only primitive ontic emergence trigger is subsystem-being, i.e. selecting a finite/\allowbreak{}local subsystem, cut or approximant inside the formal IDEAL\_infty provenance whole. All further structures are derived consequences or comparison-only readings. & User-requested ontic-minimality sharpening after regime-typed test-matrix, Schur-duality, and open-system emergence discussions: avoid importing dynamics, physics, environment, stochasticity, arithmetic or geometry as primitive assumptions. & IDEAL\_infty formal provenance whole;\newline subsystem/\allowbreak{}cut/\allowbreak{}approximant selection;\newline boundary;\newline inside/\allowbreak{}outside split;\newline complement families;\newline noOuter/\allowbreak{}HasOuter regime;\newline Schur/\allowbreak{}DtN effective operator chain & not a numerical object;\newline constrains all computable paths by requiring concrete finite subsystem traversal before derived spectra/\allowbreak{}arithmetic/\allowbreak{}physics claims & active-infrastructure & \hyperlink{phase-row-1-1-1-1-0-16}{1.1.1.1.0.16}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR0}{DBR0} & Database-ready CNNA review and documentation structure & Documentation;\newline Object & F3 & current & \cellcolor{green!18}G & A non-operational review/\allowbreak{}documentation structure that keeps the Single-YAML-Master database-ready and prepares queryable phase/\allowbreak{}object/\allowbreak{}module/\allowbreak{}handoff/\allowbreak{}theory/\allowbreak{}review representations. & User instruction plus existing Single-YAML-Master, generated views, module inventory, object register, proof dossiers, status legends, and workflow policies. & masters/\allowbreak{}cnna\_roadmap\_master.yaml;\newline generated\_exports/\allowbreak{}*.tsv;\newline repo\_inventory/\allowbreak{}raw\_export;\newline tables/\allowbreak{}*.tex;\newline figures/\allowbreak{}*.dot/\allowbreak{}pdf. & Non-operational documentation/\allowbreak{}review metadata only;\newline no ExecComplex or mathematical computation is introduced. & main-side-objective & \hyperlink{phase-row-20}{20}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR1}{DBR1} & Expert-review and no-infallibility epistemic rule & Documentation;\newline Object & F1 & current & \cellcolor{green!18}G & A global rule that Lean code is the primary truth system but not semantically infallible;\newline generated artifacts are secondary;\newline every relevant claim remains subject to discipline-specific expert review. & User instruction;\newline CNNA derived-only methodology;\newline distinction between Lean formal consistency and semantic/\allowbreak{}domain correctness;\newline GNG23-GNG24. & global\_no\_go\_guardrails GNG23-GNG24;\newline workflow\_policy DB-REVIEW;\newline status\_legend review/\allowbreak{}audit rows;\newline latest\_change\_overview V1.07. & Non-operational governance rule only;\newline no computable mathematical path. & immediate-governance & \hyperlink{phase-row-20-1}{20.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR2}{DBR2} & Database-ready YAML schema and round-trip target & Tool;\newline Infrastructure;\newline Object & F1 & current & \cellcolor{black!18}K & A future schema/\allowbreak{}export target mapping YAML phases, objects, proof dossiers, modules, handoffs, statuses, theory markings, and review states into relational or graph-friendly tables. & Single-YAML-Master schema and generated TSV/\allowbreak{}JSON/\allowbreak{}DOT exports. & cnna\_roadmap\_master.yaml;\newline generated\_exports/\allowbreak{}*.tsv;\newline repo\_inventory/\allowbreak{}raw\_export/\allowbreak{}*.json;\newline future schema audit. & Non-operational export metadata;\newline not mathematical computation. & secondary-tooling & \hyperlink{phase-row-20-2}{20.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR3}{DBR3} & Discipline-separated expert-review matrix & Documentation;\newline Object & F3 & current & \cellcolor{black!18}K & A future review matrix linking claims, objects, phases, modules, and established-theory references to required specialist disciplines and review evidence/\allowbreak{}status. & Object proof dossiers, local theory context, end-theory comparison ledger, blue/\allowbreak{}reference audit, human expert review inputs. & object\_proof\_dossiers;\newline workflow\_policy;\newline status\_legend review/\allowbreak{}audit rows;\newline future discipline review rows. & Review metadata only;\newline no operational computation. & secondary-review & \hyperlink{phase-row-20-3}{20.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR4}{DBR4} & Blue/\allowbreak{}reference-theory audit ledger & Documentation;\newline Object & F3 & current & \cellcolor{black!18}K & A future audit ledger for established-theory/\allowbreak{}reference material that may need explicit blue marking or comparison-only classification. & GNG24, local theory context versus end-theory comparison workflow, external source cross-checks, object register, proof dossiers. & status\_legend;\newline external\_source\_crosscheck;\newline consumption\_classification\_map;\newline object\_register;\newline future blue-audit rows. & Audit metadata only;\newline no operational computation. & secondary-audit & \hyperlink{phase-row-20-4}{20.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR5}{DBR5} & Interactive/\allowbreak{}online database-backed documentation views & Tool;\newline Infrastructure;\newline Object & F1 & current & \cellcolor{black!18}K & A future generated-secondary interface for querying and visualizing phases, modules, objects, DAGs, handoffs, theory markings, and review status online or interactively. & DBR2 schema/\allowbreak{}export target, DBR3 review matrix, DBR4 blue/\allowbreak{}reference audit ledger, generated exports and graph figures. & future database export;\newline generated\_exports;\newline figures;\newline tables;\newline review ledgers. & Display/\allowbreak{}query metadata only;\newline not a CNNA mathematical computation. & secondary-tooling & \hyperlink{phase-row-20-5}{20.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR6}{DBR6} & Context-filtered documentation slice generator & Generated;\newline Artifact;\newline Object & F3 & current & \cellcolor{green!18}G & A generator that creates query/\allowbreak{}profile-specific documentation packets preserving every major documentation section while emitting only rows relevant to the requested context. It consumes the Single-YAML-Master and generated TSV exports only. & DB-REVIEW side objective;\newline user requirement for targeted documentation such as DtN matrix documentation and phase-closeout change documentation;\newline generated-secondary/\allowbreak{}Lean-primary rule. & masters/\allowbreak{}cnna\_roadmap\_master.yaml;\newline generated\_exports/\allowbreak{}*.tsv;\newline context\_documentation\_profiles;\newline scripts/\allowbreak{}generate\_context\_doc.py. & Python tooling path only;\newline not an operational CNNA mathematical computation and not a Lean theorem. & active-tooling & \hyperlink{phase-row-20-6}{20.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR7}{DBR7} & Stats front section and tool-interface documentation layer & Generated;\newline Artifact;\newline Object & F3 & current & \cellcolor{green!18}G & A generated front documentation surface that summarizes project facts, embeds the repository module inventory and derivation graphs, records the tool-interface guiding metaphor, and states project licensing notices. & DB-REVIEW side objective;\newline user requirement for a concise Leitmetapher, a Stats opening section, explicit documentation/\allowbreak{}code licensing, and integration of the former repository module inventory section. & masters/\allowbreak{}cnna\_roadmap\_master.yaml;\newline repo\_inventory/\allowbreak{}raw\_export/\allowbreak{}stats.json;\newline repo\_inventory/\allowbreak{}raw\_export/\allowbreak{}modules.json;\newline generated\_exports/\allowbreak{}*.tsv;\newline scripts/\allowbreak{}generate\_tables.py. & Python documentation-generation path only;\newline not an operational CNNA mathematical computation and not a Lean theorem. & active-tooling & \hyperlink{phase-row-20-7}{20.7}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG36}{LEG36} & Semantic module consolidation ledger & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{yellow!25}Y & A pre-substantive audit ledger that classifies semantically related Lean modules and notation surfaces into safe-merge/\allowbreak{}removal candidates, facade-preserve candidates, split/\allowbreak{}keep candidates, quarantine candidates, and no-merge proof-stage chains. It records natural-layer placement and regression obligations before any code consolidation. & Generated module inventory, import graph, declaration consumption map, reuse/\allowbreak{}duplication ledger, and direct spot-checks of candidate code families. & LEG10, LEG11, LEG5, LEG42, repo\_inventory/\allowbreak{}raw\_export/\allowbreak{}modules.json, import\_edges.json, symbol\_reference\_summary.json, and manual code inspection of high-similarity module/\allowbreak{}notation clusters. & not applicable;\newline planning/\allowbreak{}refactor governance layer only. If later Lean refactor changes executable modules, the regression package must preserve concrete computable witnesses. & critical-before-new-substantive-code & \hyperlink{phase-row-1-1-1-1-5}{1.1.1.1.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG42}{LEG42} & Notation surface consumption and cleanup ledger & Lean;\newline Refactor;\newline Object & F1 & current & \cellcolor{green!18}G & Ledger classifying every CNNA Notation.lean declaration, alias and symbol wrapper by actual consumption, owner object, public/\allowbreak{}internal status, legacy/\allowbreak{}phase-alias status, collision risk, and keep/\allowbreak{}quarantine/\allowbreak{}remove/\allowbreak{}rename disposition before any neutral refactor or full inventory scan is accepted. & All repo\_snapshot/\allowbreak{}CNNA/\allowbreak{}**/\allowbreak{}Notation.lean files;\newline import graph;\newline grep/\allowbreak{}symbol-reference audit;\newline LEG5 consumption classes;\newline LEG10 module manifest;\newline public API contract. & All repo\_snapshot/\allowbreak{}CNNA/\allowbreak{}**/\allowbreak{}Notation.lean declarations;\newline static token/\allowbreak{}symbol consumer search across repo\_snapshot/\allowbreak{}CNNA/\allowbreak{}*.lean;\newline import graph context;\newline manual classification buckets recorded in TSV/\allowbreak{}JSON evidence. & Tool/\allowbreak{}planning/\allowbreak{}refactor audit only;\newline no ExecComplex path and no mathematical object claim. & high & \hyperlink{phase-row-1-1-1-1-5-1}{1.1.1.1.5.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG43}{LEG43} & Notation removal review ledger & Lean;\newline Refactor;\newline Object & F1 & current & \cellcolor{green!18}G & A row-level review ledger deciding which LEG42-unconsumed Notation.lean surfaces are genuinely removable and which must be kept, quarantined, facade-preserved, renamed, or deferred because public/\allowbreak{}API/\allowbreak{}owner/\allowbreak{}compatibility status is not yet settled. & 1.1.1.1.5.1.1;\newline closed LEG42 audit ledger;\newline generated\_exports/\allowbreak{}notation\_surface\_consumption\_cleanup\_ledger.generated.tsv;\newline generated\_exports/\allowbreak{}notation\_surface\_consumption\_cleanup\_evidence.generated.json;\newline direct Notation.lean source inspection;\newline public/\allowbreak{}API intent and owner-object review. & LEG42 TSV/\allowbreak{}JSON evidence plus conservative row-level review rules. Output: 494 LEG44-approved Arithmetic/\allowbreak{}Notation candidates (391 standalone, 103 closed-cluster) and 178 deferred unconsumed public/\allowbreak{}facade/\allowbreak{}core-symbol/\allowbreak{}owner-domain rows. & Tool/\allowbreak{}refactor audit only;\newline no ExecComplex path and no mathematical object claim. & critical-before-neutral-refactor & \hyperlink{phase-row-1-1-1-1-5-1-1}{1.1.1.1.5.1.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG44}{LEG44} & Notation removal execution certificate & Lean;\newline Refactor;\newline Object & F1 & current & \cellcolor{green!18}G & A build-verifiable certificate for deleting or retiring only those Notation.lean surfaces certified by LEG43 as genuinely unused. If no candidate is safe, it closes as a no-op certificate with explicit reasons. & 1.1.1.1.5.1.2;\newline LEG43 notation-removal review ledger;\newline LEG42 source/\allowbreak{}consumer evidence;\newline exact Notation.lean file/\allowbreak{}declaration targets;\newline local Lean build and consumer-regression evidence. & Closed LEG43 review ledger;\newline exact P1.45 declaration-range deletion ledger;\newline post-edit static source-token check;\newline regenerated static repo inventory;\newline user-reported green local lake build. & Not an ExecComplex computation;\newline if Lean code changes, all existing executable witnesses and computable paths must be preserved by the build/\allowbreak{}regression evidence. & critical-before-neutral-refactor & \hyperlink{phase-row-1-1-1-1-5-1-2}{1.1.1.1.5.1.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR8}{DBR8} & Root artifact retention and cleanup policy & Generated;\newline Artifact;\newline Object & F3 & current & \cellcolor{green!18}G & A repository hygiene rule and toolchain pair that keeps the project root source-oriented by archiving historical Markdown reports and treating root PDF/\allowbreak{}TeX/\allowbreak{}LaTeX outputs as disposable generated artifacts. & DB-REVIEW side objective;\newline user requirement that PDFs and TeX need not be retained because they can be generated at any time;\newline root-file audit after V1.12. & masters/\allowbreak{}cnna\_roadmap\_master.yaml;\newline root file inventory;\newline scripts/\allowbreak{}generate\_tables.py;\newline scripts/\allowbreak{}generate\_full\_document.py;\newline scripts/\allowbreak{}clean\_generated\_root\_artifacts.py. & Python tooling path only;\newline not an operational CNNA mathematical computation and not a Lean theorem. & active-tooling & \hyperlink{phase-row-20-8}{20.8}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR9}{DBR9} & Current README and workflow-orientation manual & Generated;\newline Artifact;\newline Object & F3 & current & \cellcolor{green!18}G & A source-root README that replaces chronological release notes with a current operational manual for the CNNA planning/\allowbreak{}documentation tool. & DB-REVIEW side objective;\newline user request for a completely new README adapted to the current version;\newline correction that the developed/\allowbreak{}tested assistant workflow is with ChatGPT, not Claude. & masters/\allowbreak{}cnna\_roadmap\_master.yaml;\newline generated\_exports/\allowbreak{}project\_stats.generated.tsv;\newline existing scripts;\newline user workflow requirements;\newline V1.13 root cleanup policy. & Not applicable;\newline README/\allowbreak{}documentation-tooling layer only. No mathematical CNNA object and no Lean theorem. & active-tooling & \hyperlink{phase-row-20-9}{20.9}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR10}{DBR10} & Root Lean/\allowbreak{}Lake project-control files & Generated;\newline Artifact;\newline Object & F3 & current & \cellcolor{green!18}G & The minimal package-root build-entry surface consisting of CNNA.lean, lakefile.lean, lake-manifest.json and lean-toolchain, with README documentation in Repository/\allowbreak{} and optionally mirrored at package root. These files are source/\allowbreak{}control configuration, not disposable generated documentation artifacts. & User correction after V1.14 that the Lean toolchain must be included in the project root;\newline uploaded lakefile.lean and CNNA.lean explicitly reference Repository/\allowbreak{}repo\_snapshot as the source location. & Uploaded CNNA.lean, lakefile.lean, lake-manifest.json, lean-toolchain;\newline repo\_snapshot/\allowbreak{}CNNA;\newline scripts/\allowbreak{}clean\_generated\_root\_artifacts.py;\newline README.md. & Not an ExecComplex mathematical computation. This is build reproducibility/\allowbreak{}toolchain configuration for local Lean/\allowbreak{}Lake builds. & active-tooling & \hyperlink{phase-row-20-10}{20.10}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR11}{DBR11} & Root license, single-root README, credits and assistant-requirement surface & Generated;\newline Artifact;\newline Object & F3 & current & \cellcolor{green!18}G & A package-root documentation/\allowbreak{}license surface that keeps the maintained README only in the root, adds a root LICENSE file, exposes editor/\allowbreak{}assistant credits, and records the minimum tested ChatGPT setup for assistant-instantiated workflows. & User requirements after V1.16: add license notices to README and root LICENSE;\newline keep README only in root;\newline add Editor Jan Seeck (antaris) and Assistant ChatGPT (OpenAI) also to generated PDFs;\newline state the minimum requirement as a ChatGPT Plus account with GPT-5.5. & User-provided licensing URLs;\newline README;\newline license\_notice table;\newline metadata editor/\allowbreak{}assistant/\allowbreak{}minimum assistant requirement;\newline full/\allowbreak{}context documentation generators;\newline root file inventory. & Not applicable;\newline documentation, licensing and tooling metadata only. No mathematical CNNA object and no Lean theorem. & active-tooling & \hyperlink{phase-row-20-11}{20.11}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR12}{DBR12} & Generated PDF section-pagebreak layout invariant & Generated;\newline Artifact;\newline Object & F3 & current & \cellcolor{green!18}G & A documentation-layout invariant requiring every top-level section in generated full and context PDFs to begin on a new page, without changing the underlying Lean/\allowbreak{}YAML truth boundary. & User requirement after V1.17 that each section should automatically start on a new page in generated documentation. & generate\_full\_document.py;\newline generate\_context\_doc.py;\newline metadata/\allowbreak{}tool version;\newline generated table/\allowbreak{}context views. & Not applicable;\newline documentation layout invariant only. No mathematical CNNA object and no Lean theorem. & active-tooling & \hyperlink{phase-row-20-12}{20.12}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR13}{DBR13} & Phase status release policy and red-lock ledger & Generated;\newline Artifact;\newline Object & F3 & current & \cellcolor{green!18}G & A phase-status governance object enforcing that direct Lean-derivation phases are locked red unless already green, uniquely active yellow, or orange by an explicit predecessor-release check;\newline white is reserved for non-Lean/\allowbreak{}tooling/\allowbreak{}refactor/\allowbreak{}infrastructure/\allowbreak{}documentation/\allowbreak{}comparison phases. & User requirement after V1.18 that all not-yet-derivable Lean-code phases default to red until the plan proves their release from derived-only Lean objects;\newline white is redefined for non-direct-Lean implementation work. & status\_legend;\newline phases;\newline implementation\_scratchpad.phase\_type;\newline pre\_implementation\_phase\_check\_results;\newline generate\_tables.py validation;\newline existing derived-only/\allowbreak{}Lean-primary rules. & Not applicable;\newline planning/\allowbreak{}status-governance layer only. No mathematical CNNA object and no Lean theorem. & active-tooling & \hyperlink{phase-row-20-13}{20.13}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR14}{DBR14} & Static documentation explanations and module-change appendix policy & Generated;\newline Artifact;\newline Object & F3 & current & \cellcolor{green!18}G & A generated-documentation contract: static prose explains each section/\allowbreak{}table source and purpose, dynamic rows remain generated from YAML/\allowbreak{}exports, and the module-change manifest is a technical appendix used only for real module/\allowbreak{}API surface changes. & User request after V1.19 that the module manifest was confusing and that each section/\allowbreak{}table should be explained more clearly without making the prose dynamic. & generate\_full\_document.py;\newline generate\_context\_doc.py;\newline generate\_tables.py;\newline Master YAML;\newline generated exports;\newline section order and module-manifest scratchpad fields. & Not applicable;\newline documentation layout/\allowbreak{}semantics only. No mathematical CNNA object and no Lean theorem. & active-tooling & \hyperlink{phase-row-20-14}{20.14}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG37}{LEG37} & Post-refactor current source intake completeness ledger & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{yellow!25}Y & A complete classification ledger for the refactored Lean source snapshot, not the pre-refactor surface: every module/\allowbreak{}declaration is linked 1:1 to an object/\allowbreak{}proof dossier, legacy/\allowbreak{}audit-only/\allowbreak{}generated/\allowbreak{}reference/\allowbreak{}tool/\allowbreak{}refactor bucket, or a newly created natural-origin ingestion phase, with total declaration classification by syntactic kind, semantic role, triviality tier, significance/\allowbreak{}documentation policy, lifecycle state, public-surface status and owning object or explicit non-object bucket. & LEG42 notation audit;\newline LEG43 notation-removal review;\newline LEG44 notation-removal execution/\allowbreak{}no-op certificate;\newline LEG38 neutral naming map;\newline LEG39 refactor certificate;\newline fresh post-refactor repo inventory;\newline CEX11 total declaration taxonomy. & Post-refactor module/\allowbreak{}import/\allowbreak{}declaration inventory, object register, proof dossiers, notation audit/\allowbreak{}review/\allowbreak{}removal evidence and manual override ledger. & not applicable;\newline source inventory and classification audit only. & critical-before-new-substantive-code & \hyperlink{phase-row-1-1-1-1-5-4}{1.1.1.1.5.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG38}{LEG38} & Neutral module-name and facade migration map & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{yellow!25}Y & A migration map assigning phase-semantic or legacy module names to neutral target names, facade modules, no-merge exceptions, and proof-stage preservation constraints. & 1.1.1.1.5.2;\newline closed LEG42 audit ledger;\newline closed LEG43 notation-removal review;\newline build-validated LEG44 notation-removal execution certificate;\newline semantic consolidation findings SCF44/\allowbreak{}SCF45/\allowbreak{}SCF52. & Closed LEG42 notation audit ledger, closed LEG43 removal-review ledger, closed/\allowbreak{}build-validated LEG44 removal certificate, plus SCF44/\allowbreak{}SCF45/\allowbreak{}SCF52 semantic consolidation findings. & not applicable until execution;\newline planned refactor surface only. & critical-before-new-substantive-code & \hyperlink{phase-row-1-1-1-1-5-2}{1.1.1.1.5.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG39}{LEG39} & Neutral refactor execution certificate & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{yellow!25}Y & A certificate for a bounded neutral-module refactor package: old-module facades, import/\allowbreak{}declaration delta, consumer breakage audit, and local full-build evidence. & 1.1.1.1.5.3;\newline LEG38 migration map;\newline LEG44 notation-removal certificate;\newline refactor regression protocol. & LEG38, LEG44, GNG03, GNG26, GNG28-GNG32, local Lean build evidence after refactor. & not an ExecComplex computation;\newline must preserve all executable witnesses. & critical-before-new-substantive-code & \hyperlink{phase-row-1-1-1-1-5-3}{1.1.1.1.5.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG40}{LEG40} & Post-refactor inventory closure certificate & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{yellow!25}Y & A regenerated inventory closure record after any neutral refactor: module graph, declaration graph, object-register delta, proof-dossier delta, public/\allowbreak{}API consumer delta, unresolved-gap ledger. & 1.1.1.1.5.4;\newline LEG39 closed refactor execution certificate;\newline LEG42/\allowbreak{}LEG43/\allowbreak{}LEG44 notation cleanup evidence;\newline regenerated inventory/\allowbreak{}export data. & build\_export\_script\_v1.8.py outputs after refactor, generated\_tables.py outputs, notation cleanup evidence, object/\allowbreak{}proof/\allowbreak{}phase registers. & not applicable;\newline inventory and release metadata only. & critical-before-new-substantive-code & \hyperlink{phase-row-1-1-1-1-5-4}{1.1.1.1.5.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-LEG41}{LEG41} & Pre-substantive-code release certificate & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{yellow!25}Y & A release certificate proving that a new substantive Lean/\allowbreak{}content phase may become active only after source intake, neutral naming/\allowbreak{}refactor, post-refactor inventory, proof-dossier updates and red-lock checks close. & 1.1.1.1.5.5;\newline LEG42-LEG44 and LEG37-LEG40 closed;\newline DBR13/\allowbreak{}GNG31 red-lock policy. & Closed LEG42, LEG43, LEG44, LEG37, LEG38, LEG39, LEG40, object proof dossiers, phase release checks, local build evidence if refactor executed. & not applicable;\newline release certificate only. & critical-before-new-substantive-code & \hyperlink{phase-row-1-1-1-1-5-5}{1.1.1.1.5.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR15}{DBR15} & provider-neutral SQL database mirror feasibility and schema design & Database;\newline Mirror;\newline Object & F1 & current & \cellcolor{white}W & Define the first DB mirror boundary: Lean/\allowbreak{}YAML remain authoritative;\newline provider-neutral SQL database is a public query/\allowbreak{}visualization mirror only. internal/\allowbreak{}api/\allowbreak{}review/\allowbreak{}admin schema split;\newline minimal tables for db\_snapshots, phases, objects, proof\_dossiers, guardrails, workflows, modules, declarations, import\_edges, phase\_object\_links, context\_profiles, static\_findings and reports. & SLTG-06 database-ready CNNA review/\allowbreak{}documentation structure and the V1.22 database mirror/\allowbreak{}public-web-frontend architecture decision. & Master YAML, generated TSV exports, repo\_inventory/\allowbreak{}raw\_export, status/\allowbreak{}guardrail/\allowbreak{}proof-dossier records and future import reports/\allowbreak{}checksums. & Not applicable;\newline database/\allowbreak{}publication tooling only. No mathematical CNNA computation and no Lean theorem. & secondary-tooling-sidechain & \hyperlink{phase-row-20-15}{20.15}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR16}{DBR16} & YAML/\allowbreak{}exports to SQL import and roundtrip contract & Database;\newline Mirror;\newline Object & F1 & current & \cellcolor{white}W & Define a reproducible importer/\allowbreak{}exporter contract from Master YAML and generated exports into provider-neutral SQL database and back to YAML/\allowbreak{}reportable snapshots. Importer must be local/\allowbreak{}admin-run with .env secrets, produce import report/\allowbreak{}checksums, and never require a admin write credential key in chat or browser. & SLTG-06 database-ready CNNA review/\allowbreak{}documentation structure and the V1.22 database mirror/\allowbreak{}public-web-frontend architecture decision. & Master YAML, generated TSV exports, repo\_inventory/\allowbreak{}raw\_export, status/\allowbreak{}guardrail/\allowbreak{}proof-dossier records and future import reports/\allowbreak{}checksums. & Not applicable;\newline database/\allowbreak{}publication tooling only. No mathematical CNNA computation and no Lean theorem. & secondary-tooling-sidechain & \hyperlink{phase-row-20-16}{20.16}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR17}{DBR17} & Append-only snapshot and checksum model & Database;\newline Mirror;\newline Object & F1 & current & \cellcolor{white}W & Define snapshot provenance so every public DB row is traceable to a Lean/\allowbreak{}YAML/\allowbreak{}tool package state. db\_snapshots with snapshot\_id, lean\_data\_version, lean\_data\_timestamp, planning\_data\_version, planning\_data\_timestamp, tool\_infrastructure\_version, tool\_infrastructure\_timestamp, yaml\_hash, repo\_inventory\_hash, tool\_hash, created\_at, created\_by, source\_zip\_name and optional import\_report\_hash. & SLTG-06 database-ready CNNA review/\allowbreak{}documentation structure and the V1.22 database mirror/\allowbreak{}public-web-frontend architecture decision. & Master YAML, generated TSV exports, repo\_inventory/\allowbreak{}raw\_export, status/\allowbreak{}guardrail/\allowbreak{}proof-dossier records and future import reports/\allowbreak{}checksums. & Not applicable;\newline database/\allowbreak{}publication tooling only. No mathematical CNNA computation and no Lean theorem. & secondary-tooling-sidechain & \hyperlink{phase-row-20-17}{20.17}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR18}{DBR18} & Public read-only API views and read-only access policies & Database;\newline Mirror;\newline Object & F1 & current & \cellcolor{white}W & Define public read-only exposure through api.* views while internal canonical tables remain non-public. public read-only clients get SELECT on api.* views only;\newline no public INSERT/\allowbreak{}UPDATE/\allowbreak{}DELETE;\newline internal.* and admin/\allowbreak{}import.* remain closed;\newline admin write credential never appears in frontend/\allowbreak{}browser. & SLTG-06 database-ready CNNA review/\allowbreak{}documentation structure and the V1.22 database mirror/\allowbreak{}public-web-frontend architecture decision. & Master YAML, generated TSV exports, repo\_inventory/\allowbreak{}raw\_export, status/\allowbreak{}guardrail/\allowbreak{}proof-dossier records and future import reports/\allowbreak{}checksums. & Not applicable;\newline database/\allowbreak{}publication tooling only. No mathematical CNNA computation and no Lean theorem. & secondary-tooling-sidechain & \hyperlink{phase-row-20-18}{20.18}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR19}{DBR19} & cnna-project.net web-frontend data contract & Database;\newline Mirror;\newline Object & F1 & current & \cellcolor{white}W & Define the read-only web frontend contract for public visualization/\allowbreak{}navigation over database mirror api.* views. Frontend can query public views with public read-only credential only and render phase map, object register, red/\allowbreak{}orange release reasons, import/\allowbreak{}module graph, proof dossiers, blue-debt dashboard and HTML context docs. & SLTG-06 database-ready CNNA review/\allowbreak{}documentation structure and the V1.22 database mirror/\allowbreak{}public-web-frontend architecture decision. & Master YAML, generated TSV exports, repo\_inventory/\allowbreak{}raw\_export, status/\allowbreak{}guardrail/\allowbreak{}proof-dossier records and future import reports/\allowbreak{}checksums. & Not applicable;\newline database/\allowbreak{}publication tooling only. No mathematical CNNA computation and no Lean theorem. & secondary-tooling-sidechain & \hyperlink{phase-row-20-19}{20.19}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR20}{DBR20} & Reviewer annotation and future admin-write model & Database;\newline Mirror;\newline Object & F1 & current & \cellcolor{white}W & Define later authenticated reviewer annotations and controlled admin/\allowbreak{}import writes without changing the initial public read-only guarantee. review.* for later authenticated comments/\allowbreak{}annotations;\newline admin/\allowbreak{}import.* for local importer or future signed server-side import endpoint;\newline no public writes and no manual table-click update as standard workflow. & SLTG-06 database-ready CNNA review/\allowbreak{}documentation structure and the V1.22 database mirror/\allowbreak{}public-web-frontend architecture decision. & Master YAML, generated TSV exports, repo\_inventory/\allowbreak{}raw\_export, status/\allowbreak{}guardrail/\allowbreak{}proof-dossier records and future import reports/\allowbreak{}checksums. & Not applicable;\newline database/\allowbreak{}publication tooling only. No mathematical CNNA computation and no Lean theorem. & secondary-tooling-sidechain & \hyperlink{phase-row-20-20}{20.20}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR21}{DBR21} & Enlarged generated-PDF typography profile & Generated;\newline Artifact;\newline Object & F3 & current & \cellcolor{green!18}G & A generated-document layout profile that raises full/\allowbreak{}context PDF body and table text one typographic step, including explicit TeX size commands and graph label sizes, without changing Lean/\allowbreak{}YAML data semantics. & User request after V1.22 to make all generated-document text one size larger. & generate\_full\_document.py, generate\_context\_doc.py, generate\_tables.py, build\_export\_script\_v1.8.py, generated TeX/\allowbreak{}PDF outputs and representative render checks. & Not applicable;\newline documentation typography only. No mathematical CNNA object and no Lean theorem. & active-tooling & \hyperlink{phase-row-20-21}{20.21}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-GA0}{GA0} & Horn quaternion/\allowbreak{}geometric-algebra reference-gate packet & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & A documentation-only packet of target patterns extracted from Horn 0709.2238v1: Hamilton quaternion relations, Pauli/\allowbreak{}Cartan relation, geometric-product basis grades, pseudoscalar duality, pure-quaternion-as-bivector interpretation and complex-quaternion eight-basis bookkeeping. & User-requested reading of Horn 0709.2238v1 as a reference/\allowbreak{}target gate, explicitly not as a CNNA input. & Horn 0709.2238v1;\newline external primary/\allowbreak{}source checks for mathlib Quaternion/\allowbreak{}CliffordAlgebra and GA formalization;\newline no Lean CNNA computation. & None. Reference metadata only;\newline no operational computation and no scalar-layer authority. & reference-gate & \hyperlink{phase-row-1-4-9}{1.4.9}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-GA1}{GA1} & Hamilton unit and Pauli/\allowbreak{}Cartan sign-convention comparison profile & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & A target profile recording unit-square, anti-commutation and sign-convention checks for Hamilton units and their Pauli/\allowbreak{}Cartan representation, with explicit separation of complex i and quaternion i. & Horn sections on quaternions and Pauli matrices;\newline mathlib Quaternion API as later formal target seam. & GA0 and external reference equations only;\newline future comparison waits for CD0-CD7 closure. & None currently;\newline future checks may be exact algebraic equalities, not ExecComplex calculations. & reference-gate & \hyperlink{phase-row-1-4-9-1}{1.4.9.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-GA2}{GA2} & Pauli bivector/\allowbreak{}pseudoscalar duality comparison profile & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & A target profile for geometric-algebra duality: scalar/\allowbreak{}trivector and vector/\allowbreak{}bivector pairing, pseudoscalar I = sigma\_x sigma\_y sigma\_z, I\textasciicircum{}2 = -1, and pure quaternions as oriented-plane/\allowbreak{}bivector targets. & Horn duality section and geometric algebra basis-grade discussion. & GA0, GA1 and external GA references;\newline no CNNA-derived orientation or dimension is assumed. & None currently. Future implementation must require CNNA-derived orientation/\allowbreak{}volume candidate before comparison. & reference-gate & \hyperlink{phase-row-1-4-9-2}{1.4.9.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-GA3}{GA3} & Complex-quaternion eight-basis multivector comparison profile & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & A target bookkeeping profile for the eight real components of complex quaternions mapped to geometric-algebra grades: scalar, vector, bivector and pseudoscalar components. & Horn complex-quaternion section and its mapping between biquaternions and geometric-algebra multivectors. & GA0-GA2;\newline external reference only, no CNNA scalar surface or C-layer assumption. & None currently. Explicitly not an ExecComplex replacement or complex scalar import. & reference-gate & \hyperlink{phase-row-1-4-9-2}{1.4.9.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-GA4}{GA4} & Boundary Pauli/\allowbreak{}Clifford comparison gate & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & A comparison gate asking whether generators produced by the CNNA-derived boundary *-algebra satisfy Pauli/\allowbreak{}Clifford-like square, star and anti-commutation targets. & Horn Pauli/\allowbreak{}geometric-algebra interpretation;\newline mathlib CliffordAlgebra universal-property API;\newline Pillar-B boundary star-algebra roadmap. & Future 13.2 boundary *-algebra plus GA0-GA3 target profiles;\newline no direct Pillar-A internals. & Potential finite matrix check only after 13.2 derives the algebra;\newline currently none. & reference-gate & \hyperlink{phase-row-13-2-1}{13.2.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-GA5}{GA5} & Dirac/\allowbreak{}spacetime-algebra comparison target gate & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & A comparison target for later CNNA-derived local-net/\allowbreak{}modular data against Dirac/\allowbreak{}spacetime-algebra Clifford signatures, Lorentz-covariance formulations and spin/\allowbreak{}CPT compatibility patterns. & Horn Dirac/\allowbreak{}quaternion discussion and GA/\allowbreak{}STA reference literature;\newline placed behind 13.6 theorem gates. & Future 13.5/\allowbreak{}13.6 outputs plus GA4;\newline no imported Dirac equation, Lorentz group or spacetime metric. & None currently;\newline later finite checks may exist only as mirror diagnostics after B data is derived. & reference-gate & \hyperlink{phase-row-13-6-1}{13.6.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-GA6}{GA6} & Geometric and conformal algebra side-comparison register & Reference;\newline Gate;\newline Object & F2 & current & \cellcolor{black!18}K & A side-comparison register for geometric algebra, spacetime algebra and conformal geometric algebra as external target surfaces for already-derived CNNA outputs. & Horn outlook and related GA/\allowbreak{}CGA reference literature;\newline CNNA side-comparison Phase 18. & GA0-GA5 and future derived CNNA outputs;\newline never from external GA as a foundation. & None. Documentation/\allowbreak{}review comparison metadata only. & secondary-reference & \hyperlink{phase-row-18-5}{18.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DBR27}{DBR27} & Phase/\allowbreak{}Object context-class taxonomy & Tool;\newline Infrastructure;\newline Object & F3 & current & \cellcolor{green!18}G & Generated-secondary context-class taxonomy: every phase/\allowbreak{}object row carries an explicit Context class separating Lean mathematical objects, Lean-facing contracts/\allowbreak{}refactors/\allowbreak{}governance, tool/\allowbreak{}database/\allowbreak{}generated/\allowbreak{}documentation artifacts and reference gates. & User-requested correction that objects and phases must be classified by overarching context;\newline OOP principle: class/\allowbreak{}type identity must be visible and separate from state/\allowbreak{}status. & Schema extension from V1.25 plus second-pass semantic class audit: phase/\allowbreak{}object rows receive Context class;\newline Lean-facing refactor/\allowbreak{}contract/\allowbreak{}governance rows are separated from tool-only rows and mathematical Lean source/\allowbreak{}target rows. & Not applicable;\newline no mathematical computation. This is schema/\allowbreak{}classification metadata for review surfaces. & critical-tooling-governance & \hyperlink{phase-row-20-27}{20.27}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX0}{CEX0} & Explorer-readiness audit ledger & Lean;\newline Refactor;\newline Object & F1 & current & \cellcolor{yellow!25}Y & A consolidated audit object that decides whether the current YAML plus generated Lean inventory is complete and coherent enough to support the Explorer. It includes YAML field coverage, entity completeness, edge semantics, object lifecycle/\allowbreak{}supersession coverage, neutral naming/\allowbreak{}refactor consolidation, complete IST Lean module/\allowbreak{}declaration/\allowbreak{}object scan and total Lean-declaration classification. & LEG37-LEG41, DBR27, context/\allowbreak{}significance taxonomy, repo\_inventory/\allowbreak{}raw\_export and user requirement that Explorer Phase 0 must precede design/\allowbreak{}implementation. & LEG37-LEG41, LEG5, DBR27, CEX10, CEX11, Master YAML, generated\_exports, repo\_inventory/\allowbreak{}raw\_export/\allowbreak{}*.json, lean\_declaration\_classification\_taxonomy & Not applicable;\newline Explorer/\allowbreak{}tooling metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-before-explorer-design & \hyperlink{phase-row-21-0}{21.0}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX1}{CEX1} & Explorer semantic graph schema & Tool;\newline Infrastructure;\newline Object & F1 & current & \cellcolor{white}W & Typed node/\allowbreak{}edge schema for the CNNA Explorer, including direction semantics and epistemic layers for Lean objects, YAML mirrors, SQL mirrors, generated artifacts, external references and hypotheses. & CEX0 readiness audit and the need for first-class graph edges. & CEX0, DBR27, phase/\allowbreak{}object/\allowbreak{}proof/\allowbreak{}scratchpad registers & Not applicable;\newline Explorer/\allowbreak{}tooling metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-explorer-schema & \hyperlink{phase-row-21-1}{21.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX2}{CEX2} & YAML2SQL/\allowbreak{}MySQL mirror contract & Database;\newline Mirror;\newline Object & F1 & current & \cellcolor{white}W & Deterministic one-way import contract from Master YAML/\allowbreak{}generated inventory and CI-emitted snapshot artifacts to a MySQL-compatible read-only presentation mirror. The database mirrors commit/\allowbreak{}YAML/\allowbreak{}inventory state;\newline it is never a source of CNNA truth. & User preference for a webhosting MySQL mirror and removal of provider-specific live-database planning. & CEX0-CEX1, DBR15-DBR18, generated exports, future commit/\allowbreak{}build/\allowbreak{}snapshot manifests & Not applicable;\newline Explorer/\allowbreak{}tooling metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-explorer-data-layer & \hyperlink{phase-row-21-2}{21.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX3}{CEX3} & Explorer read-only API/\allowbreak{}query projection contract & Database;\newline Mirror;\newline Object & F1 & current & \cellcolor{white}W & Read-only API/\allowbreak{}view contract for graph, filter, inspector, history, red-failure-history, translation and hypothesis projections over the current validated SQL snapshot, with admin/\allowbreak{}import internals hidden. & CNNA Explorer requires SQL/\allowbreak{}API projections but public access must remain read-only. & CEX1-CEX2, CEX12-CEX16, DBR18-DBR20, read-only public access policy & Not applicable;\newline Explorer/\allowbreak{}tooling metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-explorer-api & \hyperlink{phase-row-21-3}{21.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX4}{CEX4} & Dark Pillar-hub star-map UI shell & Tool;\newline Infrastructure;\newline Object & F1 & current & \cellcolor{white}W & Dark interactive CNNA root/\allowbreak{}Pillar-hub graph shell with controlled expansion and no-detail-overload policy. & User-requested immersive star-map Explorer with Pillars as largest hubs. & CEX1-CEX3, Pillar/\allowbreak{}context taxonomy & Not applicable;\newline Explorer/\allowbreak{}tooling metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-explorer-ui & \hyperlink{phase-row-21-4}{21.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX5}{CEX5} & Inspector/\allowbreak{}menu/\allowbreak{}i18n explanation contract & Tool;\newline Infrastructure;\newline Object & F1 & current & \cellcolor{white}W & Right-side inspector and explanation/\allowbreak{}i18n schema for phases, objects, modules, edges and proof dossiers. & User requested right-side data blocks, menus with prepared explanations and multilingual UI/\allowbreak{}descriptions. & CEX1-CEX4, object/\allowbreak{}proof/\allowbreak{}scratchpad registers & Not applicable;\newline Explorer/\allowbreak{}tooling metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-explorer-ui & \hyperlink{phase-row-21-5}{21.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX6}{CEX6} & Explorer filter and projection engine & Tool;\newline Infrastructure;\newline Object & F1 & current & \cellcolor{white}W & Projection/\allowbreak{}filter engine for context, theme, phase, object, module, status, edge semantics and view-depth restrictions. & User requested graph restrictions by contexts, topics, phases and objects with detail control. & CEX1-CEX5, semantic graph schema/\allowbreak{}API views & Not applicable;\newline Explorer/\allowbreak{}tooling metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-explorer-interaction & \hyperlink{phase-row-21-6}{21.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX7}{CEX7} & History and hypothesis lifecycle layer & Tool;\newline Infrastructure;\newline Object & F1 & current & \cellcolor{white}W & Timeline/\allowbreak{}diff/\allowbreak{}hypothesis model for status changes, graph changes, predictions, validations, falsifications and review evidence. & User requested filterable history and marked hypothetical/\allowbreak{}planned structures with later prediction-outcome evaluation. & CEX0-CEX6, snapshot/\allowbreak{}checksum model, proof dossiers & Not applicable;\newline Explorer/\allowbreak{}tooling metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-explorer-research-layer & \hyperlink{phase-row-21-7}{21.7}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX8}{CEX8} & Explorer lab-boundary contract & Tool;\newline Infrastructure;\newline Object & F1 & current & \cellcolor{white}W & Boundary contract for later bright/\allowbreak{}interface/\allowbreak{}dark projections, matrix-entry displays, approximants and simulations, strictly separated from Lean-derived truth. & User envisioned later live derived graphs, bright/\allowbreak{}interface/\allowbreak{}dark split simulation, matrix entries and approximations. & CEX0-CEX7, ExecComplex/\allowbreak{}computable-path metadata, DtN/\allowbreak{}Schur object registers & Not applicable;\newline Explorer/\allowbreak{}tooling metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & future-explorer-lab-boundary & \hyperlink{phase-row-21-8}{21.8}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX9}{CEX9} & CNNA Explorer deployment and Universe Explorer roadmap & Generated;\newline Artifact;\newline Object & F1 & current & \cellcolor{white}W & Deployment/\allowbreak{}release contract for a public cnna-project.net Explorer and future Universe Explorer backlog, tied to read-only snapshots, GitHub CI artifacts, Webhosting-local MySQL imports, visible red-failure-history snapshots, backup/\allowbreak{}rollback manifests and CEX15 red/\allowbreak{}green phase-state transition manifests and generated artifacts. & CNNA Explorer should grow toward Universe Explorer while remaining snapshot-bound and reviewable. & CEX0-CEX8, CEX12-CEX16, DBR18-DBR20, generated docs/\allowbreak{}release artifacts & Not applicable;\newline Explorer/\allowbreak{}tooling metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & secondary-explorer-release & \hyperlink{phase-row-21-9}{21.9}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX10}{CEX10} & Object lifecycle and historical provenance ledger & Lifecycle;\newline Governance;\newline Object & F1 & current & \cellcolor{yellow!25}Y & A planning/\allowbreak{}tooling ledger that gives every registered object an explicit lifecycle state, predecessor/\allowbreak{}successor relation, current dossier pointer and non-destructive history rule. It preserves patched, renamed, deleted or retired objects as historical rows while directing consumers to the current object/\allowbreak{}dossier. & User requirement that patched objects must not be overwritten, old provenance must remain visible, phases are never outdated, and successor/\allowbreak{}patch relations must keep the graph acyclic and coherent. & Master YAML objects, object\_proof\_dossiers, workflow\_policy, context/\allowbreak{}significance taxonomy, future repo\_inventory diffs and Explorer snapshot comparisons & Not applicable;\newline lifecycle/\allowbreak{}provenance metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-before-explorer-schema & \hyperlink{phase-row-21-0}{21.0}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX11}{CEX11} & Total Lean declaration classification ledger & Lean;\newline Governance;\newline Object & F1 & current & \cellcolor{yellow!25}Y & A planning/\allowbreak{}tooling ledger requiring every current Lean declaration in the source snapshot to be classified by declaration\_kind, semantic\_role, triviality\_tier, significance/\allowbreak{}documentation policy, lifecycle\_state, public\_surface\_status and owning CNNA object or explicit non-object bucket. It refines LEG5 consumption classification and feeds LEG37/\allowbreak{}CEX0 closure. & LEG42 notation cleanup;\newline LEG38/\allowbreak{}LEG39 neutral refactor;\newline LEG37/\allowbreak{}LEG40 post-refactor source intake;\newline generated declaration inventory;\newline manual classification policy. & Post-refactor declaration inventory, object register, proof dossiers, owner buckets, public-surface status, lifecycle fields and manual override ledger. & Not applicable;\newline declaration inventory/\allowbreak{}governance metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-before-explorer-schema-and-before-new-substantive-code & \hyperlink{phase-row-21-0}{21.0}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX12}{CEX12} & GitHub repository automation and backup-gated PR contract & Tool;\newline Infrastructure;\newline Object & F1 & current & \cellcolor{white}W & Repository automation contract requiring backup tag/\allowbreak{}branch before mutation, a work branch for changes, PR-gated review/\allowbreak{}CI, and explicit override logging for any emergency direct-main action. & User requested direct GitHub access with mandatory safety copy before automated work;\newline CNNA requires generated-secondary automation not to corrupt the primary Lean source history. & CEX0-CEX2;\newline repository default branch;\newline GitHub App/\allowbreak{}API permissions;\newline branch protection policy;\newline snapshot naming rules & Not applicable;\newline CI/\allowbreak{}backup/\allowbreak{}database/\allowbreak{}tooling metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-repository-safety & \hyperlink{phase-row-21-2-1}{21.2.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX13}{CEX13} & GitHub Actions Lean-build and snapshot-artifact pipeline & Tool;\newline Infrastructure;\newline Object & F1 & current & \cellcolor{white}W & CI pipeline contract that runs the pinned Lean/\allowbreak{}Lake build and declared scans, then emits versioned artifacts carrying commit\_sha, lean\_toolchain, yaml\_hash and inventory\_hash. Green runs emit production-snapshot candidates for validated import;\newline red runs emit typed failure artifacts for phase-state transition and public failure-history visibility, never production-current data. & CNNA can automate Lean -> YAML/\allowbreak{}inventory -> artifact -> DB/\allowbreak{}Explorer only if CI status, toolchain and snapshot provenance are explicit and non-authoritative. & CEX12;\newline lean-toolchain;\newline lake-manifest;\newline generated\_exports;\newline repo\_inventory/\allowbreak{}raw\_export;\newline root README workflow & Not applicable;\newline CI/\allowbreak{}backup/\allowbreak{}database/\allowbreak{}tooling metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-ci-snapshot-bridge & \hyperlink{phase-row-21-2-2}{21.2.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX14}{CEX14} & Webhosting-local MySQL staging import, read-only swap and rollback contract & Database;\newline Mirror;\newline Object & F1 & current & \cellcolor{white}W & Webhosting/\allowbreak{}MySQL import contract in which green CI deploys generated production snapshot payloads, the server imports locally into staging tables, validates provenance/\allowbreak{}hash/\allowbreak{}row coverage, swaps the current read-only mirror atomically and preserves rollback/\allowbreak{}archive data. Red CI failure snapshots use a separate history/\allowbreak{}evidence channel and must not replace the current green mirror. & User clarified that the practical target is classic Webhosting plus MySQL;\newline robust deployment should avoid exposing production MySQL writes directly from CI where possible. & CEX2;\newline CEX12-CEX13;\newline MySQL-compatible schema;\newline Webhosting constraints;\newline backup storage policy & Not applicable;\newline CI/\allowbreak{}backup/\allowbreak{}database/\allowbreak{}tooling metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-database-deployment-safety & \hyperlink{phase-row-21-2-3}{21.2.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX15}{CEX15} & CI build-result phase-state controller and automatic repair-phase generator & Tool;\newline Infrastructure;\newline Object & F1 & current & \cellcolor{white}W & Deterministic controller that consumes GitHub Actions Lean build results for the active phase branch/\allowbreak{}PR and updates only generated planning-state metadata: red CI marks the attempted active phase red, emits a visible failure-history snapshot, and creates/\allowbreak{}activates a predecessor repair phase at the natural source layer;\newline green CI closes the active phase and advances exactly one cursor only with complete evidence. & User required full automation of the phase loop: Lean red -> active phase red plus predecessor repair phase;\newline Lean green -> phase completed plus next active phase selected. & CEX12-CEX14;\newline status legend;\newline phase/\allowbreak{}object/\allowbreak{}proof/\allowbreak{}scratchpad registers;\newline GitHub Actions run conclusion;\newline workflow artifacts/\allowbreak{}logs;\newline last green commit;\newline dependency graph and object-link policy & Not applicable;\newline CI/\allowbreak{}phase-governance metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-ci-phase-governance & \hyperlink{phase-row-21-2-4}{21.2.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-CEX16}{CEX16} & Red-build failure visibility snapshot and repair-phase publication channel & Database;\newline Mirror;\newline Object & F1 & current & \cellcolor{white}W & Contract for publishing failed Lean/\allowbreak{}scan runs as visible read-only failure-history snapshots. A red build records the attempted active phase, run/\allowbreak{}commit evidence, failed job/\allowbreak{}log/\allowbreak{}artifact pointers, generated predecessor repair phase and no-production-current-update proof, while preserving the last green production/\allowbreak{}current Explorer/\allowbreak{}MySQL mirror. & User corrected the red-path rule: a faulty build must also be visible, just like the generated predecessor repair phase;\newline hiding red runs would create a misleading public state and obscure provenance of repair phases. & CEX13-CEX15;\newline GitHub Actions red-run artifacts/\allowbreak{}logs;\newline phase\_state\_transition\_manifest.json;\newline generated repair-phase YAML patch;\newline last green production snapshot;\newline Explorer/\allowbreak{}API history schema & Not applicable;\newline CI/\allowbreak{}database/\allowbreak{}history metadata only. No mathematical CNNA computation and no Lean theorem is introduced. & critical-red-build-visibility & \hyperlink{phase-row-21-2-5}{21.2.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-B07}{B07} & Complement-net modular B core chain & Lean;\newline Target;\newline Object & F0 & current & \cellcolor{red!20}R & Chain object for ComplementLocalNet/\allowbreak{}ComplementStateNet/\allowbreak{}ComplementGNS/\allowbreak{}SeparatingProperty/\allowbreak{}TomitaTakesakiData/\allowbreak{}ModularConjugation/\allowbreak{}ComplementKMS/\allowbreak{}ComplementSpectrumCondition/\allowbreak{}BisognanoWichmannSeed. & Original roadmap modular B chain sheet, but only as reference;\newline actual source must be A->B handoff and B local-net/\allowbreak{}state data. & A->B bright/\allowbreak{}interface handoff;\newline B local net;\newline state family;\newline GNS data;\newline separating property;\newline modular data;\newline spectrum condition. & No operational ExecComplex path;\newline analytic/\allowbreak{}operator-algebraic profile only after finite/\allowbreak{}exact source gates exist. & high & \hyperlink{phase-row-13-8}{13.8}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-B08}{B08} & Nuclearity/\allowbreak{}DHR/\allowbreak{}DR reconstruction bridge & Lean;\newline Target;\newline Object & F0 & current & \cellcolor{red!20}R & Bridge object for NuclearitySeed/\allowbreak{}Nuclearity, DHRSectorsSeed, FieldAlgebraReconstructionSeed and ChargeStatisticsCoherence above the modular B core. & Original roadmap 6g-6i extension;\newline reference target only until derived from B modular/\allowbreak{}local-net sources. & B07;\newline Haag-Kastler/\allowbreak{}quasilocal net data;\newline split/\allowbreak{}nuclearity target;\newline localized sector data;\newline charge/\allowbreak{}statistics coherence gate. & No ExecComplex path;\newline may have finite toy mirrors only as comparison after exact gate profiles exist. & high & \hyperlink{phase-row-13-9}{13.9}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-PC00}{PC00} & ParameterClosure chain & Lean;\newline Target;\newline Object & F0 & current & \cellcolor{red!20}R & Derived-only closure chain for BranchingWitness, spectral/\allowbreak{}branching/\allowbreak{}backreaction selectors, ParameterClosure, HorizonLevel, EffectiveLambda, BackreactionFixedPoint and RegularizationClosure. & Original roadmap PC-a-PC-d chain;\newline actual provenance must come from C channels/\allowbreak{}backreaction and A/\allowbreak{}D source maps. & BranchingWitness;\newline UVSpectralSelector;\newline BranchingSelector;\newline BackreactionSelector;\newline C channel/\allowbreak{}entropy data;\newline D geometry prerequisites. & May expose computable finite selectors if derived;\newline no primitive beta/\allowbreak{}Lmax/\allowbreak{}b/\allowbreak{}regularizer export permitted after closure. & high & \hyperlink{phase-row-15-5}{15.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-D04}{D04} & LCQFT/\allowbreak{}Hadamard/\allowbreak{}Wick D gate chain & Lean;\newline Target;\newline Object & F0 & current & \cellcolor{red!20}R & D-chain object for DerivedSpacetime, InterfaceCausality, LocalCovariance, RelativeCauchyEvolution, DynamicalLocality, HadamardStateSeed, MicrolocalSpectrumGate, LocalWickPolynomialsSeed, DerivedStressTensorSeed and later NCG comparison seeds. & Original roadmap D minimal file tree;\newline actual provenance must be A/\allowbreak{}C geometry exports, ParameterClosure and B modular compatibility where required. & D input contract;\newline PC00;\newline InterfaceCausality;\newline LocalCovariance;\newline Hadamard/\allowbreak{}microlocal/\allowbreak{}Wick data;\newline B modular prerequisites for QFT comparison. & No operational ExecComplex path by default;\newline finite/\allowbreak{}spectral mirrors must remain explicit comparison layers. & high & \hyperlink{phase-row-15-6}{15.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-DE00}{DE00} & D/\allowbreak{}E bridge gate chain & Lean;\newline Target;\newline Object & F0 & current & \cellcolor{red!20}R & Bridge object ordering D local covariance, Hadamard/\allowbreak{}Wick layers, DHR/\allowbreak{}DR reconstruction, CPTGate, StatisticsGate, KramersGate and charge/\allowbreak{}statistics coherence before matter promotion. & Original roadmap D/\allowbreak{}E bridge chain sheet and E Vorzone;\newline reference/\allowbreak{}migration evidence only until derived. & D04;\newline B07/\allowbreak{}B08;\newline DHR/\allowbreak{}DR sector data;\newline CPT/\allowbreak{}statistics/\allowbreak{}Kramers gates;\newline FieldAlgebraReconstructionSeed. & No ExecComplex path;\newline formal gate profile and later comparison layers only. & high & \hyperlink{phase-row-16-5}{16.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-E04}{E04} & Feynman matter audit gate & Lean;\newline Target;\newline Object & F0 & current & \cellcolor{red!20}R & Planning and future gate object enforcing that time reversal alone is not matter and that antiparticle/\allowbreak{}charge dictionary, spinor representation, CAR/\allowbreak{}Fock/\allowbreak{}statistics sign and charge-statistics coherence must precede matter promotion. & Original roadmap Feynman audit;\newline established physics used only as target/\allowbreak{}check, not as input. & B modular/\allowbreak{}spectrum data;\newline D causality/\allowbreak{}local covariance;\newline DHR/\allowbreak{}DR/\allowbreak{}field algebra reconstruction;\newline CPT/\allowbreak{}statistics/\allowbreak{}Kramers gates. & No ExecComplex path;\newline may have finite toy models only after exact source gates exist. & high & \hyperlink{phase-row-16-5}{16.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-E05}{E05} & Particle/\allowbreak{}scattering/\allowbreak{}IR horizon window & Reference;\newline Gate;\newline Object & F1 & current & \cellcolor{black!18}K & Late non-core horizon object for ClusterDecompositionSeed, HaagRuelleSeed, ParticleInterpretationWindow and InfraredChargeClassSeed. & Original roadmap late horizon layer;\newline maintained as future/\allowbreak{}reference target, not current core blocker. & ComplementSpectrumCondition;\newline charge reconstruction;\newline spectral control;\newline cluster diagnostics;\newline long-range/\allowbreak{}IR charge data if derived. & No operational path until finite/\allowbreak{}spectral/\allowbreak{}charge source data exist;\newline window remains explicitly marked. & medium & \hyperlink{phase-row-16-6}{16.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RDV0}{RDV0} & Original roadmap source/\allowbreak{}definition/\allowbreak{}notation audit ledger & Documentation;\newline Object & F1 & current & \cellcolor{black!18}K & Ledger enforcing source hierarchy, maturity mapping, canonical definition catalog and notation/\allowbreak{}register separation from the original roadmap. & Uploaded roadmap sections Dokumenttyp/\allowbreak{}Quellenhierarchie/\allowbreak{}Definitionskatalog/\allowbreak{}Notationspflicht/\allowbreak{}Register. & Uploaded roadmap;\newline current YAML object register;\newline CEX11 total declaration classification;\newline notation split phases. & Tool/\allowbreak{}planning only;\newline no ExecComplex path. & medium & \hyperlink{phase-row-22-0}{22.0}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RDV1}{RDV1} & Roadmap migration disposition ledger & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{black!18}K & Ledger classifying legacy modules/\allowbreak{}objects as direct port, semantic rewrite, bright-special-case regression oracle or late seed/\allowbreak{}diagnostic. & Uploaded roadmap migration law and extended module matrix. & Legacy module inventory;\newline current module/\allowbreak{}object register;\newline migration law categories. & Tool/\allowbreak{}planning only. & high & \hyperlink{phase-row-22-1}{22.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RDV2}{RDV2} & Roadmap de-seeding/\allowbreak{}regression/\allowbreak{}rollback workflow ledger & Governance;\newline Policy;\newline Object & F1 & current & \cellcolor{black!18}K & Ledger for de-seeding preconditions, old-path regression, immediate readability/\allowbreak{}neutral naming and rollback artifact duties. & Uploaded roadmap operative rules. & Seed/\allowbreak{}Scaffold/\allowbreak{}Window candidate modules;\newline source maps;\newline derived-only gates;\newline notation targets;\newline importgraph/\allowbreak{}rollback records. & Tool/\allowbreak{}planning only. & high & \hyperlink{phase-row-22-2}{22.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RDV3}{RDV3} & Roadmap modular B gate-sheet ledger & Reference;\newline Gate;\newline Object & F1 & current & \cellcolor{black!18}K & Ledger recording modular B chain and physical-completeness gates from the original roadmap. & Uploaded roadmap B chain sheets and gate tables. & B07;\newline B08;\newline phases 13.8-13.9;\newline HK/\allowbreak{}quasilocal and modular prerequisites. & Tool/\allowbreak{}planning only. & medium & \hyperlink{phase-row-22-3}{22.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RDV4}{RDV4} & Roadmap ParameterClosure gate-sheet ledger & Reference;\newline Gate;\newline Object & F1 & current & \cellcolor{black!18}K & Ledger recording PC-a-PC-d and rest-parameter de-primitive duties. & Uploaded roadmap ParameterClosure chain sheet. & PC00;\newline phases 15.5/\allowbreak{}17;\newline selector/\allowbreak{}closure/\allowbreak{}fixed-point prerequisites. & Tool/\allowbreak{}planning only. & medium & \hyperlink{phase-row-22-4}{22.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RDV5}{RDV5} & Roadmap D/\allowbreak{}E bridge and local-covariance gate-sheet ledger & Reference;\newline Gate;\newline Object & F1 & current & \cellcolor{black!18}K & Ledger recording D minimal file tree, LCQFT/\allowbreak{}Hadamard/\allowbreak{}Wick/\allowbreak{}StressTensor gates and D/\allowbreak{}E bridge ordering. & Uploaded roadmap D file tree and D/\allowbreak{}E chain sheet. & D04;\newline DE00;\newline phases 15.6/\allowbreak{}16.5. & Tool/\allowbreak{}planning only. & medium & \hyperlink{phase-row-22-5}{22.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RDV6}{RDV6} & Roadmap Feynman/\allowbreak{}scattering/\allowbreak{}IR audit ledger & Reference;\newline Gate;\newline Object & F1 & current & \cellcolor{black!18}K & Ledger recording Feynman matter-audit constraints and late particle/\allowbreak{}scattering/\allowbreak{}IR horizon windows. & Uploaded roadmap Feynman audit and late horizon section. & E04;\newline E05;\newline B/\allowbreak{}D/\allowbreak{}E prerequisite gates. & Tool/\allowbreak{}planning only. & medium & \hyperlink{phase-row-22-6}{22.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RLC0}{RLC0} & REALOQS v0.0605 legacy source inventory ledger & Legacy;\newline Code;\newline Reference;\newline Object & F1 & current & \cellcolor{black!18}K & Archived scan ledger for the uploaded REALOQS v0.0605 stable source, with module/\allowbreak{}declaration/\allowbreak{}AQFT/\allowbreak{}noncomputable/\allowbreak{}simp/\allowbreak{}sorry metrics. & Static scan of uploaded REALOQS v0.0605 source zip. & 270 Lean files;\newline 1727 declarations;\newline 88 PillarB files;\newline 62 PillarB/\allowbreak{}AQFT files;\newline 596 AQFT declarations;\newline no sorry/\allowbreak{}admit/\allowbreak{}axiom hits found by text scan. & Tool/\allowbreak{}planning only at this stage;\newline no ExecComplex path and no CNNA Lean object until a later derived-only phase constructs one. & high & \hyperlink{phase-row-23-0}{23.0}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RLC1}{RLC1} & REALOQS AQFT foundation migration-disposition ledger & Legacy;\newline Code;\newline Reference;\newline Object & F1 & current & \cellcolor{red!20}R & Ledger classifying legacy AQFT foundation objects as target profile, semantic rewrite, mathlib replacement candidate, regression-only or reject/\allowbreak{}defer. & Legacy AQFT foundation modules in REALOQS/\allowbreak{}PillarB/\allowbreak{}AQFT. & StarAlgebra, StateOn, CStarStateOn, CStarAlgebraBundle, LocalStarAlgebraNet and StateNet legacy structures. & Tool/\allowbreak{}planning only at this stage;\newline no ExecComplex path and no CNNA Lean object until a later derived-only phase constructs one. & high & \hyperlink{phase-row-23-1}{23.1}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RLC2}{RLC2} & REALOQS-to-CNNA A->B handoff compatibility ledger & Legacy;\newline Code;\newline Reference;\newline Object & F1 & current & \cellcolor{red!20}R & Ledger identifying legacy B dependencies on A internals/\allowbreak{}configs and mapping them to allowed CNNA A->B handoff replacements. & Legacy Derived/\allowbreak{}TreeOfCliquesFromPillarA and Meta/\allowbreak{}PillarB code;\newline current CNNA A->B handoff discipline. & Legacy import/\allowbreak{}use patterns that must be inverted before CNNA PillarB can consume them. & Tool/\allowbreak{}planning only at this stage;\newline no ExecComplex path and no CNNA Lean object until a later derived-only phase constructs one. & high & \hyperlink{phase-row-23-2}{23.2}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RLC3}{RLC3} & REALOQS boundary-matrix AQFT rewrite ledger & Legacy;\newline Code;\newline Reference;\newline Object & F1 & current & \cellcolor{red!20}R & Ledger for rewriting the advanced legacy BoundaryMatrix AQFT layer from CNNA boundary-operator data, with noncomputable isolation. & 28 legacy BoundaryMatrix derived AQFT modules. & BoundaryMatrix algebra/\allowbreak{}CStar/\allowbreak{}dynamics/\allowbreak{}exp/\allowbreak{}Gibbs/\allowbreak{}KMS/\allowbreak{}GNS/\allowbreak{}modular/\allowbreak{}split/\allowbreak{}locality/\allowbreak{}state-net code. & Tool/\allowbreak{}planning only at this stage;\newline no ExecComplex path and no CNNA Lean object until a later derived-only phase constructs one. & high & \hyperlink{phase-row-23-3}{23.3}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RLC4}{RLC4} & REALOQS Haag-Kastler gate extraction ledger & Legacy;\newline Code;\newline Reference;\newline Object & F1 & current & \cellcolor{red!20}R & Ledger extracting isotony, locality, additivity, covariance, spectrum, vacuum, time-slice, strong-additivity and split-property target gates from legacy code. & Legacy PillarB/\allowbreak{}Gates/\allowbreak{}HaagKastler and AQFT/\allowbreak{}HaagKastler modules. & HK predicates and gate theorems to be re-ordered behind CNNA-derived local-net and spacetime prerequisites. & Tool/\allowbreak{}planning only at this stage;\newline no ExecComplex path and no CNNA Lean object until a later derived-only phase constructs one. & high & \hyperlink{phase-row-23-4}{23.4}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RLC5}{RLC5} & REALOQS state-GNS-KMS-modular route map & Legacy;\newline Code;\newline Reference;\newline Object & F1 & current & \cellcolor{red!20}R & Route map for state restriction, state nets, global state cones, GNS, dynamics/\allowbreak{}KMS, modular data and time-orientation/\allowbreak{}time-reversal comparisons. & Legacy AQFT State, StateNet, GlobalCone, GNS, KMS, TimeOrientation, TimeReversal, RelativeEntropy and derived modules. & Target sequence and risk notes for future CNNA PillarB state/\allowbreak{}modular reconstruction. & Tool/\allowbreak{}planning only at this stage;\newline no ExecComplex path and no CNNA Lean object until a later derived-only phase constructs one. & high & \hyperlink{phase-row-23-5}{23.5}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RLC6}{RLC6} & REALOQS quasi-local split/\allowbreak{}nuclearity horizon map & Legacy;\newline Code;\newline Reference;\newline Object & F1 & current & \cellcolor{red!20}R & Horizon ledger aligning legacy quasi-local and split-property code with future CNNA modular B, nuclearity and DHR/\allowbreak{}DR consistency checks. & Legacy AQFT/\allowbreak{}QuasiLocal and split modules plus roadmap B08. & QuasiLocal carrier/\allowbreak{}completion/\allowbreak{}star/\allowbreak{}state-lift structures and split/\allowbreak{}nuclearity target boundary. & Tool/\allowbreak{}planning only at this stage;\newline no ExecComplex path and no CNNA Lean object until a later derived-only phase constructs one. & high & \hyperlink{phase-row-23-6}{23.6}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RLC7}{RLC7} & REALOQS examples/\allowbreak{}meta quarantine and regression ledger & Legacy;\newline Code;\newline Reference;\newline Object & F1 & current & \cellcolor{red!20}R & Ledger quarantining legacy examples/\allowbreak{}meta active-path files while extracting regression expectations and old-path oracles. & Legacy Examples/\allowbreak{}TreeOfCliques\_AQFT\_* and Meta/\allowbreak{}PillarB\_* modules. & Example/\allowbreak{}meta proofs that may become tests, not source objects or public API. & Tool/\allowbreak{}planning only at this stage;\newline no ExecComplex path and no CNNA Lean object until a later derived-only phase constructs one. & high & \hyperlink{phase-row-23-7}{23.7}\\
\hline
\addlinespace[0.24em]
\hyperlink{object-row-RLC8}{RLC8} & REALOQS declaration crosswalk and Explorer legacy overlay ledger & Legacy;\newline Code;\newline Reference;\newline Object & F1 & current & \cellcolor{red!20}R & Ledger mapping legacy declarations to CNNA target gates, owner buckets, lifecycle states and Explorer-visible legacy/\allowbreak{}reference nodes. & RLC0-RLC7;\newline CEX11 total declaration taxonomy;\newline Explorer semantic graph schema. & Declaration-level crosswalk and edge semantics for non-CNNA legacy overlay. & Tool/\allowbreak{}planning only at this stage;\newline no ExecComplex path and no CNNA Lean object until a later derived-only phase constructs one. & high & \hyperlink{phase-row-23-8}{23.8}\\
\hline
\addlinespace[0.24em]
\end{longtable}
\arrayrulecolor{black}
\normalsize
