\small
\arrayrulecolor{black!22}
\begin{longtable}{L{0.075\linewidth} L{0.245\linewidth} L{0.315\linewidth} L{0.315\linewidth}}
\hline
\textbf{Kind} & \textbf{Meaning} & \textbf{Required evidence} & \textbf{Rendering rule}\\
\hline
\endfirsthead
\hline
\textbf{Kind} & \textbf{Meaning} & \textbf{Required evidence} & \textbf{Rendering rule}\\
\hline
\endhead
direct & Phase directly owns registered object(s). & At least one object has Phase exactly equal to the phase id. & Render direct object hyperlinks. Do not aggregate child phase objects as direct ownership.\\
\hline
\addlinespace[0.24em]
scope\_only & Phase is an umbrella/\allowbreak{}routing/\allowbreak{}scope phase;\newline objects are owned by child phases. & No direct objects and at least one descendant phase has direct object(s). & Render scope-only plus a bounded child-object summary.\\
\hline
\addlinespace[0.24em]
no\_direct\_object & Phase intentionally has no direct object, e.g. baseline, audit, closeout, generator/\allowbreak{}view infrastructure without object ownership. & No direct objects and no descendant-object ownership needed for the phase semantics, plus explanation. & Render no direct object with reason;\newline never leave cell blank.\\
\hline
\addlinespace[0.24em]
moved & Historical placeholder or routing note whose active objects are owned elsewhere. & Main goal/\allowbreak{}definition/\allowbreak{}proof goal identifies the destination phase or ownership move. & Render moved placeholder and reason/\allowbreak{}destination;\newline no direct object links unless the placeholder also owns an explicit audit object.\\
\hline
\addlinespace[0.24em]
\end{longtable}
\arrayrulecolor{black}
\normalsize
