\footnotesize
\par\smallskip\noindent\begin{minipage}{0.99\linewidth}\footnotesize\raggedright\textbf{Table legend.} \colorbox{green!18}{\strut G} = green/closed and derived-only; \colorbox{orange!28}{\strut O} = orange/implementable after stated predecessor closure; \colorbox{yellow!25}{\strut Y} = yellow/active and implementable now; \colorbox{red!20}{\strut R} = red/locked Lean-derivation phase; release requires derived-only object/proof evidence. Context class is orthogonal to status.\end{minipage}\par\vspace{0.25em}
\arrayrulecolor{black!22}
\begin{longtable}{L{0.095\linewidth} L{0.055\linewidth} L{0.04\linewidth} L{0.105\linewidth} L{0.19\linewidth} L{0.25\linewidth} L{0.07\linewidth} L{0.135\linewidth}}
\hline
\textbf{ID} & \textbf{Phase} & \textbf{Status} & \textbf{Scope} & \textbf{Predecessors} & \textbf{Proof risk} & \textbf{Addressing?} & \textbf{Addressing phase}\\
\hline
\endfirsthead
\hline
\textbf{ID} & \textbf{Phase} & \textbf{Status} & \textbf{Scope} & \textbf{Predecessors} & \textbf{Proof risk} & \textbf{Addressing?} & \textbf{Addressing phase}\\
\hline
\endhead
PIC-2026-05-10-001 & 1.1.1.2 & \cellcolor{orange!28}O & after-listed-predecessors & 1.1.1.1.5.5;\newline LEG37-LEG41 & low/\allowbreak{}none: planning/\allowbreak{}generator ledger phase;\newline no Lean source edit expected. & no & none-required\\
\hline
\addlinespace[0.24em]
PIC-2026-05-10-002 & 1.1.1.3 & \cellcolor{orange!28}O & after-listed-predecessors & 1.1.1.2 & low/\allowbreak{}none: public API contract/\allowbreak{}consumer whitelist planning phase;\newline no Lean wrapper creation expected. & no & none-required\\
\hline
\addlinespace[0.24em]
PIC-2026-05-10-003 & 1.1.1.4 & \cellcolor{orange!28}O & after-listed-predecessors & 1.1.1.2;\newline 1.1.1.3 & low unless converted into deletion/\allowbreak{}removal work;\newline as ledger-only pruning classification no Lean source edit is expected. & no & none-required\\
\hline
\addlinespace[0.24em]
PIC-2026-05-10-004 & 1.1.1.5 & \cellcolor{orange!28}O & after-listed-predecessors & 1.1.1.2;\newline 1.1.1.3;\newline 1.1.1.4 & low/\allowbreak{}none for parent closeout;\newline future 1.1.1.5.x tool phases are separate and not prerequisites unless explicitly listed. & no & none-required\\
\hline
\addlinespace[0.24em]
PIC-2026-05-10-005 & 1.1.1.1.5 & \cellcolor{yellow!25}Y & now & none beyond current green path through 1.1.1.1.4 & low for audit;\newline medium for any later actual refactor because compatibility facades and full local build evidence are mandatory. & no red phase yet;\newline this phase itself is the proactive addressing gate & none-required-now\\
\hline
\addlinespace[0.24em]
PIC-2026-05-10-006 & 1.1.1.1.5.1 & \cellcolor{yellow!25}Y & now & closed governance path through 1.1.1.1.4 and V1.20 documentation/\allowbreak{}tooling updates & low for audit;\newline later refactor phases require local full-build evidence. & already generated child sequence & 1.1.1.1.5.1-1.1.1.1.5.5\\
\hline
\addlinespace[0.24em]
\end{longtable}
\arrayrulecolor{black}
\normalsize
