\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,longtable,array,enumitem}
\usepackage{etoolbox}
\usepackage{xcolor}
\usepackage{url}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}

% Uniform table typography: all table bodies use the same size as the finite-quantity table.
\AtBeginEnvironment{longtable}{\scriptsize\setlength{\tabcolsep}{3pt}}
\AtBeginEnvironment{tabular}{\scriptsize\setlength{\tabcolsep}{3pt}}
% Table rules: row separators are hairlines; the header rule is slightly heavier.
\setlength{\arrayrulewidth}{0.035pt}
\setlength{\lightrulewidth}{0.16pt}
\setlength{\cmidrulewidth}{0.16pt}
\setlength{\heavyrulewidth}{0.12pt}
\emergencystretch=4em
\sloppy
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue,pdftitle={On the Provenance of a Pre-Complex Body: A Finite Real Response-Algebra Core},pdfauthor={Jan Seeck}}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{corollary}[definition]{Corollary}
\theoremstyle{remark}
\newtheorem{remark}[definition]{Remark}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\src}[1]{{\scriptsize\path{#1}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\eps}{\varepsilon}
\newcommand{\CNNA}{\mathrm{CNNA}}
\newcommand{\doi}[1]{\href{https://doi.org/#1}{doi:\nolinkurl{#1}}}
\newcommand{\arxivref}[1]{\href{https://arxiv.org/abs/#1}{arXiv:\nolinkurl{#1}}}
\numberwithin{equation}{section}
\setlist[enumerate]{leftmargin=*,itemsep=0.25em}
\setlist[itemize]{leftmargin=*,itemsep=0.25em}
\begin{document}
\title{On the Provenance of a Pre-Complex Body: A Finite Real Response-Algebra Core}
\author{Jan Seeck\\Independent researcher\\\texttt{jan.seeck1@gmail.com}}
\date{Finite code snapshot: July 10, 2026\\Documentation revision: July 17, 2026}
\maketitle
\begin{abstract}
This article presents the discrete--finite core of the ComplemeNt Net Architecture (CNNA), initialized by an empty configuration and generated by an explicit deterministic rule family. The rooted carrier is not introduced as a discretization of a pre-existing space or spacetime, but as a finite, deterministic, and exactly inspectable substrate for genealogical provenance and boundary reduction. The structural index \(b\), depth cutoff \(L\), mode \(m\), and update schedule \(\mathfrak{s}\) are distinct; reference calculations fix \(m\) and \(\mathfrak{s}\) by stated commands rather than deriving them from the empty configuration. The term complement has a precise birth-relative meaning: an accepted birth enlarges the finite vertex carrier by a disjoint singleton coordinate, while a causal-layer update enlarges it by the direct sum of all newborn coordinates in that layer. These new carrier directions are then coupled to the existing network by directed parent--child, ancestor, and sibling weights. The implementation produces finite histories, terminal carriers, directed live and record edge layers, and a symmetrized control, without continuum fields, integrals, differential operators, or limits. For fixed inputs it computes carrier states, projectivity and orientation diagnostics, Schur-complement responses, symmetric/skew decompositions, finite \(J\)-objects, finite algebra and GNS quotients, local operator checks, sign transport, and live--record backreaction observables. Every reported object is a finite array, edge dictionary, matrix, residual, or generated row.

Dirichlet-to-Neumann terminology refers only to finite weighted networks: the maps are explicit Schur complements with declared boundary/interior partitions and residuals. No analytic boundary calculus is assumed. The calculations distinguish directed live and record structures from the symmetrized control and expose satisfied and failed finite properties. The relation to recent growing-tree models, finite-network effective operators, and tree Dirichlet-to-Neumann constructions is stated by explicit model-separation criteria rather than by a literature-wide novelty claim.

The result is not an infinite or continuum theory. It includes an exact, linearly growing real carrier system with non-unital corner embeddings, while independently reconstructed response, state, GNS, and finite-\(J\) objects retain quantified interlevel drift. Infinite completions, convergence claims, and continuum comparisons remain separate problems.
\end{abstract}
\newpage
\tableofcontents
\newpage

\section{Methodological position and scope}\label{sec:methodological-position}
The present construction is not introduced as a finite-dimensional approximation of an already specified quantum theory. Its question is logically prior: which response-theoretic and algebraic structures can be constructed before a complex Hilbert space, a complex observable algebra, a Hamiltonian, or a continuum geometry is assumed? The dependency order investigated here is
\begin{equation}
\begin{gathered}
  \emptyset
  \longrightarrow
  \text{finite }b\text{-ary address growth}
  \longrightarrow
  \text{birth-relative real carrier complements},\\
  \text{carrier complements}
  \longrightarrow
  \text{directed record/live weights}
  \longrightarrow
  \text{finite Schur boundary response},\\
  \Lambda^{\rm dir}
  \longrightarrow
  S=\tfrac12\bigl(\Lambda^{\rm dir}+(\Lambda^{\rm dir})^T\bigr),\\
  \Lambda^{\rm dir}
  \longrightarrow
  A=\tfrac12\bigl(\Lambda^{\rm dir}-(\Lambda^{\rm dir})^T\bigr),\\
  (S,A)
  \longrightarrow
  \text{finite real algebra}
  \longrightarrow
  \text{positive state},\\
  \text{positive state}
  \longrightarrow
  \text{real GNS quotient}
  \longrightarrow
  \text{finite complex-structure candidate}.
\end{gathered}
\label{eq:finite-provenance-chain}
\end{equation}
Here complement is not a metaphor and not a claim about an operator-algebraic commutant. At a birth event it is first the exact set-theoretic and coordinate-linear decomposition of the post-birth carrier into the pre-birth carrier and the newborn coordinate. The directed weights subsequently couple that new direction to the prior network. The skew sector is therefore not supplied by the word complement itself: it can occur only because the coupling rule is directed and because the resulting asymmetry survives the selected Schur reduction. Section~\ref{sec:birth-relative-complement} states these distinctions formally.

\paragraph{Substrate-selection criterion.}
The carrier choice follows a non-circularity requirement. If continuum geometry, spacetime, the causal and metric structure of spacetime, or complex-linear kinematics are among the structures whose provenance is under investigation, they cannot simultaneously be inserted as primitive input. The finite core therefore starts with neither a manifold, metric, measure, continuum field, differential operator, nor stochastic growth law. It requires instead a deterministic carrier that is finite at every stage, exposes every accepted growth event, has exact genealogical addresses, supports nontrivial branching, and admits explicit finite boundary elimination.

Subject to these requirements, rooted $b$-ary trees with $b\geq 2$ are among the simplest sufficiently rich carriers. A path carrier is combinatorially simpler but has no sibling branching, whereas an arbitrary graph would add adjacency choices that are not yet derived at the initial stage. The selection is therefore a methodological minimality statement under the stated requirements, not a uniqueness theorem and not a claim that every alternative discrete substrate has been excluded.

Earlier work with post-critically finite Sierpi\'nski-type complexes informed this selection because their finite graph approximants and finite boundary sets support a rigorous theory of compatible resistance and Dirichlet forms, Laplacians, and spectral analysis~\cite{Kigami1993,Kigami2001,Strichartz2006}. That setting supplied a controlled example of hierarchical response theory without requiring a smooth manifold as the starting object and motivated the move to an explicit branching provenance carrier. In the present finite CNNA derivation, however, no Sierpi\'nski gasket or tetrahedron, Euclidean embedding, self-similar continuum set, resistance-form limit, or fractal Laplacian is an input. The rooted tree is the primitive provenance carrier. Any later relation between that tree and a Sierpi\'nski-type complex is a separate gluing or duality problem and must be constructed and checked independently.
This order differs from frameworks in which a complex operator algebra, a quantum state space, or prescribed finite-dimensional algebraic connecting data belong to the initial specification. For example, algebraic quantum field theory starts from local observable algebras and their structural relations~\cite{HaagKastler1964}; AF constructions start from finite-dimensional $C^*$-algebras together with embedding data~\cite{Bratteli1972}; and finitely correlated spin-chain states start from a finite-dimensional auxiliary algebra and a positive map~\cite{FannesNachtergaeleWerner1992}. These comparisons locate the logical starting point of the present work; they do not assert equivalence with those theories.

A closer methodological comparator is the construction of complex structures on real jet spaces by Finster and Kamran~\cite{FinsterKamran2021}. In the setting of causal variational principles, conserved surface-layer forms are used to define an almost-complex structure, and additional conditions are analyzed under which it gives a canonical complex structure that combines with a scalar product to form a complex Hilbert space and subsequently supports bosonic Fock-space dynamics. The present article neither adopts a causal variational principle nor starts from jet spaces or surface-layer forms. It begins instead with finite real network growth and boundary response and asks whether a skew-response sector, a real algebra, a state, a real GNS quotient, and a finite $J$-candidate can be obtained along that explicit dependency chain. Consequently, unresolved sign and interlevel-naturality defects are retained as finite obstructions rather than removed by assuming the additional conditions required for a canonical complex structure. The relation between the two approaches is therefore a shared provenance question, not an identity of primitives, constructions, or results.

The distinction does not lie in the individual mathematical tools. Schur complements, finite network response maps, finite matrix algebras, positive functionals, and GNS constructions are established structures. The specific object investigated here is their connection by an explicit finite provenance chain whose interfaces are audited for hidden dependencies. The tree is therefore not interpreted directly as physical space, spacetime, or an observable algebra. It first records genealogical provenance. Each accepted address adds an exactly identifiable carrier direction complementary to the carrier already present at that update; the network character begins when this direction is coupled by the generated directed weights. Candidate observable structure appears only after this complement-coupling step, live--record separation, boundary reduction, and algebra generation.

In particular, the complex unit is not inserted through the scalar field of the initial construction. A real skew-response sector is constructed first, and only then is a finite operator $J$ tested for the algebraic relation associated with a complex structure. The residual transformation $J\mapsto-J$ is retained as an obstruction whenever the available real data do not distinguish the two orientations. Thus a successful finite $J$ test is not itself an absolute orientation theorem.

The finite restriction is deliberate. Every node, edge, response matrix, algebra generator, state, quotient operation, and residual remains explicitly inspectable. No continuum limit, von Neumann closure, modular flow, or type classification is used to justify an earlier stage of the construction. The results should therefore be read as a finite structure theory: they determine what can already be constructed or excluded at finite depth and identify the additional compatibility conditions required for an infinite operator-algebraic handoff.

The novelty claim is correspondingly limited. The article does not claim that its constituent techniques are individually new, that no related provenance-oriented construction exists, or that the finite core already defines a quantum field theory, an inductive-limit $C^*$-algebra, or a continuum spacetime model. It claims a specific auditable architecture and the finite results proved or computed within that architecture.

\paragraph{Development note.} The line of inquiry leading to the present finite core has evolved through more than four years of independent study, implementation, rejected constructions, falsification, and progressive scope reduction. Parts of this development are preserved in public, time-stamped records beginning in late 2021, including contemporaneous forum discussions; some intervening material is no longer completely recoverable. These records document the continuity and changing scope of the inquiry, not the prior existence of CNNA in its present form. Earlier exploratory formulations considered broader deterministic, fractal, network, open-system, and operator-algebraic interpretations. They are not used as premises or evidence in this article. The present work deliberately retains only the finite definitions, source-level constructions, generated results, and explicit obstructions reproducible from the supplied package. The documented history establishes the provenance of the inquiry, not the validity of its mathematical claims, which stand or fall on the construction and checks presented here.


\section{Recent related work and model separation}\label{sec:related-work}
The phrase \emph{growing tree} covers several mathematically distinct constructions. In one class the finite combinatorial carrier itself changes by the addition, deletion, or rearrangement of vertices and edges. In another class a random subtree, occupied cluster, or labeling grows inside a maximal or already specified carrier. A third class keeps the graph fixed and constructs or reconstructs a boundary-response operator on that graph. These distinctions matter here because the present finite core combines carrier growth, an immutable birth record, later updates of a separate live layer, directed real couplings, and a forward Schur boundary reduction. No single shared noun such as ``tree'', ``growth'', or ``Dirichlet-to-Neumann map'' is sufficient to identify the constructions.

\subsection{Comparison criteria}
The comparisons below use the following explicit questions.
\begin{enumerate}
\item What is primitive input: a maximal tree, a finite tree, a metric or quantum graph, or only a root and a branching bound?
\item What actually grows: the carrier, a selected subtree or occupation pattern, a labeling, or only an associated response matrix?
\item Is the evolution deterministic or stochastic, and is its ordering sequential, generation-wise, or synchronous on an active frontier?
\item Are previously accepted vertices and genealogical addresses preserved, or can the earlier tree be rearranged during a growth step?
\item Is there a birth-relative immutable record distinct from a state that is updated by later births?
\item Is a boundary response constructed, and if so, is it a forward finite Schur response or an inverse reconstruction problem?
\end{enumerate}
These criteria are descriptive. They locate the finite CNNA core among adjacent models without asserting that the cited sample exhausts the literature on random trees, branching processes, graph growth, or inverse problems.

\subsection{Recent tree-growth models}
Marckert constructs a sequence of uniformly distributed rooted $d$-ary trees in which the passage from size $n-1$ to size $n$ adds a node and rearranges part of the previous tree~\cite{Marckert2023}. This is a genuine carrier-growth construction and therefore a close combinatorial comparator. Its purpose is uniform random generation, however, and the rearrangement step means that the earlier finite tree is not retained as an immutable genealogical record in the sense used here.

Fredes and Marckert study and survey models of random subtrees of a connected graph, including uniform sampling of an $n$-vertex subtree of a specified ambient graph~\cite{FredesMarckert2023}. This cleanly illustrates the second meaning of growth used above: the selected subtree changes while the ambient carrier is already present. The present finite core instead treats accepted births as enlargements of the carrier itself; it does not sample an occupied subtree of a pre-existing graph.

Dunlop and Mardin study bounded-generation Bienaym\'e--Galton--Watson trees with nearest-neighbor ancestor interaction~\cite{DunlopMardin2022}. A random configuration is represented as a rooted subtree of a specified maximal tree, and the offspring variables and coupling determine the probability law. Thus the maximal carrier and stochastic law are primitive, whereas the present construction uses a deterministic accepted-birth sequence on the finite carrier and separates the frozen birth record from the subsequently updated live response.

Bodini, Genitrini, Mailler, and Naima study increasing and strict monotonic Schr\"oder trees generated by evolutionary rules in which labels encode the chronological order of branching events~\cite{BodiniGenitriniMaillerNaima2022}. Their first model selects one leaf at each step, while the strict monotonic model can select several leaves carrying the same chronological label. These are direct comparators for sequential versus synchronized event order. Their chronology is explicit in the labeling rule and supports random-tree enumeration and sampling; it is not a split between an immutable edge record and a later-updated network response.

Bodini, Genitrini, and Nurligareev introduce growing binary trees with internal nodes, active leaves, and dead leaves~\cite{BodiniGenitriniNurligareev2026}. Starting from one active leaf at $t=0$, every active leaf is synchronously replaced at each positive integer time either by a dead leaf or by an internal binary branch. This provides a particularly direct comparator for the \code{layer\_batch} control schedule: both organize a whole active frontier by discrete layers. The cited model adds an extinction rule and develops enumerative and sampling results; it does not construct birth-relative record/live edge layers or a network response that feeds back on previously born vertices.

\subsection{Recent boundary-response constructions on trees and finite networks}
Gernandt and Rohleder recover a finite weighted tree and its positive edge weights from the Dirichlet-to-Neumann matrix of its graph Laplacian~\cite{GernandtRohleder2022}. The tree and symmetric weighted Laplacian belong to a fixed inverse problem, and the boundary matrix is used to reconstruct weighted distances and hence the tree. The present direction is forward rather than inverse: the finite carrier and directed record/live weights are generated first, after which a selected boundary/interior partition is Schur-reduced.

Beard, Stefan, Viator, and Welters formulate effective operators for discrete electrical network problems by block-operator and Schur-complement methods and relate the finite-network effective operator to a discrete Dirichlet-to-Neumann map~\cite{BeardStefanViatorWelters2023}. This supplies a recent operator-theoretic comparator for finite elimination and variational response. Their graph and constitutive operator are fixed problem data; carrier growth, immutable birth provenance, and a directed record/live split are not part of that construction.

Peng and Song develop sparsified block elimination for Eulerian directed Laplacians, with augmented matrices whose Schur complements encode elimination errors~\cite{PengSong2022}. This confirms that Schur-based elimination has a substantial modern theory beyond symmetric graph Laplacians. The aim there is an approximate linear-system solver on a fixed directed Laplacian class; it is not an exact forward boundary response generated from a birth history, and it has no record/live distinction.

Avdonin, Khmelnytskaya, and Kravchenko give a progressive synthesis of the Weyl matrix, equivalently the transposed Dirichlet-to-Neumann map, of a quantum tree by successively attaching edges and computing the larger response from smaller ones~\cite{AvdoninKhmelnytskayaKravchenko2023}. This is especially relevant because both the tree and its boundary matrix are enlarged step by step. The quantum-tree setting nevertheless starts from metric edges, Sturm--Liouville equations, potentials, matching conditions, and a spectral parameter. The finite CNNA core starts instead from a real combinatorial carrier and directed finite weights and uses no differential equation or metric-edge input.

\begin{longtable}{>{\raggedright\arraybackslash}p{0.145\linewidth}>{\raggedright\arraybackslash}p{0.205\linewidth}>{\raggedright\arraybackslash}p{0.145\linewidth}>{\raggedright\arraybackslash}p{0.185\linewidth}>{\raggedright\arraybackslash}p{0.235\linewidth}}
\caption{Model-separation criteria for recent comparators. The entries summarize only the aspects relevant to the present finite construction.}\label{tab:recent-model-separation}\\
\toprule
\textbf{Comparator} & \textbf{Primitive carrier and actual growth} & \textbf{Order or randomness} & \textbf{Provenance and response} & \textbf{Exact separation from the present core}\\
\midrule
\endfirsthead
\toprule
\textbf{Comparator} & \textbf{Primitive carrier and actual growth} & \textbf{Order or randomness} & \textbf{Provenance and response} & \textbf{Exact separation from the present core}\\
\midrule
\endhead
Marckert~\cite{Marckert2023} & Rooted $d$-ary carrier grows by one node, with rearrangement of prior structure. & Random construction with uniform size-$n$ marginal. & No record/live response split; no Schur--DtN layer. & Close carrier-growth comparator, but previous genealogy may be rearranged and the objective is uniform random generation.\\
\hline
Fredes--Marckert~\cite{FredesMarckert2023} & Selected subtree of a fixed connected ambient graph. & Markov-chain and random sampling models. & Subtree statistics; no carrier-birth record or forward DtN response. & The occupation/subtree grows inside a pre-existing carrier; CNNA enlarges the finite carrier itself.\\
\hline
Dunlop--Mardin~\cite{DunlopMardin2022} & Random rooted subtree of a specified maximal bounded tree. & Stochastic offspring law with generation bound and interaction. & Configuration statistics and recursion; no immutable birth record or forward DtN response. & The maximal carrier and probability law are inputs; CNNA grows the accepted finite carrier deterministically.\\
\hline
Bodini--Genitrini--Mailler--Naima~\cite{BodiniGenitriniMaillerNaima2022} & Labelled Schr\"oder carrier generated by replacing selected leaves. & Sequential one-leaf or synchronized multi-leaf chronological labels; random-tree analysis. & Labels record event chronology; no record/live response split or Schur--DtN layer. & Close event-order comparator, but chronology is an explicit label rule rather than a later network response.\\
\hline
Bodini--Genitrini--Nurligareev~\cite{BodiniGenitriniNurligareev2026} & Binary active frontier grows or becomes extinct. & External integer time; synchronous update of every active leaf. & Enumerative profile and sampler; no record/live response split. & Direct comparator for \code{layer\_batch}, not for the sequential schedule or later directed backreaction.\\
\hline
Gernandt--Rohleder~\cite{GernandtRohleder2022} & Fixed finite weighted tree. & No growth dynamics. & Symmetric Laplacian DtN matrix used for inverse reconstruction. & Inverse fixed-tree problem with positive symmetric weights, rather than generated directed forward response.\\
\hline
Beard--Stefan--Viator--Welters~\cite{BeardStefanViatorWelters2023} & Fixed finite network and constitutive operator. & No carrier growth. & Effective operator and DtN map obtained by Schur methods. & Strong response-theoretic comparator, but no genealogical carrier growth or record/live layering.\\
\hline
Peng--Song~\cite{PengSong2022} & Fixed Eulerian directed Laplacian system. & Algorithmic block elimination and sparsification. & Directed Schur complements encode elimination errors; no birth provenance. & Relevant to directed elimination, but approximate solver theory rather than exact generated boundary response.\\
\hline
Avdonin--Khmelnytskaya--Kravchenko~\cite{AvdoninKhmelnytskayaKravchenko2023} & Metric quantum tree enlarged by attaching edges. & Successive constructive synthesis. & Weyl/DtN matrix of larger tree computed from smaller matrices. & Progressive response growth is close, but metric edges, differential equations, and spectral data are primitive.\\
\hline
Present finite CNNA core & Root plus branching bound; accepted births enlarge the finite real carrier. & Deterministic selector $\mathfrak{s}$; sequential reference mode and synchronous comparison mode. & Immutable record layer, later-updated live layer, directed weights, and forward finite Schur response. & The combined object studied here; stronger infinite, continuum, uniqueness, and literature-wide novelty claims are not made.\\
\bottomrule
\end{longtable}

\subsection{Claim boundary}
The cited works show that node-by-node $d$-ary growth, random subtrees of fixed graphs, interacting branching subtrees, chronology-labelled increasing trees, synchronous binary-front evolution, finite Schur effective operators, directed-Laplacian block elimination, inverse tree DtN reconstruction, and progressive quantum-tree Weyl synthesis are established but distinct constructions. The present claim is correspondingly narrow: the inspected finite source realizes a specific deterministic combination of carrier growth, birth-relative coordinate extension, immutable record data, later live updates, directed coupling, and forward Schur reduction. This section does not prove that no mathematically equivalent formulation exists elsewhere, and it does not use the publication date of a reference as evidence for or against the validity of a mathematical statement.

\paragraph{Revision note.}
This documentation revision expands the recent-literature comparison and completes DOI or persistent-link metadata in the reference list. It changes neither the finite construction, the Python source, the generated row files, the reported numerical values, nor the finite claim boundary of the July 10 code snapshot.

\section{Source surface and execution basis}
\subsection{Inspected source tree}
The inspected source surface is supplied as arXiv ancillary material in \src{anc/CNNA_structured_core_pkg}. All package paths stated below are relative to that ancillary package root. The reproducible source-surface digest is computed over the Python files in the declared source boundary and excludes the article source, environment records, license, package checks, and other ancillary metadata:
\[
\code{2612012d5149bedca71dbdbe60d0cbd075bbda6171ca008e989482787a002044}.
\]
The digest is the SHA256 value of the line-sorted manifest stored in \src{docs/SOURCE_SURFACE_MANIFEST.txt}. Per-file checksums for the complete ancillary package are stored separately in \src{CHECKSUMS.txt}. The byte hash of the outer transport ZIP is not used as the mathematical source identity, because an archive may be unpacked or repackaged without changing the declared source files.

The source boundary for this document is the Python source surface
\[
\begin{gathered}
\code{src/cnna/\_\_init\_\_.py},\quad
\code{src/cnna/config.py},\quad
\code{src/cnna/io},\\
\code{src/cnna/core},\quad
\code{src/cnna/derived\_\allowbreak{}quantities},\quad
\code{src/cnna/object\_\allowbreak{}checks},\\
\code{src/cnna/analysis\_\allowbreak{}entrypoints},\quad
\code{run\_*.py}\text{ at package root.}
\end{gathered}
\]
The \code{config.py} file supplies numerical constants and reference selectors used by row construction. The \code{io} subtree supplies row-file writers and JSON hashing. The \code{object\_\allowbreak{}checks} subtree is part of the documented source surface where the local-support, Tomita, commutant, split, entropy, and refined-basis row families are generated by their stated commands. Existing files ending in \code{.md} or \code{.csv} are not used as mathematical source text. Result files produced before the current growth rule are outside the evidential surface of this document. CSV files may be named later only as outputs generated from the current package by a stated command.

\begin{longtable}{>{\raggedright\arraybackslash}p{0.28\linewidth}>{\raggedright\arraybackslash}p{0.25\linewidth}>{\raggedright\arraybackslash}p{0.39\linewidth}}
\caption{Support files in the documented source surface.}\label{tab:support-source-surface}\\
\toprule
\textbf{Source file} & \textbf{Source object} & \textbf{Finite role}\\
\midrule
\endfirsthead
\toprule
\textbf{Source file} & \textbf{Source object} & \textbf{Finite role}\\
\midrule
\endhead
\src{src/cnna/config.py} & \code{EPS}; \code{REFERENCE\_MODE}; \code{REFERENCE\_STATE}; \code{STRUCTURAL\_RECORD\_STATE}; \code{GEN\_LABELS}; \code{CONTROL\_MODES}; \code{CONTROL\_STATES} & numerical tolerance constant, selected reference row labels, generator labels, and comparison selectors used by finite row construction\\
\hline
\src{src/cnna/io/csv\_writer.py} & \code{write\_csv}; \code{sha256\_json} & deterministic CSV field ordering and JSON hash utility for generated row data\\
\hline
\src{src/cnna/io/markdown\_report.py} & module placeholder & package-level I/O module with no finite object constructor in the current source surface\\
\bottomrule
\end{longtable}

\subsection{Minimal finite data route}
The executable route from a finite input tuple to row files is:
\[
\begin{array}{c}
(b,L,m,\mathfrak{s})
\longrightarrow \mathcal G_{b,L,m,\mathfrak{s}}
\longrightarrow (E^{\rm live},E^{\rm record},E^{\rm sym})\\[0.25em]
\longrightarrow \Lambda_B
\longrightarrow M_B=S_B+A_B
\longrightarrow (J_B^{\rm fin},\mathcal A_R,\mathcal H_R^{\rm GNS})\\[0.25em]
\longrightarrow \text{local row surfaces and live-record row surfaces}.
\end{array}
\]
For a fixed command, the row files are finite evaluations of this route. The local-operator command uses the same growth-schedule argument as the integrated command.

\subsection{Row status fields}
The row files contain text fields that record finite branch outcomes. The following strings occur as data values in the current row surface.
\begin{longtable}{>{\raggedright\arraybackslash}p{0.24\linewidth}>{\raggedright\arraybackslash}p{0.68\linewidth}}
\caption{Status strings and finite branch meanings.}\label{tab:status-strings}\\
\toprule
\textbf{Status field value} & \textbf{Finite branch meaning}\\
\midrule
\endfirsthead
\toprule
\textbf{Status field value} & \textbf{Finite branch meaning}\\
\midrule
\endhead
\code{finite\_object} & the row contains the finite matrix/vector/scalar object for the selected input tuple.\\
\hline
\code{unavailable\_rank\_below\_2} & the support used for the finite two-plane object has rank below two, so the two-plane object is not returned.\\
\hline
\code{not\_residual\_le\_tolerance} & the row exists and its residual is greater than the tolerance field carried by the row.\\
\hline
\code{coarse\_frontier} & the row uses a coarse frontier region selected by the directed-frontier cap.\\
\hline
\code{law\_fit\_eligible=0} & the row is present but excluded from the birth-relative fit route by its row fields.\\
\hline
\code{law\_fit\_eligible=1} & the row is present in the birth-relative fit route.\\
\bottomrule
\end{longtable}


\subsection{Integrated execution command}
The integrated root entrypoint for the source surface documented here is \code{run\_cnna.py}. It dispatches to \code{cnna.analysis\_\allowbreak{}entrypoints.run\_\allowbreak{}cnna\_\allowbreak{}analysis.main} and invokes the row functions exported by \code{cnna.derived\_\allowbreak{}quantities}. The following command generates the row families for the integrated row surface:
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 run_cnna.py \
  --branching 3 \
  --levels 4 5 6 \
  --modes linear log saturating \
  --states live record sym \
  --max-regions 1 \
  --max-boundary 600 \
  --max-interior 900 \
  --directed-frontier-cap 6 \
  --algebra-tol 1e-10 \
  --algebra-max-iter 8 \
  --gns-tol 1e-10 \
  --growth-schedule layer_batch \
  --outdir outputs/core_derived_documentation_run
\end{verbatim}
A smaller finite run with the same entrypoint generates a reduced row surface for layout and source-route checks:
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 run_cnna.py \
  --branching 3 \
  --levels 4 5 \
  --modes linear \
  --states live record sym \
  --max-regions 1 \
  --max-boundary 250 \
  --max-interior 350 \
  --directed-frontier-cap 5 \
  --algebra-tol 1e-10 \
  --algebra-max-iter 8 \
  --gns-tol 1e-10 \
  --growth-schedule layer_batch \
  --outdir outputs/core_derived_reduced
\end{verbatim}
The schedule \code{layer\_\allowbreak{}batch} constructs all \code{GrowthStep} objects of one causal depth from the same pre-commit state before committing the births. The schedule \code{slot\_\allowbreak{}step} applies one slot closure at a time. Both schedules are implemented by \code{EmptySetGrowthModel}; the command above selects the causal-layer schedule. Other root scripts are single-surface entrypoints. They are not read in this source-surface section. A focused runner is stated only in the later section whose rows it generates.

\paragraph{Command argument meanings.}
The arguments of the integrated command select finite constructors, row emitters, and numerical caps. They do not introduce additional mathematical objects beyond the source objects listed in Table~\ref{tab:runtime-dof}.
\begin{longtable}{>{\raggedright\arraybackslash}p{0.24\linewidth}>{\raggedright\arraybackslash}p{0.20\linewidth}>{\raggedright\arraybackslash}p{0.48\linewidth}}
\caption{Arguments of the integrated execution command.}\label{tab:integrated-command-arguments}\\
\toprule
\textbf{Argument} & \textbf{Value in the command} & \textbf{Finite role in the generated row surface}\\
\midrule
\endfirsthead
\toprule
\textbf{Argument} & \textbf{Value in the command} & \textbf{Finite role in the generated row surface}\\
\midrule
\endhead
\code{-{}-branching} & \code{3} & arity $b$ of the finite rooted tree; each node has at most $b$ child slots and saturation is measured as occupied slots over $b$\\
\hline
\code{-{}-levels} & \code{4 5 6} & terminal depths $L$ for the finite approximants; each listed value produces a separate finite growth object and downstream response rows\\
\hline
\code{-{}-modes} & \code{linear log saturating} & selector for \code{\_mode\_scale} in the birth-weight construction; \code{rule\_coefficients} depends on \code{-{}-branching} only\\
\hline
\code{-{}-states} & \code{live record sym} & edge-layer readout: \code{record} keeps birth edges, \code{live} includes later updates, and \code{sym} reads the symmetrized edge matrix\\
\hline
\code{-{}-max-\allowbreak{}regions} & \code{1} & number of region records emitted per model before region row construction stops\\
\hline
\code{-{}-max-\allowbreak{}boundary} & \code{600} & boundary-size cap for Schur--DtN and directed-response matrices\\
\hline
\code{-{}-max-\allowbreak{}interior} & \code{900} & interior-size cap for finite elimination in Schur--DtN and directed-response calculations\\
\hline
\code{-{}-directed-\allowbreak{}frontier-\allowbreak{}cap} & \code{6} & finite frontier level used by directed-region constructors when full terminal boundaries exceed the selected cap\\
\hline
\code{-{}-algebra-\allowbreak{}tol} & \code{1e-10} & tolerance used in finite algebra closure, span projection, and residual comparisons involving algebraic bases\\
\hline
\code{-{}-algebra-\allowbreak{}max-\allowbreak{}iter} & \code{8} & iteration cap for the finite multiplication/star closure procedure in the response-algebra layer\\
\hline
\code{-{}-gns-\allowbreak{}tol} & \code{1e-10} & tolerance for support, rank, Gram-spectrum, and GNS quotient decisions\\
\hline
\code{-{}-growth-\allowbreak{}schedule} & \code{layer\_batch} & growth update route: all slots of one causal depth are evaluated from the same pre-commit state and then committed\\
\hline
\code{-{}-outdir} & \src{outputs/core_derived_documentation_run} & directory receiving the generated CSV row families for the stated command\\
\bottomrule
\end{longtable}

\subsection{Tested numerical environment and licensing}
The documented snapshot was tested under Ubuntu 26.04 LTS on Linux \code{7.0.0-27-generic} (x86\_64, glibc 2.43), using CPython 3.14.4 built with GCC 15.2.0 and NumPy 2.3.5. Explicit NumPy allocations with \code{dtype=float} resolve to \code{numpy.float64}, hence IEEE~754 binary64 arithmetic, in this environment. This arithmetic precision is distinct from the package-level constant \(\code{EPS}=10^{-12}\) and from the algebraic and GNS decision tolerances \(10^{-10}\) used by the stated command.

The numerical backend is identified by runtime mapping, dynamic-link inspection, and the configured Ubuntu package providers. NumPy links to the Ubuntu/Debian reference BLAS and LAPACK implementations, both version 3.12.1, supplied by \code{libblas3} and \code{liblapack3} package version 3.12.1-7ubuntu1. After representative matrix multiplication, linear-solve, symmetric-eigenvalue, and SVD calls, \src{/proc/self/maps} records \src{/usr/lib/x86_64-linux-gnu/blas/libblas.so.3.12.1} and \src{/usr/lib/x86_64-linux-gnu/lapack/liblapack.so.3.12.1}; \code{ldd} on the relevant NumPy extension modules resolves the same system links. \code{threadpoolctl} 3.6.0 detects no thread-pool-managed native library, consistently with the configured reference providers. The complete runtime, linker, package-provider, and NumPy build record is preserved in \src{ENVIRONMENT.txt}; a concise interpretation is given in \src{ENVIRONMENT.md}. Package versions and tolerances are fixed, but bitwise identity across other BLAS/LAPACK backends, compiler builds, or processor feature sets is not asserted.

The Python software and software documentation in the ancillary package are distributed under the MIT License in \src{LICENSE}. That software license does not set the license of this article. Distribution of the article is governed by the license selected on its arXiv record.

The documented semantic edge cases are checked by
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
python3 package_consistency/check_mathematical_contracts.py
python3 package_consistency/check_finite_structure_theorems.py
python3 package_consistency/check_nested_multiscale_handoff.py
\end{verbatim}
The first check covers zero-mass normalization, normalized push-forward semantics, positive and negative GNS cyclicity controls, basis-change and nonfaithful-state quotient behavior, the support-restricted finite-\(J\) identity, and the entropy support cutoff. The second check covers finite growth replay, symmetric Schur positivity, exact finite GNS controls, sign-reversal covariance of the finite polar object, separation of backreaction observables, and prefix/carrier handoff. The third check constructs the growing first-order address-contrast carriers, verifies their exact non-unital corner embeddings and composition, checks common-ambient Schur associativity, and records the separate response, density, GNS, and finite-\(J\) naturality residuals.

\subsection{Regeneration boundary for row values}
The current growth rule changes the finite growth object before every downstream response construction. Therefore numerical statements from earlier packages, reports, CSV files, or prior runs are not inherited. Each numerical statement in later sections is written together with a command of the form displayed above, a generated row family, and a readout from rows generated by the current package. This source-surface section names commands and source routes only; it does not state numerical row values.

\subsection{Runtime degrees of freedom}
Each runtime parameter is introduced at the first object layer that uses it. Parameters are not used as labels for objects outside the layer where they first enter.
\begin{longtable}{>{\raggedright\arraybackslash}p{0.24\linewidth}>{\raggedright\arraybackslash}p{0.33\linewidth}>{\raggedright\arraybackslash}p{0.33\linewidth}}
\caption{Runtime degrees of freedom and first source layer.}\label{tab:runtime-dof}\\
\toprule
\textbf{Parameter} & \textbf{First layer where it is used} & \textbf{Source role}\\
\midrule
\endfirsthead
\toprule
\textbf{Parameter} & \textbf{First layer where it is used} & \textbf{Source role}\\
\midrule
\endhead
\code{-{}-branching} / $b$ & finite growth record from the empty state & arity of the finite rooted tree\\
\hline
\code{-{}-levels} / $L$ & finite growth record from the empty state & terminal level and approximant size\\
\hline
\code{-{}-modes} / $m$ & finite birth-weight construction & selector for the implemented scalar map $\sigma_m$ used on environment load\\
\hline
\code{-{}-growth-\allowbreak{}schedule} / $\mathfrak{s}$ & finite growth record from the empty state & update schedule: \code{slot\_\allowbreak{}step} closes one slot at a time; \code{layer\_\allowbreak{}batch} evaluates one causal layer before commit\\
\hline
\code{-{}-states} & terminal state and live/record/sym edge layer & selected edge/state layer\\
\hline
\code{-{}-max-\allowbreak{}regions} & region specification & number of emitted region records\\
\hline
\code{-{}-max-\allowbreak{}boundary} & Schur--DtN and directed response & numerical boundary cap\\
\hline
\code{-{}-max-\allowbreak{}interior} & Schur--DtN and directed response & numerical elimination cap\\
\hline
\code{-{}-directed-\allowbreak{}frontier-\allowbreak{}cap} & directed response and large-level coverage & finite frontier level used for coarse boundary construction\\
\hline
\code{-{}-algebra-\allowbreak{}tol} & response algebra and operator residual rows & tolerance for algebraic residual comparisons\\
\hline
\code{-{}-algebra-\allowbreak{}max-\allowbreak{}iter} & finite response algebra closure & closure iteration cap\\
\hline
\code{-{}-gns-\allowbreak{}tol} & finite GNS, support, rank, and projectivity rows & tolerance for support/rank decisions\\
\bottomrule
\end{longtable}

The table is a parameter taxonomy, not a claim that every listed quantity is a physical coupling. In the reference interpretation, \(b\) is the varied structural index and \(L\) is the finite-size cutoff. The mode \(m\) selects one of three implemented birth-load maps, and \(\mathfrak{s}\) selects the update semantics; both alter the generated finite object and are therefore rule-family selectors, not derived consequences of \(b\). State labels, region counts, caps, and tolerances select readout surfaces or numerical decision procedures. Any statement that only \(b\) is varied is restricted to a command in which all other selectors are explicitly fixed.

\subsection{Finite quantities and code locations}
The following table fixes the mathematical symbols used below. A symbol is introduced only at the source location where the corresponding finite object, map, matrix, row family, or residual first appears.
\setlength{\tabcolsep}{3pt}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.14\linewidth}>{\raggedright\arraybackslash}p{0.43\linewidth}>{\raggedright\arraybackslash}p{0.36\linewidth}}
\caption{Finite quantities used in the mathematical text and their source anchors.}\label{tab:finite-symbol-source-map}\\
\toprule
\textbf{Symbol} & \textbf{Source anchor and code object} & \textbf{Mathematical object described here}\\
\midrule
\endfirsthead
\toprule
\textbf{Symbol} & \textbf{Source anchor and code object} & \textbf{Mathematical object described here}\\
\midrule
\endhead
$b$ & \src{analysis_entrypoints/run_cnna_analysis.py}\par \src{core/emptyset_growth.py:41--55}\par \code{--branching}; \code{rule\_\allowbreak{}coefficients} & finite arity used by the rooted growth constructor and by the coefficient functions of the finite rule.\\
\hline
$L$ & \src{analysis_entrypoints/run_cnna_analysis.py}\par \src{core/emptyset_growth.py:121--456}\par \code{--levels}; \code{EmptySetGrowthModel} & terminal level of the finite approximant.\\
\hline
$m$ & \src{analysis_entrypoints/run_cnna_analysis.py}\par \src{core/emptyset_growth.py:131--145}\par \code{--modes}; \code{mode}; \code{\_mode\_scale} & selector for the finite scalar map $\sigma_m$ applied to environment load in the birth-weight construction.\\
\hline
$\mathfrak{s}$ & \src{analysis_entrypoints/run_cnna_analysis.py}\par \src{core/emptyset_growth.py:124--150}\par \code{--growth-\allowbreak{}schedule}; \code{growth\_\allowbreak{}schedule} & finite update schedule for open birth slots; values: \code{slot\_\allowbreak{}step}, \code{layer\_\allowbreak{}batch}.\\
\hline
$\eta$ & \src{core/emptyset_growth.py:129--150}\par \src{core/emptyset_growth.py:257--260}\par \code{sibling\_\allowbreak{}linearization}; \code{\_linearize\_\allowbreak{}open\_\allowbreak{}slots} & finite ordering used to linearize slots inside the same causal depth for comparison rows; values: \code{rank}, \code{reverse\_\allowbreak{}rank}.\\
\hline
$\varepsilon$ & \src{config.py:3}\par \code{EPS} & package-level numerical tolerance constant used by source functions that import the package configuration.\\
\hline
$\rho_{\rm ref}$ & \src{config.py:6--8}\par \code{REFERENCE\_MODE}; \code{REFERENCE\_STATE}; \code{STRUCTURAL\_RECORD\_STATE} & reference row selectors used by structural and comparison row families; values: \code{linear}, \code{live}, \code{record}.\\
\hline
$\mathcal L_{\rm gen}$ & \src{config.py:10--12}\par \code{GEN\_LABELS} & finite list of generator labels used by row surfaces and algebraic residual tables.\\
\hline
$s$ & \src{analysis_entrypoints/run_cnna_analysis.py}\par \src{core/directed_dtn.py:27--47}\par \code{--states}; \code{state\_\allowbreak{}directed\_\allowbreak{}edges} & selected edge layer used for response and transport computations; values: \code{live}, \code{record}, \code{sym}.\\
\hline
$\varepsilon_{\rm alg}$ & \src{analysis_entrypoints/run_cnna_analysis.py}\par \src{core/response_algebra.py}\par \code{algebra\_\allowbreak{}tol}; \code{algebra\_\allowbreak{}closure} & finite threshold used for basis insertion and algebra-closure residuals.\\
\hline
$\varepsilon_{\rm gns}$ & \src{analysis_entrypoints/run_cnna_analysis.py}\par \src{core/response_algebra.py}\par \code{gns\_\allowbreak{}tol}; \code{quotient\_\allowbreak{}support} & finite threshold for support rank and GNS quotient decisions.\\
\hline
$\mathcal G_{b,L,m,\mathfrak{s}}$ & \src{core/emptyset_growth.py:121--456}\par \code{EmptySetGrowthModel} & finite growth object containing nodes, events, address map, open birth slots during construction, growth steps, record edges, live edges, and node loads.\\
\hline
$c_b$ & \src{core/emptyset_growth.py:20--38}\par \src{core/emptyset_growth.py:41--55}\par \code{RuleCoefficients}; \code{rule\_\allowbreak{}coefficients} & finite tuple of coefficient values computed from $b$ only.\\
\hline
$\sigma_m$ & \src{core/emptyset_growth.py:186--191}\par \code{\_mode\_scale} & finite scalar map selected by $m$ and applied to environment load.\\
\hline
$g_{\rm birth}(v)$ & \src{core/emptyset_growth.py:272--286}\par \code{\_make\_\allowbreak{}growth\_\allowbreak{}step}; \code{birth\_g} & birth load computed from $h(p,U_p)$ by the selected scalar map $\sigma_m$.\\
\hline
$V_{b,L}$ & \src{core/emptyset_growth.py:58--72}\par \src{core/emptyset_growth.py:121--456}\par \code{Node}; \code{self.nodes} & finite node set produced by the constructor.\\
\hline
$\mathcal E_{b,L}$ & \src{core/emptyset_growth.py:75--96}\par \src{core/emptyset_growth.py:161--183}\par \code{Event}; \code{self.events} & finite ordered event list whose order is a recorded linearization, not the causal-depth order.\\
\hline
$\mathcal O(p)$ & \src{core/emptyset_growth.py:99--107}\par \src{core/emptyset_growth.py:242--255}\par \code{OpenBirthSlot}; \code{open\_\allowbreak{}birth\_\allowbreak{}slots} & finite set of unoccupied child slots of a parent node; saturation is reached when no such slot remains.\\
\hline
$\Gamma_n$ & \src{core/emptyset_growth.py:109--118}\par \src{core/emptyset_growth.py:272--286}\par \code{GrowthStep}; \code{\_make\_\allowbreak{}growth\_\allowbreak{}step} & finite update record for closing one open slot, carrying causal predecessors, environment load, birth weight, and linearization index.\\
\hline
$U_p$, $h(p,U_p)$ & \src{core/emptyset_growth.py:262--270}\par \code{\_birth\_\allowbreak{}environment\_\allowbreak{}load} & occupied sibling set of a parent and its symmetric finite environment load; sibling contributions enter by set sum divided by $|U_p|+1$, not by birth order.\\
\hline
$d(v)$, $\lambda(v)$, $q(v)$ & \src{core/emptyset_growth.py:58--72}\par \code{causal\_\allowbreak{}depth}; \code{linearization\_\allowbreak{}index}; \code{lapse\_\allowbreak{}weight} & causal depth, technical linearization index, and response weight recorded on a node.\\
\hline
$E^{\rm rec}$ & \src{core/emptyset_growth.py:155--156}\par \src{core/emptyset_growth.py:340--344}\par \code{record\_\allowbreak{}edges} & birth-edge dictionary.\\
\hline
$E^{\rm live}$ & \src{core/emptyset_growth.py:155--156}\par \src{core/emptyset_growth.py:340--368}\par \code{live\_\allowbreak{}edges} & edge dictionary after birth edges and later live updates.\\
\hline
$a$ & \src{core/emptyset_growth.py:58--72}\par \code{Node.address} & finite address tuple of a node.\\
\hline
$\pi_k(a)$ & \src{core/projective_maps.py:21--24}\par \code{prefix} & prefix truncation of an address to level $k$.\\
\hline
$\Omega_L$ & \src{core/projective_maps.py:27--29}\par \code{terminal\_\allowbreak{}carrier} & terminal address support at level $L$ with uniform carrier weights.\\
\hline
$\mu_L$ & \src{core/projective_maps.py:32--53}\par \code{terminal\_\allowbreak{}state} & normalized finite terminal state built from node load and incident response load.\\
\hline
$(\pi_k)_*\mu_L$ & \src{core/projective_maps.py:56--61}\par \code{push\_\allowbreak{}forward} & finite prefix push-forward of a terminal distribution.\\
\hline
$C_k$ and $\Omega_L\setminus C_k$ & \src{core/projective_maps.py:64--84}\par \code{center\_\allowbreak{}subset\_\allowbreak{}prefix}; \code{split\_\allowbreak{}distribution} & deterministic first-born cylinder and its complement.\\
\hline
$(F_1,F_2)$ & \src{core/signed_current.py:22--62}\par \code{orthonormal\_\allowbreak{}pair}; \code{F1\_\allowbreak{}F2\_\allowbreak{}vectors} & real two-vector plane extracted from finite address/current data.\\
\hline
$\omega_{F_1F_2}$ & \src{core/signed_current.py:65--120}\par \code{orientation\_\allowbreak{}measurement} & finite signed scalar on the whole-network $F_1/F_2$ plane.\\
\hline
$B$ and $I$ & \src{core/schur_dtn.py:45--70}\par \src{core/schur_dtn.py:73--112}\par \code{boundary}; \code{interior} & finite boundary and interior node lists for a selected cut.\\
\hline
$K$ & \src{core/schur_dtn.py:45--70}\par \src{core/schur_dtn.py:73--112}\par local Laplacian blocks & finite matrix split into $K_{BB},K_{BI},K_{IB},K_{II}$.\\
\hline
$\Lambda_B$ & \src{core/schur_dtn.py:23--29}\par \src{core/schur_dtn.py:45--70}\par \code{SchurResponse}; \code{schur\_\allowbreak{}response} & finite Schur--DtN response matrix $K_{BB}-K_{BI}K_{II}^{-1}K_{IB}$ as computed by solve.\\
\hline
$R$ & \src{core/schur_dtn.py:33--42}\par \src{core/schur_dtn.py:115--156}\par \code{RegionSpec}; \code{build\_\allowbreak{}sibling\_\allowbreak{}regions} & finite sibling-cone region record with boundary and interior lists.\\
\hline
$Q_R$ & \src{core/schur_dtn.py:159--198}\par \code{boundary\_\allowbreak{}role\_\allowbreak{}basis}; \code{compress\_\allowbreak{}response} & finite role-basis matrix and compression map $Q_R^\top\Lambda_BQ_R$.\\
\hline
$M^{\rm dir}_B$ & \src{core/directed_dtn.py:16--24}\par \src{core/directed_dtn.py:98--166}\par \code{DirectedSchurResponse}; \code{directed\_\allowbreak{}schur\_\allowbreak{}response} & finite directed boundary response matrix.\\
\hline
$S_B$ and $A_B$ & \src{core/directed_dtn.py:402--405}\par \code{split\_\allowbreak{}symmetric\_\allowbreak{}skew} & symmetric and skew parts $(M+M^\top)/2$ and $(M-M^\top)/2$.\\
\hline
$J_{B}^{\rm fin}$ & \src{core/directed_dtn.py:408--455}\par \code{j\_\allowbreak{}finite\_\allowbreak{}object\_\allowbreak{}from\_\allowbreak{}SA} & finite support-restricted comparison object built from $S_B$ and $A_B$.\\
\hline
$\mathcal A_R$ & \src{core/response_algebra.py}\par \src{core/response_algebra.py}\par \code{AlgebraBasis}; \code{build\_\allowbreak{}algebras} & finite matrix algebra basis generated by response matrices.\\
\hline
$\rho_R$ & \src{core/response_algebra.py}\par \src{core/region_response.py:52--97}\par \code{positive\_\allowbreak{}density\_\allowbreak{}from\_\allowbreak{}response}; \code{positive\_\allowbreak{}support\_\allowbreak{}density\_\allowbreak{}from\_\allowbreak{}response} & positive finite density matrix extracted from response data.\\
\hline
$\varphi_R(X)$ & \src{core/response_algebra.py}\par \code{state\_\allowbreak{}value}; \code{state\_\allowbreak{}gram} & finite state functional and its Gram matrix over the algebra basis.\\
\hline
$\mathcal H_R^{\rm GNS}$ & \src{core/response_algebra.py}\par \code{GNSData}; \code{measurement\_\allowbreak{}gns} & finite quotient-support GNS data, full-basis representation residuals, and explicit cyclic-span rank.\\
\hline
$\mathcal L_R$ & \src{core/region_response.py:101--151}\par \src{core/algebra_support.py:85--323}\par \code{RegionalResponse}; \code{local\_\allowbreak{}operator\_\allowbreak{}algebras} & regional response object and finite local support algebras.\\
\hline
$P_U$ & \src{core/algebra_support.py:169--218}\par \code{role\_\allowbreak{}support\_\allowbreak{}indices}; \code{role\_\allowbreak{}support\_\allowbreak{}projector} & diagonal projector for a selected role support.\\
\hline
$\mathcal C(\mathcal A)$ & \src{core/algebra_support.py:426--449}\par \code{commutant\_\allowbreak{}algebra\_\allowbreak{}basis}; \code{basis\_\allowbreak{}to\_\allowbreak{}algebra} & finite commutant nullspace and corresponding algebra basis.\\
\hline
$\tau_R$ & \src{core/algebra_support.py:452--636}\par \code{finite\_\allowbreak{}tomita\_\allowbreak{}star\_\allowbreak{}metrics} & finite star-map/Tomita metric data over the generated algebra and density.\\
\hline
$\widehat\mu_R$ & \src{core/compressed_state.py:24--117}\par \code{compressed\_\allowbreak{}state\_\allowbreak{}object}; \code{compressed\_\allowbreak{}projective\_\allowbreak{}distribution} & compressed carrier/GNS distribution over finite role/address keys.\\
\hline
$Q_R^{\rm ref}$ & \src{core/refined_port_basis.py:36--138}\par \code{refined\_\allowbreak{}boundary\_\allowbreak{}role\_\allowbreak{}basis}; \code{refined\_\allowbreak{}support\_\allowbreak{}algebra} & refined finite boundary/port basis and its support algebra.\\
\hline
$S(\rho)$ & \src{core/entropy_quantities.py}\par \code{von\_\allowbreak{}neumann\_\allowbreak{}entropy\_\allowbreak{}no\_\allowbreak{}epsilon} & finite entropy from positive eigenvalues of a density matrix.\\
\hline
$D(\rho\Vert\sigma)$ & \src{core/entropy_quantities.py}\par \code{quantum\_\allowbreak{}relative\_\allowbreak{}entropy\_\allowbreak{}no\_\allowbreak{}epsilon} & finite relative entropy with explicit support handling.\\
\hline
$\operatorname{JSD}(\rho,\sigma)$ & \src{core/entropy_quantities.py}\par \code{jensen\_\allowbreak{}shannon\_\allowbreak{}divergence\_\allowbreak{}no\_\allowbreak{}epsilon} & finite Jensen--Shannon divergence of two density matrices.\\
\hline
$\delta_{L\to L\prime}$ & \src{derived_quantities/operator_stack_residuals.py:23--289}\par \src{derived_quantities/operator_stack_interface_residuals.py:93--314}\par \code{interlevel\_\allowbreak{}operator\_\allowbreak{}rows}; interface row transforms & finite residuals after projection to common labels.\\
\hline
$T_{L\to L\prime}$ & \src{derived_quantities/directed_current_transport.py:68--112}\par \src{derived_quantities/directed_current_transport.py:191--341}\par \code{boundary\_\allowbreak{}prefix\_\allowbreak{}transport\_\allowbreak{}matrix}; transport rows & finite boundary-prefix transport matrix and composition comparison.\\
\hline
$\sigma_J^{\rm loc}$, $\sigma_J^{\rm glob}$ & \src{derived_quantities/j_orientation_projectivity.py:159--439}\par \src{derived_quantities/local_global_j_sign_relation.py:139--334}\par orientation and sign row families & finite local and global sign assignments compared by row functions.\\
\hline
$B_L=A^{\rm live}_L-A^{\rm record}_L$ & \src{derived_quantities/backreaction_current.py}\par \code{backreaction\_\allowbreak{}current\_\allowbreak{}rows} & finite live-record skew-response difference on the same model, region, and level.\\
\hline
$\alpha=L-L_{\rm birth}$ & \src{derived_quantities/backreaction_birth_relative.py}\par \code{birth\_\allowbreak{}relative\_\allowbreak{}backreaction\_\allowbreak{}rows}; \code{birth\_\allowbreak{}relative\_\allowbreak{}zero\_\allowbreak{}crossing\_\allowbreak{}rows} & explicit sibling-root birth-relative age and finite interpolation of the signed skew-norm difference.\\
\hline
$\Delta_{\rm lin}$ & \src{derived_quantities/birth_linearization_invariance.py:65--112}\par \code{birth\_\allowbreak{}linearization\_\allowbreak{}invariance\_\allowbreak{}rows} & finite address-level residual comparing the implemented \code{rank} and \code{reverse\_\allowbreak{}rank} linearizations; it samples the order-dependence surface of \code{slot\_\allowbreak{}step} and \code{layer\_\allowbreak{}batch}.\\
\hline
$r_\bullet$ & \src{derived_quantities/baseline.py:21--254}\par \src{derived_quantities/computed_status_rows.py:26--149}\par row-family functions; aggregation rows & generated row-family outputs attached to previously constructed finite objects.\\
\bottomrule
\end{longtable}

\newpage

\section{Reference scope for discrete finite operations}
The CNNA core presented here is a discrete--finite construction. Its primitive generated objects are finite rooted address trees, finite weighted edge surfaces, finite carrier arrays, and finite matrices. The references in this document are used only to identify standard background for finite trees, finite graphs, algebraic graph operations, Schur complements, finite matrix decompositions, and finite-dimensional operator-algebraic terminology \cite{Harary1969,Bollobas1998,GodsilRoyle2001,HornJohnson2013,Zhang2005}.

These references are not external axioms for the CNNA construction. The live, record, sym, carrier, finite \(J\), and backreaction objects are generated from an empty initial configuration by the explicit finite rules implemented in the source. The branching index \(b\) enters the coefficient map, while \(L\), the mode selector \(m\), the update schedule \(\mathfrak{s}\), region selectors, caps, and numerical tolerances have separately declared roles. The cited literature documents established mathematical language in which some of these finite operations can be described. No continuum space, no integral calculus, no differential operator, and no analytic boundary-value problem is introduced in the finite core.

The term Dirichlet-to-Neumann is used here in the discrete network sense: a finite boundary response matrix obtained by eliminating interior vertices through a Schur complement. In this document, the object is entirely finite and matrix-based. Boundary sets, interior sets, invertibility checks, solve residuals, and compressed responses are computed directly from the generated finite graph data. The relevant comparison literature is finite resistor-network response theory, not a continuum field theory \cite{CurtisMorrow1991,CurtisIngermanMorrow1998}. For weighted tree graphs, Gernandt and Rohleder likewise identify the discrete Dirichlet-to-Neumann matrix with a Laplacian Schur complement and study what tree and edge-weight information can be reconstructed from it \cite{GernandtRohleder2022}. Their inverse problem starts from a symmetric positively weighted tree and a leaf boundary; the present construction instead generates directed record/live weights and uses the Schur map in the forward provenance chain. The citation therefore supplies a close tree--DtN comparator, not an identity of problems or conclusions.

\section{Derivation graph}
\subsection{Global object order}
The documentation follows the first-use order of the objects. When one Python module contributes to several object layers, only the function block whose inputs are already available is introduced at that point.
\begin{center}
\begin{tabular}{>{\raggedleft\arraybackslash}p{0.07\linewidth}>{\raggedright\arraybackslash}p{0.84\linewidth}}
\toprule
\textbf{Order} & \textbf{Object introduced at first use}\\
\midrule
0 & $\emptyset$\\
\hline
1 & finite growth record with open slots and \code{GrowthStep}\\
\hline
1a & birth-relative set and coordinate complement of each accepted new address; causal-layer complement for \code{layer\_batch}\\
\hline
1b & directed record/live coupling of the new carrier directions to parent, ancestors, and sibling slots\\
\hline
2 & birth-linearization residual rows\\
\hline
3 & terminal carrier and prefix maps\\
\hline
4 & whole-network F1/F2 signed current\\
\hline
5 & symmetric Schur--DtN response\\
\hline
6 & region specification and role compression\\
\hline
7 & directed response and $S/A$ split\\
\hline
8 & finite $J$ comparison\\
\hline
9 & finite response algebra and GNS data\\
\hline
10 & regional response and local support algebras\\
\hline
11a & compressed carrier/GNS state layer\\
\hline
11b & refined boundary/port basis\\
\hline
12 & entropy quantities\\
\hline
13 & interlevel residuals and directed transport\\
\hline
14 & local/global $J$ sign comparison\\
\hline
15 & live-record backreaction current\\
\hline
16 & birth-relative transforms\\
\hline
17 & row aggregation\\
\bottomrule
\end{tabular}
\end{center}
Derived row modules do not introduce primitive degrees of freedom. They attach finite measurements to objects constructed earlier in the chain.

\subsection{Function-block placement}
The placement unit is sometimes a function block rather than a module. The following table records the section order used by the filled source-ordered construction.
\begin{longtable}{>{\raggedright\arraybackslash}p{0.07\linewidth}>{\raggedright\arraybackslash}p{0.29\linewidth}>{\raggedright\arraybackslash}p{0.31\linewidth}>{\raggedright\arraybackslash}p{0.25\linewidth}}
\caption{Derivation layers used for source placement.}\label{tab:derivation-layers}\\
\toprule
\textbf{Layer} & \textbf{Object layer} & \textbf{Objects introduced} & \textbf{Row functions attached here}\\
\midrule
\endfirsthead
\toprule
\textbf{Layer} & \textbf{Object layer} & \textbf{Objects introduced} & \textbf{Row functions attached here}\\
\midrule
\endhead
0 & Source tree and finite notation & package tree; finite arrays; finite dictionaries & none\\
\hline
1 & Finite scalar, vector, matrix, and distribution operations & Frobenius norm; total variation; normalization & metric helpers only\\
\hline
2 & Finite growth record and complement coupling from the empty state & \code{RuleCoefficients}; \code{Node}; \code{Event}; \code{OpenBirthSlot}; \code{GrowthStep}; \code{EmptySetGrowthModel}; birth-relative carrier complements; record/live directed couplings; growth schedule & genesis, parameter, rule-constant, birth-linearization rows\\
\hline
3 & Terminal addresses, carriers, and prefix maps & terminal carrier; terminal state; prefix; push-forward; split distribution & projection, carrier, sector rows\\
\hline
4 & Whole-network F1/F2 axes and signed current scalar & \code{orthonormal\_pair}; \code{F1\_F2\_vectors}; \code{orientation\_measurement} & orientation and history-delta rows\\
\hline
5 & Symmetric Schur--DtN response on a selected cut & \code{SchurResponse}; selected boundary/interior response & local response-density and rank/kernel rows\\
\hline
6 & Region specification and boundary role compression & \code{RegionSpec}; sibling regions; role basis; compressed response & regional response rows\\
\hline
7 & Directed response and S/A decomposition & \code{DirectedSchurResponse}; directed local matrix; $S$; $A$ & directed construction, decomposition, skew rows\\
\hline
8 & Finite J comparison on S/A support & support-restricted finite comparison from $S$ and $A$ & J snapshot rows\\
\hline
9 & Finite matrix algebra and finite GNS data & algebra basis; density; Gram matrix; quotient support & algebra/GNS rows\\
\hline
10 & Regional response object and local support algebras & regional support density; local generators; support algebras & local algebra rows when included\\
\hline
11 & Finite local algebra checks & commutator, cyclicity, commutant, Tomita, split metrics & check rows when included\\
\hline
12 & Compressed carrier/GNS state and projective distribution & compressed state object; compressed projective distribution & compressed carrier rows\\
\hline
13 & Refined boundary/port basis & refined role basis; refined regional response & refined-basis rows when included\\
\hline
14 & Entropy functionals and record/live entropy distances & entropy, relative entropy, Jensen--Shannon, record/live metrics & entropy rows when included\\
\hline
15 & Interlevel operator residuals and interface transforms & label-span projection; matrix log; commutator delta; seam rows & operator residual rows\\
\hline
16 & Directed transport and local/global J sign comparison & boundary-prefix transport; sign comparison domains & transport and sign rows\\
\hline
17 & Live-record backreaction current & $B_L=A_{\mathrm{live},L}-A_{\mathrm{record},L}$ & backreaction rows\\
\hline
18 & Birth-relative and branching transforms & birth-relative age; interpolation pair; branching comparison & zero-crossing and branching rows\\
\hline
19 & Nested multiscale carrier handoff & first-order address contrasts; growing real carriers; corner embeddings; common-ambient Schur controls & nested carrier, composition, state/GNS, and finite-\(J\) naturality rows\\
\hline
20 & Row aggregation layer & row-family collection & aggregation rows\\
\hline
S & Support source files & package constants and row-file writers & config and I/O helpers\\
\bottomrule
\end{longtable}

\newpage
\section{Core module map}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.22\linewidth}>{\raggedright\arraybackslash}p{0.13\linewidth}>{\raggedright\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}p{0.39\linewidth}}
\caption{Core modules in derivation order.}\label{tab:core-map}\\
\toprule
\textbf{Module} & \textbf{Mathematical object} & \textbf{Role in derivation} & \textbf{Principal code objects}\\
\midrule
\endfirsthead
\toprule
\textbf{Module} & \textbf{Mathematical object} & \textbf{Role in derivation} & \textbf{Principal code objects}\\
\midrule
\endhead
\code{core/math\_\allowbreak{}utils.py} & finite numerical primitives & norms, total-variation distances, normalization, row metric extraction & fro; tv; normalize\_\allowbreak{}dict; normalize\_\allowbreak{}distribution; tv\_\allowbreak{}arr\\
\hline
\code{core/emptyset\_\allowbreak{}growth.py} & empty-set growth and complement-coupling object & rooted b-ary address tree with explicit open slots, birth-relative carrier complements, growth steps, update schedule, and record/live directed edge states & class RuleCoefficients; class Node; class Event; class OpenBirthSlot; class GrowthStep; class EmptySetGrowthModel; rule\_\allowbreak{}coefficients; open\_\allowbreak{}birth\_\allowbreak{}slots\\
\hline
\code{core/projective\_\allowbreak{}maps.py} & carrier and prefix projections & terminal probability carrier and finite push-forward maps & prefix; terminal\_\allowbreak{}carrier; terminal\_\allowbreak{}state; push\_\allowbreak{}forward; center\_\allowbreak{}subset\_\allowbreak{}prefix; split\_\allowbreak{}distribution; response\_\allowbreak{}energy\_\allowbreak{}distribution\\
\hline
\code{core/signed\_\allowbreak{}current.py} & two-axis signed-current plane & F1/F2 real vectors and orientation measurement & orthonormal\_\allowbreak{}pair; F1\_\allowbreak{}F2\_\allowbreak{}vectors; orientation\_\allowbreak{}measurement\\
\hline
\code{core/schur\_\allowbreak{}dtn.py} & symmetric Schur-DtN response & finite Laplace restriction, Schur complement, role basis compression & class SchurResponse; class RegionSpec; schur\_\allowbreak{}response; schur\_\allowbreak{}response\_\allowbreak{}from\_\allowbreak{}model; build\_\allowbreak{}sibling\_\allowbreak{}regions; normalized\_\allowbreak{}indicator; boundary\_\allowbreak{}role\_\allowbreak{}basis; compress\_\allowbreak{}response; role\_\allowbreak{}for\_\allowbreak{}boundary\_\allowbreak{}node; atom\_\allowbreak{}key\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & growing address-contrast carrier & Helmert slot contrasts, nested role basis, corner maps, common-ambient Schur matrix, support graph & class NestedRoleBasis; class CommonAmbientSchurResult; nested\_\allowbreak{}address\_\allowbreak{}contrast\_\allowbreak{}basis; label\_\allowbreak{}inclusion\_\allowbreak{}matrix; role\_\allowbreak{}intertwining\_\allowbreak{}metrics; corner\_\allowbreak{}embed; corner\_\allowbreak{}restrict; common\_\allowbreak{}ambient\_\allowbreak{}interlevel\_\allowbreak{}schur; resolved\_\allowbreak{}support\_\allowbreak{}graph\_\allowbreak{}metrics\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & directed Schur-DtN response & non-symmetric local response, S/A decomposition input, finite J object & class DirectedSchurResponse; state\_\allowbreak{}directed\_\allowbreak{}edges; directed\_\allowbreak{}local\_\allowbreak{}matrix; directed\_\allowbreak{}schur\_\allowbreak{}response; directed\_\allowbreak{}schur\_\allowbreak{}response\_\allowbreak{}from\_\allowbreak{}model; directed\_\allowbreak{}environment\_\allowbreak{}port\_\allowbreak{}response\_\allowbreak{}from\_\allowbreak{}model; build\_\allowbreak{}coarse\_\allowbreak{}frontier\_\allowbreak{}sibling\_\allowbreak{}regions; region\_\allowbreak{}frontier\_\allowbreak{}level; region\_\allowbreak{}is\_\allowbreak{}coarse\_\allowbreak{}frontier; signed\_\allowbreak{}role\_\allowbreak{}basis\_\allowbreak{}F1F2; split\_\allowbreak{}symmetric\_\allowbreak{}skew; j\_\allowbreak{}finite\_\allowbreak{}object\_\allowbreak{}from\_\allowbreak{}SA\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & finite response algebra and GNS data & generator closure, state Gram quotient support, density projection & class AlgebraBasis; class GNSData; rank\_\allowbreak{}one; add\_\allowbreak{}to\_\allowbreak{}basis; algebra\_\allowbreak{}closure; project\_\allowbreak{}coeffs; reconstruct; span\_\allowbreak{}residual; positive\_\allowbreak{}density\_\allowbreak{}from\_\allowbreak{}response; gens\_\allowbreak{}from\_\allowbreak{}response; build\_\allowbreak{}algebras; state\_\allowbreak{}value; ...\\
\hline
\code{core/compressed\_\allowbreak{}state.py} & compressed carrier state & role/atom state compression and projective distributions & compressed\_\allowbreak{}state\_\allowbreak{}object; compressed\_\allowbreak{}projective\_\allowbreak{}distribution; values\_\allowbreak{}for\_\allowbreak{}keys; key\_\allowbreak{}is\_\allowbreak{}center; sector\_\allowbreak{}profile\_\allowbreak{}tv\\
\hline
\code{core/operator\_\allowbreak{}test\_\allowbreak{}config.py} & finite parameter iterator & explicit finite scan configuration & class OperatorTestConfig; iter\_\allowbreak{}growth\_\allowbreak{}models\\
\hline
\code{core/region\_\allowbreak{}response.py} & regional response object & region-level density and signed orientation metrics & class RegionalResponse; sibling\_\allowbreak{}pair\_\allowbreak{}regions; region\_\allowbreak{}size\_\allowbreak{}meta; positive\_\allowbreak{}support\_\allowbreak{}density\_\allowbreak{}from\_\allowbreak{}response; regional\_\allowbreak{}response; signed\_\allowbreak{}orientation\_\allowbreak{}metrics\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & local operator algebra support & role support, commutants, Tomita metrics, node-level embeddings & operator\_\allowbreak{}scale\_\allowbreak{}metadata; local\_\allowbreak{}operator\_\allowbreak{}generators; role\_\allowbreak{}coordinate\_\allowbreak{}mapping; role\_\allowbreak{}support\_\allowbreak{}indices; role\_\allowbreak{}support\_\allowbreak{}projector; independently\_\allowbreak{}restricted\_\allowbreak{}operator\_\allowbreak{}algebra; independent\_\allowbreak{}embedding\_\allowbreak{}metrics; local\_\allowbreak{}operator\_\allowbreak{}algebras; max\_\allowbreak{}span\_\allowbreak{}residual; max\_\allowbreak{}star\_\allowbreak{}residual; joined\_\allowbreak{}algebra; commutator\_\allowbreak{}metrics; ...\\
\hline
\code{core/entropy\_\allowbreak{}quantities.py} & finite entropy functionals & tolerance-resolved support entropy, relative entropy, Jensen-Shannon divergence & von\_\allowbreak{}neumann\_\allowbreak{}entropy\_\allowbreak{}no\_\allowbreak{}epsilon; quantum\_\allowbreak{}relative\_\allowbreak{}entropy\_\allowbreak{}no\_\allowbreak{}epsilon; jensen\_\allowbreak{}shannon\_\allowbreak{}divergence\_\allowbreak{}no\_\allowbreak{}epsilon; record\_\allowbreak{}live\_\allowbreak{}entropy\_\allowbreak{}metrics\\
\hline
\code{core/refined\_\allowbreak{}port\_\allowbreak{}basis.py} & refined port basis & boundary role refinement and refined support algebras & refined\_\allowbreak{}boundary\_\allowbreak{}role\_\allowbreak{}basis; refined\_\allowbreak{}regional\_\allowbreak{}response; refined\_\allowbreak{}support\_\allowbreak{}algebra\\
\bottomrule
\end{longtable}

\newpage
\section{Derived-quantity module map}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.23\linewidth}>{\raggedright\arraybackslash}p{0.13\linewidth}>{\raggedright\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}p{0.38\linewidth}}
\caption{Derived modules in derivation order.}\label{tab:derived-map}\\
\toprule
\textbf{Module} & \textbf{Mathematical row family} & \textbf{Role in derivation} & \textbf{Principal code objects}\\
\midrule
\endfirsthead
\toprule
\textbf{Module} & \textbf{Mathematical row family} & \textbf{Role in derivation} & \textbf{Principal code objects}\\
\midrule
\endhead
\code{derived\_\allowbreak{}quantities/baseline.py} & baseline derivation ledger & genesis, projection grammar, carrier states, orientation, region/GNS rows & level\_\allowbreak{}models; genesis\_\allowbreak{}rows; projection\_\allowbreak{}grammar\_\allowbreak{}rows; carrier\_\allowbreak{}state\_\allowbreak{}rows; orientation\_\allowbreak{}rows; region\_\allowbreak{}and\_\allowbreak{}gns\_\allowbreak{}rows\\

\hline
\code{derived\_\allowbreak{}quantities/gns\_\allowbreak{}cyclicity\_\allowbreak{}controls.py} & finite GNS cyclicity controls & full-algebra positive controls and proper-ambient-subalgebra negative controls & finite\_\allowbreak{}gns\_\allowbreak{}cyclicity\_\allowbreak{}control\_\allowbreak{}rows\\\hline
\code{derived\_\allowbreak{}quantities/finite\_\allowbreak{}structure\_\allowbreak{}theorem\_\allowbreak{}controls.py} & six finite structural controls & replay, Schur positivity, GNS, sign reversal, backreaction separation, and prefix handoff & finite\_\allowbreak{}structure\_\allowbreak{}theorem\_\allowbreak{}control\_\allowbreak{}rows\\\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & nested carrier and corner-handoff rows & growing address-coordinate roles, exact carrier embeddings, common-ambient Schur, conditional state/GNS, and finite-\(J\) naturality & build\_\allowbreak{}nested\_\allowbreak{}snapshot; nested\_\allowbreak{}carrier\_\allowbreak{}rows; nested\_\allowbreak{}handoff\_\allowbreak{}rows; common\_\allowbreak{}ambient\_\allowbreak{}schur\_\allowbreak{}rows; nested\_\allowbreak{}multiscale\_\allowbreak{}summary\_\allowbreak{}rows\\\hline
\code{derived\_\allowbreak{}quantities/birth\_\allowbreak{}linearization\_\allowbreak{}invariance.py} & birth-linearization residuals & rank/reverse-rank address-level comparisons for \code{slot\_\allowbreak{}step} and \code{layer\_\allowbreak{}batch} & birth\_\allowbreak{}linearization\_\allowbreak{}invariance\_\allowbreak{}rows\\
\hline
\code{derived\_\allowbreak{}quantities/rank\_\allowbreak{}kernel\_\allowbreak{}conditions.py} & rank-kernel measurements & local response density, coverage, constants, regional rank/kernel rows & local\_\allowbreak{}s\_\allowbreak{}response\_\allowbreak{}density; measure\_\allowbreak{}rank\_\allowbreak{}kernel\_\allowbreak{}condition\_\allowbreak{}rows; construction\_\allowbreak{}coverage\_\allowbreak{}rows; fixed\_\allowbreak{}rule\_\allowbreak{}constants\_\allowbreak{}measurement\_\allowbreak{}rows; regional\_\allowbreak{}rank\_\allowbreak{}kernel\_\allowbreak{}condition\_\allowbreak{}rows; terminal\_\allowbreak{}density\_\allowbreak{}state\_\allowbreak{}measurement\_\allowbreak{}rows\\
\hline
\code{derived\_\allowbreak{}quantities/compressed\_\allowbreak{}state\_\allowbreak{}projection\_\allowbreak{}consistency.py} & compressed-state projectivity check & compressed carrier distributions and construction track ledger & compressed\_\allowbreak{}carrier\_\allowbreak{}state\_\allowbreak{}rows; state\_\allowbreak{}construction\_\allowbreak{}track\_\allowbreak{}ledger\_\allowbreak{}rows\\
\hline
\code{derived\_\allowbreak{}quantities/structural\_\allowbreak{}ledgers.py} & live-record structural ledger & parameter purity, history delta, carrier effects, state sectors & is\_\allowbreak{}reference\_\allowbreak{}model; parameter\_\allowbreak{}purity\_\allowbreak{}rows; live\_\allowbreak{}record\_\allowbreak{}structural\_\allowbreak{}calculation\_\allowbreak{}ledger\_\allowbreak{}rows; live\_\allowbreak{}record\_\allowbreak{}history\_\allowbreak{}delta\_\allowbreak{}ledger\_\allowbreak{}rows; carrier\_\allowbreak{}effect\_\allowbreak{}operator\_\allowbreak{}rows; state\_\allowbreak{}sector\_\allowbreak{}decomposition\_\allowbreak{}rows\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & interlevel operator residuals & role projection, GNS/algebra, CE/modular residuals & label-projection helpers; matrix\_\allowbreak{}log\_\allowbreak{}spd; commutator\_\allowbreak{}delta; interlevel\_\allowbreak{}operator\_\allowbreak{}rows\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} & operator-stack seam residuals & seam localization, level scaling, map naturality & operator\_\allowbreak{}stack\_\allowbreak{}seam\_\allowbreak{}localization\_\allowbreak{}rows; operator\_\allowbreak{}stack\_\allowbreak{}live\_\allowbreak{}record\_\allowbreak{}sym\_\allowbreak{}comparison\_\allowbreak{}rows; operator\_\allowbreak{}stack\_\allowbreak{}level\_\allowbreak{}scaling\_\allowbreak{}rows; operator\_\allowbreak{}stack\_\allowbreak{}map\_\allowbreak{}naturality\_\allowbreak{}measurement\_\allowbreak{}rows; write\_\allowbreak{}operator\_\allowbreak{}stack\_\allowbreak{}residual\_\allowbreak{}report\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & operator-stack consistency checks & role dimensions, generator rank, coordinate gauge, response model, skew survival & operator\_\allowbreak{}stack\_\allowbreak{}role\_\allowbreak{}dimension\_\allowbreak{}condition\_\allowbreak{}note\_\allowbreak{}rows; operator\_\allowbreak{}stack\_\allowbreak{}generator\_\allowbreak{}rank\_\allowbreak{}condition\_\allowbreak{}note\_\allowbreak{}rows; operator\_\allowbreak{}stack\_\allowbreak{}coordinate\_\allowbreak{}gauge\_\allowbreak{}condition\_\allowbreak{}note\_\allowbreak{}rows; operator\_\allowbreak{}stack\_\allowbreak{}boundary\_\allowbreak{}response\_\allowbreak{}model\_\allowbreak{}condition\_\allowbreak{}note\_\allowbreak{}rows; operator\_\allowbreak{}stack\_\allowbreak{}skew\_\allowbreak{}survival\_\allowbreak{}condition\_\allowbreak{}note\_\allowbreak{}rows; operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks\_\allowbreak{}summary\_\allowbreak{}rows; write\_\allowbreak{}operator\_\allowbreak{}stack\_\allowbreak{}condition\_\allowbreak{}consistency\_\allowbreak{}report\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & directed operator stack & directed response construction, S/A rows, skew survival, finite J comparison & directed\_\allowbreak{}response\_\allowbreak{}construction\_\allowbreak{}rows; directed\_\allowbreak{}sa\_\allowbreak{}decomposition\_\allowbreak{}rows; directed\_\allowbreak{}signed\_\allowbreak{}role\_\allowbreak{}survival\_\allowbreak{}rows; directed\_\allowbreak{}boundary\_\allowbreak{}response\_\allowbreak{}model\_\allowbreak{}comparison\_\allowbreak{}rows; directed\_\allowbreak{}skew\_\allowbreak{}survival\_\allowbreak{}rows; directed\_\allowbreak{}operator\_\allowbreak{}transport\_\allowbreak{}rows; directed\_\allowbreak{}j\_\allowbreak{}finite\_\allowbreak{}object\_\allowbreak{}comparison\_\allowbreak{}rows; directed\_\allowbreak{}operator\_\allowbreak{}stack\_\allowbreak{}summary\_\allowbreak{}rows; write\_\allowbreak{}directed\_\allowbreak{}operator\_\allowbreak{}stack\_\allowbreak{}report\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & directed current transport & boundary prefix transport, composition, J-orientation transport, large-L coverage & directed\_\allowbreak{}current\_\allowbreak{}transport\_\allowbreak{}rows; directed\_\allowbreak{}current\_\allowbreak{}composition\_\allowbreak{}rows; directed\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}summary\_\allowbreak{}rows; write\_\allowbreak{}directed\_\allowbreak{}current\_\allowbreak{}transport\_\allowbreak{}report; directed\_\allowbreak{}large\_\allowbreak{}L\_\allowbreak{}region\_\allowbreak{}coverage\_\allowbreak{}rows; directed\_\allowbreak{}large\_\allowbreak{}L\_\allowbreak{}coverage\_\allowbreak{}summary\_\allowbreak{}rows; write\_\allowbreak{}directed\_\allowbreak{}region\_\allowbreak{}coverage\_\allowbreak{}report\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & J-orientation projectivity & orientation snapshots, interlevel transport, composition, sign scope & j\_\allowbreak{}orientation\_\allowbreak{}snapshot\_\allowbreak{}rows; j\_\allowbreak{}orientation\_\allowbreak{}transport\_\allowbreak{}rows; j\_\allowbreak{}orientation\_\allowbreak{}composition\_\allowbreak{}rows; j\_\allowbreak{}orientation\_\allowbreak{}sign\_\allowbreak{}scope\_\allowbreak{}rows; j\_\allowbreak{}orientation\_\allowbreak{}projectivity\_\allowbreak{}summary\_\allowbreak{}rows; write\_\allowbreak{}b\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}projectivity\_\allowbreak{}report; a\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}snapshot\_\allowbreak{}rows; a\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}transport\_\allowbreak{}rows; a\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}composition\_\allowbreak{}rows; a\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}projectivity\_\allowbreak{}summary\_\allowbreak{}rows; ...\\
\hline
\code{derived\_\allowbreak{}quantities/local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation.py} & local/global J sign relation & global boundary sign rows and local comparison & global\_\allowbreak{}j\_\allowbreak{}boundary\_\allowbreak{}sign\_\allowbreak{}relation\_\allowbreak{}rows; local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}comparison\_\allowbreak{}rows; local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}summary\_\allowbreak{}rows; write\_\allowbreak{}local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation\_\allowbreak{}report\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & live-record backreaction current & regional A\_\allowbreak{}live-A\_\allowbreak{}record rows, growth, sensitivity, transport & backreaction\_\allowbreak{}current\_\allowbreak{}rows; backreaction\_\allowbreak{}growth\_\allowbreak{}profile\_\allowbreak{}rows; backreaction\_\allowbreak{}region\_\allowbreak{}parameter\_\allowbreak{}sensitivity\_\allowbreak{}rows; backreaction\_\allowbreak{}transport\_\allowbreak{}rows; backreaction\_\allowbreak{}current\_\allowbreak{}summary\_\allowbreak{}rows; write\_\allowbreak{}live\_\allowbreak{}record\_\allowbreak{}backreaction\_\allowbreak{}current\_\allowbreak{}report\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}birth\_\allowbreak{}relative.py} & birth-relative backreaction current & birth-relative ages, zero crossing, branching and region family summaries & birth\_\allowbreak{}relative\_\allowbreak{}backreaction\_\allowbreak{}rows; birth\_\allowbreak{}relative\_\allowbreak{}zero\_\allowbreak{}crossing\_\allowbreak{}rows; birth\_\allowbreak{}relative\_\allowbreak{}mode\_\allowbreak{}branching\_\allowbreak{}rows; birth\_\allowbreak{}relative\_\allowbreak{}region\_\allowbreak{}family\_\allowbreak{}rows; birth\_\allowbreak{}relative\_\allowbreak{}summary\_\allowbreak{}rows; write\_\allowbreak{}birth\_\allowbreak{}relative\_\allowbreak{}backreaction\_\allowbreak{}current\_\allowbreak{}report\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}branching\_\allowbreak{}shift.py} & branching zero-crossing shift & branching comparisons of birth-relative crossing locations & read\_\allowbreak{}csv\_\allowbreak{}rows; deduplicate\_\allowbreak{}mode\_\allowbreak{}branching\_\allowbreak{}rows; branching\_\allowbreak{}shift\_\allowbreak{}curve\_\allowbreak{}rows; branching\_\allowbreak{}shift\_\allowbreak{}summary\_\allowbreak{}rows; write\_\allowbreak{}branching\_\allowbreak{}zero\_\allowbreak{}crossing\_\allowbreak{}shift\_\allowbreak{}report\\
\hline
\code{derived\_\allowbreak{}quantities/computed\_\allowbreak{}status\_\allowbreak{}rows.py} & row aggregation & final tabular row aggregation and markdown writer; not a mathematical constructor & operator\_\allowbreak{}stack\_\allowbreak{}residuals\_\allowbreak{}classification\_\allowbreak{}rows; final\_\allowbreak{}computed\_\allowbreak{}status\_\allowbreak{}rows\_\allowbreak{}full; write\_\allowbreak{}markdown\_\allowbreak{}full\\
\bottomrule
\end{longtable}

\newpage
\section{Core construction initialized by the empty configuration}
\subsection{Finite arithmetic layer}
\paragraph{Code map.} The module \code{core/math\_\allowbreak{}utils.py} defines finite numerical primitives: Frobenius norm, total variation distance, probability normalization, and row-metric extraction. These are not CNNA axioms; they are deterministic finite arithmetic functions used by all later measurements.

\begin{definition}[Finite probability normalization]
For a finite vector or dictionary, the implementation first replaces every negative entry, and for array inputs every non-finite entry, by zero. Writing the resulting values as \(x_i^+\) and \(s=\sum_i x_i^+\), the implemented normalization is
\[
  \mathcal N_{\varepsilon}(x)=
  \begin{cases}
    (x_i^+/s)_i, & s>\varepsilon,\\[0.4em]
    (1/n,\ldots,1/n), & s\le\varepsilon\text{ and }n>0,\\[0.4em]
    (), & n=0.
  \end{cases}
\]
For a non-empty zero-mass input the fallback is therefore the uniform distribution, not a zero-mass object. Dictionary normalization applies the same non-negative clipping; its keys are retained.
\end{definition}

\begin{lemma}[Total variation is a finite seminorm]
For two finite probability vectors \(p,q\), the implemented quantity
\[
  \operatorname{TV}(p,q)=\frac12\sum_i |p_i-q_i|
\]
vanishes when \(p=q\) and is non-negative.
\end{lemma}
\begin{proof}
\textbf{Object.} The object is the pair of finite arrays used by \code{tv\_\allowbreak{}arr} or dictionaries used by \code{tv}. \textbf{Proof.} Each summand \(|p_i-q_i|\) is non-negative; hence the sum and one-half multiple are non-negative. If \(p=q\), each summand is zero. \textbf{Counter-check.} The converse requires the index supports to be compared after the common-key completion used by the dictionary implementation. \textbf{Conclusion.} The quantity is an exact finite discrepancy measure, not a fitted parameter.
\end{proof}



\subsection{Empty-set growth object}
\paragraph{Code map.} The module \code{core/emptyset\_\allowbreak{}growth.py} contains \code{RuleCoefficients}, \code{Node}, \code{Event}, \code{OpenBirthSlot}, \code{GrowthStep}, and \code{EmptySetGrowthModel}. The constructor records \code{empty\_\allowbreak{}state}, creates the root by \code{birth\_\allowbreak{}root\_\allowbreak{}from\_\allowbreak{}empty}, and then processes finite open child slots. The source separates causal depth, sibling slot rank, technical linearization index, and update schedule. It does not treat the total event-list order as the source temporal object.

\begin{definition}[Finite CNNA growth approximant with schedule]
For branching arity \(b\ge 2\), level \(L\ge 0\), mode \(m\in\{\mathrm{linear},\mathrm{log},\mathrm{saturating}\}\), and growth schedule \(\mathfrak{s}\in\{\mathrm{slot\_step},\mathrm{layer\_batch}\}\), the finite approximant is
\begin{equation}
  G_{b,L,m,\mathfrak{s}}=(V,\mathcal E,E_{\mathrm{record}},E_{\mathrm{live}},a,\ell,p,d,\tau,r,\lambda,g,g_{\mathrm{birth}},q).
  \label{eq:finite-growth-approximant}
\end{equation}
Here \(V\) is the finite node list; \(a(v)\) is the finite address; \(\ell(v)\) is the address level; \(p(v)\) is the parent except for the root; \(d(v)\) is the recorded causal depth; \(\tau(v)\) is the event-list index of the selected finite execution; \(r(v)\) is the sibling slot rank; \(\lambda(v)\) is the linearization index inside the schedule; \(g(v)\) is the current node load; \(g_{\mathrm{birth}}(v)\) is the load at the birth update; and \(q(v)\) is the recorded response weight \code{lapse\_\allowbreak{}weight}. The edge dictionaries \(E_{\mathrm{record}}\) and \(E_{\mathrm{live}}\) are finite directed weighted dictionaries.
\end{definition}

\begin{definition}[Initial boundary event]
The transition from the empty state to the root is recorded as \code{birth\_\allowbreak{}root\_\allowbreak{}from\_\allowbreak{}empty}. It is the finite initial boundary event of the implemented construction. It is not derived from a prior response matrix, because before the root there is no finite parent, boundary, sibling set, or conductance environment in the source tree.
\end{definition}

\begin{definition}[Open birth slot, saturation, and finite growth step]
For a parent node \(p\), \code{open\_\allowbreak{}birth\_\allowbreak{}slots} returns one \code{OpenBirthSlot} for each unoccupied rank \(r\in\{0,\ldots,b-1\}\). A parent is saturated exactly when its \code{child\_\allowbreak{}by\_\allowbreak{}rank} dictionary has cardinality \(b\). A \code{GrowthStep} closes one such slot and records the slot, causal predecessors, occupied sibling slots before the update, environment load, birth weight, response weight, and linearization index.
\end{definition}

\begin{definition}[Growth schedules]
The schedule \code{slot\_\allowbreak{}step} linearizes open slots and applies one \code{GrowthStep} immediately. The schedule \code{layer\_\allowbreak{}batch} first constructs all \code{GrowthStep} objects for the open slots of one causal depth from the same pre-commit state, then commits the births, and then adds sibling relations by slot rank. Thus \code{layer\_\allowbreak{}batch} removes slot-sibling update order inside a causal layer; it retains parent-before-child causal order and slot-rank structure.
\end{definition}

\begin{definition}[Symmetric environment load of an open slot]
For a parent node \(p\) and the occupied sibling set \(U_p\) read from \code{child\_\allowbreak{}by\_\allowbreak{}rank}, the function \code{\_birth\_\allowbreak{}environment\_\allowbreak{}load} computes the finite scalar
\begin{equation}
  h(p,U_p)=g(p)+\sum_{a\in \mathrm{Anc}(p)}\frac{g(a)}{(\mathrm{depth}(a,p)+1)^2}
  +\begin{cases}
    \dfrac{\sum_{s\in U_p} g(s)}{|U_p|+1}, & U_p\ne\varnothing,\\[0.4em]
    0, & U_p=\varnothing .
  \end{cases}
  \label{eq:birth-environment-load}
\end{equation}
The sibling contribution is a set sum over occupied sibling nodes. It has no factor depending on the enumeration position of a sibling in a previous birth sequence.
\end{definition}

\begin{definition}[Branching-derived rule coefficients]
The function \code{rule\_coefficients} maps the arity $b$ to the tuple $c_b$ with fields and values
\begin{equation}
\begin{aligned}
  c_b.\code{env\_birth\_edge\_bias} &= \frac{1}{(b+1)^2}, &
  c_b.\code{forward\_rank\_bias} &= \frac{1}{b+3},\\
  c_b.\code{backward\_base} &= \frac12+\frac{1}{2(b+2)}, &
  c_b.\code{backward\_rank\_bias} &= \frac{1}{(b+1)(b+3)},\\
  c_b.\code{ancestor\_backreaction} &= \frac{1}{b(b+1)}, &
  c_b.\code{ancestor\_node\_load} &= \frac{1}{(b+2)^2},\\
  c_b.\code{sibling\_backreaction} &= \frac{1}{b(b+2)}, &
  c_b.\code{sibling\_forward\_asym} &= 1+\frac{1}{b+1},\\
  c_b.\code{sibling\_backward\_asym} &= 1-\frac{1}{b+1}, &
  c_b.\code{sibling\_node\_load} &= \frac{1}{(b+7)^2},\\
  c_b.\code{child\_env\_load} &= \frac{1}{(b+7)^2}.&&
\end{aligned}
\label{eq:branching-rule-coefficients}
\end{equation}
The tuple in Equation~\eqref{eq:branching-rule-coefficients} is evaluated from the single integer $b$.
\end{definition}

\begin{definition}[Mode-scale map and birth weight]
The function \code{\_mode\_scale} applies one of the three finite scalar maps
\begin{equation}
  \sigma_m(x)=
  \begin{cases}
    x, & m=\code{linear},\\
    \log(1+\max(0,x)), & m=\code{log},\\
    \dfrac{x}{1+|x|}, & m=\code{saturating}.
  \end{cases}
  \label{eq:mode-scale-map}
\end{equation}
For a slot of parent $p$, the corresponding \code{GrowthStep} stores
\begin{equation}
  g_{\rm birth}=1+\frac{\sigma_m(h(p,U_p))}{1+\ell(p)+b}.
  \label{eq:birth-weight}
\end{equation}
The same value is copied to \code{lapse\_weight}. The current load of the new child is then incremented by the separate child-environment update recorded in \code{child\_env\_load}.
\end{definition}

\begin{definition}[Base birth-edge weights]
For sibling rank $r\in\{0,\ldots,b-1\}$ let $\rho_r=(r+1)/b$ and
\begin{equation}
  w_0 = 1+c_b.\code{env\_birth\_edge\_bias}\;\sigma_m(h(p,U_p)).
  \label{eq:base-birth-edge-weight}
\end{equation}
The directed parent-child weights inserted at birth are
\begin{equation}
\begin{aligned}
  w_{p\to v} &= w_0\bigl(1+c_b.\code{forward\_rank\_bias}\;\rho_r\bigr),\\
  w_{v\to p} &= w_0\bigl(c_b.\code{backward\_base}+c_b.\code{backward\_rank\_bias}\;\rho_r\bigr).
\end{aligned}
\label{eq:directed-birth-edge-weights}
\end{equation}
These two directed weights are inserted into both the record and live edge dictionaries.
\end{definition}

\begin{proposition}[Node count of the complete finite approximant]
For \(G_{b,L,m,\mathfrak{s}}\) constructed by \code{EmptySetGrowthModel},
\begin{equation}
  |V|=\sum_{k=0}^L b^k.
  \label{eq:complete-approximant-node-count}
\end{equation}
\end{proposition}
\begin{proof}
\textbf{Object.} The object is the list \code{self.nodes}. \textbf{Step 1.} The constructor creates exactly one root node at level \(0\). \textbf{Step 2.} For every node at depth \(k<L\), \code{open\_\allowbreak{}birth\_\allowbreak{}slots} contains exactly the unoccupied ranks of that parent. \textbf{Step 3.} The schedules differ in commit order, but both close every open slot of the processed depth exactly once. \textbf{Step 4.} A closed slot of a level \(k\) parent creates one child at level \(k+1\). By induction, level \(k\) contains \(b^k\) addresses. \textbf{Counter-check.} The method \code{node\_\allowbreak{}count\_\allowbreak{}expected} implements the same finite sum. A mismatch is a construction mismatch for the selected schedule, not a continuum statement. \textbf{Conclusion.} The count is an exact finite identity of the generated approximant.
\end{proof}

\begin{proposition}[Causal depth is separated from linearization index]
For non-root nodes, \(d(v)=d(p(v))+1\) is the causal-depth relation recorded by the slot. The quantity \(\lambda(v)\) is the finite ordering index of the selected schedule and is not the parent-before-child relation.
\end{proposition}
\begin{proof}
\textbf{Object.} The object is the pair \code{OpenBirthSlot} and \code{GrowthStep}. \textbf{Step 1.} An open slot stores \code{causal\_\allowbreak{}depth = parent.level + 1}. \textbf{Step 2.} \code{\_linearize\_\allowbreak{}open\_\allowbreak{}slots} sorts slots by \code{rank} or \code{reverse\_\allowbreak{}rank} after causal depth and parent fields. \textbf{Step 3.} \code{GrowthStep.linearization\_\allowbreak{}index} records this schedule index. \textbf{Counter-check.} The derived row family \code{birth\_\allowbreak{}linearization\_\allowbreak{}invariance\_\allowbreak{}rows} compares \code{rank} and \code{reverse\_\allowbreak{}rank} by address-level residuals. In this package the \code{layer\_\allowbreak{}batch} route is the linearization-insensitive route for that comparison, while \code{slot\_\allowbreak{}step} records finite schedule dependence. \textbf{Conclusion.} The source separates causal order from slot linearization.
\end{proof}

\begin{proposition}[Layer-batch removes sampled slot-linearization dependence at address level]
For the implemented comparison \(\eta=\mathrm{rank}\) against \(\eta=\mathrm{reverse\_rank}\), the \code{layer\_\allowbreak{}batch} route gives identical address-indexed node fields and edge dictionaries up to the reported numerical tolerance. The \code{slot\_\allowbreak{}step} route need not do so.
\end{proposition}
\begin{proof}
\textbf{Object.} The objects are \code{OpenBirthSlot}, \code{GrowthStep}, and the edge dictionaries indexed back to node addresses. \textbf{Step 1.} In \code{layer\_\allowbreak{}batch}, the list of \code{GrowthStep} records is built before the corresponding children are committed. Therefore each step reads the same pre-commit occupied sibling set for its parent. \textbf{Step 2.} The environment load uses the symmetric set expression \(\sum_{s\in U_p}g(s)/(|U_p|+1)\), so it does not depend on an order of the occupied siblings. \textbf{Step 3.} The birth weights are stored inside the \code{GrowthStep} record and are then used by \code{\_apply\_\allowbreak{}growth\_\allowbreak{}step}. \textbf{Step 4.} Batch sibling relations are added after commit by grouping children by parent and sorting by \code{sibling\_\allowbreak{}rank}; the relation is a slot-rank relation, not a commit-order relation. \textbf{Counter-check.} The package exposes the \code{rank}/\code{reverse\_\allowbreak{}rank} comparison, not a full permutation harness. The \code{slot\_\allowbreak{}step} route can have non-zero residuals because each slot is applied before the next one is evaluated. \textbf{Conclusion.} The causal-layer schedule separates the finite parent-before-child relation from the sampled ordering of slots inside one causal depth.
\end{proof}

\begin{proposition}[Record-live separation]
At birth, a parent-child directed pair is inserted into both \(E_{\mathrm{record}}\) and \(E_{\mathrm{live}}\). Later ancestor and slot-sibling updates are inserted only into \(E_{\mathrm{live}}\) and node loads, not into \(E_{\mathrm{record}}\).
\end{proposition}
\begin{proof}
\textbf{Object.} The objects are the dictionaries \code{record\_\allowbreak{}edges} and \code{live\_\allowbreak{}edges}. \textbf{Step 1.} The birth edge weights \(w_{\rightarrow}\) and \(w_{\leftarrow}\) are computed from the \code{GrowthStep} record and inserted into both dictionaries in \code{\_apply\_\allowbreak{}growth\_\allowbreak{}step}. \textbf{Step 2.} Ancestor updates and sibling-slot relation updates call \code{add\_\allowbreak{}edge} only on \code{live\_\allowbreak{}edges}. \textbf{Step 3.} Under \code{layer\_\allowbreak{}batch}, the live updates of a causal layer use the \code{GrowthStep} fields evaluated from the frozen pre-commit state; record edges still store only the parent-child birth relation. \textbf{Step 4.} The same update changes current node loads \(g\), while \(g_{\mathrm{birth}}\) remains the value recorded at the birth update. \textbf{Counter-check.} \code{slot\_\allowbreak{}step} and \code{layer\_\allowbreak{}batch} can produce different live layers because \code{slot\_\allowbreak{}step} evaluates later slots after earlier commits. Record rows are closer to schedule-independent structure because they omit ancestor and slot-sibling live updates, but their numerical weights still come from the selected schedule. \textbf{Conclusion.} The code realizes two distinct finite layers: birth record and current live state.
\end{proof}

\begin{remark}[The sym edge layer is a readout, not a schedule]
The state selector \code{sym} is implemented by symmetrizing the adjacency read from \code{live\_\allowbreak{}edges}. It cancels directed skew information at readout level. It is not a separate growth schedule and it does not imply that \code{slot\_\allowbreak{}step} and \code{layer\_\allowbreak{}batch} have identical edge weights. The finite comparison represented in \code{birth\_\allowbreak{}linearization\_\allowbreak{}invariance\_\allowbreak{}rows} compares \code{rank} against \code{reverse\_\allowbreak{}rank} inside a selected schedule.
\end{remark}

\paragraph{Row-generation command: causal-layer route.}
{\scriptsize
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 run_cnna.py \
  --branching 3 \
  --levels 2 3 4 \
  --modes linear log saturating \
  --states live record sym \
  --max-regions 1 \
  --max-boundary 250 \
  --max-interior 350 \
  --directed-frontier-cap 5 \
  --algebra-tol 1e-10 \
  --algebra-max-iter 8 \
  --gns-tol 1e-10 \
  --growth-schedule layer_batch \
  --outdir outputs/growth_carrier_f1f2_layer_batch
\end{verbatim}
}

\paragraph{Comparison command: slot-step route.}
{\scriptsize
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 run_cnna.py \
  --branching 3 \
  --levels 2 3 4 \
  --modes linear log saturating \
  --states live record sym \
  --max-regions 1 \
  --max-boundary 250 \
  --max-interior 350 \
  --directed-frontier-cap 5 \
  --algebra-tol 1e-10 \
  --algebra-max-iter 8 \
  --gns-tol 1e-10 \
  --growth-schedule slot_step \
  --outdir outputs/growth_carrier_f1f2_slot_step_comparison
\end{verbatim}
}

\paragraph{Generated row families.}
The following readouts use only the two commands displayed above. They are not imported from earlier packages or reports.

\begin{longtable}{p{0.24\linewidth}p{0.20\linewidth}p{0.46\linewidth}}
\caption{Growth readout generated under the current growth rule.}\\
\toprule
\textbf{Row family} & \textbf{Schedule} & \textbf{Readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family} & \textbf{Schedule} & \textbf{Readout}\\
\midrule
\endhead
\src{emptyset_genesis_measurement.csv} & \code{layer\_batch}, \code{slot\_step} & For \(b=3\), \(L=2,3,4\), the generated node counts are \(13,40,121\), matching \(\sum_{k=0}^L3^k\); event counts are \(14,41,122\).\\\hline
\src{level_count_measurement.csv} & \code{layer\_batch}, \code{slot\_step} & Every level-count row has \code{ok=1}; generated counts are \(3^k\) at level \(k\le L\).\\\hline
\src{birth_linearization_invariance.csv} & \code{layer\_batch} & Across 27 rows, \code{edge\_linf\_by\_address}, \code{edge\_l1\_by\_address}, \code{node\_g\_linf\_by\_address}, and \code{birth\_g\_linf\_by\_address} are all zero; the largest orientation delta is \(3.6429\cdot10^{-17}\).\\\hline
\src{birth_linearization_invariance.csv} & \code{slot\_step} & Across 27 rows, the comparison records finite schedule dependence: max edge \(\ell_\infty=9.2504\cdot10^{-2}\), max edge \(\ell_1=9.2217\), max node-load \(\ell_\infty=2.5150\cdot10^{-1}\), max birth-weight \(\ell_\infty=2.3975\cdot10^{-1}\), max orientation delta \(2.6895\cdot10^{-2}\).\\\hline
\bottomrule
\end{longtable}


\subsection{Birth-relative complement meaning of CNNA}\label{sec:birth-relative-complement}
\paragraph{Terminology and code map.}
The name CNNA is used here for a \emph{ComplemeNt Net Architecture}. The word complement refers first to the finite carrier enlargement implemented by \code{EmptySetGrowthModel}; the word network refers to the directed couplings inserted when that enlargement is committed. These are two distinct steps and should not be conflated.

\begin{definition}[Birth-relative vertex complement]
Let $e$ be an accepted non-root birth event and let $v_e$ be its new node. Write $V_e^-$ for the vertex set immediately before \code{\_apply\_growth\_step} commits $v_e$, and $V_e^+$ for the vertex set immediately afterward. Then
\begin{equation}
  V_e^+=V_e^-\,\dot\cup\,\{v_e\},
  \qquad
  \{v_e\}=V_e^+\setminus V_e^-,
  \qquad
  V_e^-=V_e^+\setminus\{v_e\}.
  \label{eq:birth-relative-set-complement}
\end{equation}
The dot denotes disjoint union. The statement is relative to this finite update; it does not presuppose a fixed infinite universal carrier. The root event is the base case $V_0^-=\varnothing$, $V_0^+=\{r\}$; it creates the first coordinate but has no prior network to which it could be coupled.
\end{definition}

\begin{definition}[Coordinate complement]
For a finite vertex set $V$, let $\R^V$ denote the real coordinate space with standard basis $(\delta_v)_{v\in V}$. Zero extension along the inclusion $V_e^-\hookrightarrow V_e^+$ gives an injective map
\begin{equation}
  \iota_e:\R^{V_e^-}\longrightarrow\R^{V_e^+},
  \qquad
  (\iota_e x)(u)=
  \begin{cases}
    x(u), & u\in V_e^-,\\
    0, & u=v_e.
  \end{cases}
  \label{eq:birth-zero-extension}
\end{equation}
The post-birth carrier has the exact direct-sum decomposition
\begin{equation}
  \R^{V_e^+}
  =\iota_e(\R^{V_e^-})\oplus\operatorname{span}_{\R}\{\delta_{v_e}\}.
  \label{eq:birth-relative-coordinate-complement}
\end{equation}
Thus the newborn node contributes one new real coordinate direction complementary to the embedded pre-birth carrier.
\end{definition}

\begin{proposition}[Exactness and schedule scope of the complement step]
Equation~\eqref{eq:birth-relative-coordinate-complement} is exact for every committed node. For \code{slot\_step} it is also the primitive update decomposition. For \code{layer\_batch}, let $N_d$ be the nodes born at causal depth $d$ from one frozen pre-commit state $V_d^-$. The schedule-invariant causal statement is the batch decomposition
\begin{equation}
  V_d^+=V_d^-\,\dot\cup\,N_d,
  \qquad
  \R^{V_d^+}
  =\iota_d(\R^{V_d^-})\oplus
    \operatorname{span}_{\R}\{\delta_v:v\in N_d\}.
  \label{eq:layer-batch-coordinate-complement}
\end{equation}
The nodewise decompositions inside that batch remain exact, but their internal commit order is a technical linearization and is not promoted to an additional causal order.
\end{proposition}
\begin{proof}
\textbf{Object.} The objects are the address dictionary \code{addr\_to\_id}, the node list \code{nodes}, and the selected \code{GrowthStep} records. \textbf{Step 1.} Before committing a step, the source rejects any address already present in \code{addr\_to\_id}. Hence the new address is not in $V^-$. \textbf{Step 2.} The source appends exactly one node and enters exactly one new address, which proves Equation~\eqref{eq:birth-relative-set-complement}. \textbf{Step 3.} Every vector on $V^+$ splits uniquely into its restriction to $V^-$ and its coefficient at the new standard basis vector; this proves Equation~\eqref{eq:birth-relative-coordinate-complement}. \textbf{Step 4.} Under \code{layer\_batch}, all \code{GrowthStep} records of one depth are constructed before any of their nodes is committed. Distinct open slots have distinct addresses, so the same argument applied to the complete newborn set gives Equation~\eqref{eq:layer-batch-coordinate-complement}. \textbf{Counter-check.} The direct sum is a statement about the standard address-coordinate carrier. It is not yet a statement about orthogonality in a later response metric, GNS metric, or state-dependent inner product. \textbf{Conclusion.} The complement step is a finite exact carrier identity with an explicit schedule scope.
\end{proof}

\begin{definition}[Directed coupling of the complement]
Order the coordinates of one update as old vertices followed by the newborn set $N$. The record and live adjacency matrices have finite block forms
\begin{equation}
  W_{\rm record}^{+}
  =
  \begin{pmatrix}
    W_{\rm record}^{-} & C_{\rm parent}\\
    D_{\rm parent} & 0
  \end{pmatrix},
  \qquad
  W_{\rm live}^{+}
  =
  \begin{pmatrix}
    W_{\rm live}^{-} & C_{\rm live}\\
    D_{\rm live} & W_{NN}
  \end{pmatrix}.
  \label{eq:complement-coupling-blocks}
\end{equation}
Here $C_{\rm parent}$ and $D_{\rm parent}$ contain the two directed parent--child birth weights of Equation~\eqref{eq:directed-birth-edge-weights}. The live off-diagonal blocks additionally contain the implemented ancestor and sibling couplings, while $W_{NN}$ contains the slot-rank sibling relations among nodes born in the same layer. In a one-node \code{slot\_step} update, $W_{NN}=0$. Because the forward and backward coefficients are generally unequal, neither block matrix is required to be symmetric.
\end{definition}

\begin{proposition}[The complement is coupled rather than independent]
The carrier identity in Equation~\eqref{eq:birth-relative-coordinate-complement} does not make the newborn line dynamically independent of the old carrier. For every non-root birth, both parent--child entries in the record and live dictionaries are non-zero and are generated from the same finite growth step. The live layer can add further directed couplings to causal predecessors and sibling slots and can update existing node loads.
\end{proposition}
\begin{proof}
\textbf{Object.} The objects are \code{record\_edges}, \code{live\_edges}, and the node-load field $g$. \textbf{Step 1.} Equation~\eqref{eq:directed-birth-edge-weights} gives positive parent-to-child and child-to-parent weights for every admitted $b$, mode, and finite environment load generated by the source. \textbf{Step 2.} \code{\_apply\_growth\_step} inserts both weights into both edge dictionaries. \textbf{Step 3.} The ancestor loop inserts additional child-to-predecessor live entries and changes predecessor loads. \textbf{Step 4.} The sibling routines insert unequal forward/backward live entries according to slot rank. \textbf{Counter-check.} The set/direct-sum complement would remain true even if all cross-couplings were zero. Hence complementarity alone does not prove network interaction. \textbf{Conclusion.} CNNA combines an exact carrier complement with a separate generated coupling rule.
\end{proof}

\begin{remark}[What complement does not mean]
The term does not denote the graph complement, a Boolean complement, an orthogonal complement with respect to a derived matrix $S$, a commutant of an operator algebra, or a claim that the newborn degree of freedom is statistically independent. Relative to the terminal carrier one also has the tautology $V_L=(V_L\setminus\{v\})\dot\cup\{v\}$ for every vertex, but that terminal identity discards the birth provenance and is not the definition used here. Such stronger structures occur, if at all, only after additional definitions and tests. The primitive complement claims are the birth- and layer-relative Equations~\eqref{eq:birth-relative-set-complement}, \eqref{eq:birth-relative-coordinate-complement}, and \eqref{eq:layer-batch-coordinate-complement}.
\end{remark}

\begin{proposition}[Complement-to-response bridge and its non-implication]
Choose a finite selected set $B\dot\cup I$ after the directed complement couplings have been generated. Form the directed local matrix $K^{\rm dir}$ from the ordered weights and, when the interior solve is accepted, define
\begin{equation}
  K^{\rm dir}_{II}X=K^{\rm dir}_{IB},
  \qquad
  \Lambda_B^{\rm dir}=K^{\rm dir}_{BB}-K^{\rm dir}_{BI}X,
  \qquad
  \Lambda_B^{\rm dir}=S_B+A_B,
  \label{eq:complement-to-directed-response}
\end{equation}
with $S_B^T=S_B$ and $A_B^T=-A_B$ as in Equation~\eqref{eq:symmetric-skew-response-split}. The carrier-complement identities do not imply $A_B\ne0$. A non-zero skew response requires both asymmetric generated coupling data and survival of that asymmetry under the selected boundary/interior elimination and compression.
\end{proposition}
\begin{proof}
\textbf{Object.} The objects are the directed edge matrix, its local response matrix, and the accepted Schur response. \textbf{Step 1.} Equations~\eqref{eq:birth-relative-coordinate-complement} and \eqref{eq:layer-batch-coordinate-complement} only enlarge the coordinate domain. \textbf{Step 2.} Equation~\eqref{eq:complement-coupling-blocks} supplies the ordered couplings from which $K^{\rm dir}$ is built. \textbf{Step 3.} The Schur operation eliminates $I$ and returns a boundary matrix. \textbf{Step 4.} Every real square matrix has the exact symmetric/skew split. \textbf{Counter-check.} If the generated weights are replaced by a symmetric control, then the local Laplacian and its accepted Schur complement are symmetric and $A_B=0$ up to numerical residual. Conversely, a non-symmetric local matrix can still yield zero skew part on a particular compressed boundary. \textbf{Conclusion.} The logical chain is complement enlargement, directed coupling, Schur reduction, and only then symmetric/skew decomposition; none of these arrows may be reversed without an additional theorem.
\end{proof}

\subsection{Carrier and prefix projections}
\paragraph{Code map.} The module \code{core/projective\_\allowbreak{}maps.py} defines address truncation \code{prefix}, terminal carrier extraction, terminal state extraction, push-forward maps, center subsets, and response-energy distributions.

\begin{definition}[Normalized prefix push-forward]
Let \(\Omega_L\) be the terminal address set at level \(L\). For \(0\le k\le L\), define \(\pi_k:\Omega_L\to\Omega_k\) by address truncation and let the raw fiber sum be
\begin{equation}
  (\pi_{k\,*}^{\rm raw}\mu)(u)=\sum_{\omega:\pi_k(\omega)=u}\mu(\omega).
  \label{eq:terminal-prefix-pushforward}
\end{equation}
The function \code{push\_\allowbreak{}forward} returns \(\mathcal N_{\varepsilon}(\pi_{k\,*}^{\rm raw}\mu)\). Thus it agrees with the ordinary push-forward for an already normalized non-negative input, but it renormalizes a general finite input and applies the uniform fallback when the raw output has no positive mass.
\end{definition}

\begin{definition}[Terminal carrier and terminal diagonal state]
The terminal carrier is the uniform finite distribution on \(\Omega_L\). For a terminal node \(v\), let \(I_{\rm abs}(v)\) be the sum of absolute weights of all selected directed edges incident to \(v\), counting incoming and outgoing incidences exactly as in the edge dictionary. The unnormalized terminal-state weight is
\[
  d_s(v)=\max\!\left(\varepsilon,\,g(v)+0.05\,I_{\rm abs}(v)\right),
\]
and the terminal diagonal state is \(\mathcal N_{\varepsilon}(d_s)\). The \code{record} state reads \code{record\_edges}; \code{live} and \code{sym} use the same positive proxy from \code{live\_edges}. Consequently the terminal positive proxy does not distinguish live from sym, although their directed response readouts do. Signed current is never inserted into this positive carrier.
\end{definition}

\begin{lemma}[Probability preservation for normalized inputs]
If \(\mu\) is a finite non-negative probability distribution, then \code{push\_\allowbreak{}forward} returns the ordinary prefix push-forward and its total mass is one.
\end{lemma}
\begin{proof}
\textbf{Object.} The object is the dictionary passed to \code{push\_\allowbreak{}forward}. \textbf{Step 1.} Every terminal key has exactly one truncated prefix. \textbf{Step 2.} The raw fiber sum in Equation~\eqref{eq:terminal-prefix-pushforward} partitions the source support and therefore has total mass one. \textbf{Step 3.} Applying \(\mathcal N_{\varepsilon}\) to a non-negative mass-one dictionary leaves it unchanged. \textbf{Counter-check.} For a non-normalized input, the implementation returns the normalized raw push-forward rather than preserving the original total mass. \textbf{Conclusion.} Exact projectivity statements apply to the normalized probability inputs used by the carrier rows.
\end{proof}

\paragraph{Generated row families.}
\begin{longtable}{p{0.24\linewidth}p{0.20\linewidth}p{0.46\linewidth}}
\caption{Carrier and prefix readout generated under the current growth rule.}\\
\toprule
\textbf{Row family} & \textbf{Schedule} & \textbf{Readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family} & \textbf{Schedule} & \textbf{Readout}\\
\midrule
\endhead
\src{projection_grammar.csv} & \code{layer\_batch}, \code{slot\_step} & 9 generated rows per schedule; address truncation flag is 1 in every row; status string is \code{projection\_grammar\_residual\_le\_tolerance}.\\\hline
\src{carrier_projectivity.csv} & \code{layer\_batch}, \code{slot\_step} & 9 generated rows per schedule; max carrier TV is \(0\) for both schedules.\\\hline
\src{terminal_diagonal_state_measurement.csv} & \code{layer\_batch} & Trace range of the generated terminal diagonal states is \([1,1+2.22\cdot10^{-16}]\).\\\hline
\src{terminal_diagonal_state_projectivity.csv} & \code{layer\_batch} & Max terminal-state projectivity TV is \(9.8999\cdot10^{-4}\).\\\hline
\src{terminal_diagonal_state_projectivity.csv} & \code{slot\_step} & Max terminal-state projectivity TV is \(2.3796\cdot10^{-2}\). This comparison belongs to the schedule surface, not to the carrier identity.\\\hline
\bottomrule
\end{longtable}

\subsection{Whole-network F1/F2 axes and signed current scalar}
The historical row label \code{F2\_birth\_order} denotes the canonical sibling-slot rank encoded in node addresses. It is not the execution order of the event list; under \code{layer\_batch}, births at one causal depth are evaluated from the same pre-commit state.

\paragraph{Code map.} The module \code{core/signed\_\allowbreak{}current.py} constructs an orthonormal F1/F2 pair and an orientation measurement from finite node-address data and a selected edge dictionary. This whole-network current is introduced before Schur--DtN response; it does not require a selected boundary/interior cut.

\begin{definition}[Whole-network F1/F2 plane]
The function \code{F1\_F2\_vectors} assigns to a node $v$ with address $a(v)=(r_1,\ldots,r_{\ell(v)})$ the finite coordinates
\begin{equation}
\begin{aligned}
  F_1(v)&=\begin{cases}
    \ell(v)/L, & L>0,\\
    0, & L=0,
  \end{cases}
  &
  F_2(v)&=\sum_{d=1}^{\ell(v)}\frac{1}{d}
  \frac{r_d-(b-1)/2}{\max(1,(b-1)/2)}.
\end{aligned}
\label{eq:whole-network-f1-f2-fields}
\end{equation}
For the root the sum is empty and hence zero. The function \code{orthonormal\_pair} mean-centers and Gram-Schmidt orthonormalizes these two vectors when the finite rank is above the implemented fallback threshold.
\end{definition}

\begin{definition}[Whole-network signed-current scalar]
For a selected edge layer, \code{orientation\_\allowbreak{}measurement} computes the directed norm, symmetric norm, skew norm, relative skew norm, and the scalar circulation in the F1/F2 plane. For \code{state=sym}, the skew part is set to zero at readout level.
\end{definition}

\begin{proposition}[F1/F2 current is independent of Schur reduction]
The whole-network F1/F2 scalar is computed from the finite edge dictionary and node-address vectors before any Schur boundary/interior split is chosen.
\end{proposition}
\begin{proof}
\textbf{Object.} The object is the output of \code{orientation\_\allowbreak{}measurement}. \textbf{Step 1.} \code{F1\_\allowbreak{}F2\_\allowbreak{}vectors} reads only node levels and address ranks. \textbf{Step 2.} \code{orientation\_\allowbreak{}measurement} reads \code{record\_\allowbreak{}edges} for \code{record}, \code{live\_\allowbreak{}edges} for \code{live}, and the symmetrized readout for \code{sym}. \textbf{Step 3.} No boundary list, interior list, Schur solve, or response compression is called. \textbf{Counter-check.} Regional F1/F2 role bases in later directed-response sections are different objects; they are not this whole-network scalar. \textbf{Conclusion.} The F1/F2 current is a finite whole-network measurement attached to the growth and carrier layer.
\end{proof}

\paragraph{Generated row families.}
\begin{longtable}{p{0.24\linewidth}p{0.20\linewidth}p{0.46\linewidth}}
\caption{Whole-network F1/F2 readout generated under the current growth rule.}\\
\toprule
\textbf{Row family} & \textbf{Schedule} & \textbf{Readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family} & \textbf{Schedule} & \textbf{Readout}\\
\midrule
\endhead
\src{f1f2_skew_orientation_measurement.csv} & \code{layer\_batch} & 27 generated rows; max post-Gram-Schmidt \(|F_1\cdot F_2|=1.3245\cdot10^{-17}\); max relative skew is \(2.4203\cdot10^{-1}\) for \code{live}, \(2.6829\cdot10^{-1}\) for \code{record}, and \(0\) for \code{sym}.\\\hline
\src{f1f2_skew_orientation_measurement.csv} & \code{layer\_batch} & Max absolute F1/F2 plane circulation is \(3.2839\cdot10^{-2}\) for \code{live}, \(3.2712\cdot10^{-2}\) for \code{record}, and \(0\) for \code{sym}.\\\hline
\src{live_record_history_delta.csv} & \code{layer\_batch} & 9 generated rows; max directed live-minus-record Frobenius norm is \(7.6674\cdot10^{-1}\); max terminal-state TV between live and record is \(1.0644\cdot10^{-4}\).\\\hline
\src{f1f2_skew_orientation_measurement.csv} & \code{slot\_step} & Comparison route: max absolute F1/F2 plane circulation is \(4.5201\cdot10^{-2}\) for \code{live}, \(4.7143\cdot10^{-2}\) for \code{record}, and \(0\) for \code{sym}.\\\hline
\bottomrule
\end{longtable}


\subsection{Symmetric Schur--DtN response on a selected finite cut}
\paragraph{Code map.} The module \code{core/schur\_\allowbreak{}dtn.py} defines \code{SchurResponse}, \code{RegionSpec}, \code{schur\_\allowbreak{}response}, \code{schur\_\allowbreak{}response\_\allowbreak{}from\_\allowbreak{}model}, sibling-region construction, boundary role bases, response compression, and atom keys. The selected finite cut enters here for the first time: a boundary list \(B\), an interior list \(I\), and a finite local matrix \(K\) are passed to the Schur reduction.

\begin{definition}[Finite Schur--DtN response]
Given a finite symmetric local matrix \(K\) and a disjoint boundary/interior split \(B\sqcup I\), the finite response matrix is
\begin{equation}
  \Lambda_B = K_{BB}-K_{BI}X,\qquad K_{II}X=K_{IB}.
  \label{eq:finite-schur-dtn-response}
\end{equation}
when the interior block \(K_{II}\) satisfies the condition-number guard. The source uses \code{np.linalg.solve}; it does not form an explicit matrix inverse.
\end{definition}

\begin{proposition}[Accepted Schur response records a finite linear solve]
If \code{schur\_\allowbreak{}response} returns \code{ok=True}, then the returned object contains the Schur matrix, the condition number of \(K_{II}\), the solve residual \(\|K_{II}X-K_{IB}\|_F/\max(\|K_{IB}\|_F,\varepsilon)\), and the row-sum residual of \(\Lambda_B\).
\end{proposition}
\begin{proof}
\textbf{Object.} The object is \code{SchurResponse}. \textbf{Step 1.} The function rejects empty boundary lists, boundary/interior overlap, and interior blocks above the condition guard. \textbf{Step 2.} It solves \(K_{II}X=K_{IB}\). \textbf{Step 3.} It returns the response in Equation~\eqref{eq:finite-schur-dtn-response}, symmetrized as \((\Lambda_B+\Lambda_B^T)/2\). In \code{schur\_\allowbreak{}response\_\allowbreak{}from\_\allowbreak{}model}, diagonal degrees include conductance from selected nodes to the full current network, while off-diagonal entries are retained only between selected nodes. Omitted external neighbors therefore remain as grounded diagonal load. \textbf{Counter-check.} The resulting open-grounded response need not satisfy \(\Lambda_B\mathbf 1=0\); the row-sum residual measures this finite leakage. Non-accepted branches return an error string and no response matrix. \textbf{Conclusion.} The accepted row is a finite open-grounded Schur reduction with recorded numerical guards, not necessarily a conservative response of an isolated selected subgraph.
\end{proof}

\paragraph{Execution command.} The following command generated the row families read in this subsection and the two following subsections. It uses the current growth rule and the causal-layer schedule.
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 run_cnna.py \
  --branching 3 \
  --levels 4 \
  --modes linear log saturating \
  --states live record sym \
  --max-regions 2 \
  --max-boundary 600 \
  --max-interior 900 \
  --directed-frontier-cap 6 \
  --algebra-tol 1e-10 \
  --algebra-max-iter 8 \
  --gns-tol 1e-10 \
  --growth-schedule layer_batch \
  --outdir outputs/schur_directed_j_layer_batch_reduced
\end{verbatim}

\begin{longtable}{p{0.27\linewidth}p{0.17\linewidth}p{0.48\linewidth}}
\caption{Generated Schur response rows under the current growth rule.}\\
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endhead
\src{regional\_schur\_dtn\_response\_measurement.csv} & 18 & All rows have \code{response\_ok=1}. Max \code{cond\_KII} is \(2.5511\), max solve residual is \(1.9261\cdot10^{-16}\), max row-sum residual is \(2.1398\), and the compressed response dimension is \(3\).\\\hline
\src{regional\_schur\_dtn\_response\_measurement.csv} & 18 & Max compressed relative skew is \(1.4703\cdot10^{-17}\) for \code{live}, \(9.0776\cdot10^{-18}\) for \code{record}, and \(1.4703\cdot10^{-17}\) for \code{sym}.\\\hline
\bottomrule
\end{longtable}

\subsection{Region specification and boundary role compression}
\paragraph{Code map.} \code{RegionSpec} stores the selected sibling-cone cut. \code{build\_\allowbreak{}sibling\_\allowbreak{}regions} chooses an LCA, two adjacent child cones, a boundary consisting of the LCA plus frontier nodes, and an interior inside the two cones. \code{boundary\_\allowbreak{}role\_\allowbreak{}basis} builds finite role columns and \code{compress\_\allowbreak{}response} returns \(Q^T\Lambda_BQ\).

\begin{definition}[Boundary role compression]
For a selected region \(R\), let \(Q_R\) be the matrix whose columns are the surviving Gram-Schmidt role vectors. The compressed response is
\begin{equation}
  \Lambda_R^{\rm role}=Q_R^T\Lambda_BQ_R.
  \label{eq:boundary-role-compression}
\end{equation}
The current symmetric Schur rows use the role names \code{C\_lca}, \code{B1\_front}, and \code{B2\_front} in the accepted compressed basis.
\end{definition}

\begin{proposition}[Role compression is a finite congruence]
For an accepted Schur response and a returned role basis \(Q_R\), the compressed response is the finite matrix product \(Q_R^T\Lambda_BQ_R\).
\end{proposition}
\begin{proof}
\textbf{Object.} The objects are \code{boundary\_\allowbreak{}role\_\allowbreak{}basis} and \code{compress\_\allowbreak{}response}. \textbf{Step 1.} Role indicator columns are built from boundary node lists. \textbf{Step 2.} Modified Gram-Schmidt discards columns whose residual norm is below tolerance. \textbf{Step 3.} The returned \(Q_R\) is used in the congruence of Equation~\eqref{eq:boundary-role-compression}. \textbf{Counter-check.} If all role columns vanish numerically, the code supplies a constant fallback column. \textbf{Conclusion.} The role layer changes finite coordinates on the selected boundary; it does not add a new response solve.
\end{proof}

\subsection{Directed response and S/A decomposition}
\paragraph{Code map.} The module \code{core/directed\_\allowbreak{}dtn.py} constructs directed local matrices and directed Schur responses without pair-averaging the edge dictionary and without final Schur symmetrization. The whole-network F1/F2 scalar has already been introduced; this subsection uses a selected boundary/interior cut.

\begin{definition}[Directed local response matrix]
For directed weights \(W_{ij}\), the out-degree sign relation is
\begin{equation}
  K_{ii}=\sum_j W_{ij},\qquad K_{ij}=-W_{ij}\quad(i\ne j).
  \label{eq:directed-local-response-matrix}
\end{equation}
The in-degree sign relation applies the same formula to \(W^T\). The open-grounded response keeps external out-load on the diagonal; the closed-internal response removes this external diagonal load; the environment-port response represents outside load by one additional finite boundary port.
\end{definition}

\begin{definition}[Symmetric/skew split]
For a directed response matrix \(\Lambda\), the finite split is
\begin{equation}
  S=\frac12(\Lambda+\Lambda^T),\qquad A=\frac12(\Lambda-\Lambda^T).
  \label{eq:symmetric-skew-response-split}
\end{equation}
The row families record \(\|S\|_F\), \(\|A\|_F\), \(\|A\|_F/\|\Lambda\|_F\), symmetry residuals, and the signed F1/F2 plane scalar read from \(A\).
\end{definition}

\begin{proposition}[Directed response separates symmetric and skew finite parts]
For every generated directed response row in the stated command, the returned matrix decomposes as \(\Lambda=S+A\), with \(S^T=S\) and \(A^T=-A\) up to the recorded floating-point residuals.
\end{proposition}
\begin{proof}
\textbf{Object.} The object is the matrix returned by \code{directed\_\allowbreak{}schur\_\allowbreak{}response}. \textbf{Step 1.} The directed local matrix is built from ordered edge weights. \textbf{Step 2.} Schur elimination is applied without symmetrizing \(\Lambda\). \textbf{Step 3.} \code{split\_\allowbreak{}symmetric\_\allowbreak{}skew} forms \(S\) and \(A\) according to Equation~\eqref{eq:symmetric-skew-response-split}. \textbf{Counter-check.} The row family records separate open-grounded, closed-internal, and environment-port rows; row-sum residuals differ across these finite accounting choices. \textbf{Conclusion.} The selected-cut directed layer supplies finite symmetric and skew matrices, not a continuum operator.
\end{proof}

\begin{longtable}{p{0.27\linewidth}p{0.17\linewidth}p{0.48\linewidth}}
\caption{Generated directed-response rows under the current growth rule.}\\
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endhead
\src{directed\_response\_construction.csv} & 54 & All rows have \code{response\_ok=1}. Max \code{cond\_KII} is \(3.0449\), max solve residual is \(1.9261\cdot10^{-16}\), max row-sum residual is \(2.2103\), and max relative skew is \(1.1827\cdot10^{-1}\).\\\hline
\src{directed\_SA\_decomposition.csv} & 9 & All rows are available. Max signed-plane relative skew is \(1.9501\cdot10^{-3}\) for \code{live}, \(2.0435\cdot10^{-3}\) for \code{record}, and \(1.2106\cdot10^{-17}\) for \code{sym}.\\\hline
\src{directed\_SA\_decomposition.csv} & 9 & Max \(|\omega_{F1,F2}|\) is \(4.1050\cdot10^{-3}\) for \code{live}, \(4.1128\cdot10^{-3}\) for \code{record}, and \(2.4070\cdot10^{-17}\) for \code{sym}.\\\hline
\bottomrule
\end{longtable}

\subsection{Finite J comparison on an S/A support}
\paragraph{Code map.} The function \code{j\_\allowbreak{}finite\_\allowbreak{}object\_\allowbreak{}from\_\allowbreak{}SA} reads a symmetric matrix \(S\) and a skew matrix \(A\). It restricts to the positive spectral support of \(S\), builds \(J_{\rm raw}=S^{-1/2}AS^{-1/2}\), extracts a polar factor by singular value decomposition, and records the residual for \(J^2=-P\) on the non-zero skew support.

\begin{definition}[Finite support comparison]
Let \(P_S\) be the positive spectral support selected from \(S\). On that finite support the code computes
\begin{equation}
  J_{\rm raw}=S^{-1/2}AS^{-1/2}.
  \label{eq:finite-j-raw}
\end{equation}
If the skew support has rank at least two, the SVD block defines a polar partial isometry \(J=W_kV_k^T\) on the non-zero skew support. With \(P=W_kW_k^T\), the code compares \(J^2\) with \(-P\) through \(\|J^2+P\|_F/\|P\|_F\). Unless the skew rank equals the full positive-support dimension, \(J\) is not asserted to be orthogonal on the whole \(S\)-support.
\end{definition}

\begin{proposition}[Finite J comparison is support-restricted]
The returned \code{available} field is one only when the positive support of \(S\) and the non-zero skew support of \(A\) have sufficient finite rank for the polar comparison.
\end{proposition}
\begin{proof}
\textbf{Object.} The object is the dictionary returned by \code{j\_\allowbreak{}finite\_\allowbreak{}object\_\allowbreak{}from\_\allowbreak{}SA}. \textbf{Step 1.} The code diagonalizes the symmetric part of \(S\) and selects eigenvectors above tolerance. \textbf{Step 2.} It forms \(J_{\rm raw}\) on that support according to Equation~\eqref{eq:finite-j-raw}. \textbf{Step 3.} It computes an SVD of \(J_{\rm raw}\), retains singular directions above tolerance, and constructs the partial isometry and its range projector. \textbf{Counter-check.} If the positive support rank or skew support rank is below two, the function returns \code{available=0} with a reason string. Even skew rank is recorded but is not used as a separate acceptance gate. \textbf{Conclusion.} The finite \(J\) row tests \(J^2\simeq-P\) on the resolved non-zero skew support inside a selected matrix problem; it does not establish \(J^2=-I\) on a larger carrier.
\end{proof}

\begin{longtable}{p{0.27\linewidth}p{0.17\linewidth}p{0.48\linewidth}}
\caption{Generated finite-J comparison rows under the current growth rule.}\\
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endhead
\src{directed\_J\_finite\_object\_comparison.csv} & 9 & Six rows are available: three \code{live} and three \code{record} rows. The three \code{sym} rows return unavailable because the skew support rank is below two.\\\hline
\src{directed\_J\_finite\_object\_comparison.csv} & 9 & Among available rows, max \(\|J^2+P\|_F/\|P\|_F\) is \(0\), and max \code{Jraw\_skew\_error} is \(2.0079\cdot10^{-16}\).\\\hline
\bottomrule
\end{longtable}


\subsection{Finite response algebra and GNS quotient audit}\label{sec:finite-response-gns-audit}
\paragraph{Code map.} The module \code{core/response\_\allowbreak{}algebra.py} defines \code{AlgebraBasis}, finite closure under multiplication and transpose, response-generated generator systems, density matrices, state Gram matrices, tolerance-resolved quotient coordinates, and full-basis left-action audits. The module \code{derived\_\allowbreak{}quantities/gns\_\allowbreak{}cyclicity\_\allowbreak{}controls.py} supplies independent positive and negative ambient-support cyclicity controls.

\begin{definition}[Finite response algebra closure]
For a finite generator list \(G_1,\ldots,G_r\subset M_n(\mathbb R)\), \code{algebra\_\allowbreak{}closure} builds a numerically Frobenius-orthonormal matrix basis by repeated multiplication and transposition. A trial matrix is sequentially projected against the current basis and inserted only when the remaining Frobenius norm exceeds the algebra tolerance. Because the maintained basis is normalized by the same insertion routine, this is an orthogonal-projection residual, not a separate general least-squares solve. The loop stops when no new direction is inserted, the full matrix dimension is reached, or the iteration cap is exhausted.
\end{definition}

\begin{definition}[Finite GNS Gram data and quotient coordinates]
Given a numerically orthonormal algebra basis \(\{A_i\}_{i=1}^m\) and a density matrix \(D\), the implemented state Gram matrix is
\begin{equation}
  G_{ij}=\operatorname{tr}(D A_i^T A_j).
  \label{eq:finite-gns-gram-matrix}
\end{equation}
Let \(G=U\operatorname{diag}(\lambda)U^T\) and retain the eigenvalues satisfying \(\lambda_i>\max(\varepsilon_{\rm gns},\varepsilon_{\rm gns}\max(1,\lambda_{\max}))\). A coefficient vector \(c\in\mathbb R^m\) is represented on the finite quotient support by
\[
  q(c)=\operatorname{diag}(\sqrt{\lambda_+})U_+^T c.
\]
For the identity coefficient vector \(c_I\), \(\Omega=q(c_I)\). If \(C_i\) is the coefficient matrix of left multiplication by \(A_i\), the explicit cyclic-span test is
\begin{equation}
  r_{\rm cyc}=\operatorname{rank}\bigl[q(C_1c_I)\;\cdots\;q(C_mc_I)\bigr],
  \qquad \text{cyclic exactly when }r_{\rm cyc}=\operatorname{rank}G.
  \label{eq:finite-gns-cyclic-rank}
\end{equation}
\end{definition}

\begin{proposition}[Full-basis finite GNS audit]
For each finite algebra/density pair, \code{measurement\_\allowbreak{}gns} computes the Gram support and audits every algebra-basis element: left-closure, transpose-adjoint compatibility, stability of the Gram nullspace under left multiplication, the identity-span residual, the equality \(\pi(A_i)\Omega=[A_i]\), and the cyclic rank in Equation~\eqref{eq:finite-gns-cyclic-rank}.
\end{proposition}
\begin{proof}
\textbf{Object.} The object is \code{GNSData}. \textbf{Step 1.} Compute Equation~\eqref{eq:finite-gns-gram-matrix} and its tolerance-resolved positive support. \textbf{Step 2.} Project the identity into the algebra basis and record its span residual and norm. \textbf{Step 3.} For every basis element, compute the left-multiplication coefficient matrix and the corresponding quotient representation. \textbf{Step 4.} Compare the represented transpose with the Euclidean adjoint, test images of Gram-null vectors, and compare \(q(C_ic_I)\) with the direct class \(q(e_i)\). \textbf{Step 5.} Compute the rank of all action-on-\(\Omega\) columns. \textbf{Counter-check.} The separate file \src{finite\_gns\_cyclicity\_controls.csv} includes full-algebra positive controls and proper-subalgebra negative controls; hence the cyclicity criterion is not the tautology \(\operatorname{rank}G\le m\). \textbf{Conclusion.} The row reports a finite left-regular GNS quotient audit over the full stored basis. No Hilbert completion, von Neumann closure, or infinite cyclicity statement is made.
\end{proof}

\paragraph{Reproduction command.}
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 run_cnna.py \
  --branching 3 \
  --levels 3 4 \
  --modes linear log saturating \
  --states live record sym \
  --max-regions 1 \
  --max-boundary 600 \
  --max-interior 900 \
  --directed-frontier-cap 6 \
  --algebra-tol 1e-10 \
  --algebra-max-iter 8 \
  --gns-tol 1e-10 \
  --growth-schedule layer_batch \
  --outdir outputs/algebra_gns_state_entropy
\end{verbatim}

\begin{longtable}{p{0.31\linewidth}p{0.12\linewidth}p{0.49\linewidth}}
\caption{Generated algebra and finite-GNS rows under the current growth rule.}\\
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endhead
\src{response\_algebra\_measurement.csv} & 54 & Basis dimensions range from 3 to 9. All rows have \code{saturated=1}. Max inclusion residuals are \(7.7028\cdot10^{-16}\) for \(A_{\rm in}\to N\) and \(2.5658\cdot10^{-13}\) for \(N\to A_{\rm out}\).\\\hline
\src{finite\_gns\_pre\_representation\_measurement.csv} & 54 & GNS ranks and explicit cyclic-span ranks both range from 3 to 9; the cyclic-rank defect and Gram nullity are zero in every row. All rows have \code{gns\_psd\_ok=1}, \code{cyclic\_ok=1}, \code{representation\_ok=1}, and \code{full\_basis\_representation\_checked=1}. Max identity-span residual is \(1.4793\cdot10^{-13}\), max action-on-cyclic-vector residual is \(2.5138\cdot10^{-13}\), max star-adjoint error is \(1.0023\cdot10^{-12}\), and max left-closure residual is \(2.5658\cdot10^{-13}\).\\\hline
\src{finite\_gns\_cyclicity\_controls.csv} & 4 & Both full-\(M_2(\mathbb R)\) positive controls are cyclic on their global GNS support. The diagonal/tracial and scalar/rank-one proper-subalgebra controls have cyclic ranks \(2<4\) and \(1<2\), respectively. All four rows have \code{control\_pass=1}.\\\hline
\bottomrule
\end{longtable}

\subsection{Regional response object and local support algebras}
\paragraph{Code map.} The modules \code{core/region\_\allowbreak{}response.py} and \code{core/algebra\_\allowbreak{}support.py} build regional response containers, positive-support densities, role-coordinate maps, role support projectors, local generator systems, local algebra closures, joined algebras, commutator metrics, GNS support ranks, commutant bases, finite Tomita-star metrics, and split residuals.

\begin{definition}[Local support algebra]
For a selected regional response, the code constructs role supports as index subsets of the finite boundary-role coordinate system. The local support algebra is the finite matrix algebra generated by the response-derived matrices after restriction to the selected role support.
\end{definition}

\begin{proposition}[Local algebra rows are finite matrix comparisons]
The local algebra rows compare finite generated matrix algebras inside explicitly chosen ambient coordinates.
\end{proposition}
\begin{proof}
\textbf{Object.} The objects are role-support projectors, restricted generator lists, and algebra bases. \textbf{Step 1.} Select role coordinates from the regional response object. \textbf{Step 2.} Restrict the generator matrices to the selected support. \textbf{Step 3.} Build finite algebra bases by the same closure routine as above. \textbf{Step 4.} Compare inclusions, commutators, joins, commutants, cyclic spans, and split dimensions by finite ranks and finite norms. \textbf{Counter-check.} A non-zero residual is recorded as a finite matrix discrepancy in the selected coordinate system. \textbf{Conclusion.} The row families describe finite algebraic relations for the selected regional response.
\end{proof}

\paragraph{Reproduction command.}
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 run_local_operator_property_checks.py \
  --branching 3 \
  --levels 4 \
  --modes linear log saturating \
  --states live record sym \
  --max-regions 1 \
  --max-boundary 600 \
  --max-interior 900 \
  --directed-frontier-cap 6 \
  --algebra-tol 1e-10 \
  --rank-tol 1e-9 \
  --max-algebra-iter 8 \
  --tomita-matrix-sign_relations out_degree \
  --growth-schedule layer_batch \
  --outdir outputs/local_operator_algebras
\end{verbatim}

\begin{longtable}{p{0.30\linewidth}p{0.12\linewidth}p{0.50\linewidth}}
\caption{Generated local-support algebra rows under the current growth rule.}\\
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endhead
\src{local\_operator\_isotony.csv} & 117 & Max independent span residual is \(7.7229\cdot10^{-13}\). Max relative common-ambient residual is \(1.7277\cdot10^{-15}\).\\\hline
\src{local\_operator\_commutation.csv} & 81 & Max relative commutator is \(1.4142\). This value is a finite norm ratio for the selected local algebras.\\\hline
\src{local\_operator\_additivity.csv} & 54 & Max generated-union dimension is 9, max target-union dimension is 9, and max target-minus-generated dimension is 6. Max target-to-generated span residual is 1.\\\hline
\src{local\_vacuum\_cyclicity.csv} & 198 & Local algebra dimensions range from 2 to 9. Global GNS support dimension is 9. Cyclic span ranks range from 2 to 9, and separating-kernel dimension is 0.\\\hline
\src{faithful\_state.csv} & 81 & Algebra dimensions range from 2 to 9. State Gram ranks range from 2 to 9. State Gram nullity is 0 in the generated rows.\\\hline
\src{tomita\_standard\_form\_compatibility.csv} & 9 & Max Tomita support dimension is 9. Max star-closure residual is \(1.3174\cdot10^{-8}\), max star-involution error is \(3.0981\cdot10^{-9}\), and max polar residual is \(6.0951\cdot10^{-15}\).\\\hline
\src{commutant\_duality.csv} & 27 & Computed commutant dimensions range from 1 to 5. Complement-to-commutant residual ranges from 0 to 1, and commutant-to-complement residual ranges from \(4.5776\cdot10^{-16}\) to 1.\\\hline
\src{split\_factorization.csv} & 18 & Max generated-join dimension is 9. Max tensor-product dimension count is 25. Max dimension residual is 16.\\\hline
\bottomrule
\end{longtable}

\subsection{Compressed carrier/GNS state and projective distribution}
\paragraph{Code map.} The module \code{core/compressed\_\allowbreak{}state.py} builds a finite compressed state object over role/address keys. The corresponding row functions in \code{derived\_\allowbreak{}quantities/compressed\_\allowbreak{}state\_\allowbreak{}projection\_\allowbreak{}consistency.py} compare direct compression with projected compression at lower target levels.

\begin{definition}[Compressed carrier state]
A compressed carrier state maps terminal or boundary atoms to finite role/address keys and sums the associated weights. The object contains the compressed key set, finite state weights, trace weights, response-energy weights, and residuals for the projected response density.
\end{definition}

\begin{proposition}[Compressed projectivity is a route comparison]
For target levels \(k<\ell\), the compressed projectivity rows compare direct compression at level \(k\) with the push-forward of compression at level \(\ell\).
\end{proposition}
\begin{proof}
\textbf{Object.} The object is a pair of finite compressed distributions over role/address keys. \textbf{Step 1.} Build the compressed state at the finer target level. \textbf{Step 2.} Push it forward by address truncation. \textbf{Step 3.} Build the coarser compressed state directly. \textbf{Step 4.} Compare the two routes by total variation and sector profiles. \textbf{Counter-check.} A non-zero value records finite route dependence for the implemented compression. \textbf{Conclusion.} The row is a finite compatibility measurement for the compression map.
\end{proof}

\begin{longtable}{p{0.31\linewidth}p{0.12\linewidth}p{0.49\linewidth}}
\caption{Generated compressed-state rows under the current growth rule.}\\
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endhead
\src{compressed\_carrier\_state\_objects.csv} & 18 & All rows have \code{object\_available=1}. The compressed dimension is 3. Max projected-density residual is \(6.4860\cdot10^{-16}\). Max \(TV\) between state and trace weights is \(6.2347\cdot10^{-1}\); max \(TV\) between state and response-energy weights is \(7.7539\cdot10^{-1}\).\\\hline
\src{compressed\_carrier\_state\_projectivity.csv} & 9 & Max trace-route total variation is \(1.1102\cdot10^{-16}\). Max state-route total variation is \(8.1912\cdot10^{-2}\). Max response-energy route total variation is \(2.2005\cdot10^{-1}\).\\\hline
\src{compressed\_carrier\_state\_sector\_decomposition.csv} & 18 & Max conditional-profile total variation is \(1.8115\cdot10^{-3}\).\\\hline
\src{compressed\_carrier\_state\_composition.csv} & 0 & The generated file is empty for this reduced two-level run.\\\hline
\bottomrule
\end{longtable}

\subsection{Refined boundary/port basis}
\paragraph{Code map.} The module \code{core/refined\_\allowbreak{}port\_\allowbreak{}basis.py} splits boundary role groups into finite subgroups, builds refined regional responses, and constructs refined support algebras.

\begin{definition}[Refined role basis]
A refined role basis is a finite boundary-coordinate basis obtained by subdividing frontier role groups into named shells or chunks. It replaces a coarse role column by several normalized columns whose supports partition the original role support.
\end{definition}

\begin{longtable}{p{0.31\linewidth}p{0.12\linewidth}p{0.49\linewidth}}
\caption{Generated refined-basis rows under the current growth rule.}\\
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endhead
\src{refined\_port\_basis\_resolution.csv} & 9 & Coarse role dimension is 3 and max refined role dimension is 5. Max refined-role dimension gain is 2.\\\hline
\src{collared\_split\_refined\_basis.csv} & 27 & Max refined role dimension is 5. Max left and right dimensions are 10. Max generated-join dimension is 25 and max refined tensor-dimension residual is \(7.5\cdot10^{-1}\).\\\hline
\bottomrule
\end{longtable}

\subsection{Entropy functionals and record/live entropy distances}\label{sec:entropy-functionals-record-live}
\paragraph{Code map.} The module \code{core/entropy\_\allowbreak{}quantities.py} defines finite entropy, finite relative entropy, Jensen--Shannon divergence, and record/live entropy metrics. The generated object-check rows evaluate these functions on densities attached to regional response and local algebra data. The same finite entropy and divergence functions are read again in Section~\ref{sec:live-record-backreaction-current} through the record/live row families.

\begin{definition}[Tolerance-resolved finite entropy]
For a symmetric positive semidefinite density \(D\), let
\[
  \tau_D=\max\!\left(\varepsilon_{\rm gns},\varepsilon_{\rm gns}\max(1,\lambda_{\max}(D))\right).
\]
The function \code{von\_\allowbreak{}neumann\_\allowbreak{}entropy\_\allowbreak{}no\_\allowbreak{}epsilon} computes
\begin{equation}
  S_{\tau_D}(D)=-\sum_{\lambda_i>\tau_D}\lambda_i\log\lambda_i.
  \label{eq:finite-von-neumann-entropy}
\end{equation}
No artificial floor is inserted inside the logarithm, but eigenvalues at or below the scale-aware cutoff are treated as numerical zero. Relative support inclusion is likewise tolerance-resolved; the routine returns an infinite value when the resolved support of \(\rho\) is not contained in that of \(\sigma\).
\end{definition}

\begin{proposition}[The entropy routines expose their numerical support rule]
The entropy functions do not add an epsilon floor to force finite logarithms. They first resolve spectral support at the declared tolerance and test support leakage before the logarithmic trace expression is evaluated.
\end{proposition}
\begin{proof}
\textbf{Object.} The objects are the spectra and support projectors computed in \code{entropy\_\allowbreak{}quantities.py}. \textbf{Step 1.} Entropy sums eigenvalues above \(\tau_D\). \textbf{Step 2.} Relative entropy compares the trace leakage of \(\rho\) outside the resolved support projector of \(\sigma\) with a scale-aware tolerance. \textbf{Step 3.} Jensen--Shannon divergence uses the mixture density and the same support routine. \textbf{Counter-check.} Eigenvalues below the cutoff are not distinguished from exact zero, so the computation is not an exact symbolic-support calculation. \textbf{Conclusion.} The row values keep the implemented tolerance-resolved support relation visible without logarithmic epsilon flooring.
\end{proof}

\begin{longtable}{p{0.31\linewidth}p{0.12\linewidth}p{0.49\linewidth}}
\caption{Generated entropy rows under the current growth rule.}\\
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Readout}\\
\midrule
\endhead
\src{record\_live\_relative\_entropy.csv} & 9 & Max Jensen--Shannon live/record value is \(6.4853\cdot10^{-3}\). Max live entropy is \(4.1111\cdot10^{-1}\), and max record entropy is \(2.6051\cdot10^{-1}\).\\\hline
\src{tomita\_entropy\_flow\_alignment.csv} & 9 & Max Tomita support dimension is 9. Max polar residual is \(1.0297\cdot10^{-11}\). Max modular inverse-relation error is \(2.7825\cdot10^{-1}\).\\\hline
\src{multiscale\_port\_entropy\_resolution.csv} & 9 & Max multiscale role dimension is 7. Max Jensen--Shannon live/record value on the multiscale basis is \(1.8426\cdot10^{-2}\). Max record-tracking gain over the multiscale uniform comparison is \(4.5778\cdot10^{-1}\).\\\hline
\bottomrule
\end{longtable}

\newpage
\section{Finite structural results and exact proof boundary}\label{sec:finite-structural-results}
This section separates mathematical statements that follow from the finite definitions from numerical controls and from stronger claims that the present source does not establish. Exact statements are formulated over finite-dimensional real vector spaces and exact arithmetic. Their Python realization is additionally subject to the declared binary64 environment and tolerance rules. A passing control row checks the implementation on explicit finite cases; it is not substituted for the proof.

\begin{longtable}{>{\raggedright\arraybackslash}p{0.25\linewidth}>{\raggedright\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}p{0.47\linewidth}}
\caption{Status of the six finite structural statements.}\label{tab:finite-structural-status}\\
\toprule
\textbf{Statement} & \textbf{Status} & \textbf{Scope}\\
\midrule
\endfirsthead
\toprule
\textbf{Statement} & \textbf{Status} & \textbf{Scope}\\
\midrule
\endhead
Finite growth well-definedness & exact finite theorem & fixed admissible inputs, fixed sibling linearization, and the explicitly specified update rule.\\\hline
Symmetric Schur positivity & exact conditional theorem & non-negative symmetrized conductances; invertible interior block. Positive definiteness requires explicit grounding.\\\hline
Finite GNS quotient & exact finite theorem & a unital finite-dimensional real transpose-closed matrix algebra and a positive density matrix.\\\hline
Global orientation reversal & exact conditional obstruction & sign-even data cannot distinguish the pair obtained by simultaneous reversal of the skew orientation.\\\hline
Backreaction scalar separation & exact non-implication plus generated witness & distinguishes the matrix current, its norm, a difference of norms, and one oriented matrix coefficient.\\\hline
Interlevel handoff & exact at address/carrier level; conditional for boundary matrices; failed for a strict operator-algebra handoff & prefix maps and uniform terminal carriers compose exactly. Current response/algebra maps retain non-zero discrepancies.\\
\bottomrule
\end{longtable}

The implementation controls for this section are generated by
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 \
  package_consistency/check_finite_structure_theorems.py \
  --write-csv docs/FINITE_STRUCTURE_THEOREM_CONTROLS.csv
\end{verbatim}
The six control rows pass in the documented environment. Their role is to detect implementation regressions in the finite hypotheses used below.

\subsection{Well-definedness of the finite growth construction}
Let
\[
  \mathcal W_{b,L}=\bigcup_{d=0}^{L}\{0,\ldots,b-1\}^{d}
\]
be the finite address set, including the empty word at depth zero. Besides \((b,L,m,\mathfrak s)\), the source admits a fixed sibling linearization \(\ell\in\{\code{rank},\code{reverse\_rank}\}\). The reference calculations use \(\ell=\code{rank}\).

\begin{theorem}[Finite growth well-definedness]\label{thm:finite-growth-well-defined}
For every admissible tuple
\[
 b\ge2,\qquad L\ge0,\qquad
 m\in\{\code{linear},\code{log},\code{saturating}\},\qquad
 \mathfrak s\in\{\code{slot\_step},\code{layer\_batch}\},
\]
and every fixed sibling linearization \(\ell\), the exact finite rule determines a unique tuple
\[
  \mathcal G_{b,L,m,\mathfrak s,\ell}
  =\bigl(V,E_{\rm record},E_{\rm live},g,\mathcal E\bigr).
\]
There is exactly one node \(v_a\) for each \(a\in\mathcal W_{b,L}\), with parent \(v_{a^-}\) for every non-empty word \(a\). In particular,
\begin{equation}
  |V|=|\mathcal W_{b,L}|=\sum_{d=0}^{L}b^d=\frac{b^{L+1}-1}{b-1}.
  \label{eq:finite-growth-cardinality-theorem}
\end{equation}
The event list, record-edge dictionary, live-edge dictionary, and node loads are finite and uniquely determined by the fixed inputs and rule equations.
\end{theorem}

\begin{proof}
The proof is by induction on depth. At depth zero, \code{\_birth\_root\_from\_empty} creates the unique empty-address node. Assume that after depth \(d\) the nodes are exactly the words of lengths at most \(d\), with one node per address. Every depth-\(d\) word has precisely the unoccupied ranks \(0,\ldots,b-1\); concatenating a rank produces a distinct word of length \(d+1\), and every word of length \(d+1\) has exactly one such predecessor. The ordered slot list is a deterministic function of \(\ell\). For \code{slot\_step}, each growth step is evaluated and committed in that order. For \code{layer\_batch}, all step data at one depth are evaluated from the same pre-commit state and are then committed in the same deterministic slot order; the subsequent sibling relation loop is ordered by sibling rank. Every weight and load update is a finite arithmetic expression in the already determined state. Duplicate addresses are rejected explicitly. Hence the construction terminates after \(L\) depth loops and is unique. Counting the words gives Equation~\eqref{eq:finite-growth-cardinality-theorem}.
\end{proof}

\begin{remark}[Implementation scope]
The theorem concerns the exact rule. The control file replays 96 finite configurations covering \(b\in\{2,3\}\), \(L\in\{0,1,2,3\}\), all three modes, both schedules, and both sibling linearizations. All 96 paired replays are exactly equal in the documented environment; address, parent, and finiteness checks have zero failures. This does not claim bitwise equality across different floating-point libraries or compiler builds.
\end{remark}

\subsection{Positivity of the symmetric finite response}
For one state, let
\[
 c_{ij}=\frac{w_{ij}+w_{ji}}{2}\ge0
\]
be the undirected conductance used by the symmetric response route, and let \(L_C\) be its weighted graph Laplacian. The open-grounded local matrix constructed by \code{schur\_response\_from\_model} is the principal block \(K=(L_C)_{S,S}\) for \(S=B\sqcup I\); edges from \(S\) to omitted vertices remain in its diagonal. The proof below is the finite quadratic-form proof of the standard Schur-complement positivity statement \cite{HornJohnson2013,Zhang2005}.

\begin{theorem}[Finite Schur positivity]\label{thm:finite-schur-positivity}
The local matrix \(K\) is positive semidefinite. If \(K_{II}\) is invertible, then it is positive definite and the exact Schur response
\begin{equation}
  \Lambda_B=K_{BB}-K_{BI}K_{II}^{-1}K_{IB}
  \label{eq:schur-positivity-response}
\end{equation}
is positive semidefinite. If every connected component of the conductance graph induced on \(S\) has a positive-conductance edge to the omitted complement, then \(K\) and \(\Lambda_B\) are positive definite. If no such grounding is present and a whole connected component is retained, constants on that component can remain in the kernel; positivity then holds on the quotient by that kernel.
\end{theorem}

\begin{proof}
For \(x\in\mathbb R^S\), extension by zero outside \(S\) gives
\begin{equation}
 x^TKx
 =\sum_{\substack{i<j\\ i,j\in S}}c_{ij}(x_i-x_j)^2
  +\sum_{\substack{i\in S\\j\notin S}}c_{ij}x_i^2\ge0.
 \label{eq:grounded-laplacian-energy}
\end{equation}
Thus \(K\succeq0\). A nonsingular symmetric principal block of a positive-semidefinite matrix is positive definite, so the accepted exact interior block satisfies \(K_{II}\succ0\). For any boundary vector \(y\), minimize the quadratic form of \(K\) over interior vectors. The unique minimizer is \(z=-K_{II}^{-1}K_{IB}y\), and the minimum equals \(y^T\Lambda_By\). It is therefore non-negative. Equation~\eqref{eq:grounded-laplacian-energy} vanishes only when \(x\) is constant on each selected conductance component and zero on every component touching the omitted complement. The stated grounding condition forces \(x=0\), hence \(K\succ0\); the Schur complement of a positive-definite block matrix is positive definite.
\end{proof}

\begin{remark}[Directed limitation]
The theorem applies only to the symmetrized conductance/Laplacian route. A directed response matrix need not be symmetric or positive semidefinite; only its symmetric part can be subjected to a separate support test. The control file evaluates 36 open-grounded symmetric responses over both schedules, all three modes, two sibling regions, and the states live, record, and sym. Every response is symmetric and positive definite in that sample; the smallest observed eigenvalue is approximately \(1.2315\times10^{-1}\). The proof, rather than this sample, supplies the positive-semidefinite statement under the theorem's hypotheses.
\end{remark}

\subsection{Exact finite GNS quotient}
The numerical routine in Section~\ref{sec:finite-response-gns-audit} is an audit of an exact finite-dimensional construction. The following real finite-matrix specialization is proved directly and uses the standard GNS quotient principle \cite{GelfandNaimark1943,Segal1947}; it is independent of the tolerance-resolved eigensolver.

\begin{theorem}[Finite real GNS construction]\label{thm:finite-real-gns}
Let \(\mathcal A\subseteq M_n(\mathbb R)\) be a finite-dimensional unital algebra closed under transpose, and let \(D\succeq0\) with \(\operatorname{tr}D=1\). Define
\[
 \varphi_D(X)=\operatorname{tr}(DX),\qquad
 \langle X,Y\rangle_D=\varphi_D(X^TY),
\]
and
\begin{equation}
 \mathcal N_D=\{X\in\mathcal A:\varphi_D(X^TX)=0\}.
 \label{eq:finite-gns-nullspace-theorem}
\end{equation}
Then \(\mathcal N_D\) is a left ideal, the quotient
\[
 \mathcal H_D=\mathcal A/\mathcal N_D
\]
is a finite-dimensional real inner-product space, and
\[
 \pi_D(A)[X]=[AX]
\]
defines a transpose representation satisfying \(\pi_D(A)^*=\pi_D(A^T)\). The vector \(\Omega=[I]\) is cyclic because \(\pi_D(A)\Omega=[A]\) for every \(A\in\mathcal A\). For any basis of \(\mathcal A\), the Gram matrix in Equation~\eqref{eq:finite-gns-gram-matrix} satisfies
\begin{equation}
  \operatorname{rank}G=\dim\mathcal H_D,
  \qquad
  \operatorname{nullity}G=\dim\mathcal N_D.
  \label{eq:finite-gns-rank-nullity-theorem}
\end{equation}
\end{theorem}

\begin{proof}
Since
\[
 \varphi_D(X^TX)
 =\operatorname{tr}(D^{1/2}X^TXD^{1/2})
 =\|XD^{1/2}\|_F^2,
\]
Equation~\eqref{eq:finite-gns-nullspace-theorem} is equivalent to \(XD^{1/2}=0\). Therefore \((AX)D^{1/2}=A(XD^{1/2})=0\), so \(\mathcal N_D\) is a left ideal. The sesquilinear issues of a complex space do not occur here: the real bilinear form descends to a positive-definite inner product on the quotient. Left multiplication is well-defined by the left-ideal property, and
\[
 \langle AX,Y\rangle_D
 =\operatorname{tr}(DX^TA^TY)
 =\langle X,A^TY\rangle_D.
\]
Cyclicity follows immediately from \(\pi_D(A)[I]=[A]\). The Gram matrix is the matrix of the positive semidefinite form on the chosen basis, so its kernel is the coefficient representation of \(\mathcal N_D\) and rank-nullity gives Equation~\eqref{eq:finite-gns-rank-nullity-theorem}.
\end{proof}

\begin{remark}[What the code still has to check]
The exact theorem assumes a genuinely unital transpose-closed algebra. The generated basis is numerical and may be stopped by an iteration cap. Therefore the implementation separately records saturation, identity-span, multiplication-closure, transpose-adjoint, null-left-ideal, action-on-\(\Omega\), and cyclic-rank residuals. The four explicit controls include cyclic and non-cyclic ambient-support cases; all pass. No completion, irreducibility, factor property, or infinite GNS statement follows.
\end{remark}

\subsection{Orientation reversal and the unresolved absolute sign}
\begin{theorem}[Sign-reversal covariance of the finite polar object]\label{thm:j-sign-reversal}
Let \(S\succeq0\), let \(A^T=-A\), and form the support-restricted object
\[
 J_{\rm raw}(S,A)=S^{-1/2}AS^{-1/2}.
\]
Let \(U(S,A)\) denote its polar partial isometry on the non-zero skew support. Then
\begin{equation}
 J_{\rm raw}(S,-A)=-J_{\rm raw}(S,A),
 \qquad
 U(S,-A)=-U(S,A).
 \label{eq:j-sign-reversal-covariance}
\end{equation}
The singular values, skew rank, support projector, and square relation \(U^2=-P\) are unchanged by this reversal. Consequently, any selection rule using only \(S\) and these sign-even data cannot distinguish the two globally reversed choices.
\end{theorem}

\begin{proof}
The first identity is linearity in \(A\). The absolute value of an operator is unchanged by multiplication by \(-1\), so in the polar decomposition \(J_{\rm raw}=U|J_{\rm raw}|\), replacing \(J_{\rm raw}\) by its negative replaces \(U\) by \(-U\) on the same support. All listed diagnostics are functions of \(|J_{\rm raw}|\), the support projector, or \(U^2\), and are therefore invariant.
\end{proof}

\begin{corollary}[Relative orientation versus absolute orientation]\label{cor:relative-absolute-orientation}
Once the sibling-slot F2 coordinate is fixed, the finite rows can compare local and global signs relative to that coordinate. Under a simultaneous reversal of every such sign, each relative product is unchanged. The present core therefore supplies relative orientation data but no sign-odd predicate that declares one simultaneous global choice to be the absolute physical sign.
\end{corollary}

\begin{remark}[Conditional nature of the obstruction]
The obstruction does not say that the computed \(J\) is undefined for a given oriented \(A\); Equation~\eqref{eq:j-sign-reversal-covariance} determines it. It says that a model specification invariant under simultaneous orientation reversal cannot turn the two reversed specifications into inequivalent absolute choices without adding or deriving another sign-odd datum. The control error for \(U(S,-A)+U(S,A)\) is \(3.14\times10^{-16}\); singular values and square residuals agree within the declared tolerance.
\end{remark}

\subsection{Separation of backreaction observables}
\begin{proposition}[Backreaction non-implications]\label{prop:backreaction-nonimplications}
For skew matrices \(A_{\rm live}\) and \(A_{\rm record}\), define
\[
 B=A_{\rm live}-A_{\rm record},\qquad
 b=\|B\|_F,\qquad
 \beta=\|A_{\rm live}\|_F-\|A_{\rm record}\|_F,
\]
and \(\omega=F_1^TBF_2\) for fixed vectors \(F_1,F_2\). Then
\[
 B=0\ \Longrightarrow\ b=0,\ \beta=0,\ \omega=0,
\]
but neither \(\beta=0\Rightarrow B=0\) nor \(\beta=0\Rightarrow\omega=0\) is valid in general.
\end{proposition}

\begin{proof}
The forward implications are immediate. For the converse, take
\[
 J_2=\begin{pmatrix}0&-1\\1&0\end{pmatrix},\qquad
 A_{\rm live}=J_2,\qquad A_{\rm record}=-J_2.
\]
Then \(\beta=0\), whereas \(B=2J_2\), \(\|B\|_F=2\sqrt2\), and with \(F_1=e_1,F_2=e_2\), \(\omega=-2\). Thus equality of the two skew norms does not identify the matrices or an oriented coefficient.
\end{proof}

\begin{corollary}[Meaning of the generated crossing]\label{cor:beta-crossing-only}
A sign change of the sampled sequence \(\beta_L\) states only that the order of the two skew norms changes between the sampled levels. It does not imply an intermediate zero of a matrix-valued path \(B_L\), because no continuous matrix interpolation is defined, and it does not imply a zero of \(\omega_L\). In the documented \(b=4\), \(L=4,5,6\) rows, \(\beta_L\) changes sign while \(\|B_L\|_F>0\) at every sample and \(\omega_L<0\) throughout.
\end{corollary}

\subsection{Exact prefix handoff}
\begin{theorem}[Address and carrier handoff]\label{thm:prefix-carrier-handoff}
For \(0\le L\le M\le N\), address truncation satisfies
\begin{equation}
  \pi_L\circ\pi_M=\pi_L.
  \label{eq:prefix-map-composition}
\end{equation}
For every non-negative probability distribution \(\mu_N\) on level-\(N\) addresses,
\begin{equation}
  (\pi_L)_*\bigl((\pi_M)_*\mu_N\bigr)=(\pi_L)_*\mu_N.
  \label{eq:probability-pushforward-composition}
\end{equation}
For the uniform terminal carrier \(\Omega_N\) of the full \(b\)-ary tree,
\begin{equation}
  (\pi_L)_*\Omega_N=\Omega_L.
  \label{eq:uniform-carrier-projectivity-theorem}
\end{equation}
\end{theorem}

\begin{proof}
Equation~\eqref{eq:prefix-map-composition} is the associativity of word truncation. Push-forward composition follows by summing over the same address fibers; normalization is inactive because a non-negative probability distribution retains total mass one under each raw push-forward. For Equation~\eqref{eq:uniform-carrier-projectivity-theorem}, every length-\(L\) word has exactly \(b^{N-L}\) length-\(N\) extensions, so all target fibers have equal mass.
\end{proof}

\begin{proposition}[Conditional composition of boundary transport matrices]\label{prop:boundary-transport-composition}
Let \(R_{L\leftarrow M}\) be a boundary address-prefix matrix. If every source boundary address maps to the intermediate and target boundary sets, then the \code{fiber\_sum} matrices compose exactly. The \code{fiber\_average} and \code{fiber\_sqrt} matrices also compose when the relevant fiber cardinalities factor uniformly through the intermediate boundary. Under these conditions,
\begin{equation}
  R_{L\leftarrow N}=R_{L\leftarrow M}R_{M\leftarrow N}.
  \label{eq:boundary-transport-matrix-composition}
\end{equation}
\end{proposition}

\begin{proof}
Each source column has one address-determined target row. For \code{fiber\_sum}, matrix multiplication follows the unique intermediate row and reproduces the direct unit entry. For the two normalized weightings, the composed coefficient is the product of the two inverse fiber factors; the stated factorization condition makes this product equal to the direct inverse fiber factor.
\end{proof}

\begin{remark}[Legacy label projection versus the new carrier map]
The earlier interlevel rows use a least-squares projection between equally named generators in independently reconstructed three-role algebras.  That comparison remains non-multiplicative: its maximum product-morphism residual is~\(1\), its strict star-hom indicator is zero, its maximum GNS Gram transport error is approximately \(6.82\times10^{-1}\), and its conditional-expectation state drift reaches approximately~\(1.46\).  Those rows are retained as a negative control for that particular label-span map.  They no longer exhaust the handoff question, because the following construction introduces a genuinely nested carrier before comparing distinguished response and state data.
\end{remark}

\subsection{Growing address-contrast carriers and non-unital corner embeddings}\label{sec:nested-multiscale-handoff}
\paragraph{Code map.}
\code{core/nested\_multiscale.py} constructs the nested address-coordinate contrast basis, its label inclusion, the corner maps, the resolved support graph, and the common-ambient Schur comparison.  \code{derived\_quantities/nested\_multiscale\_handoff.py} produces the carrier, handoff, composition, state/GNS, finite-\(J\), and common-ambient rows.  The complete control is executed by
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
python3 package_consistency/check_nested_multiscale_handoff.py \
  --output-dir docs
\end{verbatim}

\begin{definition}[First-order address-contrast carrier]\label{def:first-order-address-carrier}
Fix one sibling-cone region and let the left and right frontier words have relative length~\(h\) below their sibling roots.  Let
\(\eta^{(1)},\ldots,\eta^{(b-1)}\in\R^b\)
be the real Helmert contrasts, an orthonormal basis of the subspace orthogonal to the constant slot vector.  The carrier basis contains the normalized LCA indicator, the normalized constant indicator of each sibling frontier, and, for each side \(\sigma\in\{1,2\}\), address coordinate \(d=0,\ldots,h-1\), and contrast \(r=1,\ldots,b-1\), the vector
\begin{equation}
 q_{\sigma,d,r}(a)
 =
 \begin{cases}
 b^{-(h-1)/2}\,\eta^{(r)}_{a_d},
   & a\text{ belongs to frontier }\sigma,\\
 0,&\text{otherwise}.
 \end{cases}
 \label{eq:first-order-address-contrast}
\end{equation}
The resulting real carrier \(K_{b,h}\) has dimension
\begin{equation}
 d_{b,h}=3+2h(b-1).
 \label{eq:nested-role-dimension}
\end{equation}
Only first-order address-coordinate contrasts are included; products of contrasts at different address coordinates are deliberately omitted.  Thus the carrier grows linearly in~\(h\), rather than exponentially with the full frontier size.
\end{definition}

\begin{theorem}[Exact nested carrier handoff]\label{thm:exact-nested-carrier-handoff}
Let \(L<M\), let \(R_{L\leftarrow M}\) be the \code{fiber\_sqrt} boundary prefix matrix, and put \(V_{M\leftarrow L}=R_{L\leftarrow M}^{T}\).  For complete sibling-frontier fibers, let \(Q_L,Q_M\) be the bases from Definition~\ref{def:first-order-address-carrier}.  Then there is a label-inclusion isometry
\begin{equation}
 T_{M\leftarrow L}:K_L\longrightarrow K_M,
 \qquad T_{M\leftarrow L}^{T}T_{M\leftarrow L}=I_{K_L},
 \label{eq:nested-role-inclusion}
\end{equation}
such that
\begin{equation}
 V_{M\leftarrow L}Q_L=Q_MT_{M\leftarrow L}.
 \label{eq:nested-basis-intertwining}
\end{equation}
Consequently the map
\begin{equation}
 \iota_{M\leftarrow L}(X)
 =T_{M\leftarrow L}XT_{M\leftarrow L}^{T},
 \qquad X\in M_{d_L}(\R),
 \label{eq:nonunital-corner-embedding}
\end{equation}
is an injective transpose-preserving algebra homomorphism.  Its compression
\begin{equation}
 E_{L\leftarrow M}(Y)=T_{M\leftarrow L}^{T}YT_{M\leftarrow L}
 \label{eq:corner-left-inverse}
\end{equation}
satisfies \(E_{L\leftarrow M}\circ\iota_{M\leftarrow L}=\mathrm{id}\).  If \(d_M>d_L\), the embedding is non-unital in the full target matrix algebra:
\begin{equation}
 \iota_{M\leftarrow L}(I_{d_L})
 =P_{M,L}:=T_{M\leftarrow L}T_{M\leftarrow L}^{T}
 \neq I_{d_M}.
 \label{eq:old-role-corner-projector}
\end{equation}
For \(L<M<N\), the inclusions and corner projectors compose through the intermediate level.
\end{theorem}

\begin{proof}
Each coarse frontier word has exactly \(b^{M-L}\) fine extensions.  The \code{fiber\_sqrt} coefficient is the inverse square root of this fiber size.  It therefore sends a normalized constant block to the corresponding normalized constant block.  A contrast in Equation~\eqref{eq:first-order-address-contrast} depends only on one address coordinate already present at level~\(L\); every fine extension has the same value on that coordinate, and the square-root fiber normalization again gives the level-\(M\) vector with the same label.  New level-\(M\) columns depend on later address coordinates and are orthogonal to the lifted old columns.  This proves Equations~\eqref{eq:nested-role-inclusion} and~\eqref{eq:nested-basis-intertwining}.  Multiplicativity follows from
\[
 (TXT^T)(TYT^T)=TX(T^TT)YT^T=TXYT^T,
\]
transpose preservation is immediate, and Equation~\eqref{eq:corner-left-inverse} follows from \(T^TT=I\).  Label inclusions compose, hence so do the carrier maps.
\end{proof}

\begin{proposition}[Resolved response generation of the carrier algebra]\label{prop:resolved-response-full-algebra}
Let \(\Lambda_L^{\rm ms}=Q_L^T\Lambda_LQ_L\), let \(P_i=e_ie_i^T\) be all coordinate projections of \(K_L\), and define
\begin{equation}
 \mathcal A_L^{\rm ms}
 =\operatorname{alg}^{T}\!\left(\{P_i\}_{i=1}^{d_L}\cup\{\Lambda_L^{\rm ms}\}\right).
 \label{eq:multiscale-response-algebra}
\end{equation}
If the undirected support graph with an edge \(i\!\sim\!j\) whenever
\((\Lambda_L^{\rm ms})_{ij}\neq0\) or \((\Lambda_L^{\rm ms})_{ji}\neq0\)
is connected, then
\begin{equation}
 \mathcal A_L^{\rm ms}=M_{d_L}(\R).
 \label{eq:connected-support-full-algebra}
\end{equation}
\end{proposition}

\begin{proof}
For a supported directed entry,
\(P_i\Lambda_L^{\rm ms}P_j=(\Lambda_L^{\rm ms})_{ij}E_{ij}\).
Transpose closure supplies the reverse matrix unit.  Multiplying matrix units along a path in the connected support graph produces \(E_{ij}\) for every ordered pair.  The matrix units span \(M_{d_L}(\R)\).
\end{proof}

\begin{remark}[Numerical support qualification]
Equation~\eqref{eq:connected-support-full-algebra} is an exact conditional statement.  The implementation checks its premise on the support resolved at threshold \(10^{-12}\); it does not convert a floating-point entry above threshold into a symbolic non-vanishing theorem.  All nine tested live rows for \(b=2,3,4\) and \(L=4,5,6\) have one connected symmetric and directed support component.  Their carrier dimensions are
\[
7,9,11;\qquad 11,15,19;\qquad 15,21,27,
\]
respectively, and the corresponding full carrier-algebra dimensions reach \(121\), \(361\), and \(729\) at level~6.
\end{remark}

\begin{proposition}[Conditional corner state and scaled GNS identity]\label{prop:conditional-corner-state-gns}
Let \(D_M\) be a normalized positive density on \(K_M\), let \(T=T_{M\leftarrow L}\), and define
\begin{equation}
 C_{M\downarrow L}=T^TD_MT,
 \qquad
 \lambda_{M,L}=\operatorname{tr}(C_{M\downarrow L}),
 \qquad
 D_{M\mid L}=\frac{C_{M\downarrow L}}{\lambda_{M,L}}
 \label{eq:conditional-corner-density}
\end{equation}
whenever \(\lambda_{M,L}>0\).  Then for all \(X,Y\in M_{d_L}(\R)\),
\begin{equation}
 \left\langle\iota_{M\leftarrow L}(X),
                  \iota_{M\leftarrow L}(Y)\right\rangle_{D_M}
 =
 \lambda_{M,L}\,\langle X,Y\rangle_{D_{M\mid L}}.
 \label{eq:scaled-corner-gns-isometry}
\end{equation}
Thus \(\lambda_{M,L}^{-1/2}\iota_{M\leftarrow L}\) induces an isometry between the conditional finite GNS pre-Hilbert spaces.  It induces an isometry from the independently reconstructed level-\(L\) state only if \(D_L=D_{M\mid L}\).
\end{proposition}

\begin{proof}
Using \(T^TT=I\) and cyclicity of the finite trace,
\[
 \operatorname{tr}\!\left(D_M(TXT^T)^T(TYT^T)\right)
 =\operatorname{tr}\!\left(T^TD_MT X^TY\right)
 =\lambda_{M,L}\operatorname{tr}\!\left(D_{M\mid L}X^TY\right).
\]
\end{proof}

\begin{theorem}[Common-ambient Schur positive control]\label{thm:common-ambient-interlevel-schur}
Fix one fine finite model, one open-grounded symmetric local matrix~\(K_M\), and a coarse retained boundary~\(B_L\).  Let \(C\) be an intermediate retained set containing \(B_L\).  Whenever the required interior blocks are invertible,
\begin{equation}
 \operatorname{Schur}_{B_L}(K_M)
 =
 \operatorname{Schur}_{B_L}\!\left(
   \operatorname{Schur}_{C}(K_M)
 \right).
 \label{eq:common-ambient-schur-associativity}
\end{equation}
This identity compares two elimination orders inside one ambient matrix.  It does not imply equality with the response reconstructed independently from the level-\(L\) growth object.
\end{theorem}

\begin{proof}
Both sides are the block Gaussian elimination of the same coordinates of~\(K_M\).  Eliminating the complement of~\(C\) and then \(C\setminus B_L\) gives the same Schur complement as eliminating their union in one step.
\end{proof}

\begin{table}[htbp]
\centering
\caption{Nested multiscale handoff readout.  Exact columns report maxima over the generated rows; drift columns report observed ranges and are not acceptance tolerances.}\label{tab:nested-multiscale-handoff}
\begin{tabular}{>{\raggedright\arraybackslash}p{0.43\linewidth}>{\raggedleft\arraybackslash}p{0.20\linewidth}>{\raggedright\arraybackslash}p{0.27\linewidth}}
\toprule
\textbf{Quantity} & \textbf{Readout} & \textbf{Status}\\
\midrule
boundary coisometry error & $1.64\times10^{-15}$ & exact finite control\\
role-basis intertwining error & $4.59\times10^{-16}$ & exact finite control\\
label-inclusion error & $2.11\times10^{-15}$ & exact finite control\\
corner product error & $9.44\times10^{-16}$ & exact finite control\\
corner left-inverse error & $2.10\times10^{-15}$ & exact finite control\\
carrier composition error & $7.50\times10^{-16}$ & exact finite control\\
common-ambient direct/staged Schur error & $1.26\times10^{-15}$ & exact finite control\\
conditional scaled GNS error & $5.56\times10^{-16}$ & exact finite control\\
independent directed-response drift & $0.270$--$0.393$ & distinguished object not natural\\
independent density drift & $0.367$--$0.866$ & independently reconstructed states differ\\
finite-$J$ intertwining error & $0.811$--$1.467$ & no $J$-natural family\\
finite-$J$ leakage into new roles & $0.349$--$0.759$ & old carrier not $J_M$-invariant\\
\bottomrule
\end{tabular}
\end{table}

\begin{corollary}[Record invariance and live backreaction in the common ambient]\label{cor:record-live-common-ambient}
For the tested common-ambient cases \((b,L,M)=(2,4,6),(3,4,6),(4,4,5)\), direct and staged elimination agree to at most \(1.26\times10^{-15}\).  The independently reconstructed record response agrees with the nested record response to at most \(6.67\times10^{-16}\) in the full boundary matrix and \(4.49\times10^{-16}\) after multiscale compression.  The corresponding live compressed drift is non-zero, ranging from \(0.272\) to \(0.657\).  These rows isolate immutable record extension from later live backreaction for the stated finite cases; they are not a general asymptotic theorem.
\end{corollary}

\begin{remark}[What the last arrow now contains]
The growing carrier algebras
\(M_{d_L}(\R)\) and their non-unital corner embeddings are now an exact finite directed system, and the resolved support test shows that the response together with all canonical coordinate projections generates the full carrier algebra in every sampled row.  What remains absent is a natural family of the distinguished objects.  The independently reconstructed responses and densities do not satisfy the corner restriction identities, the independently reconstructed GNS metrics therefore drift, and the finite-\(J\) operators neither intertwine nor preserve the old carrier subspaces.  Consequently the package now separates an exact algebraic carrier handoff from the still-failed response/state/GNS/\(J\) handoff.  A norm completion or physical interpretation of the resulting growing carrier system lies outside the finite scope of this article.
\end{remark}


\paragraph{Why the finite restriction is mathematically informative.}
Finiteness is used here as an audit condition rather than merely as a computational cutoff. It allows the provenance of every algebraic object to be traced back to explicit growth and response data, and it prevents unresolved limit operations from concealing failures of positivity, cyclicity, orientation, multiplicativity, or state compatibility. A property that fails in the finite core is not repaired merely by naming a continuum or operator-algebraic limit; a restoration would require an additional construction and a separate proof. Conversely, a property proved at every inspected finite level does not automatically survive an infinite limit. The finite results therefore serve both as constructive building blocks and as necessary obstruction tests for any later extension.

\subsection{Control-row summary}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.29\linewidth}>{\raggedleft\arraybackslash}p{0.14\linewidth}>{\raggedright\arraybackslash}p{0.47\linewidth}}
\caption{Generated finite structural control rows.}\label{tab:finite-structure-control-rows}\\
\toprule
\textbf{Control} & \textbf{Pass} & \textbf{Recorded readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Control} & \textbf{Pass} & \textbf{Recorded readout}\\
\midrule
\endhead
finite growth replay & 1 & 96 of 96 exact paired replays; zero address, parent, or non-finite-value failures.\\\hline
symmetric Schur positivity & 1 & 36 accepted rows; zero symmetry or PSD failures; all 36 sampled open-grounded responses are positive definite.\\\hline
finite GNS quotient/cyclicity & 1 & four of four controls pass, including two positive and two negative ambient-support cyclicity cases.\\\hline
finite \(J\) reversal & 1 & sign-flip error \(3.14\times10^{-16}\); unchanged skew rank and sign-even diagnostics.\\\hline
backreaction separation & 1 & explicit \(2\times2\) control has \(\beta=0\), \(\|B\|_F=2\sqrt2\), and \(\omega=-2\).\\\hline
prefix handoff & 1 & zero prefix/push-forward/carrier failures; boundary composition errors zero, zero, and \(3.24\times10^{-16}\) for the three weightings.\\\hline
nested multiscale handoff & 1 & exact growing carrier, corner, composition, conditional GNS, and common-ambient Schur controls; non-zero independent response/state/finite-\(J\) drift retained.\\
\bottomrule
\end{longtable}


\section{Derived quantities as finite row families}
\subsection{Baseline row families}
\paragraph{Code map.} \code{derived\_\allowbreak{}quantities/baseline.py} provides the first rows computed from core objects: node/event genesis rows, projection grammar rows, carrier-state rows, orientation rows, and region/GNS rows.

\begin{proposition}[Baseline rows are evaluations of core constructors]
Every baseline row can be traced to one of: \code{EmptySetGrowthModel}, prefix push-forward, terminal carrier/state extraction, orientation measurement, regional Schur response, or finite GNS construction.
\end{proposition}
\begin{proof}
\textbf{Object.} The object is the row family returned by the five public baseline functions. \textbf{Step 1.} \code{level\_\allowbreak{}models} enumerates finite approximants. \textbf{Step 2.} \code{genesis\_\allowbreak{}rows} reads node and event counts from the growth object. \textbf{Step 3.} \code{projection\_\allowbreak{}grammar\_\allowbreak{}rows} applies prefix push-forwards. \textbf{Step 4.} \code{carrier\_\allowbreak{}state\_\allowbreak{}rows} evaluates terminal distributions. \textbf{Step 5.} \code{orientation\_\allowbreak{}rows} and \code{region\_\allowbreak{}and\_\allowbreak{}gns\_\allowbreak{}rows} call signed-current, Schur, and algebra/GNS constructors. \textbf{Counter-check.} These rows add no independent object; mismatches identify a constructor or mapping defect. \textbf{Conclusion.} Baseline is the first complete finite evaluation layer.
\end{proof}

\subsection{Rank, kernel, coverage, and compressed projectivity}
\paragraph{Code map.} \code{rank\_\allowbreak{}kernel\_\allowbreak{}conditions.py} measures local response-density rank/kernel behavior and construction coverage. \code{compressed\_\allowbreak{}state\_\allowbreak{}projection\_\allowbreak{}consistency.py} measures whether compressed carrier states remain projective under target-level truncation.

\begin{proposition}[Compressed projectivity check]
For target levels \(k<\ell\), the projectivity rows compare a direct compression at level \(k\) against the push-forward of a compression at level \(\ell\).
\end{proposition}
\begin{proof}
\textbf{Object.} The object is a pair of compressed distributions over role/address keys. \textbf{Step 1.} Build the compressed state at the finer target level. \textbf{Step 2.} Push it forward by address truncation. \textbf{Step 3.} Build the coarser compressed state directly. \textbf{Step 4.} Compare them by total variation and sector profiles. \textbf{Counter-check.} A non-zero discrepancy can arise from role/coarse-key mismatch and is recorded as a finite discrepancy, not as a continuum anomaly. \textbf{Conclusion.} The check decides finite compatibility of the implemented compression map.
\end{proof}

\subsection{Structural live-record ledgers}
\paragraph{Code map.} \code{structural\_\allowbreak{}ledgers.py} records parameter purity, live-record structural calculations, history deltas, carrier effects, and state-sector decompositions.

\begin{proposition}[Live-record history delta uses one generated approximant]
The history-delta rows are computed from live and record states generated by the same \(b,L,m\) approximant; no additional state is fitted.
\end{proposition}
\begin{proof}
\textbf{Object.} The object is the paired row family over \(\mathrm{live}\) and \(\mathrm{record}\). \textbf{Step 1.} Construct one growth model. \textbf{Step 2.} Read both edge states from that model. \textbf{Step 3.} Compute row differences and carrier effects. \textbf{Counter-check.} If a row depends on an external parameter not present in the model arguments, it is outside this construction route. \textbf{Conclusion.} The ledger is a bookkeeping layer over core state separation.
\end{proof}

\subsection{Interlevel operator maps and interface rows}
\paragraph{Code map.} \code{operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} builds interlevel rows for GNS generator maps, algebra projection maps, conditional-expectation proxies, finite log-density preflow rows, and composition rows. \code{operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} builds seam, state-comparison, scaling, and map-naturality rows. \code{operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} builds finite condition rows for role dimensions, generator ranks, coordinate changes, boundary-response model choice, and skew survival.

\begin{definition}[Interlevel residual]
Let $X_M$ be a finite object at source level $M$ and let $X_L$ be the corresponding object at target level $L<M$. When both objects are represented on a common finite label set, the row family records residuals of the form
\begin{equation}
  \rho_{M\to L}(X)=\frac{\|\Pi_{M\to L}(X_M)-X_L\|_F}{\max(\|X_L\|_F,\eps)}.
  \label{eq:interlevel-residual}
\end{equation}
Here $\Pi_{M\to L}$ is the label-span projection or prefix-induced map implemented by the row function that produces the row.
\end{definition}

\begin{proposition}[Interlevel rows are finite discrepancies]
The interlevel rows record finite discrepancies between constructed objects at two levels. They do not construct an infinite-level object.
\end{proposition}
\begin{proof}
\textbf{Object.} The source objects are the finite response-algebra, GNS, conditional-expectation, and log-density rows at two levels. \textbf{Step 1.} Construct the level-$M$ and level-$L$ rows from the same $b$, mode, state, region rule, and growth schedule. \textbf{Step 2.} Express the two rows in shared labels when such labels are present. \textbf{Step 3.} Evaluate Frobenius, relative, or scalar residuals. \textbf{Counter-check.} A non-zero row is retained as a finite discrepancy for that map and label route. \textbf{Conclusion.} The row family is a finite comparison layer over already constructed matrix objects.
\end{proof}

\paragraph{Regenerated row command.}
The row values in this subsection are generated by the following command:
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 run_cnna.py \
  --branching 4 \
  --levels 4 5 \
  --modes linear \
  --states live record sym \
  --max-regions 2 \
  --max-boundary 700 \
  --max-interior 1000 \
  --directed-frontier-cap 6 \
  --algebra-tol 1e-10 \
  --algebra-max-iter 8 \
  --gns-tol 1e-10 \
  --growth-schedule layer_batch \
  --outdir outputs/transport_j_relation_reduced
\end{verbatim}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedleft\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}p{0.42\linewidth}}
\caption{Interlevel residual readout from the regenerated row surface.}\label{tab:interlevel-residual-readout}\\
\toprule
\textbf{Row family / quantity} & \textbf{Value} & \textbf{Finite object readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family / quantity} & \textbf{Value} & \textbf{Finite object readout}\\
\midrule
\endhead
\code{gns\_generator\_transport\_maps.csv} rows & 3 & live, record, and sym rows for the level-$5\to4$ map.\\
\hline
max GNS Gram relative error & $6.8185\times10^{-1}$ & label-span transport drift in the generated GNS rows.\\
\hline
max cyclic-vector error & $7.6898\times10^{-2}$ & cyclic-vector drift in the same rows.\\
\hline
\code{algebra\_\allowbreak{}projection\_\allowbreak{}morphism\_\allowbreak{}measurement.csv} rows & 3 & algebra projection rows for live, record, and sym.\\
\hline
max star-compatibility error & $1.4125\times10^{-16}$ & finite star compatibility residual.\\
\hline
max product-morphism residual & $1$ & product route residual in the finite algebra projection rows.\\
\hline
max center-preservation error & $2.2197\times10^{-1}$ & center preservation drift in the same rows.\\
\hline
max CE commuting-square error & $3.8206\times10^{-3}$ & conditional-expectation square residual.\\
\hline
max CE state-preservation drift & $1.4635$ & state drift in the finite conditional-expectation proxy.\\
\hline
max $K$-intertwining relative error & $2.8902\times10^{-1}$ & finite log-density preflow transport error.\\
\hline
max finite-preflow delta square error & $3.6978\times10^{-1}$ & commutator-delta square residual.\\
\hline
\code{operator\_\allowbreak{}stack\_\allowbreak{}residuals\_\allowbreak{}classification.csv} rows & 3 & live, record, and sym classification rows.\\
\hline
strict star-hom indicator & 0 & generated indicator field for the strict star-hom residual check.\\
\bottomrule
\end{longtable}

\subsection{Directed transport rows}
\paragraph{Code map.} \code{directed\_\allowbreak{}current\_\allowbreak{}transport.py} builds the boundary-prefix transport matrix, transport rows, composition rows, orientation summary rows, and finite coverage rows. The transport matrix sends source boundary indicators to target prefix classes.

\begin{proposition}[Directed transport row]
For levels $M>L$, each directed transport row compares the direct level-$L$ directed response with the transported level-$M$ directed response after applying the finite address-prefix transport matrix.
\end{proposition}
\begin{proof}
\textbf{Object.} The objects are two directed response matrices and the boundary-prefix transport matrix. \textbf{Step 1.} Build source and target boundary lists. \textbf{Step 2.} Build the finite transport matrix from address prefixes. \textbf{Step 3.} Push the source response to target coordinates. \textbf{Step 4.} Record direct-vs-transported discrepancies and scale-fit quantities. \textbf{Counter-check.} Boundary-role mismatch and open-grounded degrees can produce non-zero rows. \textbf{Conclusion.} The rows are finite transport comparisons between two constructed directed responses.
\end{proof}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.34\linewidth}>{\raggedleft\arraybackslash}p{0.16\linewidth}>{\raggedright\arraybackslash}p{0.42\linewidth}}
\caption{Directed transport readout from the regenerated row surface.}\label{tab:directed-transport-readout}\\
\toprule
\textbf{Row family / quantity} & \textbf{Value} & \textbf{Finite object readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family / quantity} & \textbf{Value} & \textbf{Finite object readout}\\
\midrule
\endhead
\code{directed\_current\_transport.csv} rows & 9 & directed transport rows for live, record, and sym in the integrated command.\\
\hline
\code{J\_orientation\_transport\_summary.csv} rows & 1 & summary row over the directed transport surface.\\
\hline
directed transport coverage field & 1 & generated coverage indicator in the summary row.\\
\hline
unavailable directed transport pairs & 0 & generated unavailable-pair count in the summary row.\\
\hline
live J/A orientation transport field & 1 & generated residual-threshold indicator in the summary row.\\
\hline
A-transport composition field & 0 & generated composition indicator in the summary row.\\
\bottomrule
\end{longtable}

\subsection{A/J orientation transport and composition}
\paragraph{Code map.} \code{j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} builds A/J orientation snapshots, transport rows, composition rows, and a summary row. These rows use the skew part $A$ on the positive support selected by the symmetric part $S$.

\begin{definition}[A/J orientation row]
An A/J row contains a finite skew-plane object, its support data, and its transported or composed counterpart. The scalar errors compare the orientation after transport or composition with the orientation obtained by direct construction at the target level.
\end{definition}

\paragraph{Regenerated row command.}
The row values in this subsection are generated by the following command:
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 run_j_orientation_projectivity.py \
  --branching 4 \
  --levels 4 5 6 \
  --modes linear \
  --max-regions 3 \
  --max-boundary 1200 \
  --max-interior 1800 \
  --directed-frontier-cap 6 \
  --gns-tol 1e-10 \
  --growth-schedule layer_batch \
  --outdir outputs/j_orientation_projectivity
\end{verbatim}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.34\linewidth}>{\raggedleft\arraybackslash}p{0.16\linewidth}>{\raggedright\arraybackslash}p{0.42\linewidth}}
\caption{A/J orientation transport and composition readout.}\label{tab:aj-orientation-readout}\\
\toprule
\textbf{Row family / quantity} & \textbf{Value} & \textbf{Finite object readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family / quantity} & \textbf{Value} & \textbf{Finite object readout}\\
\midrule
\endhead
\code{A\_J\_orientation\_snapshot.csv} rows & 18 & snapshots for levels $4,5,6$ and states live, record.\\
\hline
max snapshot $J^2+P$ error & $1.5264\times10^{-13}$ & support-level finite square residual.\\
\hline
\code{A\_J\_orientation\_transport.csv} rows & 54 & transport rows between the represented levels.\\
\hline
max scale-optimal A-orientation error & $6.1953\times10^{-14}$ & scalar orientation transport residual after scale fit.\\
\hline
\code{A\_J\_orientation\_composition.csv} rows & 18 & direct-vs-composed transport rows.\\
\hline
max direct-vs-composed A-plane residual & $3.3697\times10^{-14}$ & finite composition residual for the A-plane.\\
\hline
max direct scale-optimal A-orientation error & $2.9088\times10^{-14}$ & direct branch orientation residual.\\
\hline
max via scale-optimal A-orientation error & $2.0043\times10^{-14}$ & composed branch orientation residual.\\
\hline
summary raw A relative transport error & $9.4665\times10^{-1}$ & raw matrix relative error before scale-optimal orientation comparison.\\
\hline
summary scale-optimal A-orientation error & $1.3444\times10^{-15}$ & summary field for the fitted orientation scalar.\\
\bottomrule
\end{longtable}

\subsection{Local/global J sign relation}
\paragraph{Code map.} \code{local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation.py} builds global boundary sign rows and compares them with local region sign rows. The rows compare relative signs only; the simultaneous global flip remains represented by a separate field.

\begin{proposition}[Local/global sign rows compare relative signs]
The local/global sign rows compare a local sign with a global boundary sign on the same finite construction route. The rows retain the simultaneous sign-flip field and do not select an absolute sign.
\end{proposition}
\begin{proof}
\textbf{Object.} The objects are local finite J comparison rows and global boundary sign rows. \textbf{Step 1.} Construct global boundary sign data. \textbf{Step 2.} Construct local region sign data. \textbf{Step 3.} Compare the local sign to the global sign. \textbf{Step 4.} Evaluate the simultaneous flip field. \textbf{Counter-check.} A zero flip-invariance error records that the comparison is relative to a simultaneous sign flip. \textbf{Conclusion.} The row family represents finite relative sign data.
\end{proof}

\paragraph{Regenerated row command.}
The row values in this subsection are generated by the following command:
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 run_local_global_j_sign_relation.py \
  --branching 4 \
  --levels 4 5 \
  --modes linear \
  --max-regions 2 \
  --max-boundary 700 \
  --max-interior 1000 \
  --directed-frontier-cap 6 \
  --gns-tol 1e-10 \
  --growth-schedule layer_batch \
  --outdir outputs/local_global_j_sign_relation
\end{verbatim}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.34\linewidth}>{\raggedleft\arraybackslash}p{0.16\linewidth}>{\raggedright\arraybackslash}p{0.42\linewidth}}
\caption{Local/global J sign readout from regenerated rows.}\label{tab:local-global-j-readout}\\
\toprule
\textbf{Row family / quantity} & \textbf{Value} & \textbf{Finite object readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family / quantity} & \textbf{Value} & \textbf{Finite object readout}\\
\midrule
\endhead
\code{j\_\allowbreak{}sign\_\allowbreak{}global\_\allowbreak{}boundary\_\allowbreak{}sign\_\allowbreak{}relation.csv} rows & 16 & global boundary sign rows for levels $4,5$ and states live, record.\\
\hline
max global $J^2+P$ error & $5.5556\times10^{-15}$ & finite global sign square residual.\\
\hline
max global solve residual & $2.5045\times10^{-16}$ & Schur solve residual in the global sign rows.\\
\hline
max global row-sum residual & $4.6731$ & row-sum residual for the selected global boundary construction.\\
\hline
\code{local\_global\_J\_sign\_comparison.csv} rows & 8 & local/global comparison rows over the selected regions.\\
\hline
local/global relative sign value & $-1$ & generated relative sign value in all represented rows.\\
\hline
max local $J^2+P$ error & $3.8934\times10^{-14}$ & local finite sign square residual.\\
\hline
max global $J^2+P$ error in comparison & $5.5556\times10^{-15}$ & global square residual in comparison rows.\\
\hline
max flip-invariance error & 0 & simultaneous global flip field in the comparison rows.\\
\hline
local regions compared & 8 & count in \code{J\_sign\_sign\_relation\_summary.csv}.\\
\hline
absolute global sign fixed & 0 & generated field in the sign-relation summary row.\\
\bottomrule
\end{longtable}



\subsection{Live-record backreaction current}\label{sec:live-record-backreaction-current}
\paragraph{Code map.} \code{backreaction\_\allowbreak{}current.py} constructs regional rows for the live-record current defined in Equation~\eqref{eq:live-record-backreaction-current}, where $A_{\mathrm{live},L}$ and $A_{\mathrm{record},L}$ are the skew parts of directed Schur responses built on the same branching value, level, mode, region, boundary response model, and matrix sign relation. The same module writes growth-profile, region-sensitivity, transport, and summary rows.

\begin{definition}[Live-record backreaction current]
For a fixed finite region $R$ and level $L$, let
\begin{equation}
\begin{aligned}
  A^{R}_{\mathrm{live},L}&=\frac{M^{R}_{\mathrm{live},L}-(M^{R}_{\mathrm{live},L})^T}{2},\\
  A^{R}_{\mathrm{record},L}&=\frac{M^{R}_{\mathrm{record},L}-(M^{R}_{\mathrm{record},L})^T}{2}.
\end{aligned}
\label{eq:live-record-skew-parts}
\end{equation}
The live-record backreaction current is the finite skew matrix
\begin{equation}
  B^{R}_L=A^{R}_{\mathrm{live},L}-A^{R}_{\mathrm{record},L}.
  \label{eq:live-record-backreaction-current}
\end{equation}
Three distinct scalar readouts are used and must not be identified:
\begin{equation}
  b_L^R=\|B_L^R\|_F,\qquad
  \beta_L^R=\|A^{R}_{\mathrm{live},L}\|_F-\|A^{R}_{\mathrm{record},L}\|_F,\qquad
  \omega_L^R=\langle F_1,B_L^R F_2\rangle.
  \label{eq:backreaction-scalar-readouts}
\end{equation}
Here \(b_L^R\ge0\) is the norm of the difference matrix, \(\beta_L^R\) is a signed difference of two norms, and \(\omega_L^R\) is the oriented scalar of the compressed F1/F2 plane. A zero crossing of \(\beta_L^R\) is neither a zero of \(B_L^R\) nor a sign change of \(\omega_L^R\).
\end{definition}

\begin{proposition}[Backreaction rows compare live skew response with birth record]
The current $B^{R}_L$ in Equation~\eqref{eq:live-record-backreaction-current} is computed by subtracting the record skew response from the live skew response of Equation~\eqref{eq:live-record-skew-parts} on the same finite row coordinates.
\end{proposition}
\begin{proof}
\textbf{Object.} The inputs are two directed Schur responses with identical finite model, region, boundary, and sign-relation fields. \textbf{Step 1.} Build the live directed response and extract its skew part. \textbf{Step 2.} Build the record directed response and extract its skew part. \textbf{Step 3.} Subtract the two skew matrices. \textbf{Step 4.} Evaluate the three separate readouts in Equation~\eqref{eq:backreaction-scalar-readouts}. \textbf{Recorded branch.} The sign of \(\beta_L^R\) compares skew magnitudes; the sign of \(\omega_L^R\) concerns the selected oriented plane. Neither is a matrix-order statement, and \(b_L^R\) is unsigned. \textbf{Conclusion.} The row represents a finite matrix difference between current network response and birth-record response together with explicitly separated scalar diagnostics.
\end{proof}

\paragraph{Regenerated row command.}
The following command generates the live-record backreaction surface over three terminal levels for the displayed row values:
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 run_live_record_backreaction_current.py \
  --branching 4 \
  --levels 4 5 6 \
  --modes linear \
  --max-regions 1 \
  --max-boundary 600 \
  --max-interior 900 \
  --directed-frontier-cap 6 \
  --growth-schedule layer_batch \
  --outdir outputs/live_record_backreaction_linear_L456_layer_batch
\end{verbatim}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.16\linewidth}>{\raggedleft\arraybackslash}p{0.16\linewidth}>{\raggedleft\arraybackslash}p{0.18\linewidth}>{\raggedleft\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}p{0.24\linewidth}}
\caption{Live-record backreaction current rows generated by the stated command.}\label{tab:backreaction-current-readout}\\
\toprule
\textbf{Level} & \textbf{$b_L=\|B_L\|_F$} & \textbf{$\beta_L$} & \textbf{$\omega_L$} & \textbf{Sign fields}\\
\midrule
\endfirsthead
\toprule
\textbf{Level} & \textbf{$b_L=\|B_L\|_F$} & \textbf{$\beta_L$} & \textbf{$\omega_L$} & \textbf{Sign fields}\\
\midrule
\endhead
4 & $8.7395\times10^{-2}$ & $-7.3972\times10^{-2}$ & $-3.5\times10^{-5}$ & full-skew sign $-1$, plane sign $-1$\\
\hline
5 & $1.4179\times10^{-1}$ & $-1.5959\times10^{-2}$ & $-6.0\times10^{-5}$ & full-skew sign $-1$, plane sign $-1$\\
\hline
6 & $2.4168\times10^{-1}$ & $1.3825\times10^{-1}$ & $-9.4\times10^{-5}$ & full-skew sign $1$, plane sign $-1$\\
\bottomrule
\end{longtable}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.34\linewidth}>{\raggedleft\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}p{0.40\linewidth}}
\caption{Backreaction transport rows from the same generated surface.}\label{tab:backreaction-transport-readout}\\
\toprule
\textbf{Quantity} & \textbf{Value} & \textbf{Finite object readout}\\
\midrule
\endfirsthead
\toprule
\textbf{Quantity} & \textbf{Value} & \textbf{Finite object readout}\\
\midrule
\endhead
transport rows & 9 & three address-prefix transport routes for the level pairs in the generated surface.\\
\hline
available rows & 9 & all rows contain a constructed transported current.\\
\hline
raw relative error range & $2.0361\times10^{-1}$ to $1.1657\times10^{1}$ & amplitude-sensitive discrepancy between transported and target current.\\
\hline
scale-optimal orientation error range & $3.4987\times10^{-14}$ to $5.7964\times10^{-13}$ & residual after scalar fit of the orientation component.\\
\hline
orientation sign agreement & 9 of 9 & generated sign field comparing transported and target orientation.\\
\hline
fiber-average raw error range & $2.0361\times10^{-1}$ to $3.5119\times10^{-1}$ & row subset for the fiber-average transport route.\\
\bottomrule
\end{longtable}

\subsection{Birth-relative backreaction rows}
\paragraph{Code map.} \code{backreaction\_\allowbreak{}current.py} now writes the sibling-root birth level explicitly from \code{RegionSpec.left\_root} and verifies equality with the right sibling-root level. \code{backreaction\_\allowbreak{}birth\_\allowbreak{}relative.py} reads that field, attaches a birth-relative age, and computes zero-crossing rows from the signed norm-difference sequence \(\beta_L^R\). The age used for the law rows is
\begin{equation}
  \alpha=L_{\mathrm{frontier}}-L_{\mathrm{birth}}.
  \label{eq:birth-relative-age}
\end{equation}
Rows using coarse-frontier coverage are kept out of the law fit by the row fields.

\begin{proposition}[Birth-relative crossing row]
For one branching value, mode, and region index, the zero-crossing row is obtained from a finite list of signed scalar backreaction rows ordered by birth-relative age.
\end{proposition}
\begin{proof}
\textbf{Object.} The input is the finite row list containing \(B_L^R\) and its scalar readouts for one region family. \textbf{Step 1.} Read the explicit sibling-root birth level and attach the age in Equation~\eqref{eq:birth-relative-age}. \textbf{Step 2.} Sort the eligible full-terminal rows by \(\alpha\). \textbf{Step 3.} Read \(\beta_L^R=\code{live\_minus\_record\_skew\_norm}\). \textbf{Step 4.} If two adjacent ages carry opposite signs, record the first sign change and linearly interpolate the two sampled \(\beta\)-values. \textbf{Recorded branch.} If the sampled sequence contains no opposite signs, the crossing fields remain empty. \textbf{Conclusion.} The row is a finite interpolation of the skew-norm difference \(\beta_L^R\); it is not a zero of the matrix current \(B_L^R\), whose Frobenius norm remains non-negative, and it is not a crossing of \(\omega_L^R\).
\end{proof}

\paragraph{Regenerated row command.}
The following command generates the birth-relative rows displayed below:
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 run_birth_relative_backreaction_current.py \
  --branching 4 \
  --levels 4 5 6 \
  --modes linear \
  --max-regions 1 \
  --max-boundary 600 \
  --max-interior 900 \
  --directed-frontier-cap 6 \
  --growth-schedule layer_batch \
  --outdir outputs/birth_relative_backreaction_linear_L456_layer_batch
\end{verbatim}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.20\linewidth}>{\raggedleft\arraybackslash}p{0.14\linewidth}>{\raggedleft\arraybackslash}p{0.20\linewidth}>{\raggedleft\arraybackslash}p{0.16\linewidth}>{\raggedright\arraybackslash}p{0.22\linewidth}}
\caption{Birth-relative backreaction row sequence generated by the stated command.}\label{tab:birth-relative-readout}\\
\toprule
\textbf{Level} & \textbf{Age $\alpha$} & \textbf{$\|A_{\rm live}\|-\|A_{\rm record}\|$} & \textbf{$\|B_L\|$} & \textbf{Scalar signs}\\
\midrule
\endfirsthead
\toprule
\textbf{Level} & \textbf{Age $\alpha$} & \textbf{$\|A_{\rm live}\|-\|A_{\rm record}\|$} & \textbf{$\|B_L\|$} & \textbf{Scalar signs}\\
\midrule
\endhead
4 & 2 & $-7.3972\times10^{-2}$ & $8.7395\times10^{-2}$ & skew sign $-1$, plane sign $-1$\\
\hline
5 & 3 & $-1.5959\times10^{-2}$ & $1.4179\times10^{-1}$ & skew sign $-1$, plane sign $-1$\\
\hline
6 & 4 & $1.3825\times10^{-1}$ & $2.4168\times10^{-1}$ & skew sign $1$, plane sign $-1$\\
\bottomrule
\end{longtable}

\paragraph{Birth-relative crossing fields.}
The file \src{birth\_relative\_zero\_crossing\_by\_region.csv} is generated by the stated command. The interpolated crossing concerns \(\beta_L\) only. In the displayed sequence \(b_L>0\) at every sampled level and \(\omega_L<0\) throughout, so neither the matrix current nor the selected oriented component crosses zero. A schedule-stability value for the interpolated \(\beta\)-crossing is not stated here.


\subsection{Branching comparison and row aggregation}
\paragraph{Code map.} \code{backreaction\_\allowbreak{}branching\_\allowbreak{}shift.py} reads birth-relative mode/branching rows and writes curve and summary rows. \code{computed\_\allowbreak{}status\_\allowbreak{}rows.py} collects row families without constructing another matrix object.

\paragraph{Regenerated row command.}
The following command generates the branching comparison rows:
\begin{verbatim}
cd anc/CNNA_structured_core_pkg
PYTHONPATH=src python3 run_branching_zero_crossing_shift.py \
  --branching 3 4 5 \
  --levels 4 5 6 \
  --modes linear \
  --max-regions 1 \
  --max-boundary 600 \
  --max-interior 900 \
  --directed-frontier-cap 6 \
  --growth-schedule layer_batch \
  --outdir outputs/branching_zero_crossing_linear_L456_layer_batch
\end{verbatim}


\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\linewidth}>{\raggedleft\arraybackslash}p{0.16\linewidth}>{\raggedright\arraybackslash}p{0.38\linewidth}}
\caption{Backreaction row files generated by the stated commands.}\label{tab:backreaction-generated-row-files}\\
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Generated finite fields}\\
\midrule
\endfirsthead
\toprule
\textbf{Row family} & \textbf{Rows} & \textbf{Generated finite fields}\\
\midrule
\endhead
\code{live\_record\_backreaction\_current.csv} & 3 & live/record skew-response current fields at the sampled levels.\\
\hline
\code{backreaction\_transport.csv} & 9 & address-prefix transport fields for the same current rows.\\
\hline
\code{birth\_relative\_relative\_}\allowbreak{}\code{backreaction\_current.csv} & 3 & age-labelled current rows.\\
\hline
\code{birth\_relative\_zero\_crossing\_by\_region.csv} & 1 & interpolation fields generated from the sampled scalar sequence; no schedule-stability value is stated in this document.\\
\hline
\code{branching\_zero\_crossing\_}\allowbreak{}\code{branching\_shift\_curve.csv} & 3 & three branching-indexed rows are generated; two contain finite interpolated crossings, while the \(b=5\) row records no finite crossing under the stated levels and caps.\\
\hline
\code{branching\_zero\_crossing\_}\allowbreak{}\code{branching\_shift\_summary.csv} & 1 & row-family summary fields generated from the branching-indexed rows.\\
\bottomrule
\end{longtable}






\newpage

\section{Conclusion}
The finite core developed here provides an explicitly checkable base layer for CNNA. It begins from an empty finite configuration and introduces no external geometric background, continuum space, spacetime, field variables, integrals, or differential operators. The rooted $b$-ary tree is used as a finite provenance carrier, not as a discretized physical geometry; a Sierpi\'nski-type realization is not part of the finite derivation. Its subsequent objects are generated by a declared deterministic rule family. The branching index \(b\), depth cutoff \(L\), mode selector \(m\), update schedule \(\mathfrak{s}\), readout selectors, caps, and numerical tolerances are separated rather than collapsed into a claim of derivation from the empty configuration alone. This makes the model transparent in the finite sense: growth histories, edge weights, carrier push-forwards, response maps, algebraic closures, \(J\)-comparisons, local operator diagnostics, and backreaction rows can all be traced to finite combinatorial and matrix operations with explicit inputs.

The main value of the finite formulation is therefore not that it is already the most general or final form of the theory. Its value is that it displays the generative skeleton before further structures are placed on top of it. In a more developed formulation, one expects additional layers: larger region systems, deeper histories, refined operator surfaces, transport structures, limiting procedures, and eventually infinite or completed objects. Those layers may become mathematically more expressive, but they also make it harder to see which parts are genuinely derived and which parts have been added by representation. The present finite core is designed to keep that distinction visible.

The finite source now separates exact results from numerical observations. For fixed admissible inputs the growth object is well-defined; the symmetric open-grounded Schur response is positive semidefinite under its stated hypotheses; the finite real GNS quotient is a cyclic transpose representation; simultaneous orientation reversal leaves all sign-even finite-\(J\) diagnostics unchanged; the backreaction matrix and its scalar readouts obey explicit non-implications; address/carrier handoff composes exactly; and a linearly growing address-contrast carrier admits exact non-unital corner embeddings. Directed live and record surfaces still differ from the symmetrized control, skew components survive controlled decompositions, and local/operator transport diagnostics expose both satisfied and failed stronger properties. The first group consists of finite theorems. The remaining row statements are finite observations with residuals, not continuum theorems.

The discrete Dirichlet-to-Neumann construction is especially important in the finite sense used here. The DtN-type maps are Schur-complement response matrices on finite generated graphs. Boundary sets, interior sets, invertibility conditions, residuals, and compressed responses are explicit and directly inspectable. The complete finite provenance is now stated without a semantic gap: a birth adds a set-theoretic and coordinate-linear complement to the existing carrier; the generated directed weights couple that new direction to the prior network; a selected boundary/interior cut produces a directed Schur response; and only that response is decomposed into symmetric and skew parts. The complement identity by itself does not imply a skew sector. The construction is therefore a finite algebraic network response calculation, not an imported analytic boundary theory.

The conclusion is therefore conservative. The finite CNNA core demonstrates a coherent, reproducible discrete model initialized by an empty configuration and evolved by an explicit rule family. In comparisons where \(m\), \(\mathfrak{s}\), region selection, caps, and tolerances are fixed, \(b\) is the varied structural index and \(L\) the finite cutoff. The model supplies a controlled response calculus and a nontrivial hierarchy of finite diagnostics, but it does not establish an infinite theory or equivalence with established continuum frameworks. It provides a transparent base from which higher structures can be formulated without disguising fixed rules or numerical selectors as derived quantities.

\section{Outlook}
The next conceptual step is not to abandon the finite model, but to use it as the visible base layer for more structured extensions. The finite core should be understood as the simplest representation of the theory, not as its endpoint. Its role is comparable to a coordinate chart for the generative mechanism: it makes the construction inspectable before more complex objects, completions, or limiting procedures are introduced.

The first nontrivial carrier step has now been completed at finite level. The first-order address-contrast spaces grow with depth, intertwine exactly under the derived \code{fiber\_sqrt} prefix map, and yield composable non-unital corner embeddings of real full matrix algebras. This closes the carrier-algebra part of the handoff without pretending that the distinguished data are already natural. The independently reconstructed responses and densities drift under the corner restriction, the corresponding independent GNS metrics are not isometric, and the finite-\(J\) objects both fail to intertwine and leak into newly added role directions. The next structural problem is therefore sharper than before: derive a live evolution or completely positive transport law for these distinguished objects, or identify a state construction compatible with the exact carrier embeddings. A norm completion and its physical interpretation remain separate from the finite results proved here.

A first direction is therefore the infinite extension. This should be treated as a higher intermediate objective, not as an automatic consequence of the finite rows. Passing from finite generated carriers and matrices to infinite or completed objects would require additional mathematical control: compatible growth embeddings, stability of carrier push-forwards, convergence or projective consistency of response maps, control of residuals under depth increase, and a precise account of which finite diagnostics survive the limit. In particular, the existence of finite \(J\)-objects, finite GNS-like structures, or finite local operator checks should not by itself be read as the existence of corresponding infinite objects. Those claims require separate construction.

A second direction is deeper comparison with the discrete models separated in Section~\ref{sec:related-work}. The current comparison distinguishes carrier growth from occupation growth, sequential from synchronous event order, preservation from rearrangement of prior genealogy, forward response from inverse reconstruction, and finite combinatorial networks from metric quantum graphs. Future work should sharpen those bridges by proving explicit correspondences or incompatibility results, not by relying on shared terminology. The present model still introduces no manifold, smooth function, measure, integral, differential operator, or analytic boundary value problem. Likewise, a tree--Sierpi\'nski correspondence is not assumed: it remains a separate finite gluing or duality problem.

A third direction is structural enrichment above the finite core. The present code exposes live, record, and sym surfaces, finite boundary responses, directed decompositions, local operator diagnostics, sign transport, and backreaction currents. Higher layers could add more refined region systems, larger multi-scale carrier hierarchies, stronger consistency constraints between local and global objects, categorical or functorial descriptions of growth and projection, or completion procedures that preserve the derived-only character of the construction. The key constraint should remain that no new primitive is introduced silently. If an additional object is added, its status should be explicit: derived finite object, diagnostic row, limiting candidate, external comparison structure, or genuine new axiom.

The long-term theoretical question is whether this empty-initialized finite hierarchy can support a controlled path toward richer mathematical structures without losing its auditability. The finite core shows that substantial response, orientation, algebraic, and backreaction structure can arise after fixing an explicit deterministic rule family. Future work must determine which features are stable under changes of \(m\), \(\mathfrak{s}\), region system, and cutoff, rather than assuming those selectors are irrelevant. An infinite extension would then test whether compatible objects can be stabilized beyond finite depth. Connections to established theories become meaningful only after the relevant bridges have been built: finite-to-infinite consistency, response-map convergence, operator-domain control, and preservation of the live/record distinction.

Thus the outlook is intentionally cautious. The present work does not claim that the finite model already is a completed infinite theory or a final higher-level structure. It claims something narrower and testable: before such higher structures are invoked, there exists a reproducible discrete--finite CNNA core with an empty initial configuration, an explicit deterministic rule family, and declared finite selectors, in which the main objects can be computed, inspected, and challenged directly.


\section*{Software availability and assistance disclosure}
The complete Python source boundary documented in this article is included as arXiv ancillary material under \src{anc/CNNA_structured_core_pkg}. Generative AI assistance was used for drafting, review, code inspection, and documentation support. The author is solely responsible for the mathematical content, the implementation, the reported claims, and their interpretation.

\section{References}
The following references provide standard discrete, graph-theoretic, matrix-analytic, Schur-complement, finite network-response, and finite-dimensional operator-algebraic background, together with the recent model comparators discussed in Sections~\ref{sec:methodological-position} and~\ref{sec:related-work}. Historical primary sources are retained where they are mathematically foundational; recent references are used to locate the finite construction within current tree-growth and network-response work. They do not supply primitives for the CNNA construction.

\begin{thebibliography}{99}

\bibitem{Harary1969}
F. Harary,
\emph{Graph Theory},
Addison--Wesley, 1969,
ISBN 978-0-201-02787-7,
\url{https://search.worldcat.org/title/64676}.

\bibitem{Bollobas1998}
B. Bollob{\'a}s,
\emph{Modern Graph Theory},
Graduate Texts in Mathematics, vol. 184,
Springer, 1998,
\doi{10.1007/978-1-4612-0619-4}.

\bibitem{GodsilRoyle2001}
C. Godsil and G. Royle,
\emph{Algebraic Graph Theory},
Graduate Texts in Mathematics, vol. 207,
Springer, 2001,
\doi{10.1007/978-1-4613-0163-9}.

\bibitem{HornJohnson2013}
R. A. Horn and C. R. Johnson,
\emph{Matrix Analysis},
2nd edition,
Cambridge University Press, 2013,
ISBN 978-0-521-83940-2,
\url{https://www.cambridge.org/core/books/matrix-analysis/9CF2CB491C9E97948B15FAD835EF9A8B}.

\bibitem{Zhang2005}
F. Zhang, editor,
\emph{The Schur Complement and Its Applications},
Numerical Methods and Algorithms,
Springer, 2005,
\doi{10.1007/b105056}.

\bibitem{CurtisMorrow1991}
E. B. Curtis and J. A. Morrow,
``The Dirichlet to Neumann Map for a Resistor Network,''
\emph{SIAM Journal on Applied Mathematics},
51(4), 1011--1029, 1991,
\doi{10.1137/0151051}.

\bibitem{CurtisIngermanMorrow1998}
E. B. Curtis, D. Ingerman, and J. A. Morrow,
``Circular planar graphs and resistor networks,''
\emph{Linear Algebra and its Applications},
283(1--3), 115--150, 1998,
\doi{10.1016/S0024-3795(98)10087-3}.

\bibitem{Marckert2023}
J.-F. Marckert,
``Growing Random Uniform $d$-ary Trees,''
\emph{Annals of Combinatorics},
27, 51--66, 2023,
\doi{10.1007/s00026-022-00621-3},
\arxivref{2105.05513}.

\bibitem{FredesMarckert2023}
L. Fredes and J.-F. Marckert,
``Models of Random Subtrees of a Graph,''
\emph{Probability Surveys},
20, 722--801, 2023,
\doi{10.1214/23-PS22},
\arxivref{2102.12738}.

\bibitem{DunlopMardin2022}
F. Dunlop and A. Mardin,
``Galton--Watson Trees with First Ancestor Interaction,''
\emph{Journal of Statistical Physics},
189, article 38, 2022,
\doi{10.1007/s10955-022-03000-7},
\arxivref{2203.02253}.

\bibitem{BodiniGenitriniMaillerNaima2022}
O. Bodini, A. Genitrini, C. Mailler, and M. Naima,
``Strict Monotonic Trees Arising from Evolutionary Processes: Combinatorial and Probabilistic Study,''
\emph{Advances in Applied Mathematics},
133, article 102284, 2022,
\doi{10.1016/j.aam.2021.102284},
\url{https://hal.science/hal-02865198}.

\bibitem{BodiniGenitriniNurligareev2026}
O. Bodini, A. Genitrini, and K. Nurligareev,
``Growing Binary Trees,''
\emph{Electronic Proceedings in Theoretical Computer Science},
445, 47--56, 2026,
\doi{10.4204/EPTCS.445.7},
\arxivref{2603.25972}.

\bibitem{GernandtRohleder2022}
H. Gernandt and J. Rohleder,
``A Calder\'on Type Inverse Problem for Tree Graphs,''
\emph{Linear Algebra and its Applications},
646, 29--42, 2022,
\doi{10.1016/j.laa.2022.03.018},
\arxivref{2002.03670}.

\bibitem{BeardStefanViatorWelters2023}
K. Beard, A. Stefan, R. Viator, and A. Welters,
``Effective Operators and Their Variational Principles for Discrete Electrical Network Problems,''
\emph{Journal of Mathematical Physics},
64(7), 073501, 2023,
\doi{10.1063/5.0130429},
\arxivref{2210.05761}.

\bibitem{PengSong2022}
R. Peng and Z. Song,
``Sparsified Block Elimination for Directed Laplacians,''
in \emph{Proceedings of the 54th Annual ACM SIGACT Symposium on Theory of Computing (STOC 2022)},
557--567, 2022,
\doi{10.1145/3519935.3520053},
\arxivref{2111.10257}.

\bibitem{AvdoninKhmelnytskayaKravchenko2023}
S. A. Avdonin, K. V. Khmelnytskaya, and V. V. Kravchenko,
``Synthesis of a Quantum Tree Weyl Matrix,''
\emph{Bolet\'in de la Sociedad Matem\'atica Mexicana},
29, article 82, 2023,
\doi{10.1007/s40590-023-00561-9},
\arxivref{2308.01911}.

\bibitem{Kigami1993}
J. Kigami,
``Harmonic Calculus on p.c.f. Self-Similar Sets,''
\emph{Transactions of the American Mathematical Society},
335(2), 721--755, 1993,
\doi{10.1090/S0002-9947-1993-1076617-1}.

\bibitem{Kigami2001}
J. Kigami,
\emph{Analysis on Fractals},
Cambridge Tracts in Mathematics, vol. 143,
Cambridge University Press, 2001,
\doi{10.1017/CBO9780511470943}.

\bibitem{Strichartz2006}
R. S. Strichartz,
\emph{Differential Equations on Fractals: A Tutorial},
Princeton University Press, 2006,
\doi{10.1515/9780691186832}.

\bibitem{GelfandNaimark1943}
I. M. Gelfand and M. A. Naimark,
``On the Imbedding of Normed Rings into the Ring of Operators on Hilbert Space,''
\emph{Matematicheskii Sbornik},
12(2), 197--217, 1943,
\url{https://www.mathnet.ru/eng/sm6155}.

\bibitem{HaagKastler1964}
R. Haag and D. Kastler,
``An Algebraic Approach to Quantum Field Theory,''
\emph{Journal of Mathematical Physics},
5(7), 848--861, 1964,
\doi{10.1063/1.1704187}.

\bibitem{Bratteli1972}
O. Bratteli,
``Inductive Limits of Finite Dimensional $C^*$-Algebras,''
\emph{Transactions of the American Mathematical Society},
171, 195--234, 1972,
\doi{10.1090/S0002-9947-1972-0312282-2}.

\bibitem{FannesNachtergaeleWerner1992}
M. Fannes, B. Nachtergaele, and R. F. Werner,
``Finitely Correlated States on Quantum Spin Chains,''
\emph{Communications in Mathematical Physics},
144(3), 443--490, 1992,
\doi{10.1007/BF02099178}.

\bibitem{FinsterKamran2021}
F. Finster and N. Kamran,
``Complex Structures on Jet Spaces and Bosonic Fock Space Dynamics for Causal Variational Principles,''
\emph{Pure and Applied Mathematics Quarterly},
17(1), 55--140, 2021,
\doi{10.4310/PAMQ.2021.v17.n1.a3},
\arxivref{1808.03177}.

\bibitem{Segal1947}
I. E. Segal,
``Irreducible Representations of Operator Algebras,''
\emph{Bulletin of the American Mathematical Society},
53, 73--88, 1947,
\doi{10.1090/S0002-9904-1947-08742-5}.

\end{thebibliography}

\section{Source-tree object boundary}
The Python source constructs finite objects at fixed values of $b$, $L$, mode, state, region selectors, finite caps, and tolerances. The constructed objects include finite trees with explicit open slots, finite growth-step records, finite edge dictionaries, finite distributions, finite Schur responses, finite directed responses, finite matrix algebras, finite GNS support quotients, finite transports, finite sign comparisons, finite backreaction-current rows, and row-family tables computed from those objects.

\begin{longtable}{>{\raggedright\arraybackslash}p{0.28\linewidth}>{\raggedright\arraybackslash}p{0.64\linewidth}}
\caption{Objects constructed by the inspected source tree.}\label{tab:constructed-objects}\\
\toprule
\textbf{Object group} & \textbf{Constructed finite objects}\\
\midrule
\endfirsthead
\toprule
\textbf{Object group} & \textbf{Constructed finite objects}\\
\midrule
\endhead
Growth and schedule & \code{Node}, \code{Event}, \code{OpenBirthSlot}, \code{GrowthStep}, \code{EmptySetGrowthModel}, record/live edge dictionaries, and schedule-dependent generated rows.\\
\hline
Carrier and prefix maps & terminal address sets, uniform carrier, terminal diagonal state, prefix push-forward, center/non-center split, finite total-variation rows, nested address-contrast role carriers, label inclusions, and non-unital corner embeddings.\\
\hline
Response matrices & symmetric Schur--DtN response matrices, directed Schur response matrices, symmetric/skew decomposition, role-compressed response matrices, and finite residual fields.\\
\hline
Finite algebra layer & finite matrix-basis closure, positive density from response support, finite Gram matrices, tolerance-resolved quotient support, full-basis left-action audits, explicit cyclic-span ranks, and finite GNS data.\\
\hline
Regional/local layer & regional response records, local generator systems, support projectors, restricted finite algebras, joined algebras, commutator matrices, finite commutants, Tomita star-map matrices, and split residual rows.\\
\hline
State and entropy rows & compressed carrier/GNS-state objects, refined boundary-role bases, finite entropy, finite relative entropy, Jensen--Shannon divergence, and record/live entropy rows.\\
\hline
Transport and orientation rows & interlevel projection residuals, seam/interface rows, directed-current transport, A/J orientation snapshots, orientation transport, local/global sign comparisons, and finite sign summaries.\\
\hline
Backreaction rows & live/record skew-response matrix $B_L=A_L^{\rm live}-A_L^{\rm record}$, its norm $b_L$, skew-norm difference $\beta_L$, oriented scalar $\omega_L$, transported rows, explicit sibling-root birth levels, $\beta$-crossing rows, and branching comparisons.\\
\bottomrule
\end{longtable}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.30\linewidth}>{\raggedright\arraybackslash}p{0.62\linewidth}}
\caption{Objects absent from the inspected source tree.}\label{tab:absent-objects}\\
\toprule
\textbf{Object name} & \textbf{Status in this source tree}\\
\midrule
\endfirsthead
\toprule
\textbf{Object name} & \textbf{Status in this source tree}\\
\midrule
\endhead
Infinite-level object & The source constructs a finite directed system of growing carrier algebras and corner embeddings, but no norm completion, inductive-limit object, or projective-limit object over all $L$ is present.\\
\hline
Von Neumann algebra closure & The source constructs finite matrix algebras and finite commutant bases; it contains no weak-operator or strong-operator closure.\\
\hline
Type-III result & The source contains finite rank, nullity, support, and residual rows; it contains no Type-III classification object.\\
\hline
Continuum spacetime model & The source contains finite growth steps, finite responses, and finite transport rows; it contains no continuum metric field.\\
\hline
Lorentz signature or local eigen-time & The source records causal depth, linearization index, and response/lapse weights; it contains no Lorentzian tangent structure or eigen-time field.\\
\hline
Unique global complex orientation & The source contains finite local and global sign-comparison rows; it contains no constructor selecting one absolute global sign of $J$.\\
\hline
Asymptotic theorem over $L$ & The source emits rows at specified finite levels; it contains no theorem over all $L$ or a convergence proof.\\
\bottomrule
\end{longtable}

\newpage
\section{Generated row-file index}
The table groups the row files whose values are read in the numerical paragraphs of this document. Each entry is tied to a command shown in the section where the corresponding object is discussed. The growth-schedule argument is part of the command label.
\begin{longtable}{>{\raggedright\arraybackslash}p{0.22\linewidth}>{\raggedright\arraybackslash}p{0.17\linewidth}>{\raggedright\arraybackslash}p{0.53\linewidth}}
\caption{Row-file groups generated from the current source tree.}\label{tab:row-file-index}\\
\toprule
\textbf{Object layer} & \textbf{Command label} & \textbf{Row files}\\
\midrule
\endfirsthead
\toprule
\textbf{Object layer} & \textbf{Command label} & \textbf{Row files}\\
\midrule
\endhead
growth, carrier, and whole-network F1/F2 & integrated / layer batch & \begin{minipage}[t]{\linewidth}\raggedright \path{emptyset_genesis_measurement.csv}\\ \path{level_count_measurement.csv}\\ \path{eventlog_hashes.csv}\\ \path{projection_grammar.csv}\\ \path{carrier_projectivity.csv}\\ \path{terminal_diagonal_state_measurement.csv}\\ \path{terminal_diagonal_state_projectivity.csv}\\ \path{birth_linearization_invariance.csv}\\ \path{f1f2_skew_orientation_measurement.csv}\\ \path{live_record_history_delta.csv}\end{minipage}\\
\hline
slot-step comparison rows & integrated / slot step & \begin{minipage}[t]{\linewidth}\raggedright \path{birth_linearization_invariance.csv}\\ \path{carrier_projectivity.csv}\\ \path{terminal_diagonal_state_projectivity.csv}\\ \path{f1f2_skew_orientation_measurement.csv}\end{minipage}\\
\hline
Schur response, directed response, and finite J & integrated / layer batch & \begin{minipage}[t]{\linewidth}\raggedright \path{regional_schur_dtn_response_measurement.csv}\\ \path{directed_response_construction.csv}\\ \path{directed_SA_decomposition.csv}\\ \path{directed_skew_survival.csv}\\ \path{directed_J_finite_object_comparison.csv}\end{minipage}\\
\hline
response algebra, GNS, and compressed state rows & integrated / layer batch & \begin{minipage}[t]{\linewidth}\raggedright \path{response_algebra_measurement.csv}\\ \path{finite_gns_pre_representation_measurement.csv}\\ \path{finite_gns_cyclicity_controls.csv}\\ \path{compressed_carrier_state_projectivity.csv}\end{minipage}\\
\hline
local support algebra, Tomita, split, refined-basis, and entropy rows & local-operator run & \begin{minipage}[t]{\linewidth}\raggedright \path{local_operator_isotony.csv}\\ \path{local_operator_commutation.csv}\\ \path{local_operator_additivity.csv}\\ \path{local_vacuum_cyclicity.csv}\\ \path{faithful_state.csv}\\ \path{commutant_duality.csv}\\ \path{tomita_standard_form_compatibility.csv}\\ \path{split_factorization.csv}\\ \path{refined_port_basis_resolution.csv}\\ \path{collared_split_refined_basis.csv}\\ \path{record_live_relative_entropy.csv}\\ \path{tomita_entropy_flow_alignment.csv}\\ \path{multiscale_port_entropy_resolution.csv}\end{minipage}\\
\hline
interlevel transport and A/J orientation rows & integrated; A/J run & \begin{minipage}[t]{\linewidth}\raggedright \path{gns_generator_transport_maps.csv}\\ \path{algebra_projection_morphism_measurement.csv}\\ \path{conditional_expectation_commuting_square.csv}\\ \path{operator_stack_residuals_classification.csv}\\ \path{A_J_orientation_snapshot.csv}\\ \path{A_J_orientation_transport.csv}\\ \path{A_J_orientation_composition.csv}\end{minipage}\\
\hline
local/global J sign rows & local/global sign run & \begin{minipage}[t]{\linewidth}\raggedright \path{j_sign_global_boundary_sign_relation.csv}\\ \path{local_global_J_sign_comparison.csv}\\ \path{J_sign_sign_relation_summary.csv}\end{minipage}\\
\hline
live-record backreaction current & backreaction run & \begin{minipage}[t]{\linewidth}\raggedright \path{live_record_backreaction_current.csv}\\ \path{backreaction_growth_profile.csv}\\ \path{backreaction_transport.csv}\\ \path{backreaction_current_summary.csv}\end{minipage}\\
\hline
birth-relative backreaction rows & birth-relative run & \begin{minipage}[t]{\linewidth}\raggedright \path{birth_relative_relative_backreaction_current.csv}\\ \path{birth_relative_zero_crossing_by_region.csv}\\ \path{birth_relative_mode_branching_comparison.csv}\\ \path{birth_relative_backreaction_law_summary.csv}\end{minipage}\\
\hline
branching crossing rows & branching run & \begin{minipage}[t]{\linewidth}\raggedright \path{branching_zero_crossing_branching_shift_curve.csv}\\ \path{branching_zero_crossing_branching_shift_summary.csv}\end{minipage}\\
\hline
finite structural theorem controls & package-consistency run & \begin{minipage}[t]{\linewidth}\raggedright \path{docs/FINITE_STRUCTURE_THEOREM_CONTROLS.csv}\end{minipage}\\
\hline
nested multiscale handoff & nested handoff run & \begin{minipage}[t]{\linewidth}\raggedright \path{docs/NESTED_MULTISCALE_CARRIER.csv}\\ \path{docs/NESTED_MULTISCALE_HANDOFF.csv}\\ \path{docs/NESTED_MULTISCALE_COMPOSITION.csv}\\ \path{docs/NESTED_MULTISCALE_COMMON_AMBIENT_SCHUR.csv}\\ \path{docs/NESTED_MULTISCALE_SUMMARY.csv}\end{minipage}\\
\hline
\bottomrule
\end{longtable}
\newpage
\section{Function-level source inventory}
The table lists top-level classes and functions in the inspected Python source subtree. The line number is the definition line in the current source archive.
\begin{longtable}{>{\raggedright\arraybackslash}p{0.29\linewidth}>{\raggedright\arraybackslash}p{0.33\linewidth}>{\raggedright\arraybackslash}p{0.07\linewidth}>{\raggedright\arraybackslash}p{0.23\linewidth}}
\caption{Top-level code objects in the documented Python source surface.}\label{tab:function-inventory}\\
\toprule
\textbf{Source file} & \textbf{Code object} & \textbf{Line} & \textbf{Object type}\\
\midrule
\endfirsthead
\toprule
\textbf{Source file} & \textbf{Code object} & \textbf{Line} & \textbf{Object type}\\
\midrule
\endhead
\code{analysis\_\allowbreak{}entrypoints/run\_\allowbreak{}cnna\_\allowbreak{}analysis.py} & \code{parse\_\allowbreak{}args} & 21 & finite function\\
\hline
\code{analysis\_\allowbreak{}entrypoints/run\_\allowbreak{}cnna\_\allowbreak{}analysis.py} & \code{main} & 40 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{\_\allowbreak{}unit\_\allowbreak{}projector} & 32 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{\_\allowbreak{}sandwich} & 39 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{\_\allowbreak{}symmetric\_\allowbreak{}coupling} & 43 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{\_\allowbreak{}skew\_\allowbreak{}coupling} & 50 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{operator\_\allowbreak{}scale\_\allowbreak{}metadata} & 57 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{\_\allowbreak{}nonzero\_\allowbreak{}or\_\allowbreak{}empty} & 80 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{local\_\allowbreak{}operator\_\allowbreak{}generators} & 85 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{role\_\allowbreak{}coordinate\_\allowbreak{}mapping} & 141 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{role\_\allowbreak{}support\_\allowbreak{}indices} & 169 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{role\_\allowbreak{}support\_\allowbreak{}projector} & 213 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{independently\_\allowbreak{}restricted\_\allowbreak{}operator\_\allowbreak{}algebra} & 221 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{independent\_\allowbreak{}embedding\_\allowbreak{}metrics} & 275 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{local\_\allowbreak{}operator\_\allowbreak{}algebras} & 319 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{max\_\allowbreak{}span\_\allowbreak{}residual} & 326 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{max\_\allowbreak{}star\_\allowbreak{}residual} & 332 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{joined\_\allowbreak{}algebra} & 338 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{commutator\_\allowbreak{}metrics} & 345 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{state\_\allowbreak{}commutator\_\allowbreak{}metric} & 360 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{matrix\_\allowbreak{}rank\_\allowbreak{}from\_\allowbreak{}columns} & 368 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{gns\_\allowbreak{}support\_\allowbreak{}data} & 381 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{gns\_\allowbreak{}cyclic\_\allowbreak{}rank} & 391 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{gns\_\allowbreak{}separating\_\allowbreak{}nullity} & 401 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{nullspace} & 417 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{commutant\_\allowbreak{}algebra\_\allowbreak{}basis} & 426 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{basis\_\allowbreak{}to\_\allowbreak{}algebra} & 448 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{star\_\allowbreak{}map\_\allowbreak{}matrix} & 452 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{finite\_\allowbreak{}tomita\_\allowbreak{}star\_\allowbreak{}metrics} & 462 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{state\_\allowbreak{}pair\_\allowbreak{}backreaction\_\allowbreak{}algebras} & 639 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{live\_\allowbreak{}record\_\allowbreak{}backreaction\_\allowbreak{}algebras} & 686 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{identical\_\allowbreak{}history\_\allowbreak{}backreaction\_\allowbreak{}algebras} & 690 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{\_\allowbreak{}node\_\allowbreak{}address\_\allowbreak{}is\_\allowbreak{}prefix} & 694 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{\_\allowbreak{}descendants\_\allowbreak{}at\_\allowbreak{}exact\_\allowbreak{}level} & 698 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{\_\allowbreak{}lca\_\allowbreak{}id\_\allowbreak{}for\_\allowbreak{}nodes} & 706 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{\_\allowbreak{}cone\_\allowbreak{}interior\_\allowbreak{}to\_\allowbreak{}frontier} & 715 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{node\_\allowbreak{}level\_\allowbreak{}cut\_\allowbreak{}for\_\allowbreak{}operator\_\allowbreak{}system} & 726 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{node\_\allowbreak{}level\_\allowbreak{}schur\_\allowbreak{}embedding\_\allowbreak{}metrics} & 783 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{relative\_\allowbreak{}common\_\allowbreak{}ambient\_\allowbreak{}schur\_\allowbreak{}embedding\_\allowbreak{}metrics} & 881 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{build\_\allowbreak{}genealogical\_\allowbreak{}corridor\_\allowbreak{}regions} & 1035 & finite function\\
\hline
\code{core/algebra\_\allowbreak{}support.py} & \code{genealogical\_\allowbreak{}corridor\_\allowbreak{}metadata} & 1110 & finite function\\
\hline
\code{core/compressed\_\allowbreak{}state.py} & \code{compressed\_\allowbreak{}state\_\allowbreak{}object} & 24 & finite function\\
\hline
\code{core/compressed\_\allowbreak{}state.py} & \code{compressed\_\allowbreak{}projective\_\allowbreak{}distribution} & 95 & finite function\\
\hline
\code{core/compressed\_\allowbreak{}state.py} & \code{values\_\allowbreak{}for\_\allowbreak{}keys} & 120 & finite function\\
\hline
\code{core/compressed\_\allowbreak{}state.py} & \code{key\_\allowbreak{}is\_\allowbreak{}center} & 124 & finite function\\
\hline
\code{core/compressed\_\allowbreak{}state.py} & \code{sector\_\allowbreak{}profile\_\allowbreak{}tv} & 128 & finite function\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & \code{DirectedSchurResponse} & 16 & finite class\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & \code{state\_\allowbreak{}directed\_\allowbreak{}edges} & 27 & finite function\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & \code{directed\_\allowbreak{}local\_\allowbreak{}matrix} & 50 & finite function\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & \code{directed\_\allowbreak{}schur\_\allowbreak{}response} & 98 & finite function\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & \code{directed\_\allowbreak{}schur\_\allowbreak{}response\_\allowbreak{}from\_\allowbreak{}model} & 139 & finite function\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & \code{directed\_\allowbreak{}environment\_\allowbreak{}port\_\allowbreak{}response\_\allowbreak{}from\_\allowbreak{}model} & 169 & finite function\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & \code{\_\allowbreak{}descendants\_\allowbreak{}at\_\allowbreak{}level} & 235 & finite function\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & \code{build\_\allowbreak{}coarse\_\allowbreak{}frontier\_\allowbreak{}sibling\_\allowbreak{}regions} & 243 & finite function\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & \code{region\_\allowbreak{}frontier\_\allowbreak{}level} & 352 & finite function\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & \code{region\_\allowbreak{}is\_\allowbreak{}coarse\_\allowbreak{}frontier} & 357 & finite function\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & \code{signed\_\allowbreak{}role\_\allowbreak{}basis\_\allowbreak{}F1F2} & 360 & finite function\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & \code{split\_\allowbreak{}symmetric\_\allowbreak{}skew} & 402 & finite function\\
\hline
\code{core/directed\_\allowbreak{}dtn.py} & \code{j\_\allowbreak{}finite\_\allowbreak{}object\_\allowbreak{}from\_\allowbreak{}SA} & 408 & finite function\\
\hline
\code{core/emptyset\_\allowbreak{}growth.py} & \code{RuleCoefficients} & 20 & finite class\\
\hline
\code{core/emptyset\_\allowbreak{}growth.py} & \code{rule\_\allowbreak{}coefficients} & 41 & finite function\\
\hline
\code{core/emptyset\_\allowbreak{}growth.py} & \code{Node} & 59 & finite class\\
\hline
\code{core/emptyset\_\allowbreak{}growth.py} & \code{Event} & 76 & finite class\\
\hline
\code{core/emptyset\_\allowbreak{}growth.py} & \code{OpenBirthSlot} & 100 & finite class\\
\hline
\code{core/emptyset\_\allowbreak{}growth.py} & \code{GrowthStep} & 110 & finite class\\
\hline
\code{core/emptyset\_\allowbreak{}growth.py} & \code{EmptySetGrowthModel} & 121 & finite class\\
\hline
\code{core/entropy\_\allowbreak{}quantities.py} & \code{\_\allowbreak{}support\_\allowbreak{}projector\_\allowbreak{}from\_\allowbreak{}density} & 12 & finite function\\
\hline
\code{core/entropy\_\allowbreak{}quantities.py} & \code{von\_\allowbreak{}neumann\_\allowbreak{}entropy\_\allowbreak{}no\_\allowbreak{}epsilon} & 23 & finite function\\
\hline
\code{core/entropy\_\allowbreak{}quantities.py} & \code{quantum\_\allowbreak{}relative\_\allowbreak{}entropy\_\allowbreak{}no\_\allowbreak{}epsilon} & 37 & finite function\\
\hline
\code{core/entropy\_\allowbreak{}quantities.py} & \code{jensen\_\allowbreak{}shannon\_\allowbreak{}divergence\_\allowbreak{}no\_\allowbreak{}epsilon} & 76 & finite function\\
\hline
\code{core/entropy\_\allowbreak{}quantities.py} & \code{record\_\allowbreak{}live\_\allowbreak{}entropy\_\allowbreak{}metrics} & 94 & finite function\\
\hline
\code{core/math\_\allowbreak{}utils.py} & \code{fro} & 19 & finite function\\
\hline
\code{core/math\_\allowbreak{}utils.py} & \code{tv} & 23 & finite function\\
\hline
\code{core/math\_\allowbreak{}utils.py} & \code{normalize\_\allowbreak{}dict} & 28 & finite function\\
\hline
\code{core/math\_\allowbreak{}utils.py} & \code{normalize\_\allowbreak{}distribution} & 36 & finite function\\
\hline
\code{core/math\_\allowbreak{}utils.py} & \code{tv\_\allowbreak{}arr} & 47 & finite function\\
\hline
\code{core/math\_\allowbreak{}utils.py} & \code{\_\allowbreak{}float\_\allowbreak{}field} & 58 & finite function\\
\hline
\code{core/math\_\allowbreak{}utils.py} & \code{\_\allowbreak{}max\_\allowbreak{}metric} & 68 & finite function\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{NestedRoleBasis} & 15 & finite class\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{CommonAmbientSchurResult} & 24 & finite class\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{helmert\_\allowbreak{}slot\_\allowbreak{}contrasts} & 34 & finite function\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{\_\allowbreak{}normalized\_\allowbreak{}indicator} & 47 & finite function\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{\_\allowbreak{}relative\_\allowbreak{}depths} & 59 & finite function\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{nested\_\allowbreak{}address\_\allowbreak{}contrast\_\allowbreak{}basis} & 64 & finite function\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{label\_\allowbreak{}inclusion\_\allowbreak{}matrix} & 122 & finite function\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{role\_\allowbreak{}intertwining\_\allowbreak{}metrics} & 133 & finite function\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{corner\_\allowbreak{}embed} & 153 & finite function\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{corner\_\allowbreak{}restrict} & 157 & finite function\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{symmetric\_\allowbreak{}open\_\allowbreak{}grounded\_\allowbreak{}matrix} & 161 & finite function\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{\_\allowbreak{}nodes\_\allowbreak{}at\_\allowbreak{}level\_\allowbreak{}under} & 185 & finite function\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{\_\allowbreak{}cone\_\allowbreak{}nodes} & 196 & finite function\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{common\_\allowbreak{}ambient\_\allowbreak{}interlevel\_\allowbreak{}schur} & 209 & finite function\\
\hline
\code{core/nested\_\allowbreak{}multiscale.py} & \code{resolved\_\allowbreak{}support\_\allowbreak{}graph\_\allowbreak{}metrics} & 258 & finite function\\
\hline
\code{core/operator\_\allowbreak{}test\_\allowbreak{}config.py} & \code{OperatorTestConfig} & 10 & finite class\\
\hline
\code{core/operator\_\allowbreak{}test\_\allowbreak{}config.py} & \code{iter\_\allowbreak{}growth\_\allowbreak{}models} & 26 & finite function\\
\hline
\code{core/projective\_\allowbreak{}maps.py} & \code{prefix} & 21 & finite function\\
\hline
\code{core/projective\_\allowbreak{}maps.py} & \code{terminal\_\allowbreak{}carrier} & 27 & finite function\\
\hline
\code{core/projective\_\allowbreak{}maps.py} & \code{terminal\_\allowbreak{}state} & 32 & finite function\\
\hline
\code{core/projective\_\allowbreak{}maps.py} & \code{push\_\allowbreak{}forward} & 56 & finite function\\
\hline
\code{core/projective\_\allowbreak{}maps.py} & \code{center\_\allowbreak{}subset\_\allowbreak{}prefix} & 64 & finite function\\
\hline
\code{core/projective\_\allowbreak{}maps.py} & \code{split\_\allowbreak{}distribution} & 72 & finite function\\
\hline
\code{core/projective\_\allowbreak{}maps.py} & \code{response\_\allowbreak{}energy\_\allowbreak{}distribution} & 87 & finite function\\
\hline
\code{core/refined\_\allowbreak{}port\_\allowbreak{}basis.py} & \code{\_\allowbreak{}normalized\_\allowbreak{}indicator\_\allowbreak{}vector} & 17 & finite function\\
\hline
\code{core/refined\_\allowbreak{}port\_\allowbreak{}basis.py} & \code{\_\allowbreak{}split\_\allowbreak{}frontier\_\allowbreak{}group} & 28 & finite function\\
\hline
\code{core/refined\_\allowbreak{}port\_\allowbreak{}basis.py} & \code{refined\_\allowbreak{}boundary\_\allowbreak{}role\_\allowbreak{}basis} & 36 & finite function\\
\hline
\code{core/refined\_\allowbreak{}port\_\allowbreak{}basis.py} & \code{refined\_\allowbreak{}regional\_\allowbreak{}response} & 75 & finite function\\
\hline
\code{core/refined\_\allowbreak{}port\_\allowbreak{}basis.py} & \code{refined\_\allowbreak{}support\_\allowbreak{}algebra} & 112 & finite function\\
\hline
\code{core/region\_\allowbreak{}response.py} & \code{sibling\_\allowbreak{}pair\_\allowbreak{}regions} & 25 & finite function\\
\hline
\code{core/region\_\allowbreak{}response.py} & \code{region\_\allowbreak{}size\_\allowbreak{}meta} & 35 & finite function\\
\hline
\code{core/region\_\allowbreak{}response.py} & \code{positive\_\allowbreak{}support\_\allowbreak{}density\_\allowbreak{}from\_\allowbreak{}response} & 52 & finite function\\
\hline
\code{core/region\_\allowbreak{}response.py} & \code{RegionalResponse} & 101 & finite class\\
\hline
\code{core/region\_\allowbreak{}response.py} & \code{regional\_\allowbreak{}response} & 119 & finite function\\
\hline
\code{core/region\_\allowbreak{}response.py} & \code{signed\_\allowbreak{}orientation\_\allowbreak{}metrics} & 154 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{AlgebraBasis} & 22 & finite class\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{rank\_\allowbreak{}one} & 30 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{add\_\allowbreak{}to\_\allowbreak{}basis} & 34 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{algebra\_\allowbreak{}closure} & 45 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{project\_\allowbreak{}coeffs} & 70 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{reconstruct} & 74 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{span\_\allowbreak{}residual} & 81 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{positive\_\allowbreak{}density\_\allowbreak{}from\_\allowbreak{}response} & 88 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{gens\_\allowbreak{}from\_\allowbreak{}response} & 105 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{build\_\allowbreak{}algebras} & 144 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{state\_\allowbreak{}value} & 155 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{GNSData} & 160 & finite class\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{state\_\allowbreak{}gram} & 184 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{quotient\_\allowbreak{}support} & 195 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{left\_\allowbreak{}coeff\_\allowbreak{}matrix} & 204 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{\_\allowbreak{}column\_\allowbreak{}rank} & 216 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{measurement\_\allowbreak{}gns} & 229 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{positive\_\allowbreak{}trace\_\allowbreak{}normalize\_\allowbreak{}matrix} & 329 & finite function\\
\hline
\code{core/response\_\allowbreak{}algebra.py} & \code{project\_\allowbreak{}density\_\allowbreak{}to\_\allowbreak{}algebra\_\allowbreak{}span} & 358 & finite function\\
\hline
\code{core/schur\_\allowbreak{}dtn.py} & \code{SchurResponse} & 23 & finite class\\
\hline
\code{core/schur\_\allowbreak{}dtn.py} & \code{RegionSpec} & 33 & finite class\\
\hline
\code{core/schur\_\allowbreak{}dtn.py} & \code{schur\_\allowbreak{}response} & 45 & finite function\\
\hline
\code{core/schur\_\allowbreak{}dtn.py} & \code{schur\_\allowbreak{}response\_\allowbreak{}from\_\allowbreak{}model} & 73 & finite function\\
\hline
\code{core/schur\_\allowbreak{}dtn.py} & \code{build\_\allowbreak{}sibling\_\allowbreak{}regions} & 115 & finite function\\
\hline
\code{core/schur\_\allowbreak{}dtn.py} & \code{normalized\_\allowbreak{}indicator} & 159 & finite function\\
\hline
\code{core/schur\_\allowbreak{}dtn.py} & \code{boundary\_\allowbreak{}role\_\allowbreak{}basis} & 169 & finite function\\
\hline
\code{core/schur\_\allowbreak{}dtn.py} & \code{compress\_\allowbreak{}response} & 197 & finite function\\
\hline
\code{core/schur\_\allowbreak{}dtn.py} & \code{role\_\allowbreak{}for\_\allowbreak{}boundary\_\allowbreak{}node} & 201 & finite function\\
\hline
\code{core/schur\_\allowbreak{}dtn.py} & \code{atom\_\allowbreak{}key} & 211 & finite function\\
\hline
\code{core/signed\_\allowbreak{}current.py} & \code{orthonormal\_\allowbreak{}pair} & 22 & finite function\\
\hline
\code{core/signed\_\allowbreak{}current.py} & \code{F1\_\allowbreak{}F2\_\allowbreak{}vectors} & 44 & finite function\\
\hline
\code{core/signed\_\allowbreak{}current.py} & \code{orientation\_\allowbreak{}measurement} & 65 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}birth\_\allowbreak{}relative.py} & \code{\_\allowbreak{}to\_\allowbreak{}int} & 12 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}birth\_\allowbreak{}relative.py} & \code{\_\allowbreak{}to\_\allowbreak{}float} & 21 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}birth\_\allowbreak{}relative.py} & \code{\_\allowbreak{}sign} & 30 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}birth\_\allowbreak{}relative.py} & \code{\_\allowbreak{}region\_\allowbreak{}birth\_\allowbreak{}level} & 36 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}birth\_\allowbreak{}relative.py} & \code{birth\_\allowbreak{}relative\_\allowbreak{}backreaction\_\allowbreak{}rows} & 52 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}birth\_\allowbreak{}relative.py} & \code{\_\allowbreak{}linear\_\allowbreak{}zero\_\allowbreak{}crossing\_\allowbreak{}age} & 102 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}birth\_\allowbreak{}relative.py} & \code{birth\_\allowbreak{}relative\_\allowbreak{}zero\_\allowbreak{}crossing\_\allowbreak{}rows} & 118 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}birth\_\allowbreak{}relative.py} & \code{birth\_\allowbreak{}relative\_\allowbreak{}mode\_\allowbreak{}branching\_\allowbreak{}rows} & 179 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}birth\_\allowbreak{}relative.py} & \code{birth\_\allowbreak{}relative\_\allowbreak{}region\_\allowbreak{}family\_\allowbreak{}rows} & 213 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}birth\_\allowbreak{}relative.py} & \code{birth\_\allowbreak{}relative\_\allowbreak{}summary\_\allowbreak{}rows} & 240 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}birth\_\allowbreak{}relative.py} & \code{write\_\allowbreak{}birth\_\allowbreak{}relative\_\allowbreak{}backreaction\_\allowbreak{}current\_\allowbreak{}report} & 285 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}branching\_\allowbreak{}shift.py} & \code{\_\allowbreak{}to\_\allowbreak{}int} & 13 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}branching\_\allowbreak{}shift.py} & \code{\_\allowbreak{}to\_\allowbreak{}float} & 22 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}branching\_\allowbreak{}shift.py} & \code{read\_\allowbreak{}csv\_\allowbreak{}rows} & 31 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}branching\_\allowbreak{}shift.py} & \code{\_\allowbreak{}mode\_\allowbreak{}branching\_\allowbreak{}key} & 36 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}branching\_\allowbreak{}shift.py} & \code{deduplicate\_\allowbreak{}mode\_\allowbreak{}branching\_\allowbreak{}rows} & 40 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}branching\_\allowbreak{}shift.py} & \code{branching\_\allowbreak{}shift\_\allowbreak{}curve\_\allowbreak{}rows} & 63 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}branching\_\allowbreak{}shift.py} & \code{\_\allowbreak{}linear\_\allowbreak{}fit\_\allowbreak{}slope} & 92 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}branching\_\allowbreak{}shift.py} & \code{branching\_\allowbreak{}shift\_\allowbreak{}summary\_\allowbreak{}rows} & 102 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}branching\_\allowbreak{}shift.py} & \code{write\_\allowbreak{}branching\_\allowbreak{}zero\_\allowbreak{}crossing\_\allowbreak{}shift\_\allowbreak{}report} & 147 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{\_\allowbreak{}regions} & 29 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{\_\allowbreak{}directed\_\allowbreak{}parts} & 39 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{\_\allowbreak{}state\_\allowbreak{}pair\_\allowbreak{}snapshot} & 57 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{\_\allowbreak{}omega} & 63 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{\_\allowbreak{}sign} & 69 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{\_\allowbreak{}rel} & 75 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{\_\allowbreak{}row\_\allowbreak{}sum\_\allowbreak{}condition\_\allowbreak{}note} & 79 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{backreaction\_\allowbreak{}current\_\allowbreak{}rows} & 89 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{backreaction\_\allowbreak{}growth\_\allowbreak{}profile\_\allowbreak{}rows} & 226 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{backreaction\_\allowbreak{}region\_\allowbreak{}parameter\_\allowbreak{}sensitivity\_\allowbreak{}rows} & 291 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{\_\allowbreak{}snapshot\_\allowbreak{}for\_\allowbreak{}region} & 337 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{backreaction\_\allowbreak{}transport\_\allowbreak{}rows} & 363 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{backreaction\_\allowbreak{}current\_\allowbreak{}summary\_\allowbreak{}rows} & 443 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/backreaction\_\allowbreak{}current.py} & \code{write\_\allowbreak{}live\_\allowbreak{}record\_\allowbreak{}backreaction\_\allowbreak{}current\_\allowbreak{}report} & 506 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/baseline.py} & \code{level\_\allowbreak{}models} & 21 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/baseline.py} & \code{genesis\_\allowbreak{}rows} & 37 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/baseline.py} & \code{projection\_\allowbreak{}grammar\_\allowbreak{}rows} & 77 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/baseline.py} & \code{carrier\_\allowbreak{}state\_\allowbreak{}rows} & 106 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/baseline.py} & \code{orientation\_\allowbreak{}rows} & 156 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/baseline.py} & \code{region\_\allowbreak{}and\_\allowbreak{}gns\_\allowbreak{}rows} & 174 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/birth\_\allowbreak{}linearization\_\allowbreak{}invariance.py} & \code{\_\allowbreak{}edge\_\allowbreak{}weights\_\allowbreak{}by\_\allowbreak{}address} & 11 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/birth\_\allowbreak{}linearization\_\allowbreak{}invariance.py} & \code{\_\allowbreak{}dict\_\allowbreak{}linf} & 29 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/birth\_\allowbreak{}linearization\_\allowbreak{}invariance.py} & \code{\_\allowbreak{}dict\_\allowbreak{}l1} & 36 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/birth\_\allowbreak{}linearization\_\allowbreak{}invariance.py} & \code{\_\allowbreak{}node\_\allowbreak{}field\_\allowbreak{}by\_\allowbreak{}address} & 41 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/birth\_\allowbreak{}linearization\_\allowbreak{}invariance.py} & \code{\_\allowbreak{}rank\_\allowbreak{}reverse\_\allowbreak{}pair} & 45 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/birth\_\allowbreak{}linearization\_\allowbreak{}invariance.py} & \code{birth\_\allowbreak{}linearization\_\allowbreak{}invariance\_\allowbreak{}rows} & 65 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/compressed\_\allowbreak{}state\_\allowbreak{}projection\_\allowbreak{}consistency.py} & \code{compressed\_\allowbreak{}carrier\_\allowbreak{}state\_\allowbreak{}rows} & 21 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/compressed\_\allowbreak{}state\_\allowbreak{}projection\_\allowbreak{}consistency.py} & \code{state\_\allowbreak{}construction\_\allowbreak{}track\_\allowbreak{}ledger\_\allowbreak{}rows} & 159 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/computed\_\allowbreak{}status\_\allowbreak{}rows.py} & \code{operator\_\allowbreak{}stack\_\allowbreak{}residuals\_\allowbreak{}classification\_\allowbreak{}rows} & 26 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/computed\_\allowbreak{}status\_\allowbreak{}rows.py} & \code{final\_\allowbreak{}computed\_\allowbreak{}status\_\allowbreak{}rows\_\allowbreak{}full} & 96 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/computed\_\allowbreak{}status\_\allowbreak{}rows.py} & \code{write\_\allowbreak{}markdown\_\allowbreak{}full} & 152 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{\_\allowbreak{}first\_\allowbreak{}transport\_\allowbreak{}region} & 15 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{\_\allowbreak{}transport\_\allowbreak{}region\_\allowbreak{}meta} & 31 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{\_\allowbreak{}open\_\allowbreak{}out\_\allowbreak{}directed\_\allowbreak{}snapshot} & 40 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{\_\allowbreak{}address\_\allowbreak{}at\_\allowbreak{}target} & 61 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{\_\allowbreak{}boundary\_\allowbreak{}prefix\_\allowbreak{}transport\_\allowbreak{}matrix} & 68 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{\_\allowbreak{}safe\_\allowbreak{}rel\_\allowbreak{}err} & 115 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{\_\allowbreak{}scale\_\allowbreak{}fit\_\allowbreak{}error} & 119 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{\_\allowbreak{}skew\_\allowbreak{}orientation\_\allowbreak{}sign} & 128 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}metrics} & 135 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{\_\allowbreak{}snapshot\_\allowbreak{}cache} & 157 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{\_\allowbreak{}pair\_\allowbreak{}records} & 176 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{directed\_\allowbreak{}current\_\allowbreak{}transport\_\allowbreak{}rows} & 191 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{directed\_\allowbreak{}current\_\allowbreak{}composition\_\allowbreak{}rows} & 276 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{directed\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}summary\_\allowbreak{}rows} & 344 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{write\_\allowbreak{}directed\_\allowbreak{}current\_\allowbreak{}transport\_\allowbreak{}report} & 398 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{directed\_\allowbreak{}large\_\allowbreak{}L\_\allowbreak{}region\_\allowbreak{}coverage\_\allowbreak{}rows} & 460 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{\_\allowbreak{}safe\_\allowbreak{}region\_\allowbreak{}matrix\_\allowbreak{}metrics} & 549 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{\_\allowbreak{}safe\_\allowbreak{}region\_\allowbreak{}plane\_\allowbreak{}metrics} & 566 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{directed\_\allowbreak{}large\_\allowbreak{}L\_\allowbreak{}coverage\_\allowbreak{}summary\_\allowbreak{}rows} & 583 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}current\_\allowbreak{}transport.py} & \code{write\_\allowbreak{}directed\_\allowbreak{}region\_\allowbreak{}coverage\_\allowbreak{}report} & 639 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{\_\allowbreak{}first\_\allowbreak{}directed\_\allowbreak{}region} & 15 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{\_\allowbreak{}region\_\allowbreak{}meta} & 31 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{\_\allowbreak{}response\_\allowbreak{}for\_\allowbreak{}relations} & 42 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{\_\allowbreak{}matrix\_\allowbreak{}metrics} & 61 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{\_\allowbreak{}plane\_\allowbreak{}metrics} & 97 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{\_\allowbreak{}reference\_\allowbreak{}open\_\allowbreak{}out\_\allowbreak{}snapshot} & 124 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{directed\_\allowbreak{}response\_\allowbreak{}construction\_\allowbreak{}rows} & 133 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{directed\_\allowbreak{}sa\_\allowbreak{}decomposition\_\allowbreak{}rows} & 171 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{directed\_\allowbreak{}signed\_\allowbreak{}role\_\allowbreak{}survival\_\allowbreak{}rows} & 198 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{directed\_\allowbreak{}boundary\_\allowbreak{}response\_\allowbreak{}model\_\allowbreak{}comparison\_\allowbreak{}rows} & 232 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{directed\_\allowbreak{}skew\_\allowbreak{}survival\_\allowbreak{}rows} & 271 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{directed\_\allowbreak{}operator\_\allowbreak{}transport\_\allowbreak{}rows} & 304 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{directed\_\allowbreak{}j\_\allowbreak{}finite\_\allowbreak{}object\_\allowbreak{}comparison\_\allowbreak{}rows} & 365 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{directed\_\allowbreak{}operator\_\allowbreak{}stack\_\allowbreak{}summary\_\allowbreak{}rows} & 394 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/directed\_\allowbreak{}operator\_\allowbreak{}stack.py} & \code{write\_\allowbreak{}directed\_\allowbreak{}operator\_\allowbreak{}stack\_\allowbreak{}report} & 452 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/finite\_\allowbreak{}structure\_\allowbreak{}theorem\_\allowbreak{}controls.py} & \code{\_\allowbreak{}growth\_\allowbreak{}signature} & 21 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/finite\_\allowbreak{}structure\_\allowbreak{}theorem\_\allowbreak{}controls.py} & \code{\_\allowbreak{}expected\_\allowbreak{}addresses} & 66 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/finite\_\allowbreak{}structure\_\allowbreak{}theorem\_\allowbreak{}controls.py} & \code{growth\_\allowbreak{}well\_\allowbreak{}defined\_\allowbreak{}control} & 73 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/finite\_\allowbreak{}structure\_\allowbreak{}theorem\_\allowbreak{}controls.py} & \code{symmetric\_\allowbreak{}schur\_\allowbreak{}positivity\_\allowbreak{}control} & 133 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/finite\_\allowbreak{}structure\_\allowbreak{}theorem\_\allowbreak{}controls.py} & \code{gns\_\allowbreak{}quotient\_\allowbreak{}control} & 178 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/finite\_\allowbreak{}structure\_\allowbreak{}theorem\_\allowbreak{}controls.py} & \code{orientation\_\allowbreak{}flip\_\allowbreak{}control} & 194 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/finite\_\allowbreak{}structure\_\allowbreak{}theorem\_\allowbreak{}controls.py} & \code{backreaction\_\allowbreak{}separation\_\allowbreak{}control} & 234 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/finite\_\allowbreak{}structure\_\allowbreak{}theorem\_\allowbreak{}controls.py} & \code{prefix\_\allowbreak{}handoff\_\allowbreak{}control} & 255 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/finite\_\allowbreak{}structure\_\allowbreak{}theorem\_\allowbreak{}controls.py} & \code{finite\_\allowbreak{}structure\_\allowbreak{}theorem\_\allowbreak{}control\_\allowbreak{}rows} & 332 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/gns\_\allowbreak{}cyclicity\_\allowbreak{}controls.py} & \code{\_\allowbreak{}control\_\allowbreak{}algebras} & 11 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/gns\_\allowbreak{}cyclicity\_\allowbreak{}controls.py} & \code{finite\_\allowbreak{}gns\_\allowbreak{}cyclicity\_\allowbreak{}control\_\allowbreak{}rows} & 22 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{\_\allowbreak{}memo\_\allowbreak{}key} & 20 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{\_\allowbreak{}regions} & 24 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{\_\allowbreak{}regions\_\allowbreak{}by\_\allowbreak{}id} & 34 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{\_\allowbreak{}region\_\allowbreak{}meta} & 38 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{\_\allowbreak{}safe\_\allowbreak{}eigs} & 51 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{\_\allowbreak{}response\_\allowbreak{}parts} & 64 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{\_\allowbreak{}metric\_\allowbreak{}choice} & 79 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{\_\allowbreak{}orientation\_\allowbreak{}sign} & 89 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{\_\allowbreak{}snapshot\_\allowbreak{}for\_\allowbreak{}region} & 98 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{\_\allowbreak{}snapshot\_\allowbreak{}cache} & 143 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{j\_\allowbreak{}orientation\_\allowbreak{}snapshot\_\allowbreak{}rows} & 159 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{j\_\allowbreak{}orientation\_\allowbreak{}transport\_\allowbreak{}rows} & 207 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{j\_\allowbreak{}orientation\_\allowbreak{}composition\_\allowbreak{}rows} & 288 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{j\_\allowbreak{}orientation\_\allowbreak{}sign\_\allowbreak{}scope\_\allowbreak{}rows} & 363 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{j\_\allowbreak{}orientation\_\allowbreak{}projectivity\_\allowbreak{}summary\_\allowbreak{}rows} & 388 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{write\_\allowbreak{}b\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}projectivity\_\allowbreak{}report} & 442 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{\_\allowbreak{}snapshot\_\allowbreak{}A\_\allowbreak{}for\_\allowbreak{}state} & 530 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{\_\allowbreak{}snapshot\_\allowbreak{}A\_\allowbreak{}cache} & 570 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{a\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}snapshot\_\allowbreak{}rows} & 585 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{a\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}transport\_\allowbreak{}rows} & 631 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{a\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}composition\_\allowbreak{}rows} & 697 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{a\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}projectivity\_\allowbreak{}summary\_\allowbreak{}rows} & 734 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{write\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}a\_\allowbreak{}orientation\_\allowbreak{}projectivity\_\allowbreak{}report} & 763 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation.py} & \code{\_\allowbreak{}frontier\_\allowbreak{}nodes} & 32 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation.py} & \code{\_\allowbreak{}choose\_\allowbreak{}global\_\allowbreak{}frontier\_\allowbreak{}level} & 36 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation.py} & \code{\_\allowbreak{}global\_\allowbreak{}boundary\_\allowbreak{}sets} & 51 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation.py} & \code{\_\allowbreak{}global\_\allowbreak{}signed\_\allowbreak{}basis} & 72 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation.py} & \code{\_\allowbreak{}safe\_\allowbreak{}response} & 119 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation.py} & \code{global\_\allowbreak{}j\_\allowbreak{}boundary\_\allowbreak{}sign\_\allowbreak{}relation\_\allowbreak{}rows} & 139 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation.py} & \code{local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}comparison\_\allowbreak{}rows} & 242 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation.py} & \code{local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}summary\_\allowbreak{}rows} & 296 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation.py} & \code{write\_\allowbreak{}local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation\_\allowbreak{}report} & 343 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{RegionMeasurementSnapshot} & 25 & finite class\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{\_\allowbreak{}state\_\allowbreak{}edges} & 47 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{\_\allowbreak{}selected\_\allowbreak{}schur\_\allowbreak{}response} & 51 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{\_\allowbreak{}first\_\allowbreak{}snapshot} & 94 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{\_\allowbreak{}snapshots} & 130 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{\_\allowbreak{}span\_\allowbreak{}rank} & 140 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{operator\_\allowbreak{}stack\_\allowbreak{}role\_\allowbreak{}dimension\_\allowbreak{}condition\_\allowbreak{}note\_\allowbreak{}rows} & 156 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{operator\_\allowbreak{}stack\_\allowbreak{}generator\_\allowbreak{}rank\_\allowbreak{}condition\_\allowbreak{}note\_\allowbreak{}rows} & 200 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{operator\_\allowbreak{}stack\_\allowbreak{}coordinate\_\allowbreak{}gauge\_\allowbreak{}condition\_\allowbreak{}note\_\allowbreak{}rows} & 239 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{operator\_\allowbreak{}stack\_\allowbreak{}boundary\_\allowbreak{}response\_\allowbreak{}model\_\allowbreak{}condition\_\allowbreak{}note\_\allowbreak{}rows} & 313 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{\_\allowbreak{}orientation\_\allowbreak{}lookup} & 354 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{operator\_\allowbreak{}stack\_\allowbreak{}skew\_\allowbreak{}survival\_\allowbreak{}condition\_\allowbreak{}note\_\allowbreak{}rows} & 364 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks\_\allowbreak{}summary\_\allowbreak{}rows} & 405 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}consistency\_\allowbreak{}checks.py} & \code{write\_\allowbreak{}operator\_\allowbreak{}stack\_\allowbreak{}condition\_\allowbreak{}consistency\_\allowbreak{}report} & 452 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} & \code{\_\allowbreak{}finite} & 11 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} & \code{\_\allowbreak{}key\_\allowbreak{}pair} & 19 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} & \code{\_\allowbreak{}index} & 29 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} & \code{\_\allowbreak{}composition\_\allowbreak{}index} & 38 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} & \code{\_\allowbreak{}metric} & 57 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} & \code{\_\allowbreak{}dominant\_\allowbreak{}seam} & 63 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} & \code{\_\allowbreak{}seam\_\allowbreak{}computed\_\allowbreak{}status} & 80 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} & \code{operator\_\allowbreak{}stack\_\allowbreak{}seam\_\allowbreak{}localization\_\allowbreak{}rows} & 93 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} & \code{operator\_\allowbreak{}stack\_\allowbreak{}live\_\allowbreak{}record\_\allowbreak{}sym\_\allowbreak{}comparison\_\allowbreak{}rows} & 178 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} & \code{operator\_\allowbreak{}stack\_\allowbreak{}level\_\allowbreak{}scaling\_\allowbreak{}rows} & 225 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} & \code{operator\_\allowbreak{}stack\_\allowbreak{}map\_\allowbreak{}naturality\_\allowbreak{}measurement\_\allowbreak{}rows} & 277 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}interface\_\allowbreak{}residuals.py} & \code{write\_\allowbreak{}operator\_\allowbreak{}stack\_\allowbreak{}residual\_\allowbreak{}report} & 317 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{\_\allowbreak{}ambient\_\allowbreak{}J\_\allowbreak{}from\_\allowbreak{}SA} & 34 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{NestedSnapshot} & 72 & finite class\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{\_\allowbreak{}first\_\allowbreak{}terminal\_\allowbreak{}region} & 88 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{build\_\allowbreak{}nested\_\allowbreak{}snapshot} & 93 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{\_\allowbreak{}relative\_\allowbreak{}error} & 131 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{\_\allowbreak{}deterministic\_\allowbreak{}test\_\allowbreak{}matrices} & 135 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{\_\allowbreak{}state\_\allowbreak{}inner\_\allowbreak{}product} & 146 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{\_\allowbreak{}address\_\allowbreak{}sequence} & 150 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{\_\allowbreak{}permutation\_\allowbreak{}from\_\allowbreak{}addresses} & 154 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{nested\_\allowbreak{}carrier\_\allowbreak{}rows} & 171 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{nested\_\allowbreak{}handoff\_\allowbreak{}rows} & 236 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{common\_\allowbreak{}ambient\_\allowbreak{}schur\_\allowbreak{}rows} & 398 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{nested\_\allowbreak{}multiscale\_\allowbreak{}summary\_\allowbreak{}rows} & 496 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/nested\_\allowbreak{}multiscale\_\allowbreak{}handoff.py} & \code{nested\_\allowbreak{}multiscale\_\allowbreak{}all\_\allowbreak{}rows} & 593 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{FullRegionData} & 23 & finite class\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{build\_\allowbreak{}first\_\allowbreak{}region\_\allowbreak{}data} & 37 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{common\_\allowbreak{}labels} & 54 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{\_\allowbreak{}basis\_\allowbreak{}matrix} & 58 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{project\_\allowbreak{}to\_\allowbreak{}label\_\allowbreak{}span} & 64 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{reconstruct\_\allowbreak{}from\_\allowbreak{}labels} & 72 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{pi\_\allowbreak{}role\_\allowbreak{}project} & 83 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{role\_\allowbreak{}projection\_\allowbreak{}residual} & 88 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{matrix\_\allowbreak{}log\_\allowbreak{}spd} & 96 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{commutator\_\allowbreak{}delta} & 102 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{center\_\allowbreak{}expectation} & 106 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{generator\_\allowbreak{}list} & 115 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{generator\_\allowbreak{}gram} & 119 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/operator\_\allowbreak{}stack\_\allowbreak{}residuals.py} & \code{interlevel\_\allowbreak{}operator\_\allowbreak{}rows} & 125 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/rank\_\allowbreak{}kernel\_\allowbreak{}conditions.py} & \code{local\_\allowbreak{}s\_\allowbreak{}response\_\allowbreak{}density} & 22 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/rank\_\allowbreak{}kernel\_\allowbreak{}conditions.py} & \code{measure\_\allowbreak{}rank\_\allowbreak{}kernel\_\allowbreak{}condition\_\allowbreak{}rows} & 47 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/rank\_\allowbreak{}kernel\_\allowbreak{}conditions.py} & \code{construction\_\allowbreak{}coverage\_\allowbreak{}rows} & 122 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/rank\_\allowbreak{}kernel\_\allowbreak{}conditions.py} & \code{fixed\_\allowbreak{}rule\_\allowbreak{}constants\_\allowbreak{}measurement\_\allowbreak{}rows} & 143 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/rank\_\allowbreak{}kernel\_\allowbreak{}conditions.py} & \code{regional\_\allowbreak{}rank\_\allowbreak{}kernel\_\allowbreak{}condition\_\allowbreak{}rows} & 162 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/rank\_\allowbreak{}kernel\_\allowbreak{}conditions.py} & \code{terminal\_\allowbreak{}density\_\allowbreak{}state\_\allowbreak{}measurement\_\allowbreak{}rows} & 178 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/structural\_\allowbreak{}ledgers.py} & \code{is\_\allowbreak{}reference\_\allowbreak{}model} & 21 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/structural\_\allowbreak{}ledgers.py} & \code{parameter\_\allowbreak{}purity\_\allowbreak{}rows} & 25 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/structural\_\allowbreak{}ledgers.py} & \code{live\_\allowbreak{}record\_\allowbreak{}structural\_\allowbreak{}calculation\_\allowbreak{}ledger\_\allowbreak{}rows} & 50 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/structural\_\allowbreak{}ledgers.py} & \code{live\_\allowbreak{}record\_\allowbreak{}history\_\allowbreak{}delta\_\allowbreak{}ledger\_\allowbreak{}rows} & 114 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/structural\_\allowbreak{}ledgers.py} & \code{carrier\_\allowbreak{}effect\_\allowbreak{}operator\_\allowbreak{}rows} & 183 & finite function\\
\hline
\code{derived\_\allowbreak{}quantities/structural\_\allowbreak{}ledgers.py} & \code{state\_\allowbreak{}sector\_\allowbreak{}decomposition\_\allowbreak{}rows} & 235 & finite function\\
\hline
\code{io/csv\_\allowbreak{}writer.py} & \code{write\_\allowbreak{}csv} & 17 & finite function\\
\hline
\code{io/csv\_\allowbreak{}writer.py} & \code{sha256\_\allowbreak{}json} & 36 & finite function\\
\hline
\code{object\_\allowbreak{}checks/backreaction\_\allowbreak{}current\_\allowbreak{}localization.py} & \code{\_\allowbreak{}projectors} & 24 & finite function\\
\hline
\code{object\_\allowbreak{}checks/backreaction\_\allowbreak{}current\_\allowbreak{}localization.py} & \code{\_\allowbreak{}row\_\allowbreak{}computed\_\allowbreak{}status} & 34 & finite function\\
\hline
\code{object\_\allowbreak{}checks/backreaction\_\allowbreak{}current\_\allowbreak{}localization.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 44 & finite function\\
\hline
\code{object\_\allowbreak{}checks/backreaction\_\allowbreak{}current\_\allowbreak{}localization.py} & \code{\_\allowbreak{}summarize\_\allowbreak{}track} & 48 & finite function\\
\hline
\code{object\_\allowbreak{}checks/backreaction\_\allowbreak{}current\_\allowbreak{}localization.py} & \code{backreaction\_\allowbreak{}current\_\allowbreak{}localization\_\allowbreak{}rows} & 101 & finite function\\
\hline
\code{object\_\allowbreak{}checks/backreaction\_\allowbreak{}current\_\allowbreak{}localization.py} & \code{backreaction\_\allowbreak{}current\_\allowbreak{}localization\_\allowbreak{}report} & 170 & finite function\\
\hline
\code{object\_\allowbreak{}checks/bianconi\_\allowbreak{}simplicial\_\allowbreak{}statistics\_\allowbreak{}bridge.py} & \code{bianconi\_\allowbreak{}statistics\_\allowbreak{}bridge\_\allowbreak{}condition\_\allowbreak{}rows} & 57 & finite function\\
\hline
\code{object\_\allowbreak{}checks/bianconi\_\allowbreak{}simplicial\_\allowbreak{}statistics\_\allowbreak{}bridge.py} & \code{bianconi\_\allowbreak{}branching\_\allowbreak{}sector\_\allowbreak{}expectation\_\allowbreak{}rows} & 61 & finite function\\
\hline
\code{object\_\allowbreak{}checks/bianconi\_\allowbreak{}simplicial\_\allowbreak{}statistics\_\allowbreak{}bridge.py} & \code{bianconi\_\allowbreak{}statistics\_\allowbreak{}bridge\_\allowbreak{}report} & 91 & finite function\\
\hline
\code{object\_\allowbreak{}checks/collared\_\allowbreak{}split\_\allowbreak{}refined\_\allowbreak{}basis.py} & \code{\_\allowbreak{}median} & 25 & finite function\\
\hline
\code{object\_\allowbreak{}checks/collared\_\allowbreak{}split\_\allowbreak{}refined\_\allowbreak{}basis.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 30 & finite function\\
\hline
\code{object\_\allowbreak{}checks/collared\_\allowbreak{}split\_\allowbreak{}refined\_\allowbreak{}basis.py} & \code{\_\allowbreak{}summarize} & 34 & finite function\\
\hline
\code{object\_\allowbreak{}checks/collared\_\allowbreak{}split\_\allowbreak{}refined\_\allowbreak{}basis.py} & \code{collared\_\allowbreak{}split\_\allowbreak{}refined\_\allowbreak{}basis\_\allowbreak{}rows} & 62 & finite function\\
\hline
\code{object\_\allowbreak{}checks/collared\_\allowbreak{}split\_\allowbreak{}refined\_\allowbreak{}basis.py} & \code{collared\_\allowbreak{}split\_\allowbreak{}refined\_\allowbreak{}basis\_\allowbreak{}report} & 121 & finite function\\
\hline
\code{object\_\allowbreak{}checks/commutant\_\allowbreak{}duality.py} & \code{\_\allowbreak{}computed\_\allowbreak{}status} & 29 & finite function\\
\hline
\code{object\_\allowbreak{}checks/commutant\_\allowbreak{}duality.py} & \code{commutant\_\allowbreak{}duality\_\allowbreak{}rows} & 39 & finite function\\
\hline
\code{object\_\allowbreak{}checks/commutant\_\allowbreak{}duality.py} & \code{commutant\_\allowbreak{}report} & 82 & finite function\\
\hline
\code{object\_\allowbreak{}checks/commutator\_\allowbreak{}decay\_\allowbreak{}by\_\allowbreak{}genealogical\_\allowbreak{}distance.py} & \code{\_\allowbreak{}finite} & 31 & finite function\\
\hline
\code{object\_\allowbreak{}checks/commutator\_\allowbreak{}decay\_\allowbreak{}by\_\allowbreak{}genealogical\_\allowbreak{}distance.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 39 & finite function\\
\hline
\code{object\_\allowbreak{}checks/commutator\_\allowbreak{}decay\_\allowbreak{}by\_\allowbreak{}genealogical\_\allowbreak{}distance.py} & \code{\_\allowbreak{}summarize\_\allowbreak{}track} & 49 & finite function\\
\hline
\code{object\_\allowbreak{}checks/commutator\_\allowbreak{}decay\_\allowbreak{}by\_\allowbreak{}genealogical\_\allowbreak{}distance.py} & \code{commutator\_\allowbreak{}decay\_\allowbreak{}by\_\allowbreak{}genealogical\_\allowbreak{}distance\_\allowbreak{}rows} & 112 & finite function\\
\hline
\code{object\_\allowbreak{}checks/commutator\_\allowbreak{}decay\_\allowbreak{}by\_\allowbreak{}genealogical\_\allowbreak{}distance.py} & \code{commutator\_\allowbreak{}decay\_\allowbreak{}by\_\allowbreak{}genealogical\_\allowbreak{}distance\_\allowbreak{}report} & 179 & finite function\\
\hline
\code{object\_\allowbreak{}checks/core\_\allowbreak{}construction\_\allowbreak{}dependencies.py} & \code{core\_\allowbreak{}theory\_\allowbreak{}construction\_\allowbreak{}rows} & 146 & finite function\\
\hline
\code{object\_\allowbreak{}checks/core\_\allowbreak{}construction\_\allowbreak{}dependencies.py} & \code{presentation\_\allowbreak{}mainline\_\allowbreak{}rows} & 150 & finite function\\
\hline
\code{object\_\allowbreak{}checks/core\_\allowbreak{}construction\_\allowbreak{}dependencies.py} & \code{core\_\allowbreak{}theory\_\allowbreak{}construction\_\allowbreak{}report} & 154 & finite function\\
\hline
\code{object\_\allowbreak{}checks/core\_\allowbreak{}construction\_\allowbreak{}dependencies.py} & \code{presentation\_\allowbreak{}mainline\_\allowbreak{}report} & 196 & finite function\\
\hline
\code{object\_\allowbreak{}checks/cyclicity\_\allowbreak{}dimension\_\allowbreak{}rank\_\allowbreak{}bound.py} & \code{cyclicity\_\allowbreak{}dimension\_\allowbreak{}rank\_\allowbreak{}bound\_\allowbreak{}rows} & 31 & finite function\\
\hline
\code{object\_\allowbreak{}checks/cyclicity\_\allowbreak{}dimension\_\allowbreak{}rank\_\allowbreak{}bound.py} & \code{cyclicity\_\allowbreak{}dimension\_\allowbreak{}rank\_\allowbreak{}bound\_\allowbreak{}report} & 77 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}entropy\_\allowbreak{}flow.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}entropy\_\allowbreak{}flow.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}entropy\_\allowbreak{}flow.py} & \code{\_\allowbreak{}pearson} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}entropy\_\allowbreak{}flow.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 33 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}entropy\_\allowbreak{}flow.py} & \code{\_\allowbreak{}same\_\allowbreak{}direction} & 37 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}entropy\_\allowbreak{}flow.py} & \code{decomposed\_\allowbreak{}entropy\_\allowbreak{}flow\_\allowbreak{}rows} & 41 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}entropy\_\allowbreak{}flow.py} & \code{decomposed\_\allowbreak{}entropy\_\allowbreak{}flow\_\allowbreak{}report} & 123 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities.py} & \code{\_\allowbreak{}key} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities.py} & \code{\_\allowbreak{}component\_\allowbreak{}index} & 25 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities.py} & \code{\_\allowbreak{}ratio} & 29 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities.py} & \code{\_\allowbreak{}within} & 33 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities.py} & \code{\_\allowbreak{}dominant\_\allowbreak{}explanation} & 37 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities.py} & \code{\_\allowbreak{}surface\_\allowbreak{}track\_\allowbreak{}key} & 59 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities.py} & \code{\_\allowbreak{}summarize\_\allowbreak{}track} & 63 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities.py} & \code{\_\allowbreak{}base\_\allowbreak{}row} & 109 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities.py} & \code{decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities\_\allowbreak{}rows} & 171 & finite function\\
\hline
\code{object\_\allowbreak{}checks/decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities.py} & \code{decomposed\_\allowbreak{}geometry\_\allowbreak{}quantities\_\allowbreak{}report} & 211 & finite function\\
\hline
\code{object\_\allowbreak{}checks/deformed\_\allowbreak{}fractal\_\allowbreak{}bridge.py} & \code{deformed\_\allowbreak{}fractal\_\allowbreak{}bridge\_\allowbreak{}rows} & 6 & finite function\\
\hline
\code{object\_\allowbreak{}checks/deformed\_\allowbreak{}fractal\_\allowbreak{}bridge.py} & \code{deformed\_\allowbreak{}fractal\_\allowbreak{}bridge\_\allowbreak{}report} & 62 & finite function\\
\hline
\code{object\_\allowbreak{}checks/destroyed\_\allowbreak{}history\_\allowbreak{}oriented\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/destroyed\_\allowbreak{}history\_\allowbreak{}oriented\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/destroyed\_\allowbreak{}history\_\allowbreak{}oriented\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}key} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/destroyed\_\allowbreak{}history\_\allowbreak{}oriented\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}idx} & 25 & finite function\\
\hline
\code{object\_\allowbreak{}checks/destroyed\_\allowbreak{}history\_\allowbreak{}oriented\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}ratio} & 29 & finite function\\
\hline
\code{object\_\allowbreak{}checks/destroyed\_\allowbreak{}history\_\allowbreak{}oriented\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}control\_\allowbreak{}measures} & 33 & finite function\\
\hline
\code{object\_\allowbreak{}checks/destroyed\_\allowbreak{}history\_\allowbreak{}oriented\_\allowbreak{}geometry.py} & \code{destroyed\_\allowbreak{}history\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}rows} & 49 & finite function\\
\hline
\code{object\_\allowbreak{}checks/destroyed\_\allowbreak{}history\_\allowbreak{}oriented\_\allowbreak{}geometry.py} & \code{destroyed\_\allowbreak{}history\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}report} & 138 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}gradient\_\allowbreak{}current.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}gradient\_\allowbreak{}current.py} & \code{\_\allowbreak{}pearson} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}gradient\_\allowbreak{}current.py} & \code{\_\allowbreak{}median} & 28 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}gradient\_\allowbreak{}current.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 33 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}gradient\_\allowbreak{}current.py} & \code{entropy\_\allowbreak{}gradient\_\allowbreak{}current\_\allowbreak{}rows} & 37 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}gradient\_\allowbreak{}current.py} & \code{entropy\_\allowbreak{}gradient\_\allowbreak{}current\_\allowbreak{}report} & 110 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}measure\_\allowbreak{}parameter\_\allowbreak{}sensitivity.py} & \code{\_\allowbreak{}finite} & 26 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}measure\_\allowbreak{}parameter\_\allowbreak{}sensitivity.py} & \code{\_\allowbreak{}median} & 34 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}measure\_\allowbreak{}parameter\_\allowbreak{}sensitivity.py} & \code{\_\allowbreak{}js} & 39 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}measure\_\allowbreak{}parameter\_\allowbreak{}sensitivity.py} & \code{\_\allowbreak{}swap\_\allowbreak{}left\_\allowbreak{}right\_\allowbreak{}permutation} & 44 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}measure\_\allowbreak{}parameter\_\allowbreak{}sensitivity.py} & \code{\_\allowbreak{}density\_\allowbreak{}key} & 60 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}measure\_\allowbreak{}parameter\_\allowbreak{}sensitivity.py} & \code{\_\allowbreak{}region\_\allowbreak{}shape\_\allowbreak{}key} & 69 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}measure\_\allowbreak{}parameter\_\allowbreak{}sensitivity.py} & \code{\_\allowbreak{}base\_\allowbreak{}key\_\allowbreak{}without\_\allowbreak{}L} & 85 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}measure\_\allowbreak{}parameter\_\allowbreak{}sensitivity.py} & \code{\_\allowbreak{}base\_\allowbreak{}key\_\allowbreak{}without\_\allowbreak{}mode} & 89 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}measure\_\allowbreak{}parameter\_\allowbreak{}sensitivity.py} & \code{entropy\_\allowbreak{}measure\_\allowbreak{}parameter\_\allowbreak{}sensitivity\_\allowbreak{}rows} & 93 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}measure\_\allowbreak{}parameter\_\allowbreak{}sensitivity.py} & \code{entropy\_\allowbreak{}measure\_\allowbreak{}parameter\_\allowbreak{}sensitivity\_\allowbreak{}report} & 209 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}normalized\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}normalized\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}hist\_\allowbreak{}index} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}normalized\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}base\_\allowbreak{}key} & 26 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}normalized\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}normed} & 30 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}normalized\_\allowbreak{}geometry.py} & \code{entropy\_\allowbreak{}normalized\_\allowbreak{}geometry\_\allowbreak{}rows} & 34 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}normalized\_\allowbreak{}geometry.py} & \code{entropy\_\allowbreak{}normalized\_\allowbreak{}geometry\_\allowbreak{}report} & 151 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}complement.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}complement.py} & \code{\_\allowbreak{}hist\_\allowbreak{}index} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}complement.py} & \code{entropy\_\allowbreak{}ordered\_\allowbreak{}complement\_\allowbreak{}rows} & 24 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}complement.py} & \code{entropy\_\allowbreak{}ordered\_\allowbreak{}complement\_\allowbreak{}report} & 88 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}locality.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}locality.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}locality.py} & \code{\_\allowbreak{}hist\_\allowbreak{}index} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}locality.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 31 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}locality.py} & \code{\_\allowbreak{}summarize\_\allowbreak{}track} & 35 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}locality.py} & \code{entropy\_\allowbreak{}ordered\_\allowbreak{}locality\_\allowbreak{}rows} & 77 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}locality.py} & \code{entropy\_\allowbreak{}ordered\_\allowbreak{}locality\_\allowbreak{}report} & 137 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}split.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}split.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}split.py} & \code{\_\allowbreak{}hist\_\allowbreak{}index} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}split.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 29 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}split.py} & \code{\_\allowbreak{}summarize\_\allowbreak{}track} & 33 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}split.py} & \code{entropy\_\allowbreak{}ordered\_\allowbreak{}split\_\allowbreak{}rows} & 67 & finite function\\
\hline
\code{object\_\allowbreak{}checks/entropy\_\allowbreak{}ordered\_\allowbreak{}split.py} & \code{entropy\_\allowbreak{}ordered\_\allowbreak{}split\_\allowbreak{}report} & 115 & finite function\\
\hline
\code{object\_\allowbreak{}checks/extended\_\allowbreak{}entropy\_\allowbreak{}level\_\allowbreak{}trajectory.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/extended\_\allowbreak{}entropy\_\allowbreak{}level\_\allowbreak{}trajectory.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/extended\_\allowbreak{}entropy\_\allowbreak{}level\_\allowbreak{}trajectory.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/extended\_\allowbreak{}entropy\_\allowbreak{}level\_\allowbreak{}trajectory.py} & \code{\_\allowbreak{}trend} & 25 & finite function\\
\hline
\code{object\_\allowbreak{}checks/extended\_\allowbreak{}entropy\_\allowbreak{}level\_\allowbreak{}trajectory.py} & \code{extended\_\allowbreak{}entropy\_\allowbreak{}level\_\allowbreak{}trajectory\_\allowbreak{}rows} & 41 & finite function\\
\hline
\code{object\_\allowbreak{}checks/extended\_\allowbreak{}entropy\_\allowbreak{}level\_\allowbreak{}trajectory.py} & \code{extended\_\allowbreak{}entropy\_\allowbreak{}level\_\allowbreak{}trajectory\_\allowbreak{}report} & 105 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}unique} & 28 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}path\_\allowbreak{}from\_\allowbreak{}lca\_\allowbreak{}to\_\allowbreak{}node} & 32 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}chunks\_\allowbreak{}by\_\allowbreak{}birth\_\allowbreak{}time} & 45 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}indicator} & 59 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}gram\_\allowbreak{}schmidt} & 70 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}paired\_\allowbreak{}shells} & 88 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}multishell\_\allowbreak{}f1f2\_\allowbreak{}basis} & 113 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}profile} & 150 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}response} & 158 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}js} & 202 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}profile\_\allowbreak{}gap} & 207 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}oriented\_\allowbreak{}distance} & 214 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}transform\_\allowbreak{}matrix} & 220 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}apply\_\allowbreak{}transform} & 248 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}uniform\_\allowbreak{}density} & 255 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}cosine} & 259 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}meta\_\allowbreak{}key\_\allowbreak{}without\_\allowbreak{}L} & 268 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}meta\_\allowbreak{}key\_\allowbreak{}without\_\allowbreak{}mode} & 272 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution\_\allowbreak{}rows} & 276 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution.py} & \code{f1\_\allowbreak{}f2\_\allowbreak{}orientation\_\allowbreak{}resolution\_\allowbreak{}report} & 419 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}finite} & 27 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}js} & 35 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}coupling} & 40 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}sign} & 46 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}orientation\_\allowbreak{}gap} & 52 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}oriented\_\allowbreak{}distance} & 59 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}f1f2\_\allowbreak{}plane\_\allowbreak{}response} & 70 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}plane\_\allowbreak{}transform} & 111 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}apply\_\allowbreak{}transform} & 125 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}uniform\_\allowbreak{}plane\_\allowbreak{}density} & 134 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}meta\_\allowbreak{}key\_\allowbreak{}without\_\allowbreak{}L} & 140 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}meta\_\allowbreak{}key\_\allowbreak{}without\_\allowbreak{}mode} & 148 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure\_\allowbreak{}rows} & 156 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{f1\_\allowbreak{}f2\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure\_\allowbreak{}report} & 328 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{\_\allowbreak{}key} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{\_\allowbreak{}surface\_\allowbreak{}key} & 31 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{\_\allowbreak{}f1f2\_\allowbreak{}index} & 42 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{\_\allowbreak{}measure\_\allowbreak{}index} & 46 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{\_\allowbreak{}bool01} & 50 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{\_\allowbreak{}ratio} & 57 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{\_\allowbreak{}naive\_\allowbreak{}tensor\_\allowbreak{}status} & 61 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{\_\allowbreak{}replacement\_\allowbreak{}rule} & 85 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement\_\allowbreak{}rows} & 125 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{\_\allowbreak{}summary\_\allowbreak{}computed\_\allowbreak{}status} & 193 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement\_\allowbreak{}summary\_\allowbreak{}rows} & 210 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{\_\allowbreak{}summary\_\allowbreak{}row} & 227 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement.py} & \code{f1f2\_\allowbreak{}oriented\_\allowbreak{}geometry\_\allowbreak{}replacement\_\allowbreak{}report} & 253 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison.py} & \code{\_\allowbreak{}finite} & 24 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison.py} & \code{\_\allowbreak{}median} & 32 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison.py} & \code{\_\allowbreak{}signature} & 37 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison.py} & \code{\_\allowbreak{}signature\_\allowbreak{}gap} & 45 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison.py} & \code{\_\allowbreak{}cosine} & 51 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison.py} & \code{\_\allowbreak{}strength\_\allowbreak{}range} & 60 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison.py} & \code{\_\allowbreak{}track\_\allowbreak{}key\_\allowbreak{}from\_\allowbreak{}meta} & 70 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison.py} & \code{\_\allowbreak{}pairwise\_\allowbreak{}state\_\allowbreak{}stats} & 74 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison.py} & \code{f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison\_\allowbreak{}rows} & 135 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison.py} & \code{mode\_\allowbreak{}mode\_\allowbreak{}stable\_\allowbreak{}f1f2\_\allowbreak{}signature\_\allowbreak{}summary\_\allowbreak{}rows} & 264 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison.py} & \code{f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison\_\allowbreak{}report} & 308 & finite function\\
\hline
\code{object\_\allowbreak{}checks/f1f2\_\allowbreak{}signature\_\allowbreak{}mode\_\allowbreak{}comparison.py} & \code{mode\_\allowbreak{}mode\_\allowbreak{}stable\_\allowbreak{}f1f2\_\allowbreak{}signature\_\allowbreak{}summary\_\allowbreak{}report} & 327 & finite function\\
\hline
\code{object\_\allowbreak{}checks/faithful\_\allowbreak{}state.py} & \code{\_\allowbreak{}computed\_\allowbreak{}status} & 38 & finite function\\
\hline
\code{object\_\allowbreak{}checks/faithful\_\allowbreak{}state.py} & \code{faithful\_\allowbreak{}state\_\allowbreak{}rows} & 50 & finite function\\
\hline
\code{object\_\allowbreak{}checks/faithful\_\allowbreak{}state.py} & \code{faithful\_\allowbreak{}state\_\allowbreak{}report} & 95 & finite function\\
\hline
\code{object\_\allowbreak{}checks/finite\_\allowbreak{}complement\_\allowbreak{}relations.py} & \code{finite\_\allowbreak{}complement\_\allowbreak{}relations\_\allowbreak{}rows} & 31 & finite function\\
\hline
\code{object\_\allowbreak{}checks/finite\_\allowbreak{}complement\_\allowbreak{}relations.py} & \code{finite\_\allowbreak{}complement\_\allowbreak{}relations\_\allowbreak{}report} & 86 & finite function\\
\hline
\code{object\_\allowbreak{}checks/finite\_\allowbreak{}property\_\allowbreak{}inventory.py} & \code{finite\_\allowbreak{}finite\_\allowbreak{}property\_\allowbreak{}inventory\_\allowbreak{}rows} & 6 & finite function\\
\hline
\code{object\_\allowbreak{}checks/finite\_\allowbreak{}property\_\allowbreak{}inventory.py} & \code{previous\_\allowbreak{}reproduction\_\allowbreak{}measurement\_\allowbreak{}rows} & 132 & finite function\\
\hline
\code{object\_\allowbreak{}checks/finite\_\allowbreak{}property\_\allowbreak{}inventory.py} & \code{finite\_\allowbreak{}property\_\allowbreak{}inventory\_\allowbreak{}report} & 165 & finite function\\
\hline
\code{object\_\allowbreak{}checks/finite\_\allowbreak{}region\_\allowbreak{}net.py} & \code{FiniteRegionRecord} & 21 & finite class\\
\hline
\code{object\_\allowbreak{}checks/finite\_\allowbreak{}region\_\allowbreak{}net.py} & \code{\_\allowbreak{}descendants\_\allowbreak{}until} & 33 & finite function\\
\hline
\code{object\_\allowbreak{}checks/finite\_\allowbreak{}region\_\allowbreak{}net.py} & \code{finite\_\allowbreak{}region\_\allowbreak{}records} & 43 & finite function\\
\hline
\code{object\_\allowbreak{}checks/finite\_\allowbreak{}region\_\allowbreak{}net.py} & \code{region\_\allowbreak{}grammar\_\allowbreak{}rows} & 80 & finite function\\
\hline
\code{object\_\allowbreak{}checks/finite\_\allowbreak{}region\_\allowbreak{}net.py} & \code{region\_\allowbreak{}inclusion\_\allowbreak{}rows} & 106 & finite function\\
\hline
\code{object\_\allowbreak{}checks/finite\_\allowbreak{}region\_\allowbreak{}net.py} & \code{region\_\allowbreak{}poset\_\allowbreak{}summary} & 133 & finite function\\
\hline
\code{object\_\allowbreak{}checks/finite\_\allowbreak{}region\_\allowbreak{}net.py} & \code{region\_\allowbreak{}net\_\allowbreak{}report} & 166 & finite function\\
\hline
\code{object\_\allowbreak{}checks/fixed\_\allowbreak{}measure\_\allowbreak{}ratio\_\allowbreak{}summary.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/fixed\_\allowbreak{}measure\_\allowbreak{}ratio\_\allowbreak{}summary.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/fixed\_\allowbreak{}measure\_\allowbreak{}ratio\_\allowbreak{}summary.py} & \code{fixed\_\allowbreak{}measure\_\allowbreak{}ratio\_\allowbreak{}summary\_\allowbreak{}rows} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/fixed\_\allowbreak{}measure\_\allowbreak{}ratio\_\allowbreak{}summary.py} & \code{fixed\_\allowbreak{}measure\_\allowbreak{}ratio\_\allowbreak{}summary\_\allowbreak{}report} & 67 & finite function\\
\hline
\code{object\_\allowbreak{}checks/fixed\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/fixed\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/fixed\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}key} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/fixed\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{fixed\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure\_\allowbreak{}rows} & 25 & finite function\\
\hline
\code{object\_\allowbreak{}checks/fixed\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{fixed\_\allowbreak{}oriented\_\allowbreak{}history\_\allowbreak{}measure\_\allowbreak{}report} & 104 & finite function\\
\hline
\code{object\_\allowbreak{}checks/fock\_\allowbreak{}aqft\_\allowbreak{}bridge.py} & \code{fock\_\allowbreak{}aqft\_\allowbreak{}bridge\_\allowbreak{}comparison\_\allowbreak{}register\_\allowbreak{}rows} & 76 & finite function\\
\hline
\code{object\_\allowbreak{}checks/fock\_\allowbreak{}aqft\_\allowbreak{}bridge.py} & \code{\_\allowbreak{}dominance\_\allowbreak{}ratio} & 80 & finite function\\
\hline
\code{object\_\allowbreak{}checks/fock\_\allowbreak{}aqft\_\allowbreak{}bridge.py} & \code{fock\_\allowbreak{}aqft\_\allowbreak{}one\_\allowbreak{}particle\_\allowbreak{}comparison\_\allowbreak{}rows} & 96 & finite function\\
\hline
\code{object\_\allowbreak{}checks/fock\_\allowbreak{}aqft\_\allowbreak{}bridge.py} & \code{fock\_\allowbreak{}aqft\_\allowbreak{}bridge\_\allowbreak{}report} & 155 & finite function\\
\hline
\code{object\_\allowbreak{}checks/four\_\allowbreak{}path\_\allowbreak{}transition\_\allowbreak{}matrix.py} & \code{four\_\allowbreak{}path\_\allowbreak{}transition\_\allowbreak{}matrix\_\allowbreak{}rows} & 70 & finite function\\
\hline
\code{object\_\allowbreak{}checks/four\_\allowbreak{}path\_\allowbreak{}transition\_\allowbreak{}matrix.py} & \code{four\_\allowbreak{}path\_\allowbreak{}dependency\_\allowbreak{}table\_\allowbreak{}priority\_\allowbreak{}rows} & 74 & finite function\\
\hline
\code{object\_\allowbreak{}checks/four\_\allowbreak{}path\_\allowbreak{}transition\_\allowbreak{}matrix.py} & \code{four\_\allowbreak{}path\_\allowbreak{}literature\_\allowbreak{}bridge\_\allowbreak{}rows} & 93 & finite function\\
\hline
\code{object\_\allowbreak{}checks/four\_\allowbreak{}path\_\allowbreak{}transition\_\allowbreak{}matrix.py} & \code{closed\_\allowbreak{}finite\_\allowbreak{}results\_\allowbreak{}rows} & 130 & finite function\\
\hline
\code{object\_\allowbreak{}checks/four\_\allowbreak{}path\_\allowbreak{}transition\_\allowbreak{}matrix.py} & \code{external\_\allowbreak{}measurement\_\allowbreak{}assessment\_\allowbreak{}rows} & 171 & finite function\\
\hline
\code{object\_\allowbreak{}checks/four\_\allowbreak{}path\_\allowbreak{}transition\_\allowbreak{}matrix.py} & \code{consistency\_\allowbreak{}prerequisite\_\allowbreak{}rows} & 218 & finite function\\
\hline
\code{object\_\allowbreak{}checks/four\_\allowbreak{}path\_\allowbreak{}transition\_\allowbreak{}matrix.py} & \code{presentation\_\allowbreak{}selection\_\allowbreak{}rows} & 255 & finite function\\
\hline
\code{object\_\allowbreak{}checks/four\_\allowbreak{}path\_\allowbreak{}transition\_\allowbreak{}matrix.py} & \code{four\_\allowbreak{}path\_\allowbreak{}transition\_\allowbreak{}report} & 284 & finite function\\
\hline
\code{object\_\allowbreak{}checks/four\_\allowbreak{}path\_\allowbreak{}transition\_\allowbreak{}matrix.py} & \code{closed\_\allowbreak{}results\_\allowbreak{}report} & 309 & finite function\\
\hline
\code{object\_\allowbreak{}checks/genealogical\_\allowbreak{}corridor\_\allowbreak{}commutation.py} & \code{\_\allowbreak{}computed\_\allowbreak{}status} & 27 & finite function\\
\hline
\code{object\_\allowbreak{}checks/genealogical\_\allowbreak{}corridor\_\allowbreak{}commutation.py} & \code{genealogical\_\allowbreak{}corridor\_\allowbreak{}commutator\_\allowbreak{}rows} & 41 & finite function\\
\hline
\code{object\_\allowbreak{}checks/genealogical\_\allowbreak{}corridor\_\allowbreak{}commutation.py} & \code{genealogical\_\allowbreak{}corridor\_\allowbreak{}commutation\_\allowbreak{}report} & 81 & finite function\\
\hline
\code{object\_\allowbreak{}checks/genealogical\_\allowbreak{}corridor\_\allowbreak{}split.py} & \code{\_\allowbreak{}computed\_\allowbreak{}status} & 25 & finite function\\
\hline
\code{object\_\allowbreak{}checks/genealogical\_\allowbreak{}corridor\_\allowbreak{}split.py} & \code{genealogical\_\allowbreak{}corridor\_\allowbreak{}split\_\allowbreak{}rows} & 39 & finite function\\
\hline
\code{object\_\allowbreak{}checks/genealogical\_\allowbreak{}corridor\_\allowbreak{}split.py} & \code{genealogical\_\allowbreak{}corridor\_\allowbreak{}split\_\allowbreak{}report} & 90 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}live\_\allowbreak{}common\_\allowbreak{}measure.py} & \code{\_\allowbreak{}finite} & 34 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}live\_\allowbreak{}common\_\allowbreak{}measure.py} & \code{\_\allowbreak{}median} & 42 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}live\_\allowbreak{}common\_\allowbreak{}measure.py} & \code{\_\allowbreak{}pearson} & 47 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}live\_\allowbreak{}common\_\allowbreak{}measure.py} & \code{inherited\_\allowbreak{}uniform\_\allowbreak{}node\_\allowbreak{}density\_\allowbreak{}for\_\allowbreak{}role\_\allowbreak{}basis} & 59 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}live\_\allowbreak{}common\_\allowbreak{}measure.py} & \code{\_\allowbreak{}distance\_\allowbreak{}metrics} & 121 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}live\_\allowbreak{}common\_\allowbreak{}measure.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 147 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}live\_\allowbreak{}common\_\allowbreak{}measure.py} & \code{\_\allowbreak{}augment\_\allowbreak{}track\_\allowbreak{}summaries} & 151 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}live\_\allowbreak{}common\_\allowbreak{}measure.py} & \code{history\_\allowbreak{}live\_\allowbreak{}common\_\allowbreak{}measure\_\allowbreak{}rows} & 210 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}live\_\allowbreak{}common\_\allowbreak{}measure.py} & \code{history\_\allowbreak{}live\_\allowbreak{}common\_\allowbreak{}measure\_\allowbreak{}report} & 313 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}measure\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence.py} & \code{\_\allowbreak{}finite} & 28 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}measure\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence.py} & \code{\_\allowbreak{}median} & 36 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}measure\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 41 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}measure\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence.py} & \code{\_\allowbreak{}score} & 52 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}measure\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence.py} & \code{\_\allowbreak{}row\_\allowbreak{}for\_\allowbreak{}control} & 58 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}measure\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence.py} & \code{history\_\allowbreak{}measure\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence\_\allowbreak{}rows} & 135 & finite function\\
\hline
\code{object\_\allowbreak{}checks/history\_\allowbreak{}measure\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence.py} & \code{history\_\allowbreak{}measure\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence\_\allowbreak{}report} & 256 & finite function\\
\hline
\code{object\_\allowbreak{}checks/level\_\allowbreak{}mode\_\allowbreak{}dependence\_\allowbreak{}summary.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/level\_\allowbreak{}mode\_\allowbreak{}dependence\_\allowbreak{}summary.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/level\_\allowbreak{}mode\_\allowbreak{}dependence\_\allowbreak{}summary.py} & \code{level\_\allowbreak{}mode\_\allowbreak{}dependence\_\allowbreak{}summary\_\allowbreak{}rows} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/level\_\allowbreak{}mode\_\allowbreak{}dependence\_\allowbreak{}summary.py} & \code{level\_\allowbreak{}mode\_\allowbreak{}dependence\_\allowbreak{}summary\_\allowbreak{}report} & 82 & finite function\\
\hline
\code{object\_\allowbreak{}checks/live\_\allowbreak{}current\_\allowbreak{}cluster\_\allowbreak{}scaling.py} & \code{\_\allowbreak{}finite} & 25 & finite function\\
\hline
\code{object\_\allowbreak{}checks/live\_\allowbreak{}current\_\allowbreak{}cluster\_\allowbreak{}scaling.py} & \code{\_\allowbreak{}median} & 33 & finite function\\
\hline
\code{object\_\allowbreak{}checks/live\_\allowbreak{}current\_\allowbreak{}cluster\_\allowbreak{}scaling.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 38 & finite function\\
\hline
\code{object\_\allowbreak{}checks/live\_\allowbreak{}current\_\allowbreak{}cluster\_\allowbreak{}scaling.py} & \code{\_\allowbreak{}summarize} & 42 & finite function\\
\hline
\code{object\_\allowbreak{}checks/live\_\allowbreak{}current\_\allowbreak{}cluster\_\allowbreak{}scaling.py} & \code{live\_\allowbreak{}current\_\allowbreak{}cluster\_\allowbreak{}scaling\_\allowbreak{}rows} & 74 & finite function\\
\hline
\code{object\_\allowbreak{}checks/live\_\allowbreak{}current\_\allowbreak{}cluster\_\allowbreak{}scaling.py} & \code{live\_\allowbreak{}current\_\allowbreak{}cluster\_\allowbreak{}scaling\_\allowbreak{}report} & 131 & finite function\\
\hline
\code{object\_\allowbreak{}checks/live\_\allowbreak{}current\_\allowbreak{}property\_\allowbreak{}summary.py} & \code{\_\allowbreak{}count} & 10 & finite function\\
\hline
\code{object\_\allowbreak{}checks/live\_\allowbreak{}current\_\allowbreak{}property\_\allowbreak{}summary.py} & \code{\_\allowbreak{}append\_\allowbreak{}counts} & 19 & finite function\\
\hline
\code{object\_\allowbreak{}checks/live\_\allowbreak{}current\_\allowbreak{}property\_\allowbreak{}summary.py} & \code{live\_\allowbreak{}current\_\allowbreak{}property\_\allowbreak{}summary\_\allowbreak{}rows} & 35 & finite function\\
\hline
\code{object\_\allowbreak{}checks/live\_\allowbreak{}current\_\allowbreak{}property\_\allowbreak{}summary.py} & \code{live\_\allowbreak{}current\_\allowbreak{}property\_\allowbreak{}summary\_\allowbreak{}report} & 60 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}operator\_\allowbreak{}additivity.py} & \code{\_\allowbreak{}computed\_\allowbreak{}status} & 32 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}operator\_\allowbreak{}additivity.py} & \code{local\_\allowbreak{}operator\_\allowbreak{}additivity\_\allowbreak{}rows} & 44 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}operator\_\allowbreak{}additivity.py} & \code{additivity\_\allowbreak{}report} & 92 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}operator\_\allowbreak{}commutation.py} & \code{\_\allowbreak{}computed\_\allowbreak{}status} & 33 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}operator\_\allowbreak{}commutation.py} & \code{\_\allowbreak{}append\_\allowbreak{}commutator\_\allowbreak{}row} & 49 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}operator\_\allowbreak{}commutation.py} & \code{local\_\allowbreak{}operator\_\allowbreak{}commutator\_\allowbreak{}rows} & 68 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}operator\_\allowbreak{}commutation.py} & \code{commutation\_\allowbreak{}report} & 161 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}operator\_\allowbreak{}isotony.py} & \code{\_\allowbreak{}is\_\allowbreak{}current\_\allowbreak{}system} & 43 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}operator\_\allowbreak{}isotony.py} & \code{\_\allowbreak{}computed\_\allowbreak{}status} & 51 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}operator\_\allowbreak{}isotony.py} & \code{\_\allowbreak{}construction\_\allowbreak{}overlap} & 69 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}operator\_\allowbreak{}isotony.py} & \code{local\_\allowbreak{}operator\_\allowbreak{}isotony\_\allowbreak{}rows} & 77 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}operator\_\allowbreak{}isotony.py} & \code{isotony\_\allowbreak{}report} & 159 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}vacuum\_\allowbreak{}cyclicity.py} & \code{\_\allowbreak{}computed\_\allowbreak{}status} & 41 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}vacuum\_\allowbreak{}cyclicity.py} & \code{\_\allowbreak{}append\_\allowbreak{}row} & 57 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}vacuum\_\allowbreak{}cyclicity.py} & \code{\_\allowbreak{}graded\_\allowbreak{}closures} & 89 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}vacuum\_\allowbreak{}cyclicity.py} & \code{\_\allowbreak{}annotate\_\allowbreak{}first\_\allowbreak{}cyclic\_\allowbreak{}depth} & 121 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}vacuum\_\allowbreak{}cyclicity.py} & \code{local\_\allowbreak{}vacuum\_\allowbreak{}cyclicity\_\allowbreak{}rows} & 142 & finite function\\
\hline
\code{object\_\allowbreak{}checks/local\_\allowbreak{}vacuum\_\allowbreak{}cyclicity.py} & \code{cyclicity\_\allowbreak{}report} & 164 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablated\_\allowbreak{}measure\_\allowbreak{}summary.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablated\_\allowbreak{}measure\_\allowbreak{}summary.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablated\_\allowbreak{}measure\_\allowbreak{}summary.py} & \code{mode\_\allowbreak{}ablated\_\allowbreak{}measure\_\allowbreak{}summary\_\allowbreak{}rows} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablated\_\allowbreak{}measure\_\allowbreak{}summary.py} & \code{mode\_\allowbreak{}ablated\_\allowbreak{}measure\_\allowbreak{}summary\_\allowbreak{}report} & 93 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablation\_\allowbreak{}signature.py} & \code{\_\allowbreak{}finite} & 23 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablation\_\allowbreak{}signature.py} & \code{\_\allowbreak{}median} & 31 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablation\_\allowbreak{}signature.py} & \code{\_\allowbreak{}signature} & 36 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablation\_\allowbreak{}signature.py} & \code{\_\allowbreak{}cosine} & 44 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablation\_\allowbreak{}signature.py} & \code{\_\allowbreak{}signature\_\allowbreak{}gap} & 53 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablation\_\allowbreak{}signature.py} & \code{\_\allowbreak{}amplitude\_\allowbreak{}gap} & 59 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablation\_\allowbreak{}signature.py} & \code{\_\allowbreak{}combined} & 64 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablation\_\allowbreak{}signature.py} & \code{\_\allowbreak{}mode\_\allowbreak{}signature\_\allowbreak{}row} & 70 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablation\_\allowbreak{}signature.py} & \code{mode\_\allowbreak{}ablation\_\allowbreak{}signature\_\allowbreak{}rows} & 129 & finite function\\
\hline
\code{object\_\allowbreak{}checks/mode\_\allowbreak{}ablation\_\allowbreak{}signature.py} & \code{mode\_\allowbreak{}ablation\_\allowbreak{}signature\_\allowbreak{}report} & 218 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}entropy\_\allowbreak{}backreaction\_\allowbreak{}direction.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}entropy\_\allowbreak{}backreaction\_\allowbreak{}direction.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}entropy\_\allowbreak{}backreaction\_\allowbreak{}direction.py} & \code{\_\allowbreak{}hist\_\allowbreak{}index} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}entropy\_\allowbreak{}backreaction\_\allowbreak{}direction.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 42 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}entropy\_\allowbreak{}backreaction\_\allowbreak{}direction.py} & \code{\_\allowbreak{}summarize} & 46 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}entropy\_\allowbreak{}backreaction\_\allowbreak{}direction.py} & \code{modular\_\allowbreak{}entropy\_\allowbreak{}backreaction\_\allowbreak{}direction\_\allowbreak{}rows} & 95 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}entropy\_\allowbreak{}backreaction\_\allowbreak{}direction.py} & \code{modular\_\allowbreak{}entropy\_\allowbreak{}backreaction\_\allowbreak{}direction\_\allowbreak{}report} & 149 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}ratio\_\allowbreak{}trajectory\_\allowbreak{}by\_\allowbreak{}level.py} & \code{\_\allowbreak{}f} & 12 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}ratio\_\allowbreak{}trajectory\_\allowbreak{}by\_\allowbreak{}level.py} & \code{\_\allowbreak{}median} & 20 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}ratio\_\allowbreak{}trajectory\_\allowbreak{}by\_\allowbreak{}level.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 25 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}ratio\_\allowbreak{}trajectory\_\allowbreak{}by\_\allowbreak{}level.py} & \code{\_\allowbreak{}lambda\_\allowbreak{}trend} & 32 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}ratio\_\allowbreak{}trajectory\_\allowbreak{}by\_\allowbreak{}level.py} & \code{\_\allowbreak{}ratio\_\allowbreak{}cloud\_\allowbreak{}computed\_\allowbreak{}status} & 46 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}ratio\_\allowbreak{}trajectory\_\allowbreak{}by\_\allowbreak{}level.py} & \code{modular\_\allowbreak{}ratio\_\allowbreak{}trajectory\_\allowbreak{}by\_\allowbreak{}level\_\allowbreak{}rows} & 59 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}ratio\_\allowbreak{}trajectory\_\allowbreak{}by\_\allowbreak{}level.py} & \code{modular\_\allowbreak{}ratio\_\allowbreak{}trajectory\_\allowbreak{}by\_\allowbreak{}level\_\allowbreak{}report} & 152 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}spectrum\_\allowbreak{}trajectory.py} & \code{\_\allowbreak{}parse\_\allowbreak{}floats} & 22 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}spectrum\_\allowbreak{}trajectory.py} & \code{\_\allowbreak{}lambda\_\allowbreak{}hint} & 32 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}spectrum\_\allowbreak{}trajectory.py} & \code{modular\_\allowbreak{}spectrum\_\allowbreak{}trajectory\_\allowbreak{}rows} & 47 & finite function\\
\hline
\code{object\_\allowbreak{}checks/modular\_\allowbreak{}spectrum\_\allowbreak{}trajectory.py} & \code{modular\_\allowbreak{}spectrum\_\allowbreak{}trajectory\_\allowbreak{}report} & 123 & finite function\\
\hline
\code{object\_\allowbreak{}checks/multiscale\_\allowbreak{}port\_\allowbreak{}entropy\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}chunks} & 36 & finite function\\
\hline
\code{object\_\allowbreak{}checks/multiscale\_\allowbreak{}port\_\allowbreak{}entropy\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}indicator} & 49 & finite function\\
\hline
\code{object\_\allowbreak{}checks/multiscale\_\allowbreak{}port\_\allowbreak{}entropy\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}multiscale\_\allowbreak{}basis} & 60 & finite function\\
\hline
\code{object\_\allowbreak{}checks/multiscale\_\allowbreak{}port\_\allowbreak{}entropy\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}response} & 85 & finite function\\
\hline
\code{object\_\allowbreak{}checks/multiscale\_\allowbreak{}port\_\allowbreak{}entropy\_\allowbreak{}resolution.py} & \code{\_\allowbreak{}simple\_\allowbreak{}side\_\allowbreak{}dim} & 98 & finite function\\
\hline
\code{object\_\allowbreak{}checks/multiscale\_\allowbreak{}port\_\allowbreak{}entropy\_\allowbreak{}resolution.py} & \code{multiscale\_\allowbreak{}port\_\allowbreak{}entropy\_\allowbreak{}resolution\_\allowbreak{}rows} & 121 & finite function\\
\hline
\code{object\_\allowbreak{}checks/multiscale\_\allowbreak{}port\_\allowbreak{}entropy\_\allowbreak{}resolution.py} & \code{multiscale\_\allowbreak{}port\_\allowbreak{}entropy\_\allowbreak{}resolution\_\allowbreak{}report} & 174 & finite function\\
\hline
\code{object\_\allowbreak{}checks/observable\_\allowbreak{}state\_\allowbreak{}rows.py} & \code{state\_\allowbreak{}physical\_\allowbreak{}role} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/observable\_\allowbreak{}state\_\allowbreak{}rows.py} & \code{property\_\allowbreak{}statement\_\allowbreak{}scope} & 27 & finite function\\
\hline
\code{object\_\allowbreak{}checks/observable\_\allowbreak{}state\_\allowbreak{}rows.py} & \code{support\_\allowbreak{}loss\_\allowbreak{}interpretation} & 38 & finite function\\
\hline
\code{object\_\allowbreak{}checks/observable\_\allowbreak{}state\_\allowbreak{}rows.py} & \code{state\_\allowbreak{}relations\_\allowbreak{}fields} & 52 & finite function\\
\hline
\code{object\_\allowbreak{}checks/observable\_\allowbreak{}state\_\allowbreak{}rows.py} & \code{observable\_\allowbreak{}state\_\allowbreak{}rows\_\allowbreak{}rows} & 64 & finite function\\
\hline
\code{object\_\allowbreak{}checks/observable\_\allowbreak{}state\_\allowbreak{}rows.py} & \code{observable\_\allowbreak{}state\_\allowbreak{}rows\_\allowbreak{}report} & 101 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}geometry\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}geometry\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}geometry\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence.py} & \code{\_\allowbreak{}key} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}geometry\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence.py} & \code{\_\allowbreak{}ratio} & 31 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}geometry\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence.py} & \code{oriented\_\allowbreak{}geometry\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence\_\allowbreak{}rows} & 35 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}geometry\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence.py} & \code{oriented\_\allowbreak{}geometry\_\allowbreak{}level\_\allowbreak{}mode\_\allowbreak{}dependence\_\allowbreak{}report} & 102 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}history\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}history\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}history\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}measure\_\allowbreak{}key} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}history\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}measure\_\allowbreak{}index} & 27 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}history\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}per} & 31 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}history\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 35 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}history\_\allowbreak{}geometry.py} & \code{\_\allowbreak{}summarize\_\allowbreak{}track} & 39 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}history\_\allowbreak{}geometry.py} & \code{oriented\_\allowbreak{}history\_\allowbreak{}geometry\_\allowbreak{}rows} & 80 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}history\_\allowbreak{}geometry.py} & \code{oriented\_\allowbreak{}history\_\allowbreak{}geometry\_\allowbreak{}report} & 206 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}history\_\allowbreak{}measure\_\allowbreak{}geometry\_\allowbreak{}summary.py} & \code{oriented\_\allowbreak{}history\_\allowbreak{}measure\_\allowbreak{}geometry\_\allowbreak{}summary\_\allowbreak{}rows} & 7 & finite function\\
\hline
\code{object\_\allowbreak{}checks/oriented\_\allowbreak{}history\_\allowbreak{}measure\_\allowbreak{}geometry\_\allowbreak{}summary.py} & \code{oriented\_\allowbreak{}history\_\allowbreak{}measure\_\allowbreak{}geometry\_\allowbreak{}summary\_\allowbreak{}report} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/record\_\allowbreak{}anchor\_\allowbreak{}consistency.py} & \code{\_\allowbreak{}support\_\allowbreak{}basis} & 20 & finite function\\
\hline
\code{object\_\allowbreak{}checks/record\_\allowbreak{}anchor\_\allowbreak{}consistency.py} & \code{\_\allowbreak{}density\_\allowbreak{}support\_\allowbreak{}overlap} & 30 & finite function\\
\hline
\code{object\_\allowbreak{}checks/record\_\allowbreak{}anchor\_\allowbreak{}consistency.py} & \code{\_\allowbreak{}skew\_\allowbreak{}alignment} & 60 & finite function\\
\hline
\code{object\_\allowbreak{}checks/record\_\allowbreak{}anchor\_\allowbreak{}consistency.py} & \code{\_\allowbreak{}computed\_\allowbreak{}status} & 77 & finite function\\
\hline
\code{object\_\allowbreak{}checks/record\_\allowbreak{}anchor\_\allowbreak{}consistency.py} & \code{record\_\allowbreak{}anchor\_\allowbreak{}consistency\_\allowbreak{}rows} & 93 & finite function\\
\hline
\code{object\_\allowbreak{}checks/record\_\allowbreak{}anchor\_\allowbreak{}consistency.py} & \code{record\_\allowbreak{}anchor\_\allowbreak{}consistency\_\allowbreak{}report} & 138 & finite function\\
\hline
\code{object\_\allowbreak{}checks/record\_\allowbreak{}live\_\allowbreak{}relative\_\allowbreak{}entropy.py} & \code{\_\allowbreak{}finite} & 25 & finite function\\
\hline
\code{object\_\allowbreak{}checks/record\_\allowbreak{}live\_\allowbreak{}relative\_\allowbreak{}entropy.py} & \code{\_\allowbreak{}median} & 33 & finite function\\
\hline
\code{object\_\allowbreak{}checks/record\_\allowbreak{}live\_\allowbreak{}relative\_\allowbreak{}entropy.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 38 & finite function\\
\hline
\code{object\_\allowbreak{}checks/record\_\allowbreak{}live\_\allowbreak{}relative\_\allowbreak{}entropy.py} & \code{\_\allowbreak{}summarize\_\allowbreak{}track} & 42 & finite function\\
\hline
\code{object\_\allowbreak{}checks/record\_\allowbreak{}live\_\allowbreak{}relative\_\allowbreak{}entropy.py} & \code{record\_\allowbreak{}live\_\allowbreak{}relative\_\allowbreak{}entropy\_\allowbreak{}rows} & 82 & finite function\\
\hline
\code{object\_\allowbreak{}checks/record\_\allowbreak{}live\_\allowbreak{}relative\_\allowbreak{}entropy.py} & \code{record\_\allowbreak{}live\_\allowbreak{}relative\_\allowbreak{}entropy\_\allowbreak{}report} & 141 & finite function\\
\hline
\code{object\_\allowbreak{}checks/refined\_\allowbreak{}port\_\allowbreak{}basis\_\allowbreak{}resolution.py} & \code{refined\_\allowbreak{}port\_\allowbreak{}basis\_\allowbreak{}resolution\_\allowbreak{}rows} & 25 & finite function\\
\hline
\code{object\_\allowbreak{}checks/refined\_\allowbreak{}port\_\allowbreak{}basis\_\allowbreak{}resolution.py} & \code{refined\_\allowbreak{}port\_\allowbreak{}basis\_\allowbreak{}resolution\_\allowbreak{}report} & 71 & finite function\\
\hline
\code{object\_\allowbreak{}checks/refined\_\allowbreak{}port\_\allowbreak{}coarse\_\allowbreak{}consistency.py} & \code{\_\allowbreak{}finite} & 26 & finite function\\
\hline
\code{object\_\allowbreak{}checks/refined\_\allowbreak{}port\_\allowbreak{}coarse\_\allowbreak{}consistency.py} & \code{refined\_\allowbreak{}port\_\allowbreak{}coarse\_\allowbreak{}consistency\_\allowbreak{}rows} & 34 & finite function\\
\hline
\code{object\_\allowbreak{}checks/refined\_\allowbreak{}port\_\allowbreak{}coarse\_\allowbreak{}consistency.py} & \code{refined\_\allowbreak{}port\_\allowbreak{}coarse\_\allowbreak{}consistency\_\allowbreak{}report} & 101 & finite function\\
\hline
\code{object\_\allowbreak{}checks/relative\_\allowbreak{}common\_\allowbreak{}ambient\_\allowbreak{}schur\_\allowbreak{}isotony.py} & \code{relative\_\allowbreak{}common\_\allowbreak{}ambient\_\allowbreak{}schur\_\allowbreak{}isotony\_\allowbreak{}rows} & 33 & finite function\\
\hline
\code{object\_\allowbreak{}checks/relative\_\allowbreak{}common\_\allowbreak{}ambient\_\allowbreak{}schur\_\allowbreak{}isotony.py} & \code{relative\_\allowbreak{}common\_\allowbreak{}ambient\_\allowbreak{}schur\_\allowbreak{}isotony\_\allowbreak{}report} & 62 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure.py} & \code{\_\allowbreak{}pearson} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure.py} & \code{\_\allowbreak{}key} & 33 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 43 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure.py} & \code{\_\allowbreak{}history\_\allowbreak{}index} & 52 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure.py} & \code{\_\allowbreak{}mode\_\allowbreak{}ablation\_\allowbreak{}true\_\allowbreak{}index} & 60 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure.py} & \code{\_\allowbreak{}f1f2\_\allowbreak{}index} & 77 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure.py} & \code{\_\allowbreak{}dominance} & 85 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure.py} & \code{\_\allowbreak{}augment\_\allowbreak{}tracks} & 102 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure.py} & \code{signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure\_\allowbreak{}rows} & 157 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure.py} & \code{signature\_\allowbreak{}strength\_\allowbreak{}decomposed\_\allowbreak{}measure\_\allowbreak{}report} & 241 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}geometry\_\allowbreak{}summary.py} & \code{signature\_\allowbreak{}strength\_\allowbreak{}geometry\_\allowbreak{}summary\_\allowbreak{}rows} & 7 & finite function\\
\hline
\code{object\_\allowbreak{}checks/signature\_\allowbreak{}strength\_\allowbreak{}geometry\_\allowbreak{}summary.py} & \code{signature\_\allowbreak{}strength\_\allowbreak{}geometry\_\allowbreak{}summary\_\allowbreak{}report} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/split\_\allowbreak{}factorization.py} & \code{\_\allowbreak{}computed\_\allowbreak{}status} & 28 & finite function\\
\hline
\code{object\_\allowbreak{}checks/split\_\allowbreak{}factorization.py} & \code{split\_\allowbreak{}factorization\_\allowbreak{}rows} & 38 & finite function\\
\hline
\code{object\_\allowbreak{}checks/split\_\allowbreak{}factorization.py} & \code{split\_\allowbreak{}report} & 83 & finite function\\
\hline
\code{object\_\allowbreak{}checks/split\_\allowbreak{}residual\_\allowbreak{}by\_\allowbreak{}collar\_\allowbreak{}width.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 31 & finite function\\
\hline
\code{object\_\allowbreak{}checks/split\_\allowbreak{}residual\_\allowbreak{}by\_\allowbreak{}collar\_\allowbreak{}width.py} & \code{\_\allowbreak{}median} & 35 & finite function\\
\hline
\code{object\_\allowbreak{}checks/split\_\allowbreak{}residual\_\allowbreak{}by\_\allowbreak{}collar\_\allowbreak{}width.py} & \code{\_\allowbreak{}summarize\_\allowbreak{}track} & 40 & finite function\\
\hline
\code{object\_\allowbreak{}checks/split\_\allowbreak{}residual\_\allowbreak{}by\_\allowbreak{}collar\_\allowbreak{}width.py} & \code{split\_\allowbreak{}residual\_\allowbreak{}by\_\allowbreak{}collar\_\allowbreak{}width\_\allowbreak{}rows} & 87 & finite function\\
\hline
\code{object\_\allowbreak{}checks/split\_\allowbreak{}residual\_\allowbreak{}by\_\allowbreak{}collar\_\allowbreak{}width.py} & \code{split\_\allowbreak{}residual\_\allowbreak{}by\_\allowbreak{}collar\_\allowbreak{}width\_\allowbreak{}report} & 166 & finite function\\
\hline
\code{object\_\allowbreak{}checks/stack\_\allowbreak{}dependency\_\allowbreak{}conditions.py} & \code{topology\_\allowbreak{}precedence\_\allowbreak{}rows} & 195 & finite function\\
\hline
\code{object\_\allowbreak{}checks/stack\_\allowbreak{}dependency\_\allowbreak{}conditions.py} & \code{stack\_\allowbreak{}layer\_\allowbreak{}rows} & 199 & finite function\\
\hline
\code{object\_\allowbreak{}checks/stack\_\allowbreak{}dependency\_\allowbreak{}conditions.py} & \code{stack\_\allowbreak{}transition\_\allowbreak{}rows} & 203 & finite function\\
\hline
\code{object\_\allowbreak{}checks/stack\_\allowbreak{}dependency\_\allowbreak{}conditions.py} & \code{condition\_\allowbreak{}register\_\allowbreak{}rows} & 207 & finite function\\
\hline
\code{object\_\allowbreak{}checks/stack\_\allowbreak{}dependency\_\allowbreak{}conditions.py} & \code{cfs\_\allowbreak{}cross\_\allowbreak{}axis\_\allowbreak{}rows} & 225 & finite function\\
\hline
\code{object\_\allowbreak{}checks/stack\_\allowbreak{}dependency\_\allowbreak{}conditions.py} & \code{input\_\allowbreak{}exclusion\_\allowbreak{}rule\_\allowbreak{}rows} & 229 & finite function\\
\hline
\code{object\_\allowbreak{}checks/stack\_\allowbreak{}dependency\_\allowbreak{}conditions.py} & \code{stack\_\allowbreak{}architecture\_\allowbreak{}report} & 233 & finite function\\
\hline
\code{object\_\allowbreak{}checks/stack\_\allowbreak{}dependency\_\allowbreak{}conditions.py} & \code{condition\_\allowbreak{}register\_\allowbreak{}report} & 274 & finite function\\
\hline
\code{object\_\allowbreak{}checks/support\_\allowbreak{}rank\_\allowbreak{}trajectory.py} & \code{\_\allowbreak{}mean} & 18 & finite function\\
\hline
\code{object\_\allowbreak{}checks/support\_\allowbreak{}rank\_\allowbreak{}trajectory.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 23 & finite function\\
\hline
\code{object\_\allowbreak{}checks/support\_\allowbreak{}rank\_\allowbreak{}trajectory.py} & \code{\_\allowbreak{}trend} & 27 & finite function\\
\hline
\code{object\_\allowbreak{}checks/support\_\allowbreak{}rank\_\allowbreak{}trajectory.py} & \code{support\_\allowbreak{}rank\_\allowbreak{}trajectory\_\allowbreak{}rows} & 38 & finite function\\
\hline
\code{object\_\allowbreak{}checks/support\_\allowbreak{}rank\_\allowbreak{}trajectory.py} & \code{support\_\allowbreak{}rank\_\allowbreak{}trajectory\_\allowbreak{}report} & 142 & finite function\\
\hline
\code{object\_\allowbreak{}checks/support\_\allowbreak{}state\_\allowbreak{}summary.py} & \code{\_\allowbreak{}scope} & 17 & finite function\\
\hline
\code{object\_\allowbreak{}checks/support\_\allowbreak{}state\_\allowbreak{}summary.py} & \code{\_\allowbreak{}condition\_\allowbreak{}not\_\allowbreak{}met} & 28 & finite function\\
\hline
\code{object\_\allowbreak{}checks/support\_\allowbreak{}state\_\allowbreak{}summary.py} & \code{support\_\allowbreak{}state\_\allowbreak{}summary\_\allowbreak{}rows} & 43 & finite function\\
\hline
\code{object\_\allowbreak{}checks/support\_\allowbreak{}state\_\allowbreak{}summary.py} & \code{support\_\allowbreak{}state\_\allowbreak{}summary\_\allowbreak{}report} & 76 & finite function\\
\hline
\code{object\_\allowbreak{}checks/tomita\_\allowbreak{}entropy\_\allowbreak{}flow\_\allowbreak{}alignment.py} & \code{\_\allowbreak{}finite} & 26 & finite function\\
\hline
\code{object\_\allowbreak{}checks/tomita\_\allowbreak{}entropy\_\allowbreak{}flow\_\allowbreak{}alignment.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 34 & finite function\\
\hline
\code{object\_\allowbreak{}checks/tomita\_\allowbreak{}entropy\_\allowbreak{}flow\_\allowbreak{}alignment.py} & \code{\_\allowbreak{}summarize} & 38 & finite function\\
\hline
\code{object\_\allowbreak{}checks/tomita\_\allowbreak{}entropy\_\allowbreak{}flow\_\allowbreak{}alignment.py} & \code{tomita\_\allowbreak{}entropy\_\allowbreak{}flow\_\allowbreak{}alignment\_\allowbreak{}rows} & 80 & finite function\\
\hline
\code{object\_\allowbreak{}checks/tomita\_\allowbreak{}entropy\_\allowbreak{}flow\_\allowbreak{}alignment.py} & \code{tomita\_\allowbreak{}entropy\_\allowbreak{}flow\_\allowbreak{}alignment\_\allowbreak{}report} & 126 & finite function\\
\hline
\code{object\_\allowbreak{}checks/tomita\_\allowbreak{}standard\_\allowbreak{}form.py} & \code{\_\allowbreak{}computed\_\allowbreak{}status} & 23 & finite function\\
\hline
\code{object\_\allowbreak{}checks/tomita\_\allowbreak{}standard\_\allowbreak{}form.py} & \code{tomita\_\allowbreak{}standard\_\allowbreak{}form\_\allowbreak{}rows} & 58 & finite function\\
\hline
\code{object\_\allowbreak{}checks/tomita\_\allowbreak{}standard\_\allowbreak{}form.py} & \code{tomita\_\allowbreak{}report} & 104 & finite function\\
\hline
\code{object\_\allowbreak{}checks/two\_\allowbreak{}component\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}finite} & 8 & finite function\\
\hline
\code{object\_\allowbreak{}checks/two\_\allowbreak{}component\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}median} & 16 & finite function\\
\hline
\code{object\_\allowbreak{}checks/two\_\allowbreak{}component\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}pearson} & 21 & finite function\\
\hline
\code{object\_\allowbreak{}checks/two\_\allowbreak{}component\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}key} & 33 & finite function\\
\hline
\code{object\_\allowbreak{}checks/two\_\allowbreak{}component\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}history\_\allowbreak{}index} & 43 & finite function\\
\hline
\code{object\_\allowbreak{}checks/two\_\allowbreak{}component\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}f1f2\_\allowbreak{}index} & 51 & finite function\\
\hline
\code{object\_\allowbreak{}checks/two\_\allowbreak{}component\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}track\_\allowbreak{}key} & 55 & finite function\\
\hline
\code{object\_\allowbreak{}checks/two\_\allowbreak{}component\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{\_\allowbreak{}augment\_\allowbreak{}tracks} & 64 & finite function\\
\hline
\code{object\_\allowbreak{}checks/two\_\allowbreak{}component\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{two\_\allowbreak{}component\_\allowbreak{}history\_\allowbreak{}measure\_\allowbreak{}rows} & 116 & finite function\\
\hline
\code{object\_\allowbreak{}checks/two\_\allowbreak{}component\_\allowbreak{}history\_\allowbreak{}measure.py} & \code{two\_\allowbreak{}component\_\allowbreak{}history\_\allowbreak{}measure\_\allowbreak{}report} & 185 & finite function\\
\hline
\code{run\_\allowbreak{}birth\_\allowbreak{}relative\_\allowbreak{}backreaction\_\allowbreak{}current.py} & \code{parse\_\allowbreak{}args} & 30 & finite function\\
\hline
\code{run\_\allowbreak{}birth\_\allowbreak{}relative\_\allowbreak{}backreaction\_\allowbreak{}current.py} & \code{main} & 44 & finite function\\
\hline
\code{run\_\allowbreak{}branching\_\allowbreak{}zero\_\allowbreak{}crossing\_\allowbreak{}shift.py} & \code{parse\_\allowbreak{}args} & 30 & finite function\\
\hline
\code{run\_\allowbreak{}branching\_\allowbreak{}zero\_\allowbreak{}crossing\_\allowbreak{}shift.py} & \code{main} & 46 & finite function\\
\hline
\code{run\_\allowbreak{}directed\_\allowbreak{}region\_\allowbreak{}coverage.py} & \code{parse\_\allowbreak{}args} & 27 & finite function\\
\hline
\code{run\_\allowbreak{}directed\_\allowbreak{}region\_\allowbreak{}coverage.py} & \code{main} & 43 & finite function\\
\hline
\code{run\_\allowbreak{}finite\_\allowbreak{}emergence\_\allowbreak{}dependency\_\allowbreak{}table.py} & \code{write\_\allowbreak{}csv} & 9 & finite function\\
\hline
\code{run\_\allowbreak{}finite\_\allowbreak{}emergence\_\allowbreak{}dependency\_\allowbreak{}table.py} & \code{main} & 20 & finite function\\
\hline
\code{run\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{parse\_\allowbreak{}args} & 25 & finite function\\
\hline
\code{run\_\allowbreak{}j\_\allowbreak{}orientation\_\allowbreak{}projectivity.py} & \code{main} & 41 & finite function\\
\hline
\code{run\_\allowbreak{}live\_\allowbreak{}record\_\allowbreak{}backreaction\_\allowbreak{}current.py} & \code{parse\_\allowbreak{}args} & 26 & finite function\\
\hline
\code{run\_\allowbreak{}live\_\allowbreak{}record\_\allowbreak{}backreaction\_\allowbreak{}current.py} & \code{main} & 40 & finite function\\
\hline
\code{run\_\allowbreak{}local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation.py} & \code{parse\_\allowbreak{}args} & 18 & finite function\\
\hline
\code{run\_\allowbreak{}local\_\allowbreak{}global\_\allowbreak{}j\_\allowbreak{}sign\_\allowbreak{}relation.py} & \code{main} & 33 & finite function\\
\hline
\code{run\_\allowbreak{}local\_\allowbreak{}operator\_\allowbreak{}property\_\allowbreak{}checks.py} & \code{\_\allowbreak{}ints} & 81 & finite function\\
\hline
\code{run\_\allowbreak{}local\_\allowbreak{}operator\_\allowbreak{}property\_\allowbreak{}checks.py} & \code{\_\allowbreak{}strings} & 85 & finite function\\
\hline
\code{run\_\allowbreak{}local\_\allowbreak{}operator\_\allowbreak{}property\_\allowbreak{}checks.py} & \code{parse\_\allowbreak{}args} & 89 & finite function\\
\hline
\code{run\_\allowbreak{}local\_\allowbreak{}operator\_\allowbreak{}property\_\allowbreak{}checks.py} & \code{main} & 108 & finite function\\
\bottomrule
\end{longtable}

\end{document}
